### 2019-10-04 manuscript.tex
First draft of manuscript with section 2.5 about dimensional analysis

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,times]{extarticle}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
\usepackage{array}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}

\usepackage{todonotes}
%\usepackage{afterpage}

%\usepackage[switch]{lineno}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%\usepackage{moreverb}

\usepackage{flushend}

\makeatother

\begin{document}

\title{Multi-fluids for Representing Sub-filter-scale Buoyant Convection}

\author{Hilary Weller, William McIntyre, Daniel Shipley and Peter Clark}
\maketitle
\begin{abstract}
The important bits:

1. entrainment is equal to $-\nabla\cdot\mathbf{u}_{i}$

2. the difference in pressure between fluids is $-\gamma\nabla\cdot\mathbf{u}_{i}$

3. Two 2D dry test cases, rising buoyant bubble and radiative-convective
equilibrium.

4. Multi-fluid model in 1D reproduces conditionally averaged resolved
2D simulations
\end{abstract}

\section{Introduction}

\section{The Conditionally Averaged Boussinesq Equations}

Many of the challenges of representing convection with the conditionally
averaged Euler equations \citep[eg those described in][]{WM19} carry
over to the Boussinesq equations. Therefore for simplicity we focus
on the conditionally averaged Boussinesq equations:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\sigma_{j}S_{ji}-\sigma_{i}S_{ij}\label{eq:sigma}\\
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\label{eq:b}\\
\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
\end{eqnarray}
given the definitions of variables in table \ref{tab:defns}.

\begin{table}[h]
\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
where $\rho^{\prime}$ are departures in density from a horizontally
uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
\end{tabular}

\caption{Definitions of variables for the conditionally average Boussinesq
equations.\label{tab:defns}}
\end{table}

\subsection{Pressure of each fluid}

\citet{TEB19} and \citet{WM19} assumed that each co-located fluid
shared the same pressure, leading to unstable equations that \citet{TEB19}
stabilised using diffusion of vertical velocity and \citet{WM19}
stabilised using mass exchanges or drag between the fluids. \citet{TEB19}
achieved realistic results in single column experiments of convective
boundary layer but the amount of diffusion needed would spoil simulations
in the free troposphere. The stabilisation used by \citet{WM19} meant
that the two fluids tended to move as one which defeats the purpose
of using multi-fluid modelling.

The instabilities reported by \citet{WM19} showed growing divergence
in a fluid with vanishing volume fraction. It is mass convergence
rather than velocity convergence that leads to pressure anomalies
that remove the convergence. Therefore if the volume (or mass) fraction
of fluid is vanishingly low then convergence cannot lead to an anomaly
in the total pressure.

We will assume that pressure in each fluid is given by a parameterised
perturbation from the total pressure, $P$:
\begin{equation}
P_{i}=P+p_{i}.
\end{equation}

\citet{BN86} proposed a parameterisation for pressure differences
in a multi-phase explosion model that has been widely used in mathematics
and engineering for simulating fluidised beds of granular material
\citep[eg.][]{EHM92} and two compressible fluids \citep[eg.][]{SA99}.
In these methods, advection equations are written for the volume fraction,
$\sigma_{i}$, and conservation equations are written for mass fraction,
$\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
fluids, these equations would be:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)\label{eq:BNcompaction}\\
\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0\label{eq:rhoTransport}
\end{eqnarray}
where $\mathbf{V}$ is the velocity of the interface between fluids,
$\mu$ is the compaction viscosity which controls how quickly the
pressure of each fluid relaxes to the mean pressure and index $j$
refers to the other fluid in a two fluid system. In our Boussinesq
system $\rho_{i}$ does not appear in the continuity equation. Different
authors make different assumptions about the interface velocity but
if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
$\rho_{i}$ is constant then eqns (\ref{eq:divFree}-\ref{eq:rhoTransport})
imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.

\citet{TEB19} stabilised the multi-fluid equations by adding a diffusion
term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
If a fluid perturbation pressure is set to $-\nu\partial w/\partial z$
this is equivalent to the diffusion term in one dimension. However
addition a diffusion term will harm three dimensional simulations
of resolved convection in the free troposphere whereas adding a fluid
perturbation pressure will not. Inspired by both \citet{BN86} and
\citet{TEB19} we assume that the pressure in each fluid is given
by:
\begin{equation}
p_{i}=-\gamma\nabla\cdot\mathbf{u}_{i}\label{eq:Pi_div}
\end{equation}
where $\gamma$ is a free coefficient. This parameterisation and sensitivity
to $\gamma$ will be evaluated in section \ref{sec:results}.

\subsection{Entrainment and Detrainment}

We consider dry air without turbulence so use the dynamic entrainment
described by \citet{HC51,AK67,DBF+13}:
\begin{equation}
S_{ij}=\begin{cases}
-\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
0 & \text{otherwise}
\end{cases}
\end{equation}
which is necessary to stop air in one fluid from accumulating when
vertical motion ceases (at the top of a rising plume or at the bottom
of descending air). We will also test a common form of lateral entrainment
\citep{DBF+13}:
\begin{equation}
\varepsilon=\frac{0.2}{r_{c}}\implies S_{01}=w_{1}\frac{0.2}{r_{c}}
\end{equation}
where $\varepsilon$ is the well know fractional entrainment rate
and $r_{c}$ is the cloud or plume radius.

\subsection{Drag in the Momentum Equation\label{subsec:drag}}

Pressure differences between the fluids can lead to form drag which
is parameterised following \citet{SW69,RC15,WM19} as: 
\begin{equation}
\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
\end{equation}
where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.

\subsection{The Buoyancy and the Momentum of the Mass that is Transferred}

The different fluids may not be well mixed so the fluid transferred
may not have the mean properties of the fluid it is leaving. In fact,
the most buoyant air should be transferred from fluid 0 to fluid 1
and vice versa and the air with least downward momentum is transferred
from 0 to 1 and vice versa. The properties of the fluids transferred
should depend on modelling of sub-grid-scale variability which is
beyond the scope of this paper. Conditional averaging of high resolution
single fluid solutions depends on the sign of $w$ and so it is sensible
to assume that the vertical velocity of the fluid transferred is zero.
For two dimensional multi-fluid simulations we assume that the horizontal
velocity transferred is equal to the mean horizontal velocity of the
fluid transferred from. Therefore
\begin{equation}
\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
v_{i}\\
0
\end{pmatrix}.
\end{equation}
For buoyancy, following \citet{TEB19}, we use:
\begin{equation}
b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
\end{equation}
and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
transferred depends on the properties of the receiving fluid which
is not logical and can lead to unbounded values of $b_{i}$ in the
fluid that is loosing mass.

\subsection{Dimensional Analysis}

Dimensional analysis can guide us in our choice of $\gamma$ for the
parameterisation of the pressure difference between fluids. We make
the following assumptions:
\begin{enumerate}
\item The flow is buoyancy dominated.
\item The flow is close to inviscid.
\item The flow is slowly varying.
\item Fluid $i$ properties are anomalies from a neutrally stable resting
mean state.
\item We consider only the vertical direction where $w_{ij}^{T}=0$.
\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
\item There are two fluids, $i$ and $j$
\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
and $S_{ji}=0$.
\end{enumerate}
This leads to the following balance in the momentum equation:
\begin{equation}
\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
\end{equation}
If we also assume that fluid $i$ properties are anomalies from a
resting mean state. We non-dimensionalise using a length scale $L^{*}$,
a buoyancy scale $B^{*}$ and a time scale $T^{*}=(L^{*}/B^{*})^{\frac{1}{2}}$
to get the non-dimensional variables:
\begin{eqnarray*}
\tilde{w} & = & w_{i}(L^{*}B^{*})^{-\frac{1}{2}}\\
\tilde{b} & = & b_{i}/B^{*}\\
\tilde{z} & = & z/L^{*}.
\end{eqnarray*}
Then the non-dimensional version of (\ref{eq:wi_balances}) is then:
\begin{equation}
\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{*\frac{1}{2}}L^{*\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom}
\end{equation}
We have assumed that the flow is buoyancy dominated so $\tilde{b}$
is $O(1)$. The stabilisation term must be large enough to smooth
out oscillations in $\tilde{w}$ due to advection and buoyancy but
not too large to remove all variability in $\tilde{w}$ so we need:
\begin{equation}
\gamma\sim B^{*\frac{1}{2}}L^{*\frac{3}{2}}.
\end{equation}

\section{Numerical Solution}

The spatial discretisation follows exactly \citet{WM19}, solving
advective form equations using monotonic, finite volume advection
and C-grid, Lorenz staggering. The time-stepping is Crank-Nicolson
with no off-centering and with deferred correction of explicitly solved
variables. It differs from \citet{WM19} because here we solve the
Boussinesq equations and we need stable solutions for equations with
a separate pressure in each fluid. We use two outer iterations per
time step to update explicitly solved variables. For the first outer
iteration, predicted values for time $n+1$ are set to those from
time level $n$ and are given the superscript $\ell$. For the second
iteration, values at $\ell$ are set to those from the end of the
first iteration. The implicit numerical method for applying the transfers
between fluids is specific for two fluids because it involves the
inversion of $2\times2$ matrices.

The prognostic variables are the $b_{i}$ in cell centres, the $\sigma_{i}$
is cell centres and the velocity flux: the velocity at cell faces
dotted with the area vector for each face (normal to the face), $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$.
The pressures, $P$ and $p_{i}$ are diagnostic.

The first equation to be solved each outer iteration is eqn (\ref{eq:sigma})
for each $\sigma_{i}$, operator split; first applying advection,
then correcting $\sum_{i}\sigma_{i}=1$ and then applying mass transfers:
\begin{eqnarray}
\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\} \\
\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}\\
S_{ij} & = & \begin{cases}
-\nabla\cdot\mathbf{u}_{i}^{\ell} & \text{if }\nabla\cdot\mathbf{u}_{i}^{\ell}<0\\
0 & \text{otherwise}
\end{cases}\\
\sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
\end{eqnarray}
where $\Delta t$ is the time step and the superscripts $\prime$
and $\prime\prime$ denote intermediate values. $\sigma_{i}^{n}$
is interpolated from cell centres onto cell faces using monotonic
van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citet{WM19}
using exclusively values at time level $n$ for best accuracy and
guaranteed monotonicity. For calculating the divergence, the normal
component of $\mathbf{u}_{i}$ is needed at cell faces which are prognostic
variables of the C-grid. The $S_{ij}$ are limited to ensure $0<\sigma_{i}<1\ \forall i$.

Next eqn (\ref{eq:b}) is solved for the buoyancy in each fluid. The
transfer terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
in the transfer term for $b_{i}$.

so they are treated operator split and implicitly, with $b_{0}^{n+1}$
coming from the solution of a $2\times2$ matrix and $b_{1}^{n+1}$
being the back-substitution:
\begin{eqnarray}
b_{i}^{\prime} & = & b_{i}^{n}+\frac{\Delta t}{2}\left(b_{it}^{n}+b_{it}^{\ell}\right)\\
\text{where }b_{it} & = & -\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}-N^{2}w_{i}+\alpha\nabla^{2}b_{i}\\
b_{0}^{n+1} & = & \frac{\left(1+\Delta t\left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\right)b_{0}^{\prime}+\Delta t\left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}b_{1}^{\prime}}{1+\Delta t\left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}+\Delta t\left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}}\\
b_{1}^{n+1} & = & \frac{\Delta t\left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}b_{0}^{n+1}+b_{1}^{\prime}}{1+\Delta t\left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}}.
\end{eqnarray}
The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$ before the mass
transfers is necessary to ensure bounded and conservative transfers,
as described by \cite{MWH1x}.

Next a Poisson equation is solved to calculate the total pressure
to ensure that the total velocity is divergence free. The pressure
equation also provides updates for the velocity flux, $u_{i}$. First
an intermediate velocity flux is calculated with partial updates:
\begin{eqnarray}
u_{i}^{\prime}= & u_{i}^{n}+\frac{\Delta t}{2} & \biggl(\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{\ell}\cdot\mathbf{S}-\nabla_{f}p_{i}^{\ell}\\
 &  & +\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{n}\cdot\mathbf{S}-\nabla_{f}(P+p_{i})^{n}\biggr)
\end{eqnarray}
where operator $()_{f}$ means linear interpolation from cell centres
onto cell faces and $\nabla_{f}P$ is a compact discretisation of
$(\nabla P)_{f}\cdot\mathbf{S}$: ie the normal component of the pressure
gradient calculated from just the values of pressure either side of
the face. Once we have calculated $P^{n+1}$, the velocity flux (without
momentum transfers) is updated from the back-substitution:
\begin{equation}
u_{i}^{\prime\prime}=u_{i}^{\prime}-\frac{\Delta t}{2}\nabla_{f}P^{n+1}.\label{eq:backSub}
\end{equation}
The Poisson equation for $P$ is found by multiplying each eqn (\ref{eq:backSub})
by $\sigma_{i}$, summing over all fluids and taking the divergence.
Knowing that $\nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0$, $\sum_{i}\sigma_{i}=1$
and $\sum_{i}\sigma_{i}p_{i}=0$ gives:
\begin{equation}
\nabla\cdot\sum_{i}\sigma_{i}u_{i}^{\prime}-\frac{\Delta t}{2}\nabla^{2}P^{n+1}=0
\end{equation}
which is solved to find $P^{n+1}$.

Next, the momentum transfers due to mass transfer and due to drag
are calculated implicitly, similar to the implicit transfers of buoyancy,
calculating $u_{i}^{n+1}$ from $u_{i}^{\prime\prime}$. These do
not influence the total $P$ or total divergence because momentum
is transferred conservatively. However they do influence $p_{i}$
which is why they are calculated before $p_{i}$. The final stage
of the time step iteration is to solve Helmholtz equations for each
$p_{i}$:
\begin{equation}
\sigma_{i}^{n+1}p_{i}^{n+1}=-\gamma\nabla\cdot\left(\sigma_{if}^{n+1}u_{i}^{n+1}-\frac{\Delta t}{2}\sigma_{if}^{n+1}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right).\label{eq:pi_Helm}
\end{equation}
Both $p_{i}^{n+1}$ and $p_{i}^{\ell}$ appear in eqn (\ref{eq:pi_Helm})
because $u_{i}^{n+1}$ already contains contributions from $p_{i}^{\ell}$
so these are removed before updating $p_{i}^{n+1}$. No back substitution
for $u_{i}$ is done after calculating $p_{i}^{n+1}$ because this
would destroy the divergence free constraint. Therefore $p_{i}^{n+1}$
only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
converge and $p_{i}^{\ell}=p_{i}^{n+1}$.

The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
from $u_{i}$ following \citet{WM19}. The stages calculating $P$,
$p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$.

\section{Validation Test Cases\label{sec:results}}

Two test cases are developed to tune parameters and to validate the
use of multi-fluid equations to represent dry, two-dimensional sub-grid-scale
convection. The first is steady state with heat transfer at ground
and radiative cooling. The second is transient; the standard rising
bubble of \citet{BF02}. We aim to reproduce the vertical heat transport,
mean velocity of the rising air, bouyancy of the rising air and pressure
differences between two fluids in a single column two fluid model.
For both test cases the reference solution is a single fluid solution
of the two-dimensional Boussinesq equations at high horizontal and
vertical resolution.

\subsection{Rising Bubble}

The test case of \citet{BF02} was designed for fully compressible
models but similar solutions are obtained solving Boussinesq equations.
For the Boussinesq version we set $N^{2}=0$ in a domain of height
10\,km and width 20\,km initially at rest. The buoyant perturbation
is given by:
\begin{equation}
b=\frac{1}{15}\cos^{2}\frac{\pi L}{2}\label{eq:thetaPerturb}
\end{equation}
for $L<1$ where $L=\sqrt{\left(\frac{x-x_{c}}{x_{r}}\right)^{2}+\left(\frac{z-z_{c}}{z_{r}}\right)^{2}}$,
$x_{c}=10\ \text{km}$, $z_{c}=2\ \text{km}$ and $x_{r}=z_{r}=2\ \text{km}$.
100\,m grid spacing is used in the $x$ and $z$ directions for the
two dimensional reference simulation and $\Delta z=100\ \text{m}$
is used in the vertical for the single column simulations. All simulations
use a time-step of 2\,s.

\subsubsection{Single Fluid Solutions}

The solution of the rising buoyant bubble solving the Boussinesq equations
for 1000s is shown in \ref{fig:bubble} with buoyancy coloured and
pressure contoured. The solution is very similar to the fully compressible
solution \citep{BF02}. The pressure gradients will accelerate the
flow beneath the bubble, decelerate the flow above the bubble and
pull in air horizontally. Horizontally and conditionally averaged
fields, conditioned on $w$ are shown in the top row of figure \ref{fig:bubble_singleUnderRes}.
$\sigma_{1}$ is the volume fraction at every height that is rising,
$b_{0}$ and $b_{1}$ are the buoyancy conditioned on $w$, $w_{0}$
and $w_{1}$ are the horizontal averaging rising and falling vertical
velocity and $P_{0}$ and $P_{1}$ are the pressure of the rising
and falling fluid. An accurate multi-fluid model of convection should
reproduce these fields approximately at coarser horizontal resolution
or in a single column model.

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
\par\end{centering}
\noindent \begin{centering}
\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
\par\end{centering}
\caption{The single fluid, resolved rising bubble after 1000s. Buoyancy is
coloured and pressure is contoured, every $10\text{m}^{2}\text{s}^{-2}$,
negative contours dashed. \label{fig:bubble}}
\end{figure}

\citet{TEB19} and \citet{WM19} assumed that both fluids would share
the same pressure with differences parameterised as drag. The pressure
in figure \ref{fig:bubble} shows that this is a bad assumption. Drag
would always act to slow down the fluids whereas the negative pressure
gradients in the rising fluid just below the bubble are acting to
accelerate the rising motion.

When resolution is insufficient to resolve the rising bubble, the
vertical transports are too weak, motivating the need for convection
parameterisation. The horizontal averages are shown in figure \ref{fig:bubble_singleUnderRes}
for horizontal resolutions of nine columns, five columns, three columns
and a single column all for the 20km wide domain and all still using
$\Delta z=100\ \text{m}$. These simulations are initialised by conservative
horizontal averaging from the full resolution solution. As the horizontal
resolution is reduced, the vertical transport reduces until there
is no movement at all for a single column: there is no possibility
of fluid rising because in a single column with a single fluid there
can be no compensating subsidence.

\begin{figure}
\noindent %
\begin{tabular}{ccccc}
\begin{turn}{90}
200 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
\begin{turn}{90}
9 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
5 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
3 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
1 Column
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
\end{tabular}

\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
and a single fluid. Horizontal averages are conditioned based on $w$.
\label{fig:bubble_singleUnderRes}}
\end{figure}

\subsubsection{Multi-fluid Solutions}

\begin{figure}
\begin{tabular}{cccc}
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ $s using $S_{ij}=0$, $p_{i}=0$, $C_{D}/r_{c}=0$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{ij}=0$, $p_{i}=0$, $C_{D}/r_{c}=1/2000\text{m}^{-1}$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer_drag/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{ij}=0$, $p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$,
$C_{D}/r_{c}=0$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$,
$p_{i}=0$, $C_{D}/r_{c}=0$, $b_{ij}^{T}=b_{i}$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{01}=w_{1}0.2/r_{c}$, $p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$,
$C_{D}=0$, $r_{c}=2000\text{m}$, $b_{ij}^{T}=b_{i}$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
\end{tabular}

\caption{Solid lines are the multi-fluid, single column solutions of the rising
bubble. Dashed lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
\end{figure}

\noindent 
\begin{figure}
\begin{tabular}{cccc}
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ $s using $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$,
$p_{i}=-4\times10^{3}\nabla\cdot\mathbf{u}_{i}$, $C_{D}/r_{c}=0$,
$b_{ij}^{T}=b_{i}$ }\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$,
$p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$, $C_{D}/r_{c}=0$, $b_{ij}^{T}=b_{i}$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$,
$p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$, $C_{D}/r_{c}=1/2000\text{m}^{-1}$,
$b_{ij}^{T}=b_{i}$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$,
$p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$, $C_{D}/r_{c}=0$, $b_{ij}^{T}=0$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{Results at $t=1000\ \text{s}$ using $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$,
$p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$, $C_{D}/r_{c}=0$, $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
\end{tabular}

\caption{Solid lines are the multi-fluid, single column solutions of the rising
bubble. Dashed lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn}}
\end{figure}

Multi-fluid, single column simulations are initialised by horizontally
and conditionally averaging the full resolution single fluid initial
conditions. Sinking air is put into fluid zero and rising air into
fluid one. The velocity field after one time step is used for initialising
the partition as the air is stationary at $t=0$. Results are shown
in figures \ref{fig:multiFluidSingleColumn-bad} and \ref{fig:multiFluidSingleColumn}
for various assumptions about transfers between fluids and various
parameter values.

If there is no drag between fluids, no transfers, no diffusion and
the pressures of both fluids are assumed equal then the multi-fluid
equations are unstable \citep{TEB19}. The simulation with no transfers
($S_{ij}=0$) in the top row of figure \ref{fig:multiFluidSingleColumn-bad}
The buoyant fluid has risen very little from the initial conditions
and oscillations have developed in all fields. $\sigma$ oscillates
between zero and one meaning that only one fluid is present at some
locations so there is no possibility for the fluids to move past each
other. Including drag (second row of figure \ref{fig:multiFluidSingleColumn-bad})
improves stability a little but does not enable the fluids to move
past each other.

Parameterising the pressure difference between fluids as $P_{i}=P+p_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$
with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ stabilises the solution
and the resulting pressure gradients force the two fluids to move
past each other (third row of figure \ref{fig:multiFluidSingleColumn-bad}).
However there is an unrealistic discontinuity with no fluid 1 below
the buoyant fluid and very little falling air at the lowest height
of the rising fluid. With a single column and two fluids, all air
must rise in one fluid and sink in the other. Continuity does not
allow for any other solution. Pressure gradients can accelerate or
decelerate this flow but as the model is set up, with no transfers
between fluids, no fluid can change direction. It is therefore essential
to have transfers between fluids.

Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
can stabilise the solution and enable the fluids to move past each
other even without pressure differences between the fluids (fourth
row of figure \ref{fig:multiFluidSingleColumn-bad}). However too
much is detrained from fluid 1, fluid 1 looses too much buoyancy and
a discontinuity arises at the bubble front; the buoyancy force is
producing vertical motion but there is no pressure to make it smooth.

The other entrainment option is the commonly used fractional entrainment
rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
differences between fluids in the bottom row of figure \ref{fig:multiFluidSingleColumn-bad}.
This combination produces smooth solutions but the updraught is too
weak and too much is entrained into fluid 1. Using this entrainment,
the updraught will entrain more and more air until $\sigma_{1}=1$.

Once we use entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
and pressure difference between the fluids controlled by divergence
($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
realistic (first two rows of figure \ref{fig:multiFluidSingleColumn}).
The detrainment of buoyant fluid leads to smooth profiles behind the
bubble although $\sigma_{1}$ is lower than the resolved simulation
in the lower half of the domain and the fluid left behind is too warm.
This is expected since the detrained fluid is assumed to have the
mean fluid properties of the fluid it is leaving ($b_{ij}^{T}=b_{i}$)
whereas in reality the least buoyant fluid will leave the rising fluid
and start to fall. Smaller values of $\gamma$ leave a discontinuity
in the updraught velocity at the leading edge of the bubble and larger
values of $\gamma$ reduce the velocity further, meaning that the
bubble does not rise enough (not shown). None of the simulations reproduce
the peak updraught velocities but the simulation with $p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$
and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ comes closest, meaning that
the bubble rise is approximately correct and $\sigma_{1}$ is approximately
correct where the bubble is although it is less accurate above and
below the bubble. Using $p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$
produces accurate pressure increases above the centre of the bubble
but does not produce the large low pressure at the bottom of the bubble,
which is located at the lobes of the highest buoyancy in the resolved
simulation (figure \ref{fig:bubble}). It would be tempting to model
this by assuming hydrostatic pressure or the Bernouilli equation,
but these are both forms of the momentum equation which is used to
calculate the velocity and so cannot also be used to model the pressure.

The results in the third row of figure \ref{fig:multiFluidSingleColumn}
use $p_{i}=-10^{4}\nabla\cdot\mathbf{u}_{i}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
but this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$.
The drag slows the updraughts without increasing the mixing between
the fluids which makes the solutions less like the resolved simulations.
Although drag is known to be an important term in the momentum equations
for buoyant thermals and plumes \citep[eg][]{RC15}, the drag is related
to mixing with downdraught air which is accounted for in the entrainment
term of the momentum equation. So adding a separate term from drag
risks double counting and certainly slows the plume too much.

Two simple models for estimating the buoyancy of the fluid transferred
between updraught and downdraught have been tested. The results in
the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
that the fluid transferred has zero buoyancy in order to keep the
positively buoyant air in fluid one and the negatively buoyant air
in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
the mean buoyancy of fluid one increases. This leads to very high
buoyancy in fluid one which is not present in the resolved simulation.
The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citet{TEB19}
so that the fluid transferred is influenced by the fluid it is moving
towards as well as where it has come from. This again leads to very
large buoyancy in fluid one and also negative buoyancy in fluid zero
which should not occur for this test case. These simple models reinforce
the idea that the buoyancy of the fluid transferred should depend
on knowledge of sub-grid-scale variability of $b$ within each fluid
\textendash{} these simple assumptions can lead to unrealistic behaviour.

This section has demonstrated the value of using a single column,
multi-fluid model to simulate a buoyant rising bubble with a single
updraght fluid and a single downdraught fluid. Transfers between the
fluids have been successfully modelled using entrainment set by divergence
and the pressure difference between the fluids has also been represented
by divergence. There are clearly discrepancies between the single
fluid resolved rising bubble and the two fluid single column rising
bubble but we do wish aim to over-fit the multi-fluid model to one,
dry, two-dimensional test case.

\subsection{Radiative-Convective Equilibrium (RCE)}

A two-dimensional, dry radiative convective equilibrium test case
is devised to mimic some properties of atmospheric convection, in
particular the difficulty resolving the flow at coarse resolution.
The domain is 160km wide, 10km tall and is resolved by 640 cells in
the horizontal and 40 in the vertical ($\Delta x=\Delta z=250$m).
The top and bottom boundaries are zero velocity and the lateral boundaries
are periodic. A heat flux of $h=10^{-3}\text{m}^{2}\text{s}^{-3}$
is imposed at the bottom boundary leading to a boundary condition
of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
so as to give a Plank constant of $0.707$. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$
is applied to the domain to maintain equilibrium.

The fluid is initially stationary with $b=0$. In order to quickly
and reproducibly initialise instability, $b=10^{-4}\text{m}^{2}\text{s}^{-1}$
is imposed in a square of side length 2000m at the centre in the $x$
direction and at the ground. The simulation is run using a time step
of $5\ \text{s}$. A quasi-steady, choatic state is reached after
about $3\times10^{4}\text{s}$ and the simulation is run for a further
$2\times10^{5}\text{s}$ and conditional averages are calculated over
the final $10^{5}$s.

\subsubsection{Results of the Resolved Simulation}

This test case is designed to have strong upward velocity in narrow
plumes and weak descent elsewhere to mimic atmospheric convection
but without the complication of moisture, phase changes and three
spatial dimensions. A snapshot of the buoyancy and pressure of the
radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
are shown in figure \ref{fig:RCE_resolved} with vertical velocity
contoured showing intense, narrow updraughts.

Figure \ref{fig:RCE_resolved} shows buoyant air at the ground which
rises in narrow plumes, accelerating due to buoyancy and pressure
gradients then decelerating due to pressure gradients before reaching
the top. The plumes spread out and the sinking air is a mixture of
warm and cold with similar pressure gradients in the rising and falling
air, accelerating then decelerating the flow so as to maintain continuity.

\noindent 
\begin{figure}
\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/200000/bw}

Buoyancy ($\text{m}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/legends/bw_b}

\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/200000/Pw}

Pressure ($\text{m}^{2}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/legends/Pw_P}

\caption{Buoyancy, vertical velocity and pressure of resolved radiative-convective
equilibrium test case. Vertical velocity contours are black every
0.5m/s with negative contours dashed and the zero contour dotted.
Domain is 10km high and 160km wide and the z-direction is stretched
a factor of 2 in the plots. \label{fig:RCE_resolved}}
\end{figure}

Horizontal averages conditioned on $w$ and time averaged every 1000s
between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
in figure \ref{fig:RCE_hMean}. The rising and falling volume fractions,
$\sigma_{1}$ and $\sigma_{0}$, remain close to $\frac{1}{2}$ throughout
the depth. The rising plumes look narrow in figure \ref{fig:RCE_resolved}
but there are wide regions of slowly rising air around the plume cores.
Due to this entrained cool air and warm air sinking after hitting
the model top, the buoyancy of the rising and falling fluids are close
with the rising plume warmer near the surface. The air cools with
height then warms near the model top due to accumulation of warm air.

\noindent 
\begin{figure}
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean}\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean}\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean}\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}

\caption{Horizontal averages of the resolved RCE case averaged between $t=10^{5}\text{s}$
and $2\times10^{5}\text{s}$.  \label{fig:RCE_hMean}}
\end{figure}

The similarity of the mean values of the rising and falling fluid
is striking in the vertical velocity in figure \ref{fig:RCE_hMean}
which shows acceleration then deceleration controlled by pressure
gradients. The slightly stronger pressure gradients in the rising
fluid match the slightly higher speed.

\subsubsection{Results of the Single Column Simulations}

The tow fluid model is used to simulate the RCE test case in a single
column of 40 cells with zero buoyancy gradient at the top and a buoyancy
gradien5t of $10^{-5}\text{s}^{-2}$ at the ground for both fluids.
The two fluids are initilasied usign the time mean conditional horizontal
averages from the single fluid resolved simulation. The entrainment
model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ is used for all simulations
to account for transfers throughout the domain to represent cloud
base mass flux (at the bottom boundary), cloud top detrainment and
lateral entrainment.

Results of simulations using two values of $\gamma$, two models for
$b_{ij}^{T}$ and with and without drag are shown in figure \ref{fig:RCE_singleColumn}.
Solid lines show results of the single column, multifluid model at
$t=10^{4}\text{s}$ and dashed lines show the time averaged, horizontally
conditionally averaged resolved single fluid simulation. The entrainment
model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$ at
about 0.5 throughout the depth, as in the resolved simulatin, with
entrainemnt in the lower half of the domain ($S_{01}>0$) and detrainment
in the upper half, where the air decelerates towards the top ($S_{10}>0$).
All of the two fluid simulations maintain a larger buoyancy difference
between the two fluids than the resolved simulation; the single column
solution cannot capture the complex distribution of heat in both fluids.
The single column solutions accurately capture the large buoyancy
gradients near the ground and near uniform profile above this. The
model $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$ represents the buoyancy
of the transferred fluikd very badly, leading to strong cooling in
fluid zero near the ground due to the large transferts. It is clearly
more accurate to assume that fluids take their mean propertieds when
transferred, $b_{ij}^{T}=b_{i}$. The vertical velocity is sensitive
to the pressure differences between fluids with $\gamma=2000\text{m}^{2}\text{s}^{-1}$
giving the closest match.

\noindent 
\begin{figure}
\begin{tabular}{ccccc}
\multicolumn{5}{c}{Single column with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and $b_{ij}^{T}=b_{i}$,
$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$ versus resolved}\tabularnewline
$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_w/100000/P}\tabularnewline
\multicolumn{5}{c}{Single column with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and $b_{ij}^{T}=b_{i}$,
$\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ versus resolved}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/P}\tabularnewline
\multicolumn{5}{c}{Single column with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$,
$\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ versus resolved}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-dev/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/P}\tabularnewline
\end{tabular}

\caption{Results of single Column RCE simulations after $10^{4}\ \text{s}$.
Dashed lines show time averaged, conditionally averaged horizontal
means of the resolved simulations. \label{fig:RCE_singleColumn}}
\end{figure}

\section{Summary, Conclusions and Further Work}

\section*{Acknowledgements}

Many thanks to Peter Clark, John Thuburn and Chris Holloway for valuable
discussions and proof reading. Thanks to the NERC/Met Office Paracon
project. We acknowledge funding from the Circle-A and RevCon Paracon
projects NE/N013743/1 and NE/xxx.

\bibliographystyle{abbrvnat}
\bibliography{numerics}

\end{document}

### 2020-03-23 preSubmission/manuscript.tex
First submmitted version and empty revised version and responses to reviewer comments.

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,times]{extarticle}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
\usepackage{array}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}

\usepackage{todonotes}
%\usepackage{afterpage}

%\usepackage[switch]{lineno}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%\usepackage{moreverb}

\usepackage{flushend}

\makeatother

\begin{document}

\title{Multi-fluids for Representing Sub-filter-scale Buoyant Convection}

\author{Hilary Weller, William McIntyre, Daniel Shipley and Peter Clark}
\maketitle
\begin{abstract}
Multi-fluid modelling is a promising new method of representing sub
and near grid-scale convection allowing for consistent and accurate
treatment of net mass transport by convection, non-equilibrium and
turbulence. The air is partitioned into convecting and non-convecting
fluids each with their own velocity, temperature and constituents
so that separate equations of motion can be solved for each fluid,
thus representing features that cannot be resolved in a single fluid
at coarse resolution.

This paper presents multi-fluid Boussinesq equations for representing
under resolved dry convection. We present a new model for entrainment
and detrainment based on divergence which leads to excellent representation
of the convective area fraction. Previous multi-fluid modelling of
convection has assumed that all fluids share the same pressure. We
show that this is a bad assumption and we propose and validate a model
for the pressure difference between the fluids based on divergence.

Two vertical slice test cases are used to validate the multi-fluid
model; a buoyant rising bubble and radiative convective equilibrium
are simulated at high resolution and conditionally averaged based
on the sign of the vertical velocity. The multi-fluid model reproduces
the mean properties of the rising and falling fluids in a single column. 
\end{abstract}

\section{Introduction}

Slow progress has been made improving the parameterisation of sub-grid-scale
convection since \citet{AS74,Tied89,GR90,KF90}. Convection is still
one of the weakest aspects of large scale models of the atmosphere
\citep{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
the quasi-equilibrium assumption \citep{PR98,GG05,Par14}, including
stochasticity \citep{PC08} and allowing net mass transport by convection
\citep{KB08,MB19}. These developments have enabled limited simulation
in the grey zone, where convection is partially resolved. However
there are still systematic biases implying that improvements should
still be possible.

\citet{TWV+18} proposed multi-fluid modelling of convection in order
to treat non-equilibrium and net mass transport correctly and consistently
with the same numerics and physics controlling thermals, the stable
environment and downdraught dynamics. \citet{Yano14} derived similar
equations for multiple segments and showed how this is a generalisation
of the mass-flux formulation. The \citet{TKP+18} ``extended eddy
diffusivity mass flux'' or extended EDMF scheme also uses similar
equations but \citet{TKP+18} didn't propose a suitable numerical
method for solving the equations. Multi-fluids promises big improvements
in the representation of sub-grid-scale convection and unification
with the representation of turbulence, particularly at the grey zone.
However, there is a long way to go, particularly as multi-fluids requires
a dedicated model rather than being a stand alone parameterisation
for a dynamical core. \citet{TEB19} and \citet{WM19} presented solutions
of the multi-fluid equations assuming two fluids that share the same
pressure (or that pressure differences are predominantly due to drag
between the fluids). \citet{TEB19} showed that these equations (without
drag) are in fact unstable and can be stabilised by diffusion of vertical
velocity whereas \citet{WM19} stabilised the equations with diffusion
and drag between fluids. Neither of these stabilisation techniques
are acceptable and in this paper we show that there are significant
and sustained pressure differences between the fluids (section \ref{sec:results}).

This paper presents the multi-fluid Boussinesq equations for representing
sub-grid-scale convection including a parameterisation of the pressure
difference between fluids (section \ref{subsec:fluidPressure}) and
a new model of entrainment and detrainment (section \ref{subsec:Sij}).
The numerical method for solving the equations is described in section
\ref{sec:numerics}. We compare results of resolved dry convection
in a single-fluid two dimensional Boussinesq model with a two-fluid,
single column model in section \ref{sec:results} using two vertical
slice test cases.

\section{The Multi-fluid Boussinesq Equations}

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \citep[eg those described in][]{WM19} carry
over to the Boussinesq equations; convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Buossinesq equations. Therefore for simplicity we focus on the
multi-fluid Boussinesq equations without background stratification:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\} \label{eq:sigma}\\
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\} \label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}\\
\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
\end{eqnarray}
with variables defined in table \ref{tab:defns}.

\begin{table}[h]
\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
where $\rho^{\prime}$ are departures in density from a horizontally
uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
\end{tabular}

\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
\end{table}

\subsection{Pressure of each fluid \label{subsec:fluidPressure}}

\citet{TEB19} and \citet{WM19} assumed that each co-located fluid
shared the same pressure, leading to unstable equations that \citet{TEB19}
stabilised using diffusion of vertical velocity and \citet{WM19}
stabilised using mass exchanges or drag between the fluids. \citet{TEB19}
achieved realistic results in single column experiments of convective
boundary layer but the amount of diffusion needed would spoil simulations
in the free troposphere. The stabilisation used by \citet{WM19} meant
that the two fluids tended to move as one which defeats the purpose
of using multi-fluid modelling.

The instabilities reported by \citet{WM19} showed growing divergence
in a fluid with vanishing volume fraction. It is mass convergence
rather than velocity convergence that leads to pressure anomalies
that remove the convergence. Therefore if the volume (or mass) fraction
of fluid is vanishingly low then convergence cannot lead to an anomaly
in the total pressure.

We will assume that pressure in each fluid is given by a parameterised
perturbation, $p_{i}$, from the total pressure, $P$:
\begin{equation}
P_{i}=P+p_{i}.
\end{equation}

\citet{BN86} proposed a parameterisation for pressure differences
in a multi-phase explosion model that has been widely used in mathematics
and engineering for simulating fluidised beds of granular material
\citep[eg.][]{EHM92} and two compressible fluids \citep[eg.][]{SA99}.
In these methods, advection equations are written for the volume fraction,
$\sigma_{i}$, and conservation equations are written for mass fraction,
$\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
fluids, the \citet{BN86} equations would be:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)\label{eq:BNcompaction}\\
\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0\label{eq:rhoTransport}
\end{eqnarray}
where $\mathbf{V}$ is the velocity of the interface between fluids,
$\mu$ is the compaction viscosity which controls how quickly the
pressure of each fluid relaxes to the mean pressure and index $j$
refers to the other fluid in a two fluid system. In our Boussinesq
system $\rho_{i}$ does not appear in the continuity equation. Different
authors make different assumptions about the interface velocity but
if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
$\rho_{i}$ is constant then eqns (\ref{eq:divFree}-\ref{eq:rhoTransport})
imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.

\citet{TEB19} stabilised the multi-fluid equations by adding a diffusion
term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
If a fluid perturbation pressure is set to $-\nu\partial w/\partial z$
this is equivalent to the diffusion term in one dimension. However
adding a diffusion term will harm three dimensional simulations of
resolved convection in the free troposphere whereas adding a fluid
perturbation pressure will not. Inspired by both \citet{BN86} and
\citet{TEB19} we assume that the pressure in each fluid is given
by:
\begin{equation}
p_{i}=-\gamma\nabla\cdot\mathbf{u}_{i}\label{eq:Pi_div}
\end{equation}
where $\gamma$ is a free coefficient. Dimensional analysis in section
\ref{subsec:dimAnal} will inform the choice of $\gamma$ and sensitivity
to $\gamma$ will be evaluated in section \ref{sec:results}.

\subsection{Entrainment and Detrainment \label{subsec:Sij}}

We consider dry air without turbulence so use the dynamic entrainment
described by \citet{HC51,AK67,DBF+13}:
\begin{equation}
S_{ij}=\begin{cases}
-\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
0 & \text{otherwise}
\end{cases}
\end{equation}
which is necessary to stop air in one fluid from accumulating when
vertical motion ceases (at the top of a rising plume or at the bottom
of descending air). We will also test a common form of lateral entrainment
\citep{DBF+13}:
\begin{equation}
\varepsilon=\frac{0.2}{r_{c}}\implies S_{01}=w_{1}\frac{0.2}{r_{c}}
\end{equation}
where $\varepsilon$ is the well know fractional entrainment rate
and $r_{c}$ is the cloud or plume radius.

\subsection{Drag in the Momentum Equation\label{subsec:drag}}

Pressure differences between the fluids can lead to form drag which
is parameterised following \citet{SW69,RC15,WM19} as: 
\begin{equation}
\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
\end{equation}
where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.

\subsection{The Buoyancy and the Momentum of the Mass that is Transferred \label{subsec:transferProperties}}

The different fluids may not be well mixed so the fluid transferred
may not have the mean properties of the fluid it is leaving \citep[as was assumed by][]{WM19}.
In fact, the most buoyant air should be transferred from fluid 0 to
fluid 1 and vice versa, and the air with least downward momentum should
be transferred from 0 to 1 and vice versa. The properties of the fluids
transferred should depend on the modelling of sub-grid-scale variability
which is beyond the scope of this paper. In section \ref{sec:results}
we conditionally average high resolution solutions based on the sign
of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
Therefore the air that is transferred at the interface will have $w=0$.
For two dimensional multi-fluid simulations we assume that the horizontal
velocity transferred is equal to the mean horizontal velocity of the
fluid transferred from. Therefore
\begin{equation}
\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
v_{i}\\
0
\end{pmatrix}.
\end{equation}
For buoyancy, following \citet{TEB19}, we use:
\begin{equation}
b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
\end{equation}
and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
transferred depends on the properties of the receiving fluid which
is not logical and can lead to unbounded values of $b_{i}$ in the
fluid that is loosing mass (as demonstrated in section \ref{sec:results}).

\subsection{Dimensional Analysis\label{subsec:dimAnal}}

Dimensional analysis can guide our choice of $\gamma$ for the parameterisation
of the pressure difference between fluids. We make the following assumptions:
\begin{enumerate}
\item The flow is buoyancy dominated.
\item The flow is close to inviscid.
\item The flow is slowly varying.
\item Fluid $i$ properties are anomalies from a neutrally stable resting
mean state.
\item We consider only the vertical direction where $w_{ij}^{T}=0$.
\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
\item There are two fluids, $i$ and $j$
\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
and $S_{ji}=0$.
\end{enumerate}
This leads to the following balance in the momentum equation:
\begin{equation}
\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
\end{equation}
We non-dimensionalise using a length scale $L$, a buoyancy scale
$B$ and a time scale $T$ to get the non-dimensional variables:
\begin{eqnarray*}
\tilde{w} & = & w_{i}T/L\\
\tilde{b} & = & b_{i}/B\\
\tilde{z} & = & z/L.
\end{eqnarray*}
Then the non-dimensional version of (\ref{eq:wi_balances}) is:
\begin{equation}
\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
\end{equation}
The flow is buoyancy dominated so the buoyancy term should be $O(1)$
so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
so the non-dimensional momentum equation becomes:
\begin{equation}
\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
\end{equation}
The stabilisation term must be large enough to smooth out oscillations
in $\tilde{w}$ due to advection and buoyancy but not too large to
remove all variability in $\tilde{w}$ so we need:
\begin{equation}
\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
\end{equation}

\section{Numerical Solution \label{sec:numerics}}

The spatial discretisation follows exactly \citet{WM19}, solving
advective form equations using monotonic, finite volume advection
and C-grid, Lorenz staggering. The time-stepping is Crank-Nicolson
with no off-centering and with deferred correction of explicitly solved
variables. It differs from \citet{WM19} because here we solve the
Boussinesq equations and we need stable solutions for equations with
a separate pressure in each fluid. We use two outer iterations per
time step to update explicitly solved variables. For the first outer
iteration, predicted values for time $n+1$ are set to those from
time level $n$ and are given the superscript $\ell$. For the second
iteration, values at $\ell$ are set to those from the end of the
first iteration. The implicit numerical method for applying the transfers
between fluids is specific for two fluids because it involves the
inversion of $2\times2$ matrices.

The prognostic variables are the $b_{i}$ in cell centres, the $\sigma_{i}$
in cell centres and the velocity flux at cell faces, $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$,
which is the velocity at cell faces dotted with the area vector for
each face (normal to the face). The pressures, $P$ and $p_{i}$ are
diagnostic.

The first equation to be solved each outer iteration is eqn (\ref{eq:sigma})
for each $\sigma_{i}$, operator split; first applying advection,
then correcting $\sum_{i}\sigma_{i}=1$ and then applying mass transfers:
\begin{eqnarray}
\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\} \\
\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}\\
S_{ij} & = & \begin{cases}
-\nabla\cdot\mathbf{u}_{i}^{\ell} & \text{if }\nabla\cdot\mathbf{u}_{i}^{\ell}<0\\
0 & \text{otherwise}
\end{cases}\\
\sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
\end{eqnarray}
where $\Delta t$ is the time step and the superscripts $\prime$
and $\prime\prime$ denote intermediate values. $\sigma_{i}^{n}$
is interpolated from cell centres onto cell faces using monotonic
van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citet{WM19}
and values exclusively at time level $n$ for best accuracy and guaranteed
monotonicity. For calculating the divergence, the normal component
of $\mathbf{u}_{i}$ is needed at cell faces which are prognostic
variables of the C-grid. The $S_{ij}$ are limited to ensure $0<\sigma_{i}<1\ \forall i$.

Next eqn (\ref{eq:b}) is solved for the buoyancy in each fluid, first
transporting buoyancy and then applying the transfer terms. The transfer
terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
in the transfer term for $b_{i}$ so they are treated operator split
and implicitly:
\begin{eqnarray}
b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
 &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
\end{eqnarray}
where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
from before the mass transfers is necessary to ensure bounded and
conservative transfers, as described by \cite{MWH1x}. Simultaneous
solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
\begin{eqnarray}
b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
\end{eqnarray}
where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$

Next a Poisson equation is solved to calculate the total pressure,
$P$ to ensure that the total velocity is divergence free. The pressure
equation also provides updates for the velocity flux, $u_{i}$. First
an intermediate velocity flux is calculated with partial updates and
updates from a previous value of $p_{i}$:
\begin{eqnarray}
u_{i}^{\prime}= & u_{i}^{n}+\frac{\Delta t}{2} & \biggl(\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{\ell}\cdot\mathbf{S}-\nabla_{f}p_{i}^{\ell}\\
 &  & +\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{n}\cdot\mathbf{S}-\nabla_{f}(P+p_{i})^{n}\biggr)
\end{eqnarray}
where operator $()_{f}$ means linear interpolation from cell centres
onto cell faces and $\nabla_{f}P$ is a compact discretisation of
$(\nabla P)_{f}\cdot\mathbf{S}$: ie the normal component of the pressure
gradient calculated from just the values of pressure either side of
the face. Once we have calculated $P^{n+1}$, the velocity flux (without
momentum transfers) is updated from the back-substitution:
\begin{equation}
u_{i}^{\prime\prime}=u_{i}^{\prime}-\frac{\Delta t}{2}\nabla_{f}P^{n+1}.\label{eq:backSub}
\end{equation}
The Poisson equation for $P^{n+1}$ is found by multiplying each eqn
(\ref{eq:backSub}) by $\sigma_{i}$, summing over all fluids and
taking the divergence. Knowing that $\nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0$,
$\sum_{i}\sigma_{i}=1$ and $\sum_{i}\sigma_{i}p_{i}=0$ gives:
\begin{equation}
\nabla\cdot\sum_{i}\sigma_{i}u_{i}^{\prime}-\frac{\Delta t}{2}\nabla^{2}P^{n+1}=0
\end{equation}
which is solved to find $P^{n+1}$.

Next, the momentum transfers due to mass transfer and due to drag
are calculated implicitly, similar to the implicit transfers of buoyancy,
calculating $u_{i}^{n+1}$ from $u_{i}^{\prime\prime}$. These do
not influence the total $P$ or total divergence because momentum
is transferred conservatively. However they do influence $p_{i}$
which is why they are calculated before $p_{i}$. The final stage
of the time step iteration is to solve Helmholtz equations for each
$p_{i}$:
\begin{equation}
\sigma_{i}^{n+1}p_{i}^{n+1}=-\gamma\nabla\cdot\left(\sigma_{if}^{n+1}u_{i}^{n+1}-\frac{\Delta t}{2}\sigma_{if}^{n+1}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right).\label{eq:pi_Helm}
\end{equation}
Both $p_{i}^{n+1}$ and $p_{i}^{\ell}$ appear in eqn (\ref{eq:pi_Helm})
because $u_{i}^{n+1}$ already contains contributions from $p_{i}^{\ell}$
so these are removed before updating $p_{i}^{n+1}$. No back substitution
for $u_{i}$ is done after calculating $p_{i}^{n+1}$ because this
would destroy the divergence free constraint. Therefore $p_{i}^{n+1}$
only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
converge and $p_{i}^{\ell}=p_{i}^{n+1}$.

The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
from $u_{i}$ following \citet{WM19}. The stages calculating $P$,
$p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$.

\section{Validation Test Cases\label{sec:results}}

Two test cases are developed to tune parameters and to validate the
use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
convection. The first is transient; the standard rising bubble of
\citet{BF02}. We aim to reproduce the vertical heat transport, the
mean velocity of the rising air, the bouyancy of the rising air and
pressure differences between two fluids in a single column two fluid
model. The second test case is steady state with heat transfer at
the ground and uniform radiative cooling. For both test cases the
reference solution is a single fluid solution of the two-dimensional
Boussinesq equations at high horizontal and vertical resolution.

\subsection{Rising Bubble}

The test case of \citet{BF02} was designed for fully compressible
models but similar solutions are obtained solving Boussinesq equations.
The Boussinesq version has no background stratification in a domain
of height 10\,km and width 20\,km initially at rest. The buoyant
perturbation is given by:
\begin{equation}
b=\frac{1}{15}\cos^{2}\frac{\pi L}{2}\label{eq:thetaPerturb}
\end{equation}
for $L<1$ where $L=\sqrt{\left(\frac{x-x_{c}}{x_{r}}\right)^{2}+\left(\frac{z-z_{c}}{z_{r}}\right)^{2}}$,
$x_{c}=10\ \text{km}$, $z_{c}=2\ \text{km}$ and $x_{r}=z_{r}=2\ \text{km}$.
100\,m grid spacing is used in the $x$ and $z$ directions for the
two dimensional reference simulation and $\Delta z=100\ \text{m}$
is used in the vertical for the single column simulations. All simulations
use a time-step of 2\,s.

\subsubsection{Single Fluid Solutions}

The solution of the rising buoyant bubble solving the Boussinesq equations
for 1000s is shown in figure \ref{fig:bubble} with buoyancy coloured,
pressure contoured and the $w=0$ contour dotted. The solution is
very similar to the fully compressible solution \citep{BF02}. The
pressure gradients accelerate the flow beneath the bubble, decelerate
the flow above the bubble and pull in air horizontally. Horizontally
and conditionally averaged fields, conditioned on $w$, are shown
in the top row of figure \ref{fig:bubble_singleUnderRes}. $\sigma_{1}$
is the volume fraction of rising fluid at every height, $b_{0}$ and
$b_{1}$ are the buoyancy conditioned on $w\le0$ and $w>0$, $w_{0}$
and $w_{1}$ are the horizontal averaging rising and falling vertical
velocity and $P_{0}$ and $P_{1}$ are the pressure of the rising
and falling fluid. An accurate multi-fluid model of convection should
reproduce these fields approximately at coarser horizontal resolution
or in a single column model.

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
\par\end{centering}
\noindent \begin{centering}
\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
\par\end{centering}
\caption{The single fluid, resolved rising bubble after 1000s. Buoyancy is
coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
negative contours dashed. The $w=0$ contour is dotted. \label{fig:bubble}}
\end{figure}

\citet{TEB19} and \citet{WM19} assumed that both fluids would share
the same pressure with differences parameterised as drag. The pressure
in figure \ref{fig:bubble} shows that this is a bad assumption since
the large pressure anomalies are in the rising fluid. Drag would always
act to slow down the fluids whereas the negative pressure gradients
in the rising fluid just below the bubble are acting to accelerate
the rising motion.

The horizontal averages are shown in figure \ref{fig:bubble_singleUnderRes}
for horizontal resolutions of nine columns, five columns, three columns
and a single column all for the 20km wide domain and all still using
$\Delta z=100\ \text{m}$. These simulations are initialised by conservative
horizontal averaging from the full resolution solution. As the horizontal
resolution is reduced, the vertical transport reduces until there
is no movement at all for a single column: there is no possibility
of fluid rising because in a single column with a single fluid there
can be no compensating subsidence. The lack of vertical transport
at coarse resolution motivates convection parameterisation.

\begin{figure}
\noindent %
\begin{tabular}{ccccc}
\begin{turn}{90}
200 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
\begin{turn}{90}
9 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
5 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
3 Columns
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
\begin{turn}{90}
1 Column
\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
\end{tabular}

\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
and a single fluid. Horizontal averages are conditioned based on $w$.
\label{fig:bubble_singleUnderRes}}
\end{figure}

\subsubsection{Results of the Two-fluid, Single Column Simulations}

Multi-fluid, single column simulations are initialised by horizontally
and conditionally averaging the high resolution single fluid initial
conditions. Sinking air is put into fluid zero and rising air into
fluid one. The velocity field after one time step is used for initialisation
as the air is stationary at $t=0$. Results are shown in figures \ref{fig:multiFluidSingleColumn-bad}
and \ref{fig:multiFluidSingleColumn} for various assumptions about
transfers between fluids and various parameter values.

\begin{figure}
\begin{tabular}{cccc}
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=0$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=0$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=0$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\end{tabular}

\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
the multi-fluid, single column solutions of the rising bubble. Dashed
lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
\end{figure}

\begin{figure}
\begin{tabular}{cccc}
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=1/2000\text{m}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage} }\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=0$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{01}=w_{1}0.2/r_{c}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0/2000\text{m}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=0$%
\end{minipage} }\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.25\columnwidth}%
$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$%
\end{minipage}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\end{tabular}

\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
the multi-fluid, single column solutions of the rising bubble. Dashed
lines are the single fluid, resolved solutions.\label{fig:multiFluidSingleColumn}}
\end{figure}

If there is no drag between fluids, no transfers, no diffusion and
the pressures of both fluids are assumed equal then the multi-fluid
equations are unstable \citep{TEB19}. The simulation with ($S_{ij}=0$)
in the top row of figure \ref{fig:multiFluidSingleColumn-bad} actually
has small transfers to prevent either $\sigma_{i}$ from becoming
negative. This is sufficient to stabilise the solution but does not
prevent oscillations from developing in all fields. The buoyant fluid
has risen very little from the initial conditions. $\sigma$ oscillates
between zero and one meaning that only one fluid is present at some
locations so there is no possibility for the fluids to move past each
other.

Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
stabilises the solution and enable the fluids to move past each other
even without pressure differences between the fluids (second row of
figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
detrained from fluid 1, fluid 1 looses too much buoyancy and a discontinuity
arises at the bubble leading edge; the buoyancy force is producing
vertical motion but there is no pressure to make it smooth.

Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
and pressure difference between the fluids controlled by divergence
($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
Three values of $\gamma$ are tested. $\gamma$ is set from equation
(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
radius and a buoyancy scale equal to the initial maximum buoyancy
to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
the velocity profile too smooth and the updraught too weak so the
bubble does not rise enough. It is reasonable to consider smaller
values of $\gamma$ because the buoyancy does not retain its initial
maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
leads to the leading edge of the bubble rising too quickly. Smaller
values of $\gamma$ leave a discontinuity in the updraught velocity
at the leading edge of the bubble and larger values of $\gamma$ reduce
the velocity further, meaning that the bubble does not rise enough
(not shown). None of the values of $\gamma$ reproduce the peak updraught
velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
meaning that the bubble rise and $\sigma_{1}$ are approximately correct
and pressure increases above the centre of the bubble are realisitic.
The large low pressure at the bottom of the bubble is not reproduced.
This is located at the lobes of the highest buoyancy in the resolved
simulation (figure \ref{fig:bubble}). It would be tempting to model
this by assuming hydrostatic pressure or the Bernouilli equation,
but these are both forms of the momentum equation which is used to
calculate the velocity and so cannot also be used to model the pressure.

The results in the top row of figure \ref{fig:multiFluidSingleColumn}
use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
drag slows the updraughts without increasing the mixing between the
fluids which makes the solutions less like the resolved simulations.
Although drag is known to be an important term in the momentum equations
for buoyant thermals and plumes \citep[eg][]{RC15}, the drag is related
to mixing with downdraught air which is accounted for in the entrainment
term of the momentum equation. So adding a separate term from drag
risks double counting and slows the plume too much.

If we include pressure difference between fluids with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$but
omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidSingleColumn})
the fluids move past each other but there is an unrealistic discontinuity
with no fluid 1 below the buoyant fluid and very little falling air
at the lowest height of the rising fluid. With a single column and
two fluids, all air must rise in one fluid and sink in the other.
Continuity does not allow for any other solution. Pressure gradients
can accelerate or decelerate this flow but as the model is set up,
with no transfers between fluids, no fluid can change direction. It
is therefore essential to have transfers between fluids.

The other entrainment option is the commonly used fractional entrainment
rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
This combination produces smooth solutions but the updraught is too
weak and too much is entrained into fluid 1. Using this entrainment,
the updraught will entrain more and more air until $\sigma_{1}=1$.
The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
entrainment and detrainment for this test case using conditional averaging
based on $w$.

Two alternative models for estimating the buoyancy of the fluid transferred
between updraught and downdraught have been tested. The results in
the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
that the fluid transferred has zero buoyancy in order to keep the
positively buoyant air in fluid one and the negatively buoyant air
in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
the mean buoyancy of fluid one increases. This leads to very high
buoyancy in fluid one which is not present in the resolved simulation.
The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citet{TEB19}
so that the fluid transferred is influenced by the fluid it is moving
towards as well as where it has come from. This again leads to very
large buoyancy in fluid one and also negative buoyancy in fluid zero
which should not occur for this test case. These simple models reinforce
the idea that the buoyancy of the fluid transferred should depend
on knowledge of sub-grid-scale variability of $b$ within each fluid
\textendash{} these simple assumptions can lead to unrealistic behaviour.
The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
fluid transferred takes the mean properties with it.

This section has demonstrated the value of using a single column,
multi-fluid model to simulate a buoyant rising bubble with a single
updraught fluid and a single downdraught fluid. Transfers between
the fluids have been successfully modelled using entrainment set by
divergence giving realistic updraught fractions. Entrainment calculated
as the reciprocal of plume width was not successful. The pressure
difference between the fluids has also been represented by divergence
with a coefficient close to that expected from dimensional analysis.
Including drag between the fluids did not improve simulations. Two
models of transferring non-mean properties between fluids were tested
but neither was plausible. There are clearly discrepancies between
the single fluid resolved rising bubble and the two fluid single column
rising bubble but we do not want to over fit the multi-fluid model
to one, dry, two dimensional test case.

\subsection{Radiative-Convective Equilibrium (RCE)}

A two-dimensional, dry radiative convective equilibrium test case
is devised to mimic some properties of atmospheric convection, in
particular the difficulty resolving the flow at coarse resolution.
The domain is 160km wide, 10km tall and is resolved by 640 cells in
the horizontal and 40 in the vertical ($\Delta x=\Delta z=250$m).
The top and bottom boundaries are zero velocity and the lateral boundaries
are periodic. A heat flux of $h=10^{-3}\text{m}^{2}\text{s}^{-3}$
is imposed at the bottom boundary leading to a boundary condition
of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
so as to give a Plank constant of $0.707$. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$
is applied to the domain to maintain equilibrium.

The fluid is initially stationary with $b=0$. In order to quickly
and reproducibly initialise instability, $b=10^{-4}\text{m}^{2}\text{s}^{-1}$
is imposed in a square of side length 2000m at the centre in the $x$
direction and at the ground. The simulation is run using a time step
of $5\ \text{s}$. A quasi-steady, choatic state is reached after
about $3\times10^{4}\text{s}$ and the simulation is run for $2\times10^{5}\text{s}$
and conditional averages are calculated over the final $10^{5}$s.

\subsubsection{Single Fluid Solutions}

This test case is designed to have strong updraughts in narrow plumes
and weak descent elsewhere to mimic atmospheric convection but without
the complication of moisture, phase changes and three spatial dimensions.
A snapshot of the buoyancy, vertical velocity and pressure of the
radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
updraughts. The buoyant air at the ground rises in narrow plumes,
accelerating due to buoyancy and pressure gradients then decelerating
due to pressure gradients before reaching the top. The plumes spread
out and the sinking air is a mixture of warm and cold with similar
pressure gradients in the rising and falling air, accelerating then
decelerating the flow so as to maintain continuity.

\noindent 
\begin{figure}
\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/bw}

Buoyancy ($\text{m}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/bw_b}

\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/Pw}

Pressure ($\text{m}^{2}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/Pw_P}

\caption{Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
of the resolved radiative-convective equilibrium test case. Vertical
velocity contours are black every 0.5m/s with negative contours dashed
and the zero contour dotted. The domain is 10km high and 160km wide
and the z-direction is stretched a factor of 2 in the plots. \label{fig:RCE_resolved}}
\end{figure}

Horizontal averages conditioned on $w$ and time averaged every 1000s
between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
in the top row of figure \ref{fig:RCE_singleColumn}. The rising and
falling volume fractions, $\sigma_{1}$ and $\sigma_{0}$, remain
close to $\frac{1}{2}$ throughout the depth. The rising plumes look
narrow in figure \ref{fig:RCE_resolved} but there are wide regions
of slowly rising air around the plume cores. The entrained rising
cool air and warm air sinking that has hit the model top mean that
the rising and falling air have similar average buoyancy away from
the ground. The ascending air gradually accelerates towards the middle
of the domain then decelerates towards the model top. At the ground
the acceleration is forced by buoyancy and away from the ground the
acceleration is controlled by pressure gradients. The descending air
mean velocity is close to equal and opposite to the ascending air,
as expected since $\sigma_{1}=0.5$.

\subsubsection{Results of the Two-fluid, Single Column Simulations}

The two fluid model is used to simulate the RCE test case in a single
column of 40 cells with zero buoyancy gradient at the top and a buoyancy
gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
and uniform radiative cooling. The two fluids are initialised using
the time mean conditional horizontal averages from the single fluid
resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
is used for all simulations to account for transfers throughout the
domain to represent cloud base mass flux (at the bottom boundary),
cloud top detrainment and lateral entrainment. $\gamma$ is set from
equation (\ref{eq:gammaDimAnal}) using the depth of the super adiabatic
layer as the length scale ($L=800\text{m}$) and the buoyancy scale
$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. A simulation using
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
is shown in the second row of figure \ref{fig:RCE_singleColumn}.
The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
at about 0.5 throughout the depth, as in the resolved simulation,
with entrainment in the lower half of the domain ($S_{01}>0$) and
detrainment in the upper half ($S_{10}>0$), where the air decelerates
towards the top. The single column model reproduces the super-adiabatic
layer near the ground and the near uniform buoyancy away from the
ground but the buoyancy difference between the fluids is too large.
The updraught and downdraught velocities are captured well. The pressure
differences between fluids are too large which is consistent with
the over estimated buoyancy difference between fluids.

Results of a simulations using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
This model of the buoyancy of the transferred fluid is bad; it leads
to strong cooling in fluid zero near the ground due to the large transfers.
It is more accurate to assume that fluids take their mean properties
when transferred, $b_{ij}^{T}=b_{i}$.

\noindent 
\begin{figure}
\setlength\tabcolsep{0.5pt}%
\begin{tabular}{ccccc}
$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case between $t=10^{5}\text{s}$
and $2\times10^{5}\text{s}$}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}\tabularnewline
\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
$b_{ij}^{T}=b_{i}$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
versus resolved (dashed)}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/P_1}\tabularnewline
\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
$b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
versus resolved (dashed)}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/P_1}\tabularnewline
\end{tabular}

\caption{Results of the RCE simulations. The top row shows horizontal averages
of the resolved case between $t=10^{5}$s and $2\times10^{5}$s. The
bottom two rows show results of the single column multi-fluid model
after $10^{4}\ \text{s}$. \label{fig:RCE_singleColumn}}
\end{figure}

\section{Summary, Conclusions and Further Work}

This paper presents solutions of the multi-fluid Boussinesq equations
for convection, reproducing aspects of highly resolved dry convection
at coarse horizontal resolution. Two test cases are used to validate
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citet{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single fluid simulations are conditionally averaged based on the sign
of vertical velocity ($w$) in order to create rising and falling
fluids which each have their own mean buoyancy, velocity and pressure.
The two-fluid, single column Boussinesq model reproduces mean vertical
heat and mass transport of these test cases.

The multi-fluid Boussinesq equations can have divergence in each fluid
while the divergence averaged over all fluids is zero. A model is
proposed and validated for the pressure difference between the rising
and falling fluids based on the divergence of each fluid. The use
of a different pressure for each fluid is not only realistic but also
leads to stable solutions of the multi-fluid equations.

Conditionally averaging the high resolution solutions based on $w$
leads to convecting and non-convecting regions with area fractions,
$\sigma_{i}$, which are approximately uniform with height. Models
for entrainment and detrainment into and out of convecting regions
must clearly be consistent with the definition of the convecting region.
We propose a model for entrainment and detrainment based on divergence
that leads to excellent agreement with $\sigma$ from the high resolution
solutions. We also test a more conventional fractional entrainment
rate based on the reciprocal of the plume width which leads to unrealistic
convecting area fractions.

A set of unknowns in the multi-fluid equations are the properties
of the fluid that are transferred from one fluid to another. An obvious
first guess would be that fluid takes its mean buoyancy and velocity
with it when it is transferred. However sub-grid-scale variability
of each fluid means that we expect that the most buoyant fluid will
be transferred to the rising fluid or the fluid with the largest vertical
velocity will be transferred to the rising fluid and vice versa. An
accurate estimate of these would depend on knowledge of the sub-grid-scale
variability of each fluid which we do not have. Instead we assume
that the fluid transferred in each direction has zero vertical velocity
which is consistent with our conditional averaging. We have tested
three models for the buoyancy of the fluid transferred. The most successful
is to assume that the fluid takes its mean buoyancy with it. Assuming
that the buoyancy of the transferred fluid is an average of the buoyancy
of both fluids can lead to unrealistically large or small, unbounded
buoyancies. Similarly, if we assume that one fluid has negative buoyancy
and the other positive buoyancy and we transfer fluid of zero buoyancy,
then unbounded buoyancy can occur. A better model of the buoyancy
of the fluid transferred would rely on more information the sub-grid-scale
variability.

Single column multi-fluid modelling with moisture has already been
demonstrated by \citet{TEB19}. Two important next steps are to simulate
convection in the grey zone (where it is partially resolved) and to
represent sub-grid-scale variability within each fluid by solving
multi-fluid prognostic equations for turbulent kinetic energy and
other moments of the sub-grid variability. These can be used to inform
cloud base mass flux (since only the most buoyant fluid will transfer
from the stable environment to the buoyant plume) and inform models
of the properties of the fluid that is transferred. This will lead
to a unified parameterisation of turbulence and convection and will
take multi-fluid modelling of convection beyond existing paradigms.

\section*{Acknowledgements}

Many thanks to John Thuburn and Chris Holloway for valuable discussions.
Thanks to the NERC/Met Office Paracon project. We acknowledge funding
from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1.

\bibliographystyle{abbrvnat}
\bibliography{numerics}

\end{document}

### 2020-03-23 responses/responses.tex
First submmitted version and empty revised version and responses to reviewer comments.

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[authoryear]{natbib}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\newenvironment{lyxlist}[1]
{\begin{list}{}
{\settowidth{\labelwidth}{#1}
 \setlength{\leftmargin}{\labelwidth}
 \addtolength{\leftmargin}{\labelsep}
 \renewcommand{\makelabel}[1]{##1\hfil}}}
{\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{xcolor}
\renewenvironment{quote}
               {\list{}{\rightmargin\leftmargin}%
                \item\relax\color{blue}}
               {\endlist}

\begin{document}

\title{Responses to Reviewer Comments on\\
2019MS001966\\
Multi-fluids for Representing Sub-filter-scale Convection}

\author{Hilary Weller, William McIntyre, Dan Shipley and Peter Clark}
\maketitle
\begin{quote}
Author responses and additional text in the manuscript are in blue.
\end{quote}

\section*{Responses to Reviewer 1}

The paper is written in a manner that relies too heavily on an assumption
that the reader is familiar with previous works by the authors, yet
these works are rather new in the field of convective parameterizations
and I believe that the authors should give more context. The introduction
could be made more detailed, referencing some key works such as the
Lappen and Randell 2011 (a,b,c) and other approaches to convection
sub as the high order closures and specifically the CLUBB (e.g. Golaz
et al., 2013). Section 2 should place the reader on a better footing
before presenting the model equations (I leave it to the authors to
decide if they need more equations, an appendix, or only text referencing
to their previous works to do so).
\begin{quote}
Response
\end{quote}
The paper present results from a bubble experiment and RCE. The bubble
turns out to be more challenging than the RCE. Can you please elaborate
in your discussion why do you think that is the case? Does it has
anything to do with the fact that in the RCE your multi-fluid updraft
fluid represent the average of many rising plumes while in the bubble
your multi-fluid updraft represents single bubble?
\begin{quote}
Response
\end{quote}

\subsection*{Specific Comments: }
\begin{lyxlist}{00.00.0000}

\item [{Line\ 45:}] ``Improvement have been made \textbf{by}''?
\begin{quote}
 Response
\end{quote}
\item [{Line\ 56}] you wrote ``\cite{TKP+18} didn't
propose a suitable numerical method for solving the equations''.
\cite{TKP+18} do present numerical solutions of their model (BOMEX test
case and some modification of it) - either change that statement or
elaborate what do you mean by ``didn't
propose a suitable numerical method for solving the equations''.
\begin{quote}
 Response
\end{quote}
\end{lyxlist}
\bibliographystyle{abbrvnat}
\bibliography{numerics}

\end{document}

### 2020-03-23 submit1/manuscript.tex
First submmitted version and empty revised version and responses to reviewer comments.

--- 2020-03-23 preSubmission/manuscript.tex
@@
-%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[12pt,times]{extarticle}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
+%
+% This file includes commands and instructions
+% given in the order necessary to produce a final output that will
+% satisfy AGU requirements, including customized APA reference formatting.
+%
+% You may copy this file and give it your
+% article name, and enter your text.
+%
+%
+% Step 1: Set the \documentclass
+%
+%
+
+%% To submit your paper:
+\documentclass[draft]{agujournal2019}
+\usepackage{url} %this package should fix any errors with URLs in refs.
+\usepackage{lineno}
+\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage{soul}
+\linenumbers
+%%%%%%%
+% As of 2018 we recommend use of the TrackChanges package to mark revisions.
+% The trackchanges package adds five new LaTeX commands:
+%
+%  \note[editor]{The note}
+%  \annote[editor]{Text to annotate}{The note}
+%  \add[editor]{Text to add}
+%  \remove[editor]{Text to remove}
+%  \change[editor]{Text to remove}{Text to add}
+%
+% complete documentation is here: http://trackchanges.sourceforge.net/
+%%%%%%%
+
+\draftfalse
+
+\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}
+
 \usepackage{mathptmx}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage{geometry}
-\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
 \usepackage{array}
@@
 \usepackage{graphicx}
-\usepackage[authoryear]{natbib}
-
-\makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
-\usepackage { fancybox}
-\usepackage[export]{adjustbox}
-
-\usepackage{todonotes}
-%\usepackage{afterpage}
-
-%\usepackage[switch]{lineno}
-
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
-
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-%\usepackage{moreverb}
-
-\usepackage{flushend}
-
-\makeatother
 
@@
 
-\title{Multi-fluids for Representing Sub-filter-scale Buoyant Convection}
-
-\author{Hilary Weller, William McIntyre, Daniel Shipley and Peter Clark}
-\maketitle
+\title{Multi-fluids for Representing Sub-filter-scale Convection}
+
+\authors
+{
+    Hilary Weller\affil{1}\thanks{Meteorology, University of Reading, UK}
+    ,
+    William McIntyre\affil{1}
+    ,
+    Daniel Shipley\affil{1}
+    , and 
+    Peter Clark\affil{1}
+}
+
+\affiliation{1}{Meteorology, University of Reading, UK}
+
+\correspondingauthor{Hilary Weller}{h.weller@reading.ac.uk}
+
+\begin{keypoints}
+\item Multi-fluid modelling enables net mass transport by parameterised convection and non-equlibrium.
+\item Multi-fluid modelling means a new dynamical core rather than a parameterisation for an existing core
+\item Closure for the pressure difference between fluids and entrainment and detrainment are provided
+\end{keypoints}
+
 \begin{abstract}
@@
 
+\section*{Plain Language Summary}
+Clouds and buoyant convection are often smaller than the grid size in weather and climate prediction models but they are of central importance.
+Therefore their effects are parameterised -- their interactions with the larger scales are estimated based on properties of the larger scales.
+Convection parameterisations are a large source of error in models of the atmosphere despite decades of effort to improve them.
+An important assumption in most convection parameterisations is that convection moves heat and moisture upwards but not mass.
+This makes it much simpler to incorporate convection parameterisations into existing models.
+Multi-fluid modelling will enable mass transport by convection but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model.
+This paper provides some closures necessary for multi-fluid modelling and validation of the technique for two dimensional dry convection.
+
 \section{Introduction}
@@
 Slow progress has been made improving the parameterisation of sub-grid-scale
-convection since \citet{AS74,Tied89,GR90,KF90}. Convection is still
+convection since \citeA{AS74}, \citeA{Tied89}, \citeA{GR90} and \citeA{KF90}. Convection is still
 one of the weakest aspects of large scale models of the atmosphere
-\citep{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
-the quasi-equilibrium assumption \citep{PR98,GG05,Par14}, including
-stochasticity \citep{PC08} and allowing net mass transport by convection
-\citep{KB08,MB19}. These developments have enabled limited simulation
+\cite{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
+the quasi-equilibrium assumption \cite{PR98,GG05,Par14}, including
+stochasticity \cite{PC08} and allowing net mass transport by convection
+\cite{KB08,MB19}. These developments have enabled limited simulation
 in the grey zone, where convection is partially resolved. However
@@
 
-\citet{TWV+18} proposed multi-fluid modelling of convection in order
+\citeA{TWV+18} proposed multi-fluid modelling of convection in order
 to treat non-equilibrium and net mass transport correctly and consistently
 with the same numerics and physics controlling thermals, the stable
-environment and downdraught dynamics. \citet{Yano14} derived similar
+environment and downdraught dynamics. \citeA{Yano14} derived similar
 equations for multiple segments and showed how this is a generalisation
-of the mass-flux formulation. The \citet{TKP+18} ``extended eddy
+of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
 diffusivity mass flux'' or extended EDMF scheme also uses similar
-equations but \citet{TKP+18} didn't propose a suitable numerical
+equations but \citeA{TKP+18} didn't propose a suitable numerical
 method for solving the equations. Multi-fluids promises big improvements
@@
 a dedicated model rather than being a stand alone parameterisation
-for a dynamical core. \citet{TEB19} and \citet{WM19} presented solutions
+for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
 of the multi-fluid equations assuming two fluids that share the same
 pressure (or that pressure differences are predominantly due to drag
-between the fluids). \citet{TEB19} showed that these equations (without
+between the fluids). \citeA{TEB19} showed that these equations (without
 drag) are in fact unstable and can be stabilised by diffusion of vertical
-velocity whereas \citet{WM19} stabilised the equations with diffusion
+velocity whereas \citeA{WM19} stabilised the equations with diffusion
 and drag between fluids. Neither of these stabilisation techniques
@@
 Many of the challenges of representing convection with the multi-fluid
-Navier-Stokes equations \citep[eg those described in][]{WM19} carry
+Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
 over to the Boussinesq equations; convection is buoyancy dominated
@@
 
-\citet{TEB19} and \citet{WM19} assumed that each co-located fluid
-shared the same pressure, leading to unstable equations that \citet{TEB19}
-stabilised using diffusion of vertical velocity and \citet{WM19}
-stabilised using mass exchanges or drag between the fluids. \citet{TEB19}
+\citeA{TEB19} and \citeA{WM19} assumed that each co-located fluid
+shared the same pressure, leading to unstable equations that \citeA{TEB19}
+stabilised using diffusion of vertical velocity and \citeA{WM19}
+stabilised using mass exchanges or drag between the fluids. \citeA{TEB19}
 achieved realistic results in single column experiments of convective
 boundary layer but the amount of diffusion needed would spoil simulations
-in the free troposphere. The stabilisation used by \citet{WM19} meant
+in the free troposphere. The stabilisation used by \citeA{WM19} meant
 that the two fluids tended to move as one which defeats the purpose
@@
 
-The instabilities reported by \citet{WM19} showed growing divergence
+The instabilities reported by \citeA{WM19} showed growing divergence
 in a fluid with vanishing volume fraction. It is mass convergence
@@
 
-\citet{BN86} proposed a parameterisation for pressure differences
+\citeA{BN86} proposed a parameterisation for pressure differences
 in a multi-phase explosion model that has been widely used in mathematics
 and engineering for simulating fluidised beds of granular material
-\citep[eg.][]{EHM92} and two compressible fluids \citep[eg.][]{SA99}.
+\cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}.
 In these methods, advection equations are written for the volume fraction,
@@
 $\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
-fluids, the \citet{BN86} equations would be:
+fluids, the \citeA{BN86} equations would be:
 \begin{eqnarray}
@@
 
-\citet{TEB19} stabilised the multi-fluid equations by adding a diffusion
+\citeA{TEB19} stabilised the multi-fluid equations by adding a diffusion
 term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
@@
 resolved convection in the free troposphere whereas adding a fluid
-perturbation pressure will not. Inspired by both \citet{BN86} and
-\citet{TEB19} we assume that the pressure in each fluid is given
+perturbation pressure will not. Inspired by both \citeA{BN86} and
+\citeA{TEB19} we assume that the pressure in each fluid is given
 by:
@@
 We consider dry air without turbulence so use the dynamic entrainment
-described by \citet{HC51,AK67,DBF+13}:
+described by \citeA{HC51},\citeA{AK67} and \citeA{DBF+13}:
 \begin{equation}
@@
 of descending air). We will also test a common form of lateral entrainment
-\citep{DBF+13}:
+\cite{DBF+13}:
 \begin{equation}
@@
 Pressure differences between the fluids can lead to form drag which
-is parameterised following \citet{SW69,RC15,WM19} as: 
+is parameterised following \citeA{SW69}, \citeA{RC15} and \citeA{WM19} as: 
 \begin{equation}
@@
 The different fluids may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \citep[as was assumed by][]{WM19}.
+may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}.
 In fact, the most buoyant air should be transferred from fluid 0 to
@@
 \end{equation}
-For buoyancy, following \citet{TEB19}, we use:
+For buoyancy, following \citeA{TEB19}, we use:
 \begin{equation}
@@
 
-The spatial discretisation follows exactly \citet{WM19}, solving
+The spatial discretisation follows exactly \citeA{WM19}, solving
 advective form equations using monotonic, finite volume advection
@@
 with no off-centering and with deferred correction of explicitly solved
-variables. It differs from \citet{WM19} because here we solve the
+variables. It differs from \citeA{WM19} because here we solve the
 Boussinesq equations and we need stable solutions for equations with
@@
 is interpolated from cell centres onto cell faces using monotonic
-van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citet{WM19}
+van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citeA{WM19}
 and values exclusively at time level $n$ for best accuracy and guaranteed
@@
 The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
-from $u_{i}$ following \citet{WM19}. The stages calculating $P$,
+from $u_{i}$ following \citeA{WM19}. The stages calculating $P$,
 $p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
@@
 convection. The first is transient; the standard rising bubble of
-\citet{BF02}. We aim to reproduce the vertical heat transport, the
+\citeA{BF02}. We aim to reproduce the vertical heat transport, the
 mean velocity of the rising air, the bouyancy of the rising air and
@@
 
-The test case of \citet{BF02} was designed for fully compressible
+The test case of \citeA{BF02} was designed for fully compressible
 models but similar solutions are obtained solving Boussinesq equations.
@@
 pressure contoured and the $w=0$ contour dotted. The solution is
-very similar to the fully compressible solution \citep{BF02}. The
+very similar to the fully compressible solution \cite{BF02}. The
 pressure gradients accelerate the flow beneath the bubble, decelerate
@@
 
-\citet{TEB19} and \citet{WM19} assumed that both fluids would share
+\citeA{TEB19} and \citeA{WM19} assumed that both fluids would share
 the same pressure with differences parameterised as drag. The pressure
@@
 the pressures of both fluids are assumed equal then the multi-fluid
-equations are unstable \citep{TEB19}. The simulation with ($S_{ij}=0$)
+equations are unstable \cite{TEB19}. The simulation with ($S_{ij}=0$)
 in the top row of figure \ref{fig:multiFluidSingleColumn-bad} actually
@@
 Although drag is known to be an important term in the momentum equations
-for buoyant thermals and plumes \citep[eg][]{RC15}, the drag is related
+for buoyant thermals and plumes \cite<e.g.,>{RC15}, the drag is related
 to mixing with downdraught air which is accounted for in the entrainment
@@
 The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
-use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citet{TEB19}
+use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citeA{TEB19}
 so that the fluid transferred is influenced by the fluid it is moving
@@
 
-\noindent 
 \begin{figure}
@@
 the multi-fluid model. The first is a Boussinesq version of the well
-known two dimensional dry rising bubble of \citet{BF02} and the second
+known two dimensional dry rising bubble of \citeA{BF02} and the second
 is a dry two dimensional version of radiative-convective equilibrium
@@
 Single column multi-fluid modelling with moisture has already been
-demonstrated by \citet{TEB19}. Two important next steps are to simulate
+demonstrated by \citeA{TEB19}. Two important next steps are to simulate
 convection in the grey zone (where it is partially resolved) and to
@@
 
-\section*{Acknowledgements}
+\acknowledgments
 
@@
 from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1.
-
-\bibliographystyle{abbrvnat}
+All the code can be downloaded from \url{https://github.com/AtmosFOAM/AtmosFOAM-multiFluid} and the test cases from \url{https://github.com/AtmosFOAM/hilaryRun}.
+
 \bibliography{numerics}

### 2020-03-27 submit2/manuscript.tex
First submmitted version and empty revised version and responses to reviewer comments.
Hilary started working on revisions

--- 2020-03-23 submit1/manuscript.tex
@@
 %%%%%%%
+\addeditor{HW}
 
@@
 one of the weakest aspects of large scale models of the atmosphere
-\cite{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
+\cite{HPB+14,SAB+13,ipcc41}. Improvements have been made \add[HW]{by} relaxing
 the quasi-equilibrium assumption \cite{PR98,GG05,Par14}, including
@@
 diffusivity mass flux'' or extended EDMF scheme also uses similar
-equations but \citeA{TKP+18} didn't propose a suitable numerical
-method for solving the equations. Multi-fluids promises big improvements
+equations but \citeA{TKP+18}
+\change[HW]{didn't propose a suitable numerical method for solving the equations.}
+{only solve the equations in a single column without coupling to the continuity equation of a dynamical core.}
+Multi-fluids promises big improvements
 in the representation of sub-grid-scale convection and unification
@@
 
-Many of the challenges of representing convection with the multi-fluid
-Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
-over to the Boussinesq equations; convection is buoyancy dominated
-and close to incompressible. The resolved test cases presented in
-section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore for simplicity we focus on the
-multi-fluid Boussinesq equations without background stratification:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\} \label{eq:sigma}\\
-\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\} \label{eq:mom}\\
-\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}\\
-\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
-\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
-\end{eqnarray}
-with variables defined in table \ref{tab:defns}.
-
-\begin{table}[h]
+\begin{table}[ht]
 \begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
@@
 \end{tabular}
-
 \caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
 \end{table}
+
+Many of the challenges of representing convection with the multi-fluid
+Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
+over to the Boussinesq equations; convection is buoyancy dominated
+and close to incompressible. The resolved test cases presented in
+section \ref{sec:results} give very similar results for Navier-Stokes
+and Buossinesq equations. Therefore for simplicity we focus on the
+\remove[HW]{multi-fluid} Boussinesq equations without background stratification:
+\note[HW]{This is additional material until the start of 2.1}
+\begin{eqnarray}
+\frac{D\mathbf{u}}{Dt}+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
+\label{eq:singleMom}
+\\
+\frac{Db}{Dt} & = & \alpha\nabla^{2}b
+\label{eq:singleb}
+\\
+\nabla\cdot\mathbf{u} & = & 0
+\label{eq:singleDivFree}
+\end{eqnarray}
+where variables are defined in table \ref{tab:defns}. 
+These equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations.
+Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere and satisfy:
+\begin{equation}
+\frac{DI_i}{Dt}=0.
+\label{eq:LagrangianLabel}
+\end{equation}
+Applying the conditional average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$:
+\begin{eqnarray}
+\sigma_i &=& \overline{I_i} \\
+\sigma_i \mathbf{u}_i &=& \overline{I_i \mathbf{u}} \\
+\sigma_i b_i &=& \overline{I_i b}
+\label{eq:defineFluidFields}
+\end{eqnarray}
+which implies
+\begin{equation}
+\sum_{i}\sigma_{i}  =  1.
+\label{eq:sumOne}
+\end{equation}
+As we are considering the Boussinesq equations we assume that variations in density only affect the buoyancy terms so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.
+
+To derive a transport equation for $\sigma_i$ we combine (\ref{eq:LagrangianLabel}) with $I_i$ times (\ref{eq:singleDivFree}) and volume average.
+After permuting operators with the averaging \cite<as described by>{TWV+18} and using the definitions of $\sigma_i$ and $\mathbf{u}_i$ we get the evolution equation for $\sigma_i$:
+\begin{equation}
+\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i}  =  \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\}
+\label{eq:sigma}
+\end{equation}
+which also includes transfers between fluids with $\sigma_{i}S_{ij}$ being the transfer from fluid $i$ to $j$.
+
+Next we will consider conditionally averaging the terms of the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations.
+Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
+\begin{eqnarray}
+\overline{I_i \mathbf{u} \cdot \nabla \mathbf{u}} &=& \sigma_i \mathbf{u}_i \cdot \nabla \mathbf{u}_i + F_\text{SF}^{\mathbf{u}_i} \\
+\overline{I_i \mathbf{u} \cdot \nabla b} &=& \sigma_i \mathbf{u}_i \cdot \nabla b_i + F_\text{SF}^{b_i}
+\label{eq:filterAdvection}
+\end{eqnarray}
+The sub-filter-scale fluxes will be absorbed into the diffusion terms for momentum and buoyancy.
+
+Since viscosity ($\nu$) and thermal diffusivity ($\alpha$) are constant, conditional averaging of the diffusion terms is straightforward:
+\begin{eqnarray}
+\overline{I_i \nabla \cdot \nu \nabla \mathbf{u}} &=& \sigma_i \nabla\cdot\bigl(\nu \nabla\mathbf{u}_i \bigr) \\
+\overline{I_i \nabla \cdot \alpha \nabla b} &=& \sigma_i \nabla\cdot\bigl(\alpha \nabla b_i \bigr).
+\end{eqnarray}
+
+Unlike \citeA{TWV+18} we define separate pressures for each fluid, $P_i$. The pressures are defined to satisfy:
+\begin{equation}
+\sigma_i \nabla P_i = \overline{I_i \nabla P}.
+\end{equation}
+Combining these gives the conditionally averaged momentum and buoyancy equations:
+\begin{eqnarray}
+\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i}
+& = &
+b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\}
+\label{eq:mom}\\
+\frac{D_{i}b_{i}}{Dt}
+& = &
+\alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}
+\end{eqnarray}
+where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$, $\mathbf{u}_{ij}^T$ is the velocity of the fluid transferred from $i$ to $j$, $b_{ij}^T$ is the buoyancy of the fluid transferred from $i$ to $j$ and $\mathbf{D}_{ij}$ is the drag of fluid $j$ on fluid $i$.
+It is not clear that drag between fluids is appropriate for this form of the equations but it is commonly used in multi-phase modelling \cite<eg>{?} so we will investigate sensitivity to drag in section \ref{sec:results}.
+
+Finally the multi-fluid version incompressibility is
+\begin{equation}
+\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i}  = \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0.
+\label{eq:divFree}
+\end{equation}
 
@@
 \begin{figure}
+\setlength{\tabcolsep}{2pt}
 \begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
+$S_{ij}=0$, \hspace{6pt}
+$\gamma=0$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=b_{i}$.
+}} \tabularnewline 
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
+$\gamma=0$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=b_{i}$.
+}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
+$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=b_{i}$.
+}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
+$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=b_{i}$.
+}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
+$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=b_{i}$.
+}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
+$\sigma_{1}$ ($\text{m}^3/\text{m}^3$) & $b$ and $b_{i}$ ($\text{m}\text{s}^{-2}$) & $w_{0}$ and $w_{1}$ (m/s) & $P_{0}$ and $P_{1}$ ($\text{m}^2 \text{s}^{-2}$)\tabularnewline
 \end{tabular}
@@
 \begin{figure}
+\setlength{\tabcolsep}{2pt}
 \begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=1/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage} }\tabularnewline
+\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
+$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
+$C_{D}/r_{c}=1/2000\text{m}^{-1}$, \hspace{6pt}
+$b_{ij}^{T}=b_{i}$.
+} }\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
+$S_{ij}=0$, \hspace{6pt}
+$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=b_{i}$.
+}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{01}=w_{1}0.2/r_{c}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
+$S_{01}=w_{1}0.2/r_{c}$, \hspace{4pt}
+$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{4pt}
+$C_{D}/r_{c}=0/2000\text{m}^{-1}$, \hspace{4pt}
+$b_{ij}^{T}=b_{i}$.
+}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=0$%
-\end{minipage} }\tabularnewline
+\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
+$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=0$.
+} }\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.25\columnwidth}%
-$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
+$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
+$C_{D}/r_{c}=0$, \hspace{6pt}
+$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$.
+}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
@@
 $\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
-\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case between $t=10^{5}\text{s}$
-and $2\times10^{5}\text{s}$}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=b_{i}$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/P_1}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
+\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case}\tabularnewline
+\includegraphics[scale=0.7]
+{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean}
+&
+\includegraphics[scale=0.7]
+{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer}
+&
+\includegraphics[scale=0.7]
+{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}
+\tabularnewline
+\multicolumn{5}{c}{Single column with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
+$b_{ij}^{T}=b_{i}$, $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
+}\tabularnewline
+\includegraphics[scale=0.7]
+{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma_1}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b_1}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u_1}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P_1}
+\tabularnewline
+\multicolumn{5}{c}{Single column  with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
 $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/P_1}\tabularnewline
+}\tabularnewline
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma_1}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b_1}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u_1}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P_1}\tabularnewline
 \end{tabular}
@@
 \caption{Results of the RCE simulations. The top row shows horizontal averages
-of the resolved case between $t=10^{5}$s and $2\times10^{5}$s. The
+of the resolved case between $t=10^{5}\text{s}$ and $2\times10^{5}\text{s}$. The
 bottom two rows show results of the single column multi-fluid model
@@
 The multi-fluid Boussinesq equations can have divergence in each fluid
-while the divergence averaged over all fluids is zero. A model is
-proposed and validated for the pressure difference between the rising
+while the divergence averaged over all fluids is 
+\change[HW]{zero}
+{constrained to be zero following the single-fluid Boussinesq equations.}
+A model is proposed and validated for the pressure difference between the rising
 and falling fluids based on the divergence of each fluid. The use
@@
 Single column multi-fluid modelling with moisture has already been
-demonstrated by \citeA{TEB19}. Two important next steps are to simulate
+demonstrated by \citeA{TEB19} 
+\add[HW]{and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19} }.
+Two important next steps are to simulate
 convection in the grey zone (where it is partially resolved) and to

### 2020-03-27 submit2/manuscript.tex
Responded to more of reviewer 1's comments

@@
 
-\begin{table}[ht]
+Many of the challenges of representing convection with the multi-fluid
+Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
+over to the Boussinesq equations; convection is buoyancy dominated
+and close to incompressible. The resolved test cases presented in
+section \ref{sec:results} give very similar results for Navier-Stokes
+and Buossinesq equations. Therefore for simplicity we focus on the
+\remove[HW]{multi-fluid} Boussinesq equations without background stratification:
+\note[HW]{This is additional material until the start of 2.1}
+\begin{eqnarray}
+\frac{\partial \mathbf{u}}{\partial t} + \nabla\cdot(\mathbf{u}\mathbf{u})
++\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
+\label{eq:singleMom}
+\\
+\frac{\partial b}{\partial t} + \nabla\cdot(\mathbf{u}b)
+ & = & \alpha\nabla^{2}b
+\label{eq:singleb}
+\\
+\nabla\cdot\mathbf{u} & = & 0
+\label{eq:singleDivFree}
+\end{eqnarray}
+where variables are defined in table \ref{tab:defns}.
+
+\begin{table}
 \begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
 $\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
+$\mathbf{u}$ & 
+Velocity of the single-fluid equations  ($\text{m}\text{s}^{-1}$) and velocity averaged over all fluids of the multi-fluid equations
+\tabularnewline
 $\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
 $w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
-$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
+$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)
+\tabularnewline
+$P$ & Non-hydrostatic pressure of the single-fluid equations $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$) and pressure averaged over all fluids of the multi-fluid equations
+\tabularnewline
+$P_{i}$ & Non-hydrostatic pressure of fluid $i$ 
+\tabularnewline
+$p_{i}$ & $P_i - P$
+\tabularnewline
 $\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
-$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
+$b$ & Buoyancy of single-fluid equations defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
 where $\rho^{\prime}$ are departures in density from a horizontally
-uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
+uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$) and buoyancy averaged over all fluids of the multi-fluid equations
+\tabularnewline
 $b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
@@
 \end{tabular}
-\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
+\caption{Definitions of variables for the single- and multi-fluid Boussinesq equations.\label{tab:defns}}
 \end{table}
 
-Many of the challenges of representing convection with the multi-fluid
-Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
-over to the Boussinesq equations; convection is buoyancy dominated
-and close to incompressible. The resolved test cases presented in
-section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore for simplicity we focus on the
-\remove[HW]{multi-fluid} Boussinesq equations without background stratification:
-\note[HW]{This is additional material until the start of 2.1}
-\begin{eqnarray}
-\frac{D\mathbf{u}}{Dt}+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
-\label{eq:singleMom}
-\\
-\frac{Db}{Dt} & = & \alpha\nabla^{2}b
-\label{eq:singleb}
-\\
-\nabla\cdot\mathbf{u} & = & 0
-\label{eq:singleDivFree}
-\end{eqnarray}
-where variables are defined in table \ref{tab:defns}. 
-These equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations.
+The single-fluid Boussinesq equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations.
 Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere and satisfy:
@@
 \begin{eqnarray}
-\overline{I_i \mathbf{u} \cdot \nabla \mathbf{u}} &=& \sigma_i \mathbf{u}_i \cdot \nabla \mathbf{u}_i + F_\text{SF}^{\mathbf{u}_i} \\
-\overline{I_i \mathbf{u} \cdot \nabla b} &=& \sigma_i \mathbf{u}_i \cdot \nabla b_i + F_\text{SF}^{b_i}
+\overline{I_i \nabla \cdot (\mathbf{u} \mathbf{u})} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
+\overline{I_i \nabla (\mathbf{u} b)} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
 \label{eq:filterAdvection}
@@
 
-Since viscosity ($\nu$) and thermal diffusivity ($\alpha$) are constant, conditional averaging of the diffusion terms is straightforward:
+\note[HW]{Dan, can we do better than this?}
+Lots of terms appear when attempting to conditionally average the diffusion terms which we do not know how to parameterise. Therefore we will use simply:
 \begin{eqnarray}
-\overline{I_i \nabla \cdot \nu \nabla \mathbf{u}} &=& \sigma_i \nabla\cdot\bigl(\nu \nabla\mathbf{u}_i \bigr) \\
-\overline{I_i \nabla \cdot \alpha \nabla b} &=& \sigma_i \nabla\cdot\bigl(\alpha \nabla b_i \bigr).
+\overline{I_i \nu \nabla^2 \mathbf{u}} &=& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
+\overline{I_i \alpha \nabla^2 b} &=& \sigma_i \alpha \nabla^2b_i .
 \end{eqnarray}
@@
 \begin{equation}
-\sigma_i \nabla P_i = \overline{I_i \nabla P}.
-\end{equation}
+\overline{I_i \nabla P} = \sigma_i \nabla P_i.
+\end{equation}
+
 Combining these gives the conditionally averaged momentum and buoyancy equations:
+\begin{eqnarray}
+\frac{\partial\sigma_i\mathbf{u}_{i}}{\partial t} + 
+\nabla\cdot(\sigma_i \mathbf{u}_{i} \mathbf{u}_{i})
++ \sigma_i \nabla P_{i}
+& = &
+\sigma_i b_{i}\mathbf{k}
++
+\nu\sigma_i\nabla^{2}\mathbf{u}_{i}
++
+\sum_{j\ne i}\left\{ \sigma_{j}S_{ji}\mathbf{u}_{ji}^{T}
+ - \sigma_{i}\mathbf{D}_{ij}\right\}
+\label{eq:momFlux}\\
+\frac{\partial\sigma_i b_{i}}{\partial t} + 
+\nabla\cdot(\sigma_i \mathbf{u}_{i} b_{i})
+& = &
+\alpha\sigma_i\nabla^{2}b_{i}
++
+\sum_{j\ne i} \sigma_{j}S_{ji} b_{ji}^{T}.
+\label{eq:bFlux}
+\end{eqnarray}
+These equations include mass transfers between fluids with $\mathbf{u}_{ij}^T$ being the velocity of the fluid transferred from $i$ to $j$ and $b_{ij}^T$ being the buoyancy of the fluid transferred from $i$ to $j$.
+A drag term, $\mathbf{D}_{ij}$ is also included to parameterise some of the missing terms because it is commonly used when conditional averaging is applied in fields such as multi-phase modelling \cite<eg>{GBB+07}.
+Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.
+
+Eqns ({eq:momFlux}) and ({eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated:
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$, $\mathbf{u}_{ij}^T$ is the velocity of the fluid transferred from $i$ to $j$, $b_{ij}^T$ is the buoyancy of the fluid transferred from $i$ to $j$ and $\mathbf{D}_{ij}$ is the drag of fluid $j$ on fluid $i$.
-It is not clear that drag between fluids is appropriate for this form of the equations but it is commonly used in multi-phase modelling \cite<eg>{?} so we will investigate sensitivity to drag in section \ref{sec:results}.
+where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$,
 
@@
 The instabilities reported by \citeA{WM19} showed growing divergence
-in a fluid with vanishing volume fraction. It is mass convergence
+in a fluid with vanishing volume fraction. \change[HW]{It is mass convergence
 rather than velocity convergence that leads to pressure anomalies
@@
 of fluid is vanishingly low then convergence cannot lead to an anomaly
-in the total pressure.
+in the total pressure.}{For single-fluid equations, divergence would lead to pressure anomalies which would act as a negative feedback on the divergence.
+However for multi-fluids if one of the volume fractions is too small then it cannot force pressure anomalies big enough to stabilise the divergence.
+Use of separate pressure for each fluid is proposed to ensure stability.}
 
@@
 \end{equation}
+\add[HW]{In order to derive a suitable form of parameterisation for $p_i$ we will first consider the} \citeA{BN86} \add{model.}
+
+\subsubsection{\add[HW]{The \protect\citeA{BN86} model}}
 
@@
 in a multi-phase explosion model that has been widely used in mathematics
-and engineering for simulating fluidised beds of granular material
-\cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}.
-In these methods, advection equations are written for the volume fraction,
-$\sigma_{i}$, and conservation equations are written for mass fraction,
-$\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
-fluids, the \citeA{BN86} equations would be:
+and engineering for simulating, \add[HW]{for example}, fluidised beds of granular material \cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}.
+\add[HW]{This model is not used here but is examined in order to derive a method suitable for atmospheric convection.}
+\citeA{SA99} wrote transport equations for both the volume fraction,
+$\sigma_{i}$, and for the mass fraction,
+$\sigma_{i}\rho_{i}$  without transfers between fluids which in our notation are:
 \begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)\label{eq:BNcompaction}\\
-\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0\label{eq:rhoTransport}
+\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)
+\label{eq:BNcompaction}
+\\
+\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0
+\label{eq:rhoTransport}
 \end{eqnarray}
@@
 if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
-$\rho_{i}$ is constant then eqns (\ref{eq:divFree}-\ref{eq:rhoTransport})
+$\rho_{i}$ is constant then eqns (\ref{eq:divFree}), (\ref{eq:sumOne}), (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport})
 imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
@@
 we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.
+
+\subsubsection{\add[HW]{Proposed Model for Pressure Differences between Fluids}}
 
@@
 \begin{equation}
-p_{i}=-\gamma\nabla\cdot\mathbf{u}_{i}\label{eq:Pi_div}
-\end{equation}
-where $\gamma$ is a free coefficient. Dimensional analysis in section
+p_{i}=-\gamma\nabla\cdot(\sigma_i \mathbf{u}_{i})
+\label{eq:Pi_div}
+\end{equation}
+where $\gamma$ is a \change[HW]{free coefficient}{compressibility with units $\text{m}^s \text{s}^{-1}$. 
+This parameterisation of $p_i$ has $\sigma_i$ inside the divergence in order to ensure that $\sum_i p_i =0$ and $\therefore$ that $\sum_i P_i = P$.}
+
+\change[HW]{Dimensional}{Scale} analysis in section
 \ref{subsec:dimAnal} will inform the choice of $\gamma$ and sensitivity
@@
 \begin{equation}
-\varepsilon=\frac{0.2}{r_{c}}\implies S_{01}=w_{1}\frac{0.2}{r_{c}}
+\varepsilon=\frac{0.2}{r_{c}}
 \end{equation}
 where $\varepsilon$ is the well know fractional entrainment rate
-and $r_{c}$ is the cloud or plume radius.
+and $r_{c}$ is the cloud or plume radius. Fractional entrainment is related to mass transfers by:
+\begin{equation}
+S_{01} = w_{1}\varepsilon.
+\end{equation}
 
@@
 and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
+\add[HW]{
+$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<eg.>{AK67,AS74}.
+}
 Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
@@
 
-\subsection{Dimensional Analysis\label{subsec:dimAnal}}
+\subsection{\change[HW]{Dimensional}{Scale} Analysis\label{subsec:dimAnal}}
 
@@
 Next a Poisson equation is solved to calculate the total pressure,
-$P$ to ensure that the total velocity is divergence free. The pressure
+$P$ to ensure that the total velocity is divergence free. \add[HW]{This is the standard approach for ensuring divergence constraints \protect\cite<eg>{SKW14}.} The pressure
 equation also provides updates for the velocity flux, $u_{i}$. First

### 2020-03-29 submit2/manuscript.tex
First draft and responses and revisions for reviewer 1.

@@
 so that separate equations of motion can be solved for each fluid,
-thus representing features that cannot be resolved in a single fluid
+thus representing features that cannot be resolved in a single-fluid
 at coarse resolution.
@@
 on the sign of the vertical velocity. The multi-fluid model reproduces
-the mean properties of the rising and falling fluids in a single column. 
+the mean properties of the rising and falling fluids in a \change[HW]{single}{one} column. 
 \end{abstract}
@@
 in a single-fluid two dimensional Boussinesq model with a two-fluid,
-single column model in section \ref{sec:results} using two vertical
+\change[HW]{single}{one} column model in section \ref{sec:results} using two vertical
 slice test cases.
@@
 stabilised using mass exchanges or drag between the fluids. \citeA{TEB19}
-achieved realistic results in single column experiments of convective
+achieved realistic results in \change[HW]{single}{one} column experiments of convective
 boundary layer but the amount of diffusion needed would spoil simulations
@@
 
-Dimensional analysis can guide our choice of $\gamma$ for the parameterisation
-of the pressure difference between fluids. We make the following assumptions:
+Dimensional analysis can guide our choice of $\gamma$ for the parameterisation of the pressure difference between fluids. We make the following assumptions
+\add[HW]{in this analysis}:
 \begin{enumerate}
@@
 \item Fluid $i$ properties are anomalies from a neutrally stable resting
-mean state.
+mean state 
+\add[HW]{implying that the average over all fluids of $b_i$, $\mathbf{u}_i$ and $P_i$ are zero}.
 \item We consider only the vertical direction where $w_{ij}^{T}=0$.
@@
 
+\subsection{\add[HW]{Discrete Conditional Averaging} \label{sec:cAveraging}}
+
+\note[HW]{This whole sub-section is new}
+
+A single-fluid solution is conditionally averaged by:
+\begin{equation}
+i =
+\begin{cases}
+    0 & \text{ if }w\le 0 \\
+    1 & \text{ otherwise.}
+\end{cases}
+\end{equation}
+If an entire grid box is assigned to be either in fluid 0 or fluid 1 based on $w$ at the cell centre then $\sigma$ can only take a small number of discrete values depending on the resolution of the conditional averaging.
+For example, if conditional averaging goes from $n$ columns to 1 column with vertical resolution staying the same, then $\sigma$ can only take values $\frac{k}{n}$ where $k$ is an integer between zero and $n$.
+This means that $\sigma$ is either uniform (for small $n$) or has jumps in the vertical (for larger $n$).
+An alternative is therefore proposed in order to approximate $\sigma$ based on $w$ and $\nabla w$ at cell centres.
+This is based on the intersection between a grid box and the surface of $w=0$.
+Given a grid box with centre $\mathbf{x}_c$, the surface of points, $\mathbf{x}_w$ of $w=0$ satisfies:
+\begin{equation}
+\nabla w \cdot \left(\mathbf{x}_c - \mathbf{x}_w\right) = 0
+\end{equation}
+Rather than the expense of calculating exact grid box volume fractions either side of this surface, the signed distance of each grid box vertex, $\mathbf{x}_v$, to the surface is calculated:
+\begin{equation}
+d_v = \left(
+     \mathbf{x}_v - \mathbf{x}_c + \frac{w \nabla w}{|\nabla w|^2} 
+\right) \cdot \frac{\nabla w}{|\nabla w|}.
+\end{equation}
+The volume fraction either side of the $w=0$ surface is approximated by the average distance to vertices in one side of the surface divided by the average distance to vertices on both side:
+\begin{equation}
+\sigma_0 = 
+\frac{-\text{mean}\bigl(\text{all } d_v \text{ with } d_v \le 0\bigr)}
+{\text{mean}\bigl(\text{all } |d_v| \bigl)}
+\;\;\;\;\;\;
+\sigma_1 = 
+\frac{\text{mean}\bigl(\text{all } d_v \text{ with } d_v > 0\bigr)}
+{\text{mean}\bigl(\text{all } |d_v| \bigl)}.
+\end{equation}
+This gives smooth $\sigma$ fields that will be shown in section \ref{sec:results}.
+
 \section{Validation Test Cases\label{sec:results}}
@@
 convection. The first is transient; the standard rising bubble of
-\citeA{BF02}. We aim to reproduce the vertical heat transport, the
+\citeA{BF02}. \remove{We aim to reproduce the vertical heat transport, the
 mean velocity of the rising air, the bouyancy of the rising air and
 pressure differences between two fluids in a single column two fluid
-model. The second test case is steady state with heat transfer at
+model.} The second test case is steady state with heat transfer at
 the ground and uniform radiative cooling. For both test cases the
-reference solution is a single fluid solution of the two-dimensional
+reference solution is a single-fluid solution of the two-dimensional
 Boussinesq equations at high horizontal and vertical resolution.
+\add[HW]{This will be compared with the two-fluid model run using one column.
+We aim to reproduce the vertical heat transport, the mean velocity of the rising air, the bouyancy of the rising air and the pressure differences between fluids in one column two-fluid model.}
 
@@
 
-The test case of \citeA{BF02} was designed for fully compressible
+The \add[HW]{two dimensional} test case of \citeA{BF02} was designed for fully compressible
 models but similar solutions are obtained solving Boussinesq equations.
@@
 two dimensional reference simulation and $\Delta z=100\ \text{m}$
-is used in the vertical for the single column simulations. All simulations
+is used in the vertical for the \change[HW]{single}{one} column simulations. All simulations
 use a time-step of 2\,s.
 
-\subsubsection{Single Fluid Solutions}
-
-The solution of the rising buoyant bubble solving the Boussinesq equations
+\subsubsection{Single-Fluid Solutions}
+
+The solution of the \add[HW]{resolved 2D} rising buoyant bubble solving the Boussinesq equations
 for 1000s is shown in figure \ref{fig:bubble} with buoyancy coloured,
@@
 reproduce these fields approximately at coarser horizontal resolution
-or in a single column model.
+or in a \change[HW]{single}{one} column model.
 
@@
 \par\end{centering}
-\caption{The single fluid, resolved rising bubble after 1000s. Buoyancy is
+\caption{The single-fluid, resolved \add[HW]{2D} rising bubble after 1000s. Buoyancy is
 coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
-negative contours dashed. The $w=0$ contour is dotted. \label{fig:bubble}}
+negative contours dashed. The $w=0$ contour is dotted.
+\label{fig:bubble}}
 \end{figure}
@@
 for horizontal resolutions of nine columns, five columns, three columns
-and a single column all for the 20km wide domain and all still using
+and \change[HW]{a single}{one} column \change{HW}{all for}{covering} the 20km wide domain and all \remove[HW]{still} using
 $\Delta z=100\ \text{m}$. These simulations are initialised by conservative
@@
 resolution is reduced, the vertical transport reduces until there
-is no movement at all for a single column: there is no possibility
-of fluid rising because in a single column with a single fluid there
+is no movement at all for \change[HW]{a single column}{the one column simulation}: there is no possibility
+of fluid rising because in \change[HW]{a single}{one} column with a single-fluid there
 can be no compensating subsidence. The lack of vertical transport
@@
 \caption{The rising bubble after 1000s simulated with coarse horizontal resolution
-and a single fluid. Horizontal averages are conditioned based on $w$.
+and a single-fluid. Horizontal averages are conditioned based on $w$.
 \label{fig:bubble_singleUnderRes}}
@@
 
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-Multi-fluid, single column simulations are initialised by horizontally
-and conditionally averaging the high resolution single fluid initial
+\subsubsection{Results of the Two-fluid, \change[HW]{Single}{One} Column Simulations}
+
+\change[HW]{Multi-fluid, single}{Two-fluid, one} column simulations are initialised by horizontally
+and conditionally averaging the high resolution single-fluid initial
 conditions. Sinking air is put into fluid zero and rising air into
@@
 \caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
+the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
+lines are the single-fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
 \end{figure}
@@
 
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions.\label{fig:multiFluidSingleColumn}}
+\caption{\change[HW]{Results of the rising bubble at $t=1000\ \text{s}$.
+Solid lines are the multi-fluid, single column solutions of the rising bubble.
+Dashed lines are the single-fluid, resolved solutions.}
+{As figure \protect\ref{fig:multiFluidSingleColumn-bad} but different parameterisation options.}
+\label{fig:multiFluidSingleColumn}}
 \end{figure}
@@
 with no fluid 1 below the buoyant fluid and very little falling air
-at the lowest height of the rising fluid. With a single column and
+at the lowest height of the rising fluid. With \change[HW]{single}{one} column and
 two fluids, all air must rise in one fluid and sink in the other.
@@
 
-This section has demonstrated the value of using a single column,
+This section has demonstrated the value of using \change[HW]{single}{one} column,
 multi-fluid model to simulate a buoyant rising bubble with a single
@@
 but neither was plausible. There are clearly discrepancies between
-the single fluid resolved rising bubble and the two fluid single column
+the single-fluid resolved rising bubble and the two fluid \change[HW]{single}{one} column
 rising bubble but we do not want to over fit the multi-fluid model
@@
 
-\subsubsection{Single Fluid Solutions}
+\subsubsection{Single-Fluid Solutions}
 
@@
 
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-The two fluid model is used to simulate the RCE test case in a single
+\subsubsection{Results of the Two-fluid, \change[HW]{Single}{One} Column Simulations}
+
+The two fluid model is used to simulate the RCE test case in \change[HW]{single}{one}
 column of 40 cells with zero buoyancy gradient at the top and a buoyancy
@@
 and uniform radiative cooling. The two fluids are initialised using
-the time mean conditional horizontal averages from the single fluid
+the time mean conditional horizontal averages from the single-fluid
 resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
@@
 detrainment in the upper half ($S_{10}>0$), where the air decelerates
-towards the top. The single column model reproduces the super-adiabatic
+towards the top. The \change[HW]{single}{one} column model reproduces the super-adiabatic
 layer near the ground and the near uniform buoyancy away from the
@@
 \tabularnewline
-\multicolumn{5}{c}{Single column with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
+\multicolumn{5}{c}{\change[HW]{Single}{One} column with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
 $b_{ij}^{T}=b_{i}$, $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
@@
 \tabularnewline
-\multicolumn{5}{c}{Single column  with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
+\multicolumn{5}{c}{\change[HW]{Single}{One} column  with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
 $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
@@
 of the resolved case between $t=10^{5}\text{s}$ and $2\times10^{5}\text{s}$. The
-bottom two rows show results of the single column multi-fluid model
+bottom two rows show results of the \change[HW]{single}{one} column multi-fluid model
 after $10^{4}\ \text{s}$. \label{fig:RCE_singleColumn}}
@@
 with heating at the ground and uniform radiative cooling. High resolution
-single fluid simulations are conditionally averaged based on the sign
+single-fluid simulations are conditionally averaged based on the sign
 of vertical velocity ($w$) in order to create rising and falling
 fluids which each have their own mean buoyancy, velocity and pressure.
-The two-fluid, single column Boussinesq model reproduces mean vertical
+The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
 heat and mass transport of these test cases.
@@
 
-Single column multi-fluid modelling with moisture has already been
+\change[HW]{Single}{One} column multi-fluid modelling with moisture has already been
 demonstrated by \citeA{TEB19} 

### 2020-03-31 submit2/manuscript.tex
Started revisions and responses to reviewer 2

@@
 and near grid-scale convection allowing for consistent and accurate
-treatment of net mass transport by convection, non-equilibrium and
-turbulence. The air is partitioned into convecting and non-convecting
-fluids each with their own velocity, temperature and constituents
-so that separate equations of motion can be solved for each fluid,
+treatment of net mass transport by convection \add[HW]{and of} non-equilibrium \add[HW]{dynamics} \remove[HW]{and turbulence}.
+The air is partitioned into \change[HW]{convecting and non-convecting}{two or more}
+fluids \add[HW]{which may represent, for example, updrafts and the stable environment.} \change[HW]{each with their}{Each fluid has its} own velocity, temperature and constituents
+with separate equations of motion. \remove[HW]{can be solved for each fluid,
 thus representing features that cannot be resolved in a single-fluid
-at coarse resolution.
-
-This paper presents multi-fluid Boussinesq equations for representing
-under resolved dry convection. We present a new model for entrainment
+at coarse resolution.}
+
+This paper presents \change[HW]{multi}{two}-fluid Boussinesq equations for representing
+under-resolved dry convection \add[HW]{with sinking and $w=0$ air in fluid 0 and rising air in fluid 1}. We present a \remove[HW]{new} model for entrainment
 and detrainment based on divergence which leads to excellent representation
 of the convective area fraction. Previous multi-fluid modelling of
-convection has assumed that all fluids share the same pressure. We
-show that this is a bad assumption and we propose and validate a model
-for the pressure difference between the fluids based on divergence.
-
-Two vertical slice test cases are used to validate the multi-fluid
-model; a buoyant rising bubble and radiative convective equilibrium
+convection has assumed that \change[HW]{all}{both} fluids share the same pressure.
+\change[HW]{We show that this is}{This is shown to be} a bad assumption and \remove[HW]{we propose and validate} a model
+for the pressure difference between the fluids based on divergence \add[HW]{is presented}.
+
+Two vertical slice test cases are used to \change[HW]{validate}{evaluate} the \change[HW]{multi}{two}-fluid
+model; a buoyant rising bubble and radiative convective equilibrium. \add[HW]{These}
 are simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity. The multi-fluid model reproduces
-the mean properties of the rising and falling fluids in a \change[HW]{single}{one} column. 
+on the sign of the vertical velocity. The \change[HW]{multi}{two}-fluid model reproduces
+the mean properties of the rising and falling fluids in \change[HW]{a single}{one} column. 
 \end{abstract}
@@
 Multi-fluid modelling will enable mass transport by convection but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model.
-This paper provides some closures necessary for multi-fluid modelling and validation of the technique for two dimensional dry convection.
+This paper provides some closures necessary for multi-fluid modelling and \change[HW]{validation}{evaluation} of the technique for two dimensional dry convection.
 
@@
 
+\add[HW]{
+\protect\citeA{LR01} introduced the ``assumed-distribution higher-order closure'' (ADHOC) parameterisation of the boundary layer and convection which solves prognostic equations for higher-order moments of the sub-grid-scale flow, such as the triple correlation of the vertical velocity anomalies, and diagnoses updraft and downdraft means from the higher-order moments.
+Thus all necessary statistics can be calculated from the grid-box-mean values that are predicted by the dynamical core.
+Net mass transport by convection is included because it is part of the grid-box-mean.
+ADHOC was extended by \protect\citeA{GLC02} to use bi-Gaussian probability distribution functions (PDFs) rather than top-hat distributions to represent sub-grid-scale variability.
+This formed the basis of the ``Cloud Layers Unified By Binormals'' (CLUBB) parameterization \protect\cite<>{LSW+12} which was first used at grey zone resolutions.}
+
 \citeA{TWV+18} proposed multi-fluid modelling of convection in order
-to treat non-equilibrium and net mass transport correctly and consistently
-with the same numerics and physics controlling thermals, the stable
-environment and downdraught dynamics. \citeA{Yano14} derived similar
-equations for multiple segments and showed how this is a generalisation
+to treat non-equilibrium and net mass transport \remove[HW]{correctly and} consistently.
+\change{with}{This involves using} the same numerics and physics to \change[HW]{control thermals}{prognose properties of separate parts of the fluid, for example updrafts}, the stable environment and downdrafts \remove[HW]{dynamics}.
+\citeA{Yano14} derived similar
+equations \remove[HW]{for multiple segments} and showed how this is a generalisation
 of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
@@
 {only solve the equations in a single column without coupling to the continuity equation of a dynamical core.}
-Multi-fluids promises big improvements
+\change[HW]{Multi-fluids promises big improvements
 in the representation of sub-grid-scale convection and unification
 with the representation of turbulence, particularly at the grey zone.
-However, there is a long way to go, particularly as multi-fluids requires
+However, there is a long way to go, particularly as}
+{The multi-fluids approach has an advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments (means of eg.
+updraft and environment) directly rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment.
+Solving directly for sub-fluid means should be less sensitive to closure assumptions.
+However} multi-fluids require
 a dedicated model rather than being a stand alone parameterisation
@@
 of the multi-fluid equations assuming two fluids that share the same
-pressure (or that pressure differences are predominantly due to drag
-between the fluids). \citeA{TEB19} showed that these equations (without
-drag) are in fact unstable and can be stabilised by diffusion of vertical
+pressure. \remove[HW]{(or that pressure differences are predominantly due to drag
+between the fluids)}. \citeA{TEB19} showed that these equations \remove[HW]{(without
+drag)} are in fact unstable and can be stabilised by diffusion of vertical
 velocity whereas \citeA{WM19} stabilised the equations with diffusion
 and drag between fluids. Neither of these stabilisation techniques
-are acceptable and in this paper we show that there are significant
-and sustained pressure differences between the fluids (section \ref{sec:results}).
+are acceptable;
+\add[HW]{sufficient diffusion to stabilise the multi-fluid equations may smooth out real features of the flow and the diffusion between fluids and drag used by \protect\citeA{WM19} meant that both fluids tended to move together rather than through each other.}
+In this paper we show that there are significant
+and sustained pressure differences between the fluids (section \ref{sec:results}) \add[HW]{and that the use of separate pressures stabilises the equations}.
 
@@
 in a single-fluid two dimensional Boussinesq model with a two-fluid,
-\change[HW]{single}{one} column model in section \ref{sec:results} using two vertical
-slice test cases.
+\change[HW]{single}{one} column model in section \ref{sec:results} using two vertical slice test cases.
 
@@
 Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
-over to the Boussinesq equations; convection is buoyancy dominated
+over to the Boussinesq equations \add[HW]{because} convection is buoyancy dominated
 and close to incompressible. The resolved test cases presented in
@@
 The single-fluid Boussinesq equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations.
-Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere and satisfy:
+Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere.
+In this paper, $I_0$ labels sinking and $w=0$ fluid and $I_1$ labels rising fluid.
+$I_i$ satisfies:
 \begin{equation}
@@
 \end{equation}
-Applying the conditional average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$:
+Applying conditional volume average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$:
 \begin{eqnarray}
@@
 
-Eqns ({eq:momFlux}) and ({eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated:
+Eqns (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated due to the mass transfer terms in \ref{eq:sigma}:
 \begin{eqnarray}
@@
 
-\citeA{TEB19} and \citeA{WM19} assumed that each co-located fluid
-shared the same pressure, leading to unstable equations that \citeA{TEB19}
+\citeA{TEB19} and \citeA{WM19} assumed that each \remove[HW]{co-located} fluid
+shared the same pressure \change[HW]{leading}{field. This lead} to unstable equations that \citeA{TEB19}
 stabilised using diffusion of vertical velocity and \citeA{WM19}
 stabilised using mass exchanges or drag between the fluids. \citeA{TEB19}
-achieved realistic results in \change[HW]{single}{one} column experiments of convective
+achieved realistic results in \change[HW]{single}{one} column experiments of \add[HW]{the} convective
 boundary layer but the amount of diffusion needed would spoil simulations
-in the free troposphere. The stabilisation used by \citeA{WM19} meant
+in the free troposphere \add[HW]{by diffusing real features as well as spurious artifacts}. The stabilisation used by \citeA{WM19} meant
 that the two fluids tended to move as one which defeats the purpose
@@
 
-We will assume that pressure in each fluid is given by a parameterised
+We will assume that pressure in each fluid is given by a \remove[HW]{parameterised}
 perturbation, $p_{i}$, from the total pressure, $P$:
@@
 be transferred from 0 to 1 and vice versa. The properties of the fluids
-transferred should depend on the modelling of sub-grid-scale variability
+transferred should depend on the modelling of \change[HW]{sub-grid-scale}{sub-filter-scale} variability \add[HW]{(i.e. the variability within each fluid)}
 which is beyond the scope of this paper. In section \ref{sec:results}
@@
 
-\section{Numerical Solution \label{sec:numerics}}
+\section{Numerical \change[HW]{Solution}{Method} \label{sec:numerics}}
 
@@
 
-\section{Validation Test Cases\label{sec:results}}
-
-Two test cases are developed to tune parameters and to validate the
+\section{\change[HW]{Validation}{Evaluation} Test Cases\label{sec:results}}
+
+Two test cases are developed to tune parameters and to \change[HW]{validate}{evaluate} the
 use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
@@
 pressure differences between two fluids in a single column two fluid
-model.} The second test case is steady state with heat transfer at
-the ground and uniform radiative cooling. For both test cases the
+model.} The second \remove[HW]{test case} is steady state with heat transfer at
+the ground and uniform radiative cooling \add[HW]{(radiative convective equilibrium)}. For both test cases, the
 reference solution is a single-fluid solution of the two-dimensional
@@
 (third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
-the velocity profile too smooth and the updraught too weak so the
+the velocity profile too smooth and the updraft too weak so the
 bubble does not rise enough. It is reasonable to consider smaller
@@
 leads to the leading edge of the bubble rising too quickly. Smaller
-values of $\gamma$ leave a discontinuity in the updraught velocity
+values of $\gamma$ leave a discontinuity in the updraft velocity
 at the leading edge of the bubble and larger values of $\gamma$ reduce
 the velocity further, meaning that the bubble does not rise enough
-(not shown). None of the values of $\gamma$ reproduce the peak updraught
+(not shown). None of the values of $\gamma$ reproduce the peak updraft
 velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
@@
 this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
-drag slows the updraughts without increasing the mixing between the
+drag slows the updrafts without increasing the mixing between the
 fluids which makes the solutions less like the resolved simulations.
@@
 for buoyant thermals and plumes \cite<e.g.,>{RC15}, the drag is related
-to mixing with downdraught air which is accounted for in the entrainment
+to mixing with downdraft air which is accounted for in the entrainment
 term of the momentum equation. So adding a separate term from drag
@@
 differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
-This combination produces smooth solutions but the updraught is too
+This combination produces smooth solutions but the updraft is too
 weak and too much is entrained into fluid 1. Using this entrainment,
-the updraught will entrain more and more air until $\sigma_{1}=1$.
+the updraft will entrain more and more air until $\sigma_{1}=1$.
 The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
@@
 Two alternative models for estimating the buoyancy of the fluid transferred
-between updraught and downdraught have been tested. The results in
+between updraft and downdraft have been tested. The results in
 the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
@@
 positively buoyant air in fluid one and the negatively buoyant air
-in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
+in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraft),
 the mean buoyancy of fluid one increases. This leads to very high
@@
 multi-fluid model to simulate a buoyant rising bubble with a single
-updraught fluid and a single downdraught fluid. Transfers between
+updraft fluid and a single downdraft fluid. Transfers between
 the fluids have been successfully modelled using entrainment set by
-divergence giving realistic updraught fractions. Entrainment calculated
+divergence giving realistic updraft fractions. Entrainment calculated
 as the reciprocal of plume width was not successful. The pressure
@@
 
-This test case is designed to have strong updraughts in narrow plumes
+This test case is designed to have strong updrafts in narrow plumes
 and weak descent elsewhere to mimic atmospheric convection but without
@@
 are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
-updraughts. The buoyant air at the ground rises in narrow plumes,
+updrafts. The buoyant air at the ground rises in narrow plumes,
 accelerating due to buoyancy and pressure gradients then decelerating
@@
 ground but the buoyancy difference between the fluids is too large.
-The updraught and downdraught velocities are captured well. The pressure
+The updraft and downdraft velocities are captured well. The pressure
 differences between fluids are too large which is consistent with
@@
 for convection, reproducing aspects of highly resolved dry convection
-at coarse horizontal resolution. Two test cases are used to validate
+at coarse horizontal resolution. Two test cases are used to \change[HW]{validate}{evaluate}
 the multi-fluid model. The first is a Boussinesq version of the well
@@
 {constrained to be zero following the single-fluid Boussinesq equations.}
-A model is proposed and validated for the pressure difference between the rising
+A model is proposed and \change[HW]{validated}{evaluated} for the pressure difference between the rising
 and falling fluids based on the divergence of each fluid. The use

### 2020-04-03 submit2/manuscript.tex
Nearly finished responding to revier 2's annotated comments

@@
 
-Two vertical slice test cases are used to \change[HW]{validate}{evaluate} the \change[HW]{multi}{two}-fluid
-model; a buoyant rising bubble and radiative convective equilibrium. \add[HW]{These}
-are simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity. The \change[HW]{multi}{two}-fluid model reproduces
+Two vertical slice test cases are \change[HW]{used}{developed} to \add[HW]{tune parameters and to} \change[HW]{validate}{evaluate} the \change[HW]{multi}{use of two}-fluid
+\change[HW]{model}{equations to represent dry, two-dimensional, sub-grid-scale convection}; a buoyant rising bubble and radiative convective equilibrium. \add[HW]{These}
+are \add[HW]{first} simulated at high resolution and conditionally averaged based
+on the sign of the vertical velocity \add[HW]{and next simulated with the two-fluid model in one vertical column}. The \change[HW]{multi}{two}-fluid model reproduces
 the mean properties of the rising and falling fluids in \change[HW]{a single}{one} column. 
@@
 
-\section{Introduction}
+\section{Introduction \label{sec:intro}}
 
@@
 
-\section{The Multi-fluid Boussinesq Equations}
+\section{The Multi-fluid Boussinesq Equations \label{sec:multiBouEqns}}
 
@@
 
-We consider dry air without turbulence so use the dynamic entrainment
-described by \citeA{HC51},\citeA{AK67} and \citeA{DBF+13}:
+\add[HW]{The transfers between fluids are related to entrainment, $\varepsilon$, and detrainment, $\delta$. Fluid 0 is the environment and fluid 1 is updrafts implying:}
+\begin{equation}
+S_{01} = w_1\varepsilon, \;\;\;\;\;\;\;
+S_{10} = w_0\delta.
+\end{equation}
+\add[HW]{Results using two formulations of entrainment are presented in section \protect\ref{sec:results}. The first is}
+\remove[HW]{We consider dry air without turbulence so use}
+the dynamic entrainment described by
+\citeA{HC51}, \citeA{AK67} and \citeA{DBF+13}:
 \begin{equation}
@@
 -\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
-0 & \text{otherwise}
+0 & \text{otherwise.}
 \end{cases}
 \end{equation}
-which is necessary to stop air in one fluid from accumulating when
-vertical motion ceases (at the top of a rising plume or at the bottom
-of descending air). We will also test a common form of lateral entrainment
-\cite{DBF+13}:
+\change[HW]{which is necessary to stop air in}{This formulation prevents} one fluid from accumulating when vertical motion ceases (at the top of a rising plume or at the bottom of descending air).
+\remove[HW]{We will also test a}{A} common form of lateral entrainment \cite<eg.>{DBF+13} \add[HW]{is also tested in section \protect\ref{sec:results}}:
 \begin{equation}
@@
 \end{equation}
-where $\varepsilon$ is the well know fractional entrainment rate
-and $r_{c}$ is the cloud or plume radius. Fractional entrainment is related to mass transfers by:
-\begin{equation}
-S_{01} = w_{1}\varepsilon.
-\end{equation}
+where $r_{c}$ is the cloud or plume radius. 
+\remove[HW]{Fractional entrainment is related to mass transfers by:}
 
@@
 
-The different fluids may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}.
-In fact, the most buoyant air should be transferred from fluid 0 to
-fluid 1 and vice versa, and the air with least downward momentum should
-be transferred from 0 to 1 and vice versa. The properties of the fluids
-transferred should depend on the modelling of \change[HW]{sub-grid-scale}{sub-filter-scale} variability \add[HW]{(i.e. the variability within each fluid)}
-which is beyond the scope of this paper. In section \ref{sec:results}
+\change[HW]{The different}{Each} fluid may not be well mixed so the fluid transferred
+may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. In fact, 
+\change[HW]
+{the most buoyant air should be transferred from fluid 0 to
+fluid 1 and vice versa, and the air with least downward momentum}
+{since we are conditionally averaging based on the vertical velocity, $w$, the sub-set of fluid 0 that is accelerating and about to be rising}
+should be transferred from 0 to 1 and vice versa.
+\change[HW]{The properties of the fluids transferred should depend on the modelling of sub-grid-scale variability which}
+{A realistic estimate of the properties of the fluid transferred can only be made based on knowledge of sub-filter-scale variability (i.e.
+the variability within each fluid).
+Modelling of sub-filter-scale variability}
+is beyond the scope of this paper.
+%
+In section \ref{sec:results}
 we conditionally average high resolution solutions based on the sign
@@
 
-\subsection{\change[HW]{Dimensional}{Scale} Analysis\label{subsec:dimAnal}}
+\subsection{\label{subsec:dimAnal}\change[HW]{Dimensional}{Scale}
+ Analysis}
 
@@
 \item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
-\item There are two fluids, $i$ and $j$
+\item There are two fluids, \change[HW]{$i$ and $j$}{0 and 1.}
 \item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
@@
 \end{enumerate}
-This leads to the following balance in the momentum equation:
+\change[HW]{This leads to the following balance in the momentum equation}{These assumptions can be used to simplify the multi-fluid $w$ equation, (\protect\ref{eq:mom})}:
 \begin{equation}
@@
 in $\tilde{w}$ due to advection and buoyancy but not too large to
-remove all variability in $\tilde{w}$ so we need:
+remove all variability in $\tilde{w}$. \change[HW]{so we need}{Therefore the stabilisation term should be $O(1)$ which implies that}:
 \begin{equation}
@@
 \end{equation}
-
-\section{Numerical \change[HW]{Solution}{Method} \label{sec:numerics}}
+\add[HW]{This will be used to guide the choice of $\gamma$ in section \protect\ref{sec:results}.}
+\section{\label{sec:numerics}Numerical \change[HW]{Solution}{Method}}
 
@@
 
-\subsection{\add[HW]{Discrete Conditional Averaging} \label{sec:cAveraging}}
+\subsection{\label{sec:cAveraging}\add[HW]{Discrete Conditional Averaging} }
 
@@
 
-\section{\change[HW]{Validation}{Evaluation} Test Cases\label{sec:results}}
+\section{\label{sec:results}\change[HW]{Validation}{Evaluation} Test Cases}
 
@@
 figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
-detrained from fluid 1, fluid 1 looses too much buoyancy and a discontinuity
+detrained from fluid 1, fluid 1 loses too much buoyancy and a discontinuity
 arises at the bubble leading edge; the buoyancy force is producing
@@
 and pressure difference between the fluids controlled by divergence
-($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
+($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$), \add[HW]{the} simulations are more
 realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
@@
 The other entrainment option is the commonly used fractional entrainment
-rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
+rate, $\varepsilon=0.2/r_{c}$. This is used \change[HW]{combined}{in combination with} with pressure
 differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
@@
 the updraft will entrain more and more air until $\sigma_{1}=1$.
-The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
-entrainment and detrainment for this test case using conditional averaging
-based on $w$.
+The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives
+\change[HW]{much more accurate entrainment and detrainment for this test case using conditional averaging based on $w$.}
+{results closer to the reference solution conditionally averaged based on $w$.}
 
@@
 between updraft and downdraft have been tested. The results in
-the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
+the fourth row \change[HW]{if}{of} figure \ref{fig:multiFluidSingleColumn} assume
 that the fluid transferred has zero buoyancy in order to keep the
@@
 large buoyancy in fluid one and also negative buoyancy in fluid zero
-which should not occur for this test case. These simple models reinforce
+which \change[HW]{should not occurfor this test case.}{does not occur in the conditionally averaged reference solution.} These simple models reinforce
 the idea that the buoyancy of the fluid transferred should depend
-on knowledge of sub-grid-scale variability of $b$ within each fluid
+on knowledge of \change[HW]{sub-grid-scale}{sub-filter-scale} variability of $b$ within each fluid
 \textendash{} these simple assumptions can lead to unrealistic behaviour.
 The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
-fluid transferred takes the mean properties with it.
-
-This section has demonstrated the value of using \change[HW]{single}{one} column,
-multi-fluid model to simulate a buoyant rising bubble with a single
+fluid transferred takes the mean properties with it. \add[HW]{Modelling of higher-order moments of variability within each fluid is an area of active research.}
+
+This section has demonstrated the \change[HW]{value of using}{plausible utility of} \change[HW]{single column, multi-}{a two-}fluid model to simulate a \add[HW]{sub-grid-scale} buoyant rising bubble with a single
 updraft fluid and a single downdraft fluid. Transfers between
-the fluids have been successfully modelled using entrainment set by
-divergence giving realistic updraft fractions. Entrainment calculated
+the fluids have been \remove[HW]{successfully} modelled using entrainment set by divergence giving \remove[HW]{realistic} updraft fractions \add[HW]{close to the conditionally averaged reference solution}.
+Entrainment calculated
 as the reciprocal of plume width was not successful. The pressure
@@
 to one, dry, two dimensional test case.
+
+\add[HW]{Using the lessons learned from modelling the rising bubble, a statistically stationary case with many plumes is simulated next.}
 
@@
 
-\section{Summary, Conclusions and Further Work}
-
-This paper presents solutions of the multi-fluid Boussinesq equations
-for convection, reproducing aspects of highly resolved dry convection
-at coarse horizontal resolution. Two test cases are used to \change[HW]{validate}{evaluate}
+\section{Summary, Conclusions and Further Work \label{sec:concs}}
+
+\change[HW}{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
+at coarse horizontal resolution.}
+{This paper presents solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) which reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
+Two test cases are used to \change[HW]{validate}{evaluate}
 the multi-fluid model. The first is a Boussinesq version of the well
@@
 with heating at the ground and uniform radiative cooling. High resolution
-single-fluid simulations are conditionally averaged based on the sign
-of vertical velocity ($w$) in order to create rising and falling
+single-fluid simulations are coditionally averaged based on the sign
+of vertical velocity ($w$) in order to \change[HW]{create}{define} rising and falling
 fluids which each have their own mean buoyancy, velocity and pressure.
@@
 for entrainment and detrainment into and out of convecting regions
-must clearly be consistent with the definition of the convecting region.
-We propose a model for entrainment and detrainment based on divergence
+\change[HW]{must clearly}{need to} be consistent with the definition of the convecting region.
+\change[HW]{We propose a}{A} model for entrainment and detrainment based on divergence \add[HW]{is proposed}
 that leads to excellent agreement with $\sigma$ from the high resolution
-solutions. We also test a more conventional fractional entrainment
-rate based on the reciprocal of the plume width which leads to unrealistic
-convecting area fractions.
-
-A set of unknowns in the multi-fluid equations are the properties
-of the fluid that are transferred from one fluid to another. An obvious
+solutions.
+\change[HW]{We also test a}{A} more conventional fractional entrainment rate based on the reciprocal of the plume width \add[HW]{is also tested} which leads to unrealistic convecting area fractions.
+
+\change{A set of unknowns in the multi-fluid equations are the}{The} properties of the fluid that are transferred from one fluid to another \add[HW]{are unknowns in the multi-fluid equations that require closure}.
+An obvious
 first guess would be that fluid takes its mean buoyancy and velocity
-with it when it is transferred. However sub-grid-scale variability
+with it when it is transferred. However sub-\change{grid}{filter}-scale variability
 of each fluid means that we expect that the most buoyant fluid will

### 2020-04-06 submit2/manuscript.tex
First draft responding to reviewer comments

@@
 
-\change[HW}{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
+\change[HW]{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
 at coarse horizontal resolution.}
@@
 first guess would be that fluid takes its mean buoyancy and velocity
-with it when it is transferred. However sub-\change{grid}{filter}-scale variability
+with it when it is transferred.
+\change[HW]{However sub-grid-scale variability
 of each fluid means that we expect that the most buoyant fluid will
 be transferred to the rising fluid or the fluid with the largest vertical
-velocity will be transferred to the rising fluid and vice versa. An
-accurate estimate of these would depend on knowledge of the sub-grid-scale
+velocity will be transferred to the rising fluid and vice versa. An accurate estimate of these would depend on knowledge of the sub-grid-scale
 variability of each fluid which we do not have. Instead we assume
 that the fluid transferred in each direction has zero vertical velocity
-which is consistent with our conditional averaging. We have tested
-three models for the buoyancy of the fluid transferred. The most successful
+which is consistent with our conditional averaging.}
+{Improvements on this assumption will depend on knowledge of sub-filter-scale variablity.
+However since conditional averaging is on $w$, it is consistent to assume that the fluid transferred has $w=0$.}
+\remove[HW]{We have tested}
+Three models for the buoyancy of the fluid transferred 
+\add[HW]{are proposed}. The most successful
 is to assume that the fluid takes its mean buoyancy with it. Assuming
@@
 of both fluids can lead to unrealistically large or small, unbounded
-buoyancies. Similarly, if we assume that one fluid has negative buoyancy
-and the other positive buoyancy and we transfer fluid of zero buoyancy,
+buoyancies. 
+\change[HW]{Similarly, if we assume}{Assuming}
+that one fluid has negative buoyancy and the other positive buoyancy and 
+\remove[HW]{we transfer}
+fluid of zero buoyancy \add[HW]{is transferred},
 then unbounded buoyancy can occur. A better model of the buoyancy
-of the fluid transferred would rely on more information the sub-grid-scale
-variability.
-
-\change[HW]{Single}{One} column multi-fluid modelling with moisture has already been
-demonstrated by \citeA{TEB19} 
+of the fluid transferred would rely on more information \add[HW]{of} the
+sub-\change[HW]{grid}{filter}-scale variability.
+
+\change[HW]{Single}{One} column multi-fluid modelling with moisture has already been demonstrated by \citeA{TEB19} 
 \add[HW]{and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19} }.
-Two important next steps are to simulate
-convection in the grey zone (where it is partially resolved) and to
-represent sub-grid-scale variability within each fluid by solving
-multi-fluid prognostic equations for turbulent kinetic energy and
-other moments of the sub-grid variability. These can be used to inform
-cloud base mass flux (since only the most buoyant fluid will transfer
+Two important next steps are to simulate convection in the grey zone (where it is partially resolved) and to represent sub-\change[HW]{grid}{filter}-scale variability within each fluid by solving multi-fluid prognostic equations for turbulent kinetic energy and other moments of the sub-\change[HW]{grid}{filter} variability.
+\remove[HW]{These can be used to inform}
+Cloud base mass flux \add[HW]{could then be estimated based on higher-order moments of the vertical velocity and buoyancy within the environment fluid.}
+\remove{(since only the most buoyant fluid will transfer
 from the stable environment to the buoyant plume) and inform models
-of the properties of the fluid that is transferred. This will lead
+of the properties of the fluid that is transferred.}
+This will lead
 to a unified parameterisation of turbulence and convection and will

### 2020-04-06 submit2/makeFigs/multiFluidBubble_1000.tex
Putting figures into a single .ps file per figure

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{calc}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage { fancybox}
\usepackage[pdftex]{graphicx,color}
\usepackage{rotating}
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}
\usepackage{amsmath}

\makeatother

\usepackage{babel}
\begin{document}
\begin{tabular}{cccc}
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=0$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\end{tabular}
\end{document}

### 2020-04-06 submit2/makeFigs/multiFluidBubble_500_1.tex
Putting figures into a single .ps file per figure

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{calc}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage { fancybox}
\usepackage[pdftex]{graphicx,color}
\usepackage{rotating}
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}
\usepackage{amsmath}

\makeatother

\usepackage{babel}
\begin{document}
\begin{tabular}{cccc}
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=0$, \hspace{6pt} $\gamma=0$, \hspace{6pt} $C_{D}/r_{c}=0$,
\hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=0$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=6\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/Pcompare}\tabularnewline
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\end{tabular}
\end{document}

### 2020-04-06 submit2/makeFigs/multiFluidBubble_500_2.tex
Putting figures into a single .ps file per figure

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{calc}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage { fancybox}
\usepackage[pdftex]{graphicx,color}
\usepackage{rotating}
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}
\usepackage{amsmath}

\makeatother

\usepackage{babel}
\begin{document}
\begin{tabular}{cccc}
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=1/2000\text{m}^{-1}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=0$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=w_{1}0.2/r_{c}$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0/2000\text{m}^{-1}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=0$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/Pcompare}\tabularnewline
\multicolumn{4}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/Pcompare}\tabularnewline
$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
\end{tabular}
\end{document}

### 2020-04-06 submit2/manuscript.tex
Putting figures into a single .ps file per figure

@@
 \noindent \begin{centering}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
+\includegraphics[width=\textwidth]{figures/bubble.pdf}
 \par\end{centering}
-\noindent \begin{centering}
-\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
-\par\end{centering}
-\caption{The single-fluid, resolved \add[HW]{2D} rising bubble after 1000s. Buoyancy is
-coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
+\caption{The single-fluid, resolved \add[HW]{2D} rising bubble after \add[HW]{0s, 500s and }1000s. Buoyancy is coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
 negative contours dashed. The $w=0$ contour is dotted.
@@
 \begin{figure}
-\noindent %
-\begin{tabular}{ccccc}
-\begin{turn}{90}
-200 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-9 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-5 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-3 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-1 Column
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
-\end{tabular}
-
-\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
+\noindent \begin{centering}
+\includegraphics[width=\textwidth]{figures/bubble_singleUnderRes.pdf}
+\par\end{centering}
+\caption{The rising bubble after 1000s simulated with varying horizontal resolution
 and a single-fluid. Horizontal averages are conditioned based on $w$.
@@
 \begin{figure}
-\setlength{\tabcolsep}{2pt}
-\begin{tabular}{cccc}
-\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
-$S_{ij}=0$, \hspace{6pt}
-$\gamma=0$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=b_{i}$.
-}} \tabularnewline 
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
-$\gamma=0$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=b_{i}$.
-}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
-$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=b_{i}$.
-}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=b_{i}$.
-}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
-$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=b_{i}$.
-}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ ($\text{m}^3/\text{m}^3$) & $b$ and $b_{i}$ ($\text{m}\text{s}^{-2}$) & $w_{0}$ and $w_{1}$ (m/s) & $P_{0}$ and $P_{1}$ ($\text{m}^2 \text{s}^{-2}$)\tabularnewline
-\end{tabular}
-
+\noindent
+\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_1.pdf}
+\caption{Results of the rising bubble at $t=500\ \text{s}$. Solid lines are
+the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
+lines are the single-fluid, resolved solutions.
+\label{fig:multiFluidBubble_500_1}}
+\end{figure}
+
+\begin{figure}
+\noindent
+\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_2.pdf}
+\caption{As figure \ref{fig:multiFluidBubble_500_1} but different parameterisation options.
+\label{fig:multiFluidBubble_500_2}}
+\end{figure}
+
+\begin{figure}
+\noindent
+\includegraphics[width=\linewidth]{figures/multiFluidBubble_1000.pdf}
 \caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
 the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
-lines are the single-fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
-\end{figure}
-
-\begin{figure}
-\setlength{\tabcolsep}{2pt}
-\begin{tabular}{cccc}
-\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
-$C_{D}/r_{c}=1/2000\text{m}^{-1}$, \hspace{6pt}
-$b_{ij}^{T}=b_{i}$.
-} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
-$S_{ij}=0$, \hspace{6pt}
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=b_{i}$.
-}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
-$S_{01}=w_{1}0.2/r_{c}$, \hspace{4pt}
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{4pt}
-$C_{D}/r_{c}=0/2000\text{m}^{-1}$, \hspace{4pt}
-$b_{ij}^{T}=b_{i}$.
-}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=0$.
-} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
-\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
-$C_{D}/r_{c}=0$, \hspace{6pt}
-$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$.
-}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{\change[HW]{Results of the rising bubble at $t=1000\ \text{s}$.
-Solid lines are the multi-fluid, single column solutions of the rising bubble.
-Dashed lines are the single-fluid, resolved solutions.}
-{As figure \protect\ref{fig:multiFluidSingleColumn-bad} but different parameterisation options.}
-\label{fig:multiFluidSingleColumn}}
+lines are the single-fluid, resolved solutions.
+\label{fig:multiFluidBubble_1000}}
 \end{figure}
@@
 \begin{tabular}{ccccc}
-$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
+$\sigma$
+&
+$\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
 \multicolumn{5}{c}{Horizontal averages of the resolved RCE test case}\tabularnewline
@@
 &
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean}
+&
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}
 \tabularnewline

### 2020-04-06 submit2/makeFigs.sh

@@ -1,0 +1,18 @@
+#!/bin/bash -e
+cd makeFigs
+
+for file in bubble bubble_singleUnderRes multiFluidBubble_500_1 multiFluidBubble_500_2 multiFluidBubble_1000; do
+    echo $file
+    lyx --export pdflatex -f $file
+    pdflatex $file
+    pdf2ps $file.pdf
+    makebb $file.ps
+    mv $file.ps $file.eps
+    pdfcrop $file.pdf $file.cropped.pdf
+    mv $file.cropped.pdf $file.pdf
+    mv $file.eps $file.pdf ../figures
+    gv ../figures/$file.eps &
+done
+
+cd ..
+

### 2020-04-11 submit2/makeFigs/RCE_resolved.tex
First complete draft with Hilary's revisions and responses to reviewers.

--- 2020-03-23 preSubmission/manuscript.tex
@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[12pt,times]{extarticle}
+\documentclass[12pt,british,times]{article}
 \usepackage{mathptmx}
@@
 \usepackage[latin9]{inputenc}
-\usepackage{geometry}
-\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
-\usepackage{array}
-\usepackage{rotating}
-\usepackage{amsmath}
+\usepackage[pdftex,a4paper]{geometry}
+\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
+\pagestyle{empty}
+\setcounter{secnumdepth}{5}
+\setcounter{tocdepth}{5}
+\setlength{\parskip}{\smallskipamount}
+\setlength{\parindent}{0pt}
+\usepackage{amstext}
 \usepackage{amssymb}
-\usepackage{graphicx}
+\usepackage[pdftex]{graphicx}
 \usepackage[authoryear]{natbib}
@@
 \makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage { fancybox}
+\usepackage[pdftex]{graphicx,color}
+\usepackage{rotating}
 \newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
@@
 \usepackage[export]{adjustbox}
-
-\usepackage{todonotes}
-%\usepackage{afterpage}
-
-%\usepackage[switch]{lineno}
-
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
-
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-%\usepackage{moreverb}
-
-\usepackage{flushend}
+\usepackage{amsmath}
 
@@
 
+\usepackage{babel}
 \begin{document}
-
-\title{Multi-fluids for Representing Sub-filter-scale Buoyant Convection}
-
-\author{Hilary Weller, William McIntyre, Daniel Shipley and Peter Clark}
-\maketitle
-\begin{abstract}
-Multi-fluid modelling is a promising new method of representing sub
-and near grid-scale convection allowing for consistent and accurate
-treatment of net mass transport by convection, non-equilibrium and
-turbulence. The air is partitioned into convecting and non-convecting
-fluids each with their own velocity, temperature and constituents
-so that separate equations of motion can be solved for each fluid,
-thus representing features that cannot be resolved in a single fluid
-at coarse resolution.
-
-This paper presents multi-fluid Boussinesq equations for representing
-under resolved dry convection. We present a new model for entrainment
-and detrainment based on divergence which leads to excellent representation
-of the convective area fraction. Previous multi-fluid modelling of
-convection has assumed that all fluids share the same pressure. We
-show that this is a bad assumption and we propose and validate a model
-for the pressure difference between the fluids based on divergence.
-
-Two vertical slice test cases are used to validate the multi-fluid
-model; a buoyant rising bubble and radiative convective equilibrium
-are simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity. The multi-fluid model reproduces
-the mean properties of the rising and falling fluids in a single column. 
-\end{abstract}
-
-\section{Introduction}
-
-Slow progress has been made improving the parameterisation of sub-grid-scale
-convection since \citet{AS74,Tied89,GR90,KF90}. Convection is still
-one of the weakest aspects of large scale models of the atmosphere
-\citep{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
-the quasi-equilibrium assumption \citep{PR98,GG05,Par14}, including
-stochasticity \citep{PC08} and allowing net mass transport by convection
-\citep{KB08,MB19}. These developments have enabled limited simulation
-in the grey zone, where convection is partially resolved. However
-there are still systematic biases implying that improvements should
-still be possible.
-
-\citet{TWV+18} proposed multi-fluid modelling of convection in order
-to treat non-equilibrium and net mass transport correctly and consistently
-with the same numerics and physics controlling thermals, the stable
-environment and downdraught dynamics. \citet{Yano14} derived similar
-equations for multiple segments and showed how this is a generalisation
-of the mass-flux formulation. The \citet{TKP+18} ``extended eddy
-diffusivity mass flux'' or extended EDMF scheme also uses similar
-equations but \citet{TKP+18} didn't propose a suitable numerical
-method for solving the equations. Multi-fluids promises big improvements
-in the representation of sub-grid-scale convection and unification
-with the representation of turbulence, particularly at the grey zone.
-However, there is a long way to go, particularly as multi-fluids requires
-a dedicated model rather than being a stand alone parameterisation
-for a dynamical core. \citet{TEB19} and \citet{WM19} presented solutions
-of the multi-fluid equations assuming two fluids that share the same
-pressure (or that pressure differences are predominantly due to drag
-between the fluids). \citet{TEB19} showed that these equations (without
-drag) are in fact unstable and can be stabilised by diffusion of vertical
-velocity whereas \citet{WM19} stabilised the equations with diffusion
-and drag between fluids. Neither of these stabilisation techniques
-are acceptable and in this paper we show that there are significant
-and sustained pressure differences between the fluids (section \ref{sec:results}).
-
-This paper presents the multi-fluid Boussinesq equations for representing
-sub-grid-scale convection including a parameterisation of the pressure
-difference between fluids (section \ref{subsec:fluidPressure}) and
-a new model of entrainment and detrainment (section \ref{subsec:Sij}).
-The numerical method for solving the equations is described in section
-\ref{sec:numerics}. We compare results of resolved dry convection
-in a single-fluid two dimensional Boussinesq model with a two-fluid,
-single column model in section \ref{sec:results} using two vertical
-slice test cases.
-
-\section{The Multi-fluid Boussinesq Equations}
-
-Many of the challenges of representing convection with the multi-fluid
-Navier-Stokes equations \citep[eg those described in][]{WM19} carry
-over to the Boussinesq equations; convection is buoyancy dominated
-and close to incompressible. The resolved test cases presented in
-section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore for simplicity we focus on the
-multi-fluid Boussinesq equations without background stratification:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\} \label{eq:sigma}\\
-\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\} \label{eq:mom}\\
-\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}\\
-\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
-\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
-\end{eqnarray}
-with variables defined in table \ref{tab:defns}.
-
-\begin{table}[h]
-\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
-$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
-$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
-$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
-$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
-$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
-where $\rho^{\prime}$ are departures in density from a horizontally
-uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
-$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
-$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
-$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-\end{tabular}
-
-\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
-\end{table}
-
-\subsection{Pressure of each fluid \label{subsec:fluidPressure}}
-
-\citet{TEB19} and \citet{WM19} assumed that each co-located fluid
-shared the same pressure, leading to unstable equations that \citet{TEB19}
-stabilised using diffusion of vertical velocity and \citet{WM19}
-stabilised using mass exchanges or drag between the fluids. \citet{TEB19}
-achieved realistic results in single column experiments of convective
-boundary layer but the amount of diffusion needed would spoil simulations
-in the free troposphere. The stabilisation used by \citet{WM19} meant
-that the two fluids tended to move as one which defeats the purpose
-of using multi-fluid modelling.
-
-The instabilities reported by \citet{WM19} showed growing divergence
-in a fluid with vanishing volume fraction. It is mass convergence
-rather than velocity convergence that leads to pressure anomalies
-that remove the convergence. Therefore if the volume (or mass) fraction
-of fluid is vanishingly low then convergence cannot lead to an anomaly
-in the total pressure.
-
-We will assume that pressure in each fluid is given by a parameterised
-perturbation, $p_{i}$, from the total pressure, $P$:
-\begin{equation}
-P_{i}=P+p_{i}.
-\end{equation}
-
-\citet{BN86} proposed a parameterisation for pressure differences
-in a multi-phase explosion model that has been widely used in mathematics
-and engineering for simulating fluidised beds of granular material
-\citep[eg.][]{EHM92} and two compressible fluids \citep[eg.][]{SA99}.
-In these methods, advection equations are written for the volume fraction,
-$\sigma_{i}$, and conservation equations are written for mass fraction,
-$\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
-fluids, the \citet{BN86} equations would be:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)\label{eq:BNcompaction}\\
-\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0\label{eq:rhoTransport}
-\end{eqnarray}
-where $\mathbf{V}$ is the velocity of the interface between fluids,
-$\mu$ is the compaction viscosity which controls how quickly the
-pressure of each fluid relaxes to the mean pressure and index $j$
-refers to the other fluid in a two fluid system. In our Boussinesq
-system $\rho_{i}$ does not appear in the continuity equation. Different
-authors make different assumptions about the interface velocity but
-if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
-$\rho_{i}$ is constant then eqns (\ref{eq:divFree}-\ref{eq:rhoTransport})
-imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
-If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
-we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.
-
-\citet{TEB19} stabilised the multi-fluid equations by adding a diffusion
-term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
-If a fluid perturbation pressure is set to $-\nu\partial w/\partial z$
-this is equivalent to the diffusion term in one dimension. However
-adding a diffusion term will harm three dimensional simulations of
-resolved convection in the free troposphere whereas adding a fluid
-perturbation pressure will not. Inspired by both \citet{BN86} and
-\citet{TEB19} we assume that the pressure in each fluid is given
-by:
-\begin{equation}
-p_{i}=-\gamma\nabla\cdot\mathbf{u}_{i}\label{eq:Pi_div}
-\end{equation}
-where $\gamma$ is a free coefficient. Dimensional analysis in section
-\ref{subsec:dimAnal} will inform the choice of $\gamma$ and sensitivity
-to $\gamma$ will be evaluated in section \ref{sec:results}.
-
-\subsection{Entrainment and Detrainment \label{subsec:Sij}}
-
-We consider dry air without turbulence so use the dynamic entrainment
-described by \citet{HC51,AK67,DBF+13}:
-\begin{equation}
-S_{ij}=\begin{cases}
--\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
-0 & \text{otherwise}
-\end{cases}
-\end{equation}
-which is necessary to stop air in one fluid from accumulating when
-vertical motion ceases (at the top of a rising plume or at the bottom
-of descending air). We will also test a common form of lateral entrainment
-\citep{DBF+13}:
-\begin{equation}
-\varepsilon=\frac{0.2}{r_{c}}\implies S_{01}=w_{1}\frac{0.2}{r_{c}}
-\end{equation}
-where $\varepsilon$ is the well know fractional entrainment rate
-and $r_{c}$ is the cloud or plume radius.
-
-\subsection{Drag in the Momentum Equation\label{subsec:drag}}
-
-Pressure differences between the fluids can lead to form drag which
-is parameterised following \citet{SW69,RC15,WM19} as: 
-\begin{equation}
-\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
-\end{equation}
-where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
-Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.
-
-\subsection{The Buoyancy and the Momentum of the Mass that is Transferred \label{subsec:transferProperties}}
-
-The different fluids may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \citep[as was assumed by][]{WM19}.
-In fact, the most buoyant air should be transferred from fluid 0 to
-fluid 1 and vice versa, and the air with least downward momentum should
-be transferred from 0 to 1 and vice versa. The properties of the fluids
-transferred should depend on the modelling of sub-grid-scale variability
-which is beyond the scope of this paper. In section \ref{sec:results}
-we conditionally average high resolution solutions based on the sign
-of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
-Therefore the air that is transferred at the interface will have $w=0$.
-For two dimensional multi-fluid simulations we assume that the horizontal
-velocity transferred is equal to the mean horizontal velocity of the
-fluid transferred from. Therefore
-\begin{equation}
-\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
-v_{i}\\
-0
-\end{pmatrix}.
-\end{equation}
-For buoyancy, following \citet{TEB19}, we use:
-\begin{equation}
-b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
-\end{equation}
-and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
-Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
-transferred depends on the properties of the receiving fluid which
-is not logical and can lead to unbounded values of $b_{i}$ in the
-fluid that is loosing mass (as demonstrated in section \ref{sec:results}).
-
-\subsection{Dimensional Analysis\label{subsec:dimAnal}}
-
-Dimensional analysis can guide our choice of $\gamma$ for the parameterisation
-of the pressure difference between fluids. We make the following assumptions:
-\begin{enumerate}
-\item The flow is buoyancy dominated.
-\item The flow is close to inviscid.
-\item The flow is slowly varying.
-\item Fluid $i$ properties are anomalies from a neutrally stable resting
-mean state.
-\item We consider only the vertical direction where $w_{ij}^{T}=0$.
-\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
-\item There are two fluids, $i$ and $j$
-\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
-and $S_{ji}=0$.
-\end{enumerate}
-This leads to the following balance in the momentum equation:
-\begin{equation}
-\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
-\end{equation}
-We non-dimensionalise using a length scale $L$, a buoyancy scale
-$B$ and a time scale $T$ to get the non-dimensional variables:
-\begin{eqnarray*}
-\tilde{w} & = & w_{i}T/L\\
-\tilde{b} & = & b_{i}/B\\
-\tilde{z} & = & z/L.
-\end{eqnarray*}
-Then the non-dimensional version of (\ref{eq:wi_balances}) is:
-\begin{equation}
-\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
-\end{equation}
-The flow is buoyancy dominated so the buoyancy term should be $O(1)$
-so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
-so the non-dimensional momentum equation becomes:
-\begin{equation}
-\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
-\end{equation}
-The stabilisation term must be large enough to smooth out oscillations
-in $\tilde{w}$ due to advection and buoyancy but not too large to
-remove all variability in $\tilde{w}$ so we need:
-\begin{equation}
-\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
-\end{equation}
-
-\section{Numerical Solution \label{sec:numerics}}
-
-The spatial discretisation follows exactly \citet{WM19}, solving
-advective form equations using monotonic, finite volume advection
-and C-grid, Lorenz staggering. The time-stepping is Crank-Nicolson
-with no off-centering and with deferred correction of explicitly solved
-variables. It differs from \citet{WM19} because here we solve the
-Boussinesq equations and we need stable solutions for equations with
-a separate pressure in each fluid. We use two outer iterations per
-time step to update explicitly solved variables. For the first outer
-iteration, predicted values for time $n+1$ are set to those from
-time level $n$ and are given the superscript $\ell$. For the second
-iteration, values at $\ell$ are set to those from the end of the
-first iteration. The implicit numerical method for applying the transfers
-between fluids is specific for two fluids because it involves the
-inversion of $2\times2$ matrices.
-
-The prognostic variables are the $b_{i}$ in cell centres, the $\sigma_{i}$
-in cell centres and the velocity flux at cell faces, $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$,
-which is the velocity at cell faces dotted with the area vector for
-each face (normal to the face). The pressures, $P$ and $p_{i}$ are
-diagnostic.
-
-The first equation to be solved each outer iteration is eqn (\ref{eq:sigma})
-for each $\sigma_{i}$, operator split; first applying advection,
-then correcting $\sum_{i}\sigma_{i}=1$ and then applying mass transfers:
-\begin{eqnarray}
-\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\} \\
-\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}\\
-S_{ij} & = & \begin{cases}
--\nabla\cdot\mathbf{u}_{i}^{\ell} & \text{if }\nabla\cdot\mathbf{u}_{i}^{\ell}<0\\
-0 & \text{otherwise}
-\end{cases}\\
-\sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
-\end{eqnarray}
-where $\Delta t$ is the time step and the superscripts $\prime$
-and $\prime\prime$ denote intermediate values. $\sigma_{i}^{n}$
-is interpolated from cell centres onto cell faces using monotonic
-van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citet{WM19}
-and values exclusively at time level $n$ for best accuracy and guaranteed
-monotonicity. For calculating the divergence, the normal component
-of $\mathbf{u}_{i}$ is needed at cell faces which are prognostic
-variables of the C-grid. The $S_{ij}$ are limited to ensure $0<\sigma_{i}<1\ \forall i$.
-
-Next eqn (\ref{eq:b}) is solved for the buoyancy in each fluid, first
-transporting buoyancy and then applying the transfer terms. The transfer
-terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
-in the transfer term for $b_{i}$ so they are treated operator split
-and implicitly:
-\begin{eqnarray}
-b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
- &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
-b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
-b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
-\end{eqnarray}
-where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
-from before the mass transfers is necessary to ensure bounded and
-conservative transfers, as described by \cite{MWH1x}. Simultaneous
-solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
-\begin{eqnarray}
-b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
-b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
-\end{eqnarray}
-where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$
-
-Next a Poisson equation is solved to calculate the total pressure,
-$P$ to ensure that the total velocity is divergence free. The pressure
-equation also provides updates for the velocity flux, $u_{i}$. First
-an intermediate velocity flux is calculated with partial updates and
-updates from a previous value of $p_{i}$:
-\begin{eqnarray}
-u_{i}^{\prime}= & u_{i}^{n}+\frac{\Delta t}{2} & \biggl(\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{\ell}\cdot\mathbf{S}-\nabla_{f}p_{i}^{\ell}\\
- &  & +\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{n}\cdot\mathbf{S}-\nabla_{f}(P+p_{i})^{n}\biggr)
-\end{eqnarray}
-where operator $()_{f}$ means linear interpolation from cell centres
-onto cell faces and $\nabla_{f}P$ is a compact discretisation of
-$(\nabla P)_{f}\cdot\mathbf{S}$: ie the normal component of the pressure
-gradient calculated from just the values of pressure either side of
-the face. Once we have calculated $P^{n+1}$, the velocity flux (without
-momentum transfers) is updated from the back-substitution:
-\begin{equation}
-u_{i}^{\prime\prime}=u_{i}^{\prime}-\frac{\Delta t}{2}\nabla_{f}P^{n+1}.\label{eq:backSub}
-\end{equation}
-The Poisson equation for $P^{n+1}$ is found by multiplying each eqn
-(\ref{eq:backSub}) by $\sigma_{i}$, summing over all fluids and
-taking the divergence. Knowing that $\nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0$,
-$\sum_{i}\sigma_{i}=1$ and $\sum_{i}\sigma_{i}p_{i}=0$ gives:
-\begin{equation}
-\nabla\cdot\sum_{i}\sigma_{i}u_{i}^{\prime}-\frac{\Delta t}{2}\nabla^{2}P^{n+1}=0
-\end{equation}
-which is solved to find $P^{n+1}$.
-
-Next, the momentum transfers due to mass transfer and due to drag
-are calculated implicitly, similar to the implicit transfers of buoyancy,
-calculating $u_{i}^{n+1}$ from $u_{i}^{\prime\prime}$. These do
-not influence the total $P$ or total divergence because momentum
-is transferred conservatively. However they do influence $p_{i}$
-which is why they are calculated before $p_{i}$. The final stage
-of the time step iteration is to solve Helmholtz equations for each
-$p_{i}$:
-\begin{equation}
-\sigma_{i}^{n+1}p_{i}^{n+1}=-\gamma\nabla\cdot\left(\sigma_{if}^{n+1}u_{i}^{n+1}-\frac{\Delta t}{2}\sigma_{if}^{n+1}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right).\label{eq:pi_Helm}
-\end{equation}
-Both $p_{i}^{n+1}$ and $p_{i}^{\ell}$ appear in eqn (\ref{eq:pi_Helm})
-because $u_{i}^{n+1}$ already contains contributions from $p_{i}^{\ell}$
-so these are removed before updating $p_{i}^{n+1}$. No back substitution
-for $u_{i}$ is done after calculating $p_{i}^{n+1}$ because this
-would destroy the divergence free constraint. Therefore $p_{i}^{n+1}$
-only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
-converge and $p_{i}^{\ell}=p_{i}^{n+1}$.
-
-The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
-from $u_{i}$ following \citet{WM19}. The stages calculating $P$,
-$p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
-The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$.
-
-\section{Validation Test Cases\label{sec:results}}
-
-Two test cases are developed to tune parameters and to validate the
-use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
-convection. The first is transient; the standard rising bubble of
-\citet{BF02}. We aim to reproduce the vertical heat transport, the
-mean velocity of the rising air, the bouyancy of the rising air and
-pressure differences between two fluids in a single column two fluid
-model. The second test case is steady state with heat transfer at
-the ground and uniform radiative cooling. For both test cases the
-reference solution is a single fluid solution of the two-dimensional
-Boussinesq equations at high horizontal and vertical resolution.
-
-\subsection{Rising Bubble}
-
-The test case of \citet{BF02} was designed for fully compressible
-models but similar solutions are obtained solving Boussinesq equations.
-The Boussinesq version has no background stratification in a domain
-of height 10\,km and width 20\,km initially at rest. The buoyant
-perturbation is given by:
-\begin{equation}
-b=\frac{1}{15}\cos^{2}\frac{\pi L}{2}\label{eq:thetaPerturb}
-\end{equation}
-for $L<1$ where $L=\sqrt{\left(\frac{x-x_{c}}{x_{r}}\right)^{2}+\left(\frac{z-z_{c}}{z_{r}}\right)^{2}}$,
-$x_{c}=10\ \text{km}$, $z_{c}=2\ \text{km}$ and $x_{r}=z_{r}=2\ \text{km}$.
-100\,m grid spacing is used in the $x$ and $z$ directions for the
-two dimensional reference simulation and $\Delta z=100\ \text{m}$
-is used in the vertical for the single column simulations. All simulations
-use a time-step of 2\,s.
-
-\subsubsection{Single Fluid Solutions}
-
-The solution of the rising buoyant bubble solving the Boussinesq equations
-for 1000s is shown in figure \ref{fig:bubble} with buoyancy coloured,
-pressure contoured and the $w=0$ contour dotted. The solution is
-very similar to the fully compressible solution \citep{BF02}. The
-pressure gradients accelerate the flow beneath the bubble, decelerate
-the flow above the bubble and pull in air horizontally. Horizontally
-and conditionally averaged fields, conditioned on $w$, are shown
-in the top row of figure \ref{fig:bubble_singleUnderRes}. $\sigma_{1}$
-is the volume fraction of rising fluid at every height, $b_{0}$ and
-$b_{1}$ are the buoyancy conditioned on $w\le0$ and $w>0$, $w_{0}$
-and $w_{1}$ are the horizontal averaging rising and falling vertical
-velocity and $P_{0}$ and $P_{1}$ are the pressure of the rising
-and falling fluid. An accurate multi-fluid model of convection should
-reproduce these fields approximately at coarser horizontal resolution
-or in a single column model.
-
-\begin{figure}
-\noindent \begin{centering}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
-\par\end{centering}
-\noindent \begin{centering}
-\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
-\par\end{centering}
-\caption{The single fluid, resolved rising bubble after 1000s. Buoyancy is
-coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
-negative contours dashed. The $w=0$ contour is dotted. \label{fig:bubble}}
-\end{figure}
-
-\citet{TEB19} and \citet{WM19} assumed that both fluids would share
-the same pressure with differences parameterised as drag. The pressure
-in figure \ref{fig:bubble} shows that this is a bad assumption since
-the large pressure anomalies are in the rising fluid. Drag would always
-act to slow down the fluids whereas the negative pressure gradients
-in the rising fluid just below the bubble are acting to accelerate
-the rising motion.
-
-The horizontal averages are shown in figure \ref{fig:bubble_singleUnderRes}
-for horizontal resolutions of nine columns, five columns, three columns
-and a single column all for the 20km wide domain and all still using
-$\Delta z=100\ \text{m}$. These simulations are initialised by conservative
-horizontal averaging from the full resolution solution. As the horizontal
-resolution is reduced, the vertical transport reduces until there
-is no movement at all for a single column: there is no possibility
-of fluid rising because in a single column with a single fluid there
-can be no compensating subsidence. The lack of vertical transport
-at coarse resolution motivates convection parameterisation.
-
-\begin{figure}
-\noindent %
-\begin{tabular}{ccccc}
-\begin{turn}{90}
-200 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-9 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-5 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-3 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-1 Column
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
-\end{tabular}
-
-\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
-and a single fluid. Horizontal averages are conditioned based on $w$.
-\label{fig:bubble_singleUnderRes}}
-\end{figure}
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-Multi-fluid, single column simulations are initialised by horizontally
-and conditionally averaging the high resolution single fluid initial
-conditions. Sinking air is put into fluid zero and rising air into
-fluid one. The velocity field after one time step is used for initialisation
-as the air is stationary at $t=0$. Results are shown in figures \ref{fig:multiFluidSingleColumn-bad}
-and \ref{fig:multiFluidSingleColumn} for various assumptions about
-transfers between fluids and various parameter values.
-
-\begin{figure}
-\begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
-\end{figure}
-
-\begin{figure}
-\begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=1/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{01}=w_{1}0.2/r_{c}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=0$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.25\columnwidth}%
-$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions.\label{fig:multiFluidSingleColumn}}
-\end{figure}
-
-If there is no drag between fluids, no transfers, no diffusion and
-the pressures of both fluids are assumed equal then the multi-fluid
-equations are unstable \citep{TEB19}. The simulation with ($S_{ij}=0$)
-in the top row of figure \ref{fig:multiFluidSingleColumn-bad} actually
-has small transfers to prevent either $\sigma_{i}$ from becoming
-negative. This is sufficient to stabilise the solution but does not
-prevent oscillations from developing in all fields. The buoyant fluid
-has risen very little from the initial conditions. $\sigma$ oscillates
-between zero and one meaning that only one fluid is present at some
-locations so there is no possibility for the fluids to move past each
-other.
-
-Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-stabilises the solution and enable the fluids to move past each other
-even without pressure differences between the fluids (second row of
-figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
-detrained from fluid 1, fluid 1 looses too much buoyancy and a discontinuity
-arises at the bubble leading edge; the buoyancy force is producing
-vertical motion but there is no pressure to make it smooth.
-
-Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
-and pressure difference between the fluids controlled by divergence
-($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
-realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
-Three values of $\gamma$ are tested. $\gamma$ is set from equation
-(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
-radius and a buoyancy scale equal to the initial maximum buoyancy
-to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
-(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
-the velocity profile too smooth and the updraught too weak so the
-bubble does not rise enough. It is reasonable to consider smaller
-values of $\gamma$ because the buoyancy does not retain its initial
-maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
-gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
-leads to the leading edge of the bubble rising too quickly. Smaller
-values of $\gamma$ leave a discontinuity in the updraught velocity
-at the leading edge of the bubble and larger values of $\gamma$ reduce
-the velocity further, meaning that the bubble does not rise enough
-(not shown). None of the values of $\gamma$ reproduce the peak updraught
-velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
-meaning that the bubble rise and $\sigma_{1}$ are approximately correct
-and pressure increases above the centre of the bubble are realisitic.
-The large low pressure at the bottom of the bubble is not reproduced.
-This is located at the lobes of the highest buoyancy in the resolved
-simulation (figure \ref{fig:bubble}). It would be tempting to model
-this by assuming hydrostatic pressure or the Bernouilli equation,
-but these are both forms of the momentum equation which is used to
-calculate the velocity and so cannot also be used to model the pressure.
-
-The results in the top row of figure \ref{fig:multiFluidSingleColumn}
-use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
-this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
-drag slows the updraughts without increasing the mixing between the
-fluids which makes the solutions less like the resolved simulations.
-Although drag is known to be an important term in the momentum equations
-for buoyant thermals and plumes \citep[eg][]{RC15}, the drag is related
-to mixing with downdraught air which is accounted for in the entrainment
-term of the momentum equation. So adding a separate term from drag
-risks double counting and slows the plume too much.
-
-If we include pressure difference between fluids with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$but
-omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidSingleColumn})
-the fluids move past each other but there is an unrealistic discontinuity
-with no fluid 1 below the buoyant fluid and very little falling air
-at the lowest height of the rising fluid. With a single column and
-two fluids, all air must rise in one fluid and sink in the other.
-Continuity does not allow for any other solution. Pressure gradients
-can accelerate or decelerate this flow but as the model is set up,
-with no transfers between fluids, no fluid can change direction. It
-is therefore essential to have transfers between fluids.
-
-The other entrainment option is the commonly used fractional entrainment
-rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
-differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
-This combination produces smooth solutions but the updraught is too
-weak and too much is entrained into fluid 1. Using this entrainment,
-the updraught will entrain more and more air until $\sigma_{1}=1$.
-The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
-entrainment and detrainment for this test case using conditional averaging
-based on $w$.
-
-Two alternative models for estimating the buoyancy of the fluid transferred
-between updraught and downdraught have been tested. The results in
-the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
-that the fluid transferred has zero buoyancy in order to keep the
-positively buoyant air in fluid one and the negatively buoyant air
-in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
-the mean buoyancy of fluid one increases. This leads to very high
-buoyancy in fluid one which is not present in the resolved simulation.
-The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
-use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citet{TEB19}
-so that the fluid transferred is influenced by the fluid it is moving
-towards as well as where it has come from. This again leads to very
-large buoyancy in fluid one and also negative buoyancy in fluid zero
-which should not occur for this test case. These simple models reinforce
-the idea that the buoyancy of the fluid transferred should depend
-on knowledge of sub-grid-scale variability of $b$ within each fluid
-\textendash{} these simple assumptions can lead to unrealistic behaviour.
-The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
-fluid transferred takes the mean properties with it.
-
-This section has demonstrated the value of using a single column,
-multi-fluid model to simulate a buoyant rising bubble with a single
-updraught fluid and a single downdraught fluid. Transfers between
-the fluids have been successfully modelled using entrainment set by
-divergence giving realistic updraught fractions. Entrainment calculated
-as the reciprocal of plume width was not successful. The pressure
-difference between the fluids has also been represented by divergence
-with a coefficient close to that expected from dimensional analysis.
-Including drag between the fluids did not improve simulations. Two
-models of transferring non-mean properties between fluids were tested
-but neither was plausible. There are clearly discrepancies between
-the single fluid resolved rising bubble and the two fluid single column
-rising bubble but we do not want to over fit the multi-fluid model
-to one, dry, two dimensional test case.
-
-\subsection{Radiative-Convective Equilibrium (RCE)}
-
-A two-dimensional, dry radiative convective equilibrium test case
-is devised to mimic some properties of atmospheric convection, in
-particular the difficulty resolving the flow at coarse resolution.
-The domain is 160km wide, 10km tall and is resolved by 640 cells in
-the horizontal and 40 in the vertical ($\Delta x=\Delta z=250$m).
-The top and bottom boundaries are zero velocity and the lateral boundaries
-are periodic. A heat flux of $h=10^{-3}\text{m}^{2}\text{s}^{-3}$
-is imposed at the bottom boundary leading to a boundary condition
-of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
-is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
-Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
-so as to give a Plank constant of $0.707$. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$
-is applied to the domain to maintain equilibrium.
-
-The fluid is initially stationary with $b=0$. In order to quickly
-and reproducibly initialise instability, $b=10^{-4}\text{m}^{2}\text{s}^{-1}$
-is imposed in a square of side length 2000m at the centre in the $x$
-direction and at the ground. The simulation is run using a time step
-of $5\ \text{s}$. A quasi-steady, choatic state is reached after
-about $3\times10^{4}\text{s}$ and the simulation is run for $2\times10^{5}\text{s}$
-and conditional averages are calculated over the final $10^{5}$s.
-
-\subsubsection{Single Fluid Solutions}
-
-This test case is designed to have strong updraughts in narrow plumes
-and weak descent elsewhere to mimic atmospheric convection but without
-the complication of moisture, phase changes and three spatial dimensions.
-A snapshot of the buoyancy, vertical velocity and pressure of the
-radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
-are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
-updraughts. The buoyant air at the ground rises in narrow plumes,
-accelerating due to buoyancy and pressure gradients then decelerating
-due to pressure gradients before reaching the top. The plumes spread
-out and the sinking air is a mixture of warm and cold with similar
-pressure gradients in the rising and falling air, accelerating then
-decelerating the flow so as to maintain continuity.
-
-\noindent 
-\begin{figure}
 \includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/bw}
@@
 Pressure ($\text{m}^{2}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/Pw_P}
-
-\caption{Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
-of the resolved radiative-convective equilibrium test case. Vertical
-velocity contours are black every 0.5m/s with negative contours dashed
-and the zero contour dotted. The domain is 10km high and 160km wide
-and the z-direction is stretched a factor of 2 in the plots. \label{fig:RCE_resolved}}
-\end{figure}
-
-Horizontal averages conditioned on $w$ and time averaged every 1000s
-between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
-in the top row of figure \ref{fig:RCE_singleColumn}. The rising and
-falling volume fractions, $\sigma_{1}$ and $\sigma_{0}$, remain
-close to $\frac{1}{2}$ throughout the depth. The rising plumes look
-narrow in figure \ref{fig:RCE_resolved} but there are wide regions
-of slowly rising air around the plume cores. The entrained rising
-cool air and warm air sinking that has hit the model top mean that
-the rising and falling air have similar average buoyancy away from
-the ground. The ascending air gradually accelerates towards the middle
-of the domain then decelerates towards the model top. At the ground
-the acceleration is forced by buoyancy and away from the ground the
-acceleration is controlled by pressure gradients. The descending air
-mean velocity is close to equal and opposite to the ascending air,
-as expected since $\sigma_{1}=0.5$.
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-The two fluid model is used to simulate the RCE test case in a single
-column of 40 cells with zero buoyancy gradient at the top and a buoyancy
-gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
-and uniform radiative cooling. The two fluids are initialised using
-the time mean conditional horizontal averages from the single fluid
-resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-is used for all simulations to account for transfers throughout the
-domain to represent cloud base mass flux (at the bottom boundary),
-cloud top detrainment and lateral entrainment. $\gamma$ is set from
-equation (\ref{eq:gammaDimAnal}) using the depth of the super adiabatic
-layer as the length scale ($L=800\text{m}$) and the buoyancy scale
-$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
-giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. A simulation using
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
-is shown in the second row of figure \ref{fig:RCE_singleColumn}.
-The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
-at about 0.5 throughout the depth, as in the resolved simulation,
-with entrainment in the lower half of the domain ($S_{01}>0$) and
-detrainment in the upper half ($S_{10}>0$), where the air decelerates
-towards the top. The single column model reproduces the super-adiabatic
-layer near the ground and the near uniform buoyancy away from the
-ground but the buoyancy difference between the fluids is too large.
-The updraught and downdraught velocities are captured well. The pressure
-differences between fluids are too large which is consistent with
-the over estimated buoyancy difference between fluids.
-
-Results of a simulations using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
-is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
-This model of the buoyancy of the transferred fluid is bad; it leads
-to strong cooling in fluid zero near the ground due to the large transfers.
-It is more accurate to assume that fluids take their mean properties
-when transferred, $b_{ij}^{T}=b_{i}$.
-
-\noindent 
-\begin{figure}
-\setlength\tabcolsep{0.5pt}%
-\begin{tabular}{ccccc}
-$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
-\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case between $t=10^{5}\text{s}$
-and $2\times10^{5}\text{s}$}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=b_{i}$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/P_1}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/P_1}\tabularnewline
-\end{tabular}
-
-\caption{Results of the RCE simulations. The top row shows horizontal averages
-of the resolved case between $t=10^{5}$s and $2\times10^{5}$s. The
-bottom two rows show results of the single column multi-fluid model
-after $10^{4}\ \text{s}$. \label{fig:RCE_singleColumn}}
-\end{figure}
-
-\section{Summary, Conclusions and Further Work}
-
-This paper presents solutions of the multi-fluid Boussinesq equations
-for convection, reproducing aspects of highly resolved dry convection
-at coarse horizontal resolution. Two test cases are used to validate
-the multi-fluid model. The first is a Boussinesq version of the well
-known two dimensional dry rising bubble of \citet{BF02} and the second
-is a dry two dimensional version of radiative-convective equilibrium
-with heating at the ground and uniform radiative cooling. High resolution
-single fluid simulations are conditionally averaged based on the sign
-of vertical velocity ($w$) in order to create rising and falling
-fluids which each have their own mean buoyancy, velocity and pressure.
-The two-fluid, single column Boussinesq model reproduces mean vertical
-heat and mass transport of these test cases.
-
-The multi-fluid Boussinesq equations can have divergence in each fluid
-while the divergence averaged over all fluids is zero. A model is
-proposed and validated for the pressure difference between the rising
-and falling fluids based on the divergence of each fluid. The use
-of a different pressure for each fluid is not only realistic but also
-leads to stable solutions of the multi-fluid equations.
-
-Conditionally averaging the high resolution solutions based on $w$
-leads to convecting and non-convecting regions with area fractions,
-$\sigma_{i}$, which are approximately uniform with height. Models
-for entrainment and detrainment into and out of convecting regions
-must clearly be consistent with the definition of the convecting region.
-We propose a model for entrainment and detrainment based on divergence
-that leads to excellent agreement with $\sigma$ from the high resolution
-solutions. We also test a more conventional fractional entrainment
-rate based on the reciprocal of the plume width which leads to unrealistic
-convecting area fractions.
-
-A set of unknowns in the multi-fluid equations are the properties
-of the fluid that are transferred from one fluid to another. An obvious
-first guess would be that fluid takes its mean buoyancy and velocity
-with it when it is transferred. However sub-grid-scale variability
-of each fluid means that we expect that the most buoyant fluid will
-be transferred to the rising fluid or the fluid with the largest vertical
-velocity will be transferred to the rising fluid and vice versa. An
-accurate estimate of these would depend on knowledge of the sub-grid-scale
-variability of each fluid which we do not have. Instead we assume
-that the fluid transferred in each direction has zero vertical velocity
-which is consistent with our conditional averaging. We have tested
-three models for the buoyancy of the fluid transferred. The most successful
-is to assume that the fluid takes its mean buoyancy with it. Assuming
-that the buoyancy of the transferred fluid is an average of the buoyancy
-of both fluids can lead to unrealistically large or small, unbounded
-buoyancies. Similarly, if we assume that one fluid has negative buoyancy
-and the other positive buoyancy and we transfer fluid of zero buoyancy,
-then unbounded buoyancy can occur. A better model of the buoyancy
-of the fluid transferred would rely on more information the sub-grid-scale
-variability.
-
-Single column multi-fluid modelling with moisture has already been
-demonstrated by \citet{TEB19}. Two important next steps are to simulate
-convection in the grey zone (where it is partially resolved) and to
-represent sub-grid-scale variability within each fluid by solving
-multi-fluid prognostic equations for turbulent kinetic energy and
-other moments of the sub-grid variability. These can be used to inform
-cloud base mass flux (since only the most buoyant fluid will transfer
-from the stable environment to the buoyant plume) and inform models
-of the properties of the fluid that is transferred. This will lead
-to a unified parameterisation of turbulence and convection and will
-take multi-fluid modelling of convection beyond existing paradigms.
-
-\section*{Acknowledgements}
-
-Many thanks to John Thuburn and Chris Holloway for valuable discussions.
-Thanks to the NERC/Met Office Paracon project. We acknowledge funding
-from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1.
-
-\bibliographystyle{abbrvnat}
-\bibliography{numerics}
-
 \end{document}

### 2020-04-11 submit2/makeFigs/RCE_singleColumn.tex
First complete draft with Hilary's revisions and responses to reviewers.

--- 2020-03-23 preSubmission/manuscript.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage { fancybox}
+\usepackage[pdftex]{graphicx,color}
+\usepackage{rotating}
 \newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
@@
 
+\usepackage{babel}
 \begin{document}
-
-\title{Multi-fluids for Representing Sub-filter-scale Buoyant Convection}
-
-\author{Hilary Weller, William McIntyre, Daniel Shipley and Peter Clark}
-\maketitle
-\begin{abstract}
-Multi-fluid modelling is a promising new method of representing sub
-and near grid-scale convection allowing for consistent and accurate
-treatment of net mass transport by convection, non-equilibrium and
-turbulence. The air is partitioned into convecting and non-convecting
-fluids each with their own velocity, temperature and constituents
-so that separate equations of motion can be solved for each fluid,
-thus representing features that cannot be resolved in a single fluid
-at coarse resolution.
-
-This paper presents multi-fluid Boussinesq equations for representing
-under resolved dry convection. We present a new model for entrainment
-and detrainment based on divergence which leads to excellent representation
-of the convective area fraction. Previous multi-fluid modelling of
-convection has assumed that all fluids share the same pressure. We
-show that this is a bad assumption and we propose and validate a model
-for the pressure difference between the fluids based on divergence.
-
-Two vertical slice test cases are used to validate the multi-fluid
-model; a buoyant rising bubble and radiative convective equilibrium
-are simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity. The multi-fluid model reproduces
-the mean properties of the rising and falling fluids in a single column. 
-\end{abstract}
-
-\section{Introduction}
-
-Slow progress has been made improving the parameterisation of sub-grid-scale
-convection since \citet{AS74,Tied89,GR90,KF90}. Convection is still
-one of the weakest aspects of large scale models of the atmosphere
-\citep{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
-the quasi-equilibrium assumption \citep{PR98,GG05,Par14}, including
-stochasticity \citep{PC08} and allowing net mass transport by convection
-\citep{KB08,MB19}. These developments have enabled limited simulation
-in the grey zone, where convection is partially resolved. However
-there are still systematic biases implying that improvements should
-still be possible.
-
-\citet{TWV+18} proposed multi-fluid modelling of convection in order
-to treat non-equilibrium and net mass transport correctly and consistently
-with the same numerics and physics controlling thermals, the stable
-environment and downdraught dynamics. \citet{Yano14} derived similar
-equations for multiple segments and showed how this is a generalisation
-of the mass-flux formulation. The \citet{TKP+18} ``extended eddy
-diffusivity mass flux'' or extended EDMF scheme also uses similar
-equations but \citet{TKP+18} didn't propose a suitable numerical
-method for solving the equations. Multi-fluids promises big improvements
-in the representation of sub-grid-scale convection and unification
-with the representation of turbulence, particularly at the grey zone.
-However, there is a long way to go, particularly as multi-fluids requires
-a dedicated model rather than being a stand alone parameterisation
-for a dynamical core. \citet{TEB19} and \citet{WM19} presented solutions
-of the multi-fluid equations assuming two fluids that share the same
-pressure (or that pressure differences are predominantly due to drag
-between the fluids). \citet{TEB19} showed that these equations (without
-drag) are in fact unstable and can be stabilised by diffusion of vertical
-velocity whereas \citet{WM19} stabilised the equations with diffusion
-and drag between fluids. Neither of these stabilisation techniques
-are acceptable and in this paper we show that there are significant
-and sustained pressure differences between the fluids (section \ref{sec:results}).
-
-This paper presents the multi-fluid Boussinesq equations for representing
-sub-grid-scale convection including a parameterisation of the pressure
-difference between fluids (section \ref{subsec:fluidPressure}) and
-a new model of entrainment and detrainment (section \ref{subsec:Sij}).
-The numerical method for solving the equations is described in section
-\ref{sec:numerics}. We compare results of resolved dry convection
-in a single-fluid two dimensional Boussinesq model with a two-fluid,
-single column model in section \ref{sec:results} using two vertical
-slice test cases.
-
-\section{The Multi-fluid Boussinesq Equations}
-
-Many of the challenges of representing convection with the multi-fluid
-Navier-Stokes equations \citep[eg those described in][]{WM19} carry
-over to the Boussinesq equations; convection is buoyancy dominated
-and close to incompressible. The resolved test cases presented in
-section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore for simplicity we focus on the
-multi-fluid Boussinesq equations without background stratification:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\} \label{eq:sigma}\\
-\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\} \label{eq:mom}\\
-\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}\\
-\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
-\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
-\end{eqnarray}
-with variables defined in table \ref{tab:defns}.
-
-\begin{table}[h]
-\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
-$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
-$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
-$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
-$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
-$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
-where $\rho^{\prime}$ are departures in density from a horizontally
-uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
-$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
-$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
-$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-\end{tabular}
-
-\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
-\end{table}
-
-\subsection{Pressure of each fluid \label{subsec:fluidPressure}}
-
-\citet{TEB19} and \citet{WM19} assumed that each co-located fluid
-shared the same pressure, leading to unstable equations that \citet{TEB19}
-stabilised using diffusion of vertical velocity and \citet{WM19}
-stabilised using mass exchanges or drag between the fluids. \citet{TEB19}
-achieved realistic results in single column experiments of convective
-boundary layer but the amount of diffusion needed would spoil simulations
-in the free troposphere. The stabilisation used by \citet{WM19} meant
-that the two fluids tended to move as one which defeats the purpose
-of using multi-fluid modelling.
-
-The instabilities reported by \citet{WM19} showed growing divergence
-in a fluid with vanishing volume fraction. It is mass convergence
-rather than velocity convergence that leads to pressure anomalies
-that remove the convergence. Therefore if the volume (or mass) fraction
-of fluid is vanishingly low then convergence cannot lead to an anomaly
-in the total pressure.
-
-We will assume that pressure in each fluid is given by a parameterised
-perturbation, $p_{i}$, from the total pressure, $P$:
-\begin{equation}
-P_{i}=P+p_{i}.
-\end{equation}
-
-\citet{BN86} proposed a parameterisation for pressure differences
-in a multi-phase explosion model that has been widely used in mathematics
-and engineering for simulating fluidised beds of granular material
-\citep[eg.][]{EHM92} and two compressible fluids \citep[eg.][]{SA99}.
-In these methods, advection equations are written for the volume fraction,
-$\sigma_{i}$, and conservation equations are written for mass fraction,
-$\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
-fluids, the \citet{BN86} equations would be:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)\label{eq:BNcompaction}\\
-\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0\label{eq:rhoTransport}
-\end{eqnarray}
-where $\mathbf{V}$ is the velocity of the interface between fluids,
-$\mu$ is the compaction viscosity which controls how quickly the
-pressure of each fluid relaxes to the mean pressure and index $j$
-refers to the other fluid in a two fluid system. In our Boussinesq
-system $\rho_{i}$ does not appear in the continuity equation. Different
-authors make different assumptions about the interface velocity but
-if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
-$\rho_{i}$ is constant then eqns (\ref{eq:divFree}-\ref{eq:rhoTransport})
-imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
-If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
-we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.
-
-\citet{TEB19} stabilised the multi-fluid equations by adding a diffusion
-term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
-If a fluid perturbation pressure is set to $-\nu\partial w/\partial z$
-this is equivalent to the diffusion term in one dimension. However
-adding a diffusion term will harm three dimensional simulations of
-resolved convection in the free troposphere whereas adding a fluid
-perturbation pressure will not. Inspired by both \citet{BN86} and
-\citet{TEB19} we assume that the pressure in each fluid is given
-by:
-\begin{equation}
-p_{i}=-\gamma\nabla\cdot\mathbf{u}_{i}\label{eq:Pi_div}
-\end{equation}
-where $\gamma$ is a free coefficient. Dimensional analysis in section
-\ref{subsec:dimAnal} will inform the choice of $\gamma$ and sensitivity
-to $\gamma$ will be evaluated in section \ref{sec:results}.
-
-\subsection{Entrainment and Detrainment \label{subsec:Sij}}
-
-We consider dry air without turbulence so use the dynamic entrainment
-described by \citet{HC51,AK67,DBF+13}:
-\begin{equation}
-S_{ij}=\begin{cases}
--\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
-0 & \text{otherwise}
-\end{cases}
-\end{equation}
-which is necessary to stop air in one fluid from accumulating when
-vertical motion ceases (at the top of a rising plume or at the bottom
-of descending air). We will also test a common form of lateral entrainment
-\citep{DBF+13}:
-\begin{equation}
-\varepsilon=\frac{0.2}{r_{c}}\implies S_{01}=w_{1}\frac{0.2}{r_{c}}
-\end{equation}
-where $\varepsilon$ is the well know fractional entrainment rate
-and $r_{c}$ is the cloud or plume radius.
-
-\subsection{Drag in the Momentum Equation\label{subsec:drag}}
-
-Pressure differences between the fluids can lead to form drag which
-is parameterised following \citet{SW69,RC15,WM19} as: 
-\begin{equation}
-\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
-\end{equation}
-where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
-Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.
-
-\subsection{The Buoyancy and the Momentum of the Mass that is Transferred \label{subsec:transferProperties}}
-
-The different fluids may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \citep[as was assumed by][]{WM19}.
-In fact, the most buoyant air should be transferred from fluid 0 to
-fluid 1 and vice versa, and the air with least downward momentum should
-be transferred from 0 to 1 and vice versa. The properties of the fluids
-transferred should depend on the modelling of sub-grid-scale variability
-which is beyond the scope of this paper. In section \ref{sec:results}
-we conditionally average high resolution solutions based on the sign
-of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
-Therefore the air that is transferred at the interface will have $w=0$.
-For two dimensional multi-fluid simulations we assume that the horizontal
-velocity transferred is equal to the mean horizontal velocity of the
-fluid transferred from. Therefore
-\begin{equation}
-\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
-v_{i}\\
-0
-\end{pmatrix}.
-\end{equation}
-For buoyancy, following \citet{TEB19}, we use:
-\begin{equation}
-b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
-\end{equation}
-and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
-Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
-transferred depends on the properties of the receiving fluid which
-is not logical and can lead to unbounded values of $b_{i}$ in the
-fluid that is loosing mass (as demonstrated in section \ref{sec:results}).
-
-\subsection{Dimensional Analysis\label{subsec:dimAnal}}
-
-Dimensional analysis can guide our choice of $\gamma$ for the parameterisation
-of the pressure difference between fluids. We make the following assumptions:
-\begin{enumerate}
-\item The flow is buoyancy dominated.
-\item The flow is close to inviscid.
-\item The flow is slowly varying.
-\item Fluid $i$ properties are anomalies from a neutrally stable resting
-mean state.
-\item We consider only the vertical direction where $w_{ij}^{T}=0$.
-\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
-\item There are two fluids, $i$ and $j$
-\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
-and $S_{ji}=0$.
-\end{enumerate}
-This leads to the following balance in the momentum equation:
-\begin{equation}
-\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
-\end{equation}
-We non-dimensionalise using a length scale $L$, a buoyancy scale
-$B$ and a time scale $T$ to get the non-dimensional variables:
-\begin{eqnarray*}
-\tilde{w} & = & w_{i}T/L\\
-\tilde{b} & = & b_{i}/B\\
-\tilde{z} & = & z/L.
-\end{eqnarray*}
-Then the non-dimensional version of (\ref{eq:wi_balances}) is:
-\begin{equation}
-\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
-\end{equation}
-The flow is buoyancy dominated so the buoyancy term should be $O(1)$
-so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
-so the non-dimensional momentum equation becomes:
-\begin{equation}
-\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
-\end{equation}
-The stabilisation term must be large enough to smooth out oscillations
-in $\tilde{w}$ due to advection and buoyancy but not too large to
-remove all variability in $\tilde{w}$ so we need:
-\begin{equation}
-\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
-\end{equation}
-
-\section{Numerical Solution \label{sec:numerics}}
-
-The spatial discretisation follows exactly \citet{WM19}, solving
-advective form equations using monotonic, finite volume advection
-and C-grid, Lorenz staggering. The time-stepping is Crank-Nicolson
-with no off-centering and with deferred correction of explicitly solved
-variables. It differs from \citet{WM19} because here we solve the
-Boussinesq equations and we need stable solutions for equations with
-a separate pressure in each fluid. We use two outer iterations per
-time step to update explicitly solved variables. For the first outer
-iteration, predicted values for time $n+1$ are set to those from
-time level $n$ and are given the superscript $\ell$. For the second
-iteration, values at $\ell$ are set to those from the end of the
-first iteration. The implicit numerical method for applying the transfers
-between fluids is specific for two fluids because it involves the
-inversion of $2\times2$ matrices.
-
-The prognostic variables are the $b_{i}$ in cell centres, the $\sigma_{i}$
-in cell centres and the velocity flux at cell faces, $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$,
-which is the velocity at cell faces dotted with the area vector for
-each face (normal to the face). The pressures, $P$ and $p_{i}$ are
-diagnostic.
-
-The first equation to be solved each outer iteration is eqn (\ref{eq:sigma})
-for each $\sigma_{i}$, operator split; first applying advection,
-then correcting $\sum_{i}\sigma_{i}=1$ and then applying mass transfers:
-\begin{eqnarray}
-\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\} \\
-\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}\\
-S_{ij} & = & \begin{cases}
--\nabla\cdot\mathbf{u}_{i}^{\ell} & \text{if }\nabla\cdot\mathbf{u}_{i}^{\ell}<0\\
-0 & \text{otherwise}
-\end{cases}\\
-\sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
-\end{eqnarray}
-where $\Delta t$ is the time step and the superscripts $\prime$
-and $\prime\prime$ denote intermediate values. $\sigma_{i}^{n}$
-is interpolated from cell centres onto cell faces using monotonic
-van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citet{WM19}
-and values exclusively at time level $n$ for best accuracy and guaranteed
-monotonicity. For calculating the divergence, the normal component
-of $\mathbf{u}_{i}$ is needed at cell faces which are prognostic
-variables of the C-grid. The $S_{ij}$ are limited to ensure $0<\sigma_{i}<1\ \forall i$.
-
-Next eqn (\ref{eq:b}) is solved for the buoyancy in each fluid, first
-transporting buoyancy and then applying the transfer terms. The transfer
-terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
-in the transfer term for $b_{i}$ so they are treated operator split
-and implicitly:
-\begin{eqnarray}
-b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
- &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
-b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
-b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
-\end{eqnarray}
-where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
-from before the mass transfers is necessary to ensure bounded and
-conservative transfers, as described by \cite{MWH1x}. Simultaneous
-solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
-\begin{eqnarray}
-b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
-b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
-\end{eqnarray}
-where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$
-
-Next a Poisson equation is solved to calculate the total pressure,
-$P$ to ensure that the total velocity is divergence free. The pressure
-equation also provides updates for the velocity flux, $u_{i}$. First
-an intermediate velocity flux is calculated with partial updates and
-updates from a previous value of $p_{i}$:
-\begin{eqnarray}
-u_{i}^{\prime}= & u_{i}^{n}+\frac{\Delta t}{2} & \biggl(\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{\ell}\cdot\mathbf{S}-\nabla_{f}p_{i}^{\ell}\\
- &  & +\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{n}\cdot\mathbf{S}-\nabla_{f}(P+p_{i})^{n}\biggr)
-\end{eqnarray}
-where operator $()_{f}$ means linear interpolation from cell centres
-onto cell faces and $\nabla_{f}P$ is a compact discretisation of
-$(\nabla P)_{f}\cdot\mathbf{S}$: ie the normal component of the pressure
-gradient calculated from just the values of pressure either side of
-the face. Once we have calculated $P^{n+1}$, the velocity flux (without
-momentum transfers) is updated from the back-substitution:
-\begin{equation}
-u_{i}^{\prime\prime}=u_{i}^{\prime}-\frac{\Delta t}{2}\nabla_{f}P^{n+1}.\label{eq:backSub}
-\end{equation}
-The Poisson equation for $P^{n+1}$ is found by multiplying each eqn
-(\ref{eq:backSub}) by $\sigma_{i}$, summing over all fluids and
-taking the divergence. Knowing that $\nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0$,
-$\sum_{i}\sigma_{i}=1$ and $\sum_{i}\sigma_{i}p_{i}=0$ gives:
-\begin{equation}
-\nabla\cdot\sum_{i}\sigma_{i}u_{i}^{\prime}-\frac{\Delta t}{2}\nabla^{2}P^{n+1}=0
-\end{equation}
-which is solved to find $P^{n+1}$.
-
-Next, the momentum transfers due to mass transfer and due to drag
-are calculated implicitly, similar to the implicit transfers of buoyancy,
-calculating $u_{i}^{n+1}$ from $u_{i}^{\prime\prime}$. These do
-not influence the total $P$ or total divergence because momentum
-is transferred conservatively. However they do influence $p_{i}$
-which is why they are calculated before $p_{i}$. The final stage
-of the time step iteration is to solve Helmholtz equations for each
-$p_{i}$:
-\begin{equation}
-\sigma_{i}^{n+1}p_{i}^{n+1}=-\gamma\nabla\cdot\left(\sigma_{if}^{n+1}u_{i}^{n+1}-\frac{\Delta t}{2}\sigma_{if}^{n+1}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right).\label{eq:pi_Helm}
-\end{equation}
-Both $p_{i}^{n+1}$ and $p_{i}^{\ell}$ appear in eqn (\ref{eq:pi_Helm})
-because $u_{i}^{n+1}$ already contains contributions from $p_{i}^{\ell}$
-so these are removed before updating $p_{i}^{n+1}$. No back substitution
-for $u_{i}$ is done after calculating $p_{i}^{n+1}$ because this
-would destroy the divergence free constraint. Therefore $p_{i}^{n+1}$
-only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
-converge and $p_{i}^{\ell}=p_{i}^{n+1}$.
-
-The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
-from $u_{i}$ following \citet{WM19}. The stages calculating $P$,
-$p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
-The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$.
-
-\section{Validation Test Cases\label{sec:results}}
-
-Two test cases are developed to tune parameters and to validate the
-use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
-convection. The first is transient; the standard rising bubble of
-\citet{BF02}. We aim to reproduce the vertical heat transport, the
-mean velocity of the rising air, the bouyancy of the rising air and
-pressure differences between two fluids in a single column two fluid
-model. The second test case is steady state with heat transfer at
-the ground and uniform radiative cooling. For both test cases the
-reference solution is a single fluid solution of the two-dimensional
-Boussinesq equations at high horizontal and vertical resolution.
-
-\subsection{Rising Bubble}
-
-The test case of \citet{BF02} was designed for fully compressible
-models but similar solutions are obtained solving Boussinesq equations.
-The Boussinesq version has no background stratification in a domain
-of height 10\,km and width 20\,km initially at rest. The buoyant
-perturbation is given by:
-\begin{equation}
-b=\frac{1}{15}\cos^{2}\frac{\pi L}{2}\label{eq:thetaPerturb}
-\end{equation}
-for $L<1$ where $L=\sqrt{\left(\frac{x-x_{c}}{x_{r}}\right)^{2}+\left(\frac{z-z_{c}}{z_{r}}\right)^{2}}$,
-$x_{c}=10\ \text{km}$, $z_{c}=2\ \text{km}$ and $x_{r}=z_{r}=2\ \text{km}$.
-100\,m grid spacing is used in the $x$ and $z$ directions for the
-two dimensional reference simulation and $\Delta z=100\ \text{m}$
-is used in the vertical for the single column simulations. All simulations
-use a time-step of 2\,s.
-
-\subsubsection{Single Fluid Solutions}
-
-The solution of the rising buoyant bubble solving the Boussinesq equations
-for 1000s is shown in figure \ref{fig:bubble} with buoyancy coloured,
-pressure contoured and the $w=0$ contour dotted. The solution is
-very similar to the fully compressible solution \citep{BF02}. The
-pressure gradients accelerate the flow beneath the bubble, decelerate
-the flow above the bubble and pull in air horizontally. Horizontally
-and conditionally averaged fields, conditioned on $w$, are shown
-in the top row of figure \ref{fig:bubble_singleUnderRes}. $\sigma_{1}$
-is the volume fraction of rising fluid at every height, $b_{0}$ and
-$b_{1}$ are the buoyancy conditioned on $w\le0$ and $w>0$, $w_{0}$
-and $w_{1}$ are the horizontal averaging rising and falling vertical
-velocity and $P_{0}$ and $P_{1}$ are the pressure of the rising
-and falling fluid. An accurate multi-fluid model of convection should
-reproduce these fields approximately at coarser horizontal resolution
-or in a single column model.
-
-\begin{figure}
-\noindent \begin{centering}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
-\par\end{centering}
-\noindent \begin{centering}
-\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
-\par\end{centering}
-\caption{The single fluid, resolved rising bubble after 1000s. Buoyancy is
-coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
-negative contours dashed. The $w=0$ contour is dotted. \label{fig:bubble}}
-\end{figure}
-
-\citet{TEB19} and \citet{WM19} assumed that both fluids would share
-the same pressure with differences parameterised as drag. The pressure
-in figure \ref{fig:bubble} shows that this is a bad assumption since
-the large pressure anomalies are in the rising fluid. Drag would always
-act to slow down the fluids whereas the negative pressure gradients
-in the rising fluid just below the bubble are acting to accelerate
-the rising motion.
-
-The horizontal averages are shown in figure \ref{fig:bubble_singleUnderRes}
-for horizontal resolutions of nine columns, five columns, three columns
-and a single column all for the 20km wide domain and all still using
-$\Delta z=100\ \text{m}$. These simulations are initialised by conservative
-horizontal averaging from the full resolution solution. As the horizontal
-resolution is reduced, the vertical transport reduces until there
-is no movement at all for a single column: there is no possibility
-of fluid rising because in a single column with a single fluid there
-can be no compensating subsidence. The lack of vertical transport
-at coarse resolution motivates convection parameterisation.
-
-\begin{figure}
-\noindent %
-\begin{tabular}{ccccc}
-\begin{turn}{90}
-200 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-9 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-5 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-3 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-1 Column
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
-\end{tabular}
-
-\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
-and a single fluid. Horizontal averages are conditioned based on $w$.
-\label{fig:bubble_singleUnderRes}}
-\end{figure}
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-Multi-fluid, single column simulations are initialised by horizontally
-and conditionally averaging the high resolution single fluid initial
-conditions. Sinking air is put into fluid zero and rising air into
-fluid one. The velocity field after one time step is used for initialisation
-as the air is stationary at $t=0$. Results are shown in figures \ref{fig:multiFluidSingleColumn-bad}
-and \ref{fig:multiFluidSingleColumn} for various assumptions about
-transfers between fluids and various parameter values.
-
-\begin{figure}
-\begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
-\end{figure}
-
-\begin{figure}
-\begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=1/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{01}=w_{1}0.2/r_{c}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=0$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.25\columnwidth}%
-$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions.\label{fig:multiFluidSingleColumn}}
-\end{figure}
-
-If there is no drag between fluids, no transfers, no diffusion and
-the pressures of both fluids are assumed equal then the multi-fluid
-equations are unstable \citep{TEB19}. The simulation with ($S_{ij}=0$)
-in the top row of figure \ref{fig:multiFluidSingleColumn-bad} actually
-has small transfers to prevent either $\sigma_{i}$ from becoming
-negative. This is sufficient to stabilise the solution but does not
-prevent oscillations from developing in all fields. The buoyant fluid
-has risen very little from the initial conditions. $\sigma$ oscillates
-between zero and one meaning that only one fluid is present at some
-locations so there is no possibility for the fluids to move past each
-other.
-
-Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-stabilises the solution and enable the fluids to move past each other
-even without pressure differences between the fluids (second row of
-figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
-detrained from fluid 1, fluid 1 looses too much buoyancy and a discontinuity
-arises at the bubble leading edge; the buoyancy force is producing
-vertical motion but there is no pressure to make it smooth.
-
-Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
-and pressure difference between the fluids controlled by divergence
-($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
-realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
-Three values of $\gamma$ are tested. $\gamma$ is set from equation
-(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
-radius and a buoyancy scale equal to the initial maximum buoyancy
-to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
-(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
-the velocity profile too smooth and the updraught too weak so the
-bubble does not rise enough. It is reasonable to consider smaller
-values of $\gamma$ because the buoyancy does not retain its initial
-maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
-gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
-leads to the leading edge of the bubble rising too quickly. Smaller
-values of $\gamma$ leave a discontinuity in the updraught velocity
-at the leading edge of the bubble and larger values of $\gamma$ reduce
-the velocity further, meaning that the bubble does not rise enough
-(not shown). None of the values of $\gamma$ reproduce the peak updraught
-velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
-meaning that the bubble rise and $\sigma_{1}$ are approximately correct
-and pressure increases above the centre of the bubble are realisitic.
-The large low pressure at the bottom of the bubble is not reproduced.
-This is located at the lobes of the highest buoyancy in the resolved
-simulation (figure \ref{fig:bubble}). It would be tempting to model
-this by assuming hydrostatic pressure or the Bernouilli equation,
-but these are both forms of the momentum equation which is used to
-calculate the velocity and so cannot also be used to model the pressure.
-
-The results in the top row of figure \ref{fig:multiFluidSingleColumn}
-use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
-this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
-drag slows the updraughts without increasing the mixing between the
-fluids which makes the solutions less like the resolved simulations.
-Although drag is known to be an important term in the momentum equations
-for buoyant thermals and plumes \citep[eg][]{RC15}, the drag is related
-to mixing with downdraught air which is accounted for in the entrainment
-term of the momentum equation. So adding a separate term from drag
-risks double counting and slows the plume too much.
-
-If we include pressure difference between fluids with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$but
-omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidSingleColumn})
-the fluids move past each other but there is an unrealistic discontinuity
-with no fluid 1 below the buoyant fluid and very little falling air
-at the lowest height of the rising fluid. With a single column and
-two fluids, all air must rise in one fluid and sink in the other.
-Continuity does not allow for any other solution. Pressure gradients
-can accelerate or decelerate this flow but as the model is set up,
-with no transfers between fluids, no fluid can change direction. It
-is therefore essential to have transfers between fluids.
-
-The other entrainment option is the commonly used fractional entrainment
-rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
-differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
-This combination produces smooth solutions but the updraught is too
-weak and too much is entrained into fluid 1. Using this entrainment,
-the updraught will entrain more and more air until $\sigma_{1}=1$.
-The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
-entrainment and detrainment for this test case using conditional averaging
-based on $w$.
-
-Two alternative models for estimating the buoyancy of the fluid transferred
-between updraught and downdraught have been tested. The results in
-the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
-that the fluid transferred has zero buoyancy in order to keep the
-positively buoyant air in fluid one and the negatively buoyant air
-in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
-the mean buoyancy of fluid one increases. This leads to very high
-buoyancy in fluid one which is not present in the resolved simulation.
-The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
-use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citet{TEB19}
-so that the fluid transferred is influenced by the fluid it is moving
-towards as well as where it has come from. This again leads to very
-large buoyancy in fluid one and also negative buoyancy in fluid zero
-which should not occur for this test case. These simple models reinforce
-the idea that the buoyancy of the fluid transferred should depend
-on knowledge of sub-grid-scale variability of $b$ within each fluid
-\textendash{} these simple assumptions can lead to unrealistic behaviour.
-The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
-fluid transferred takes the mean properties with it.
-
-This section has demonstrated the value of using a single column,
-multi-fluid model to simulate a buoyant rising bubble with a single
-updraught fluid and a single downdraught fluid. Transfers between
-the fluids have been successfully modelled using entrainment set by
-divergence giving realistic updraught fractions. Entrainment calculated
-as the reciprocal of plume width was not successful. The pressure
-difference between the fluids has also been represented by divergence
-with a coefficient close to that expected from dimensional analysis.
-Including drag between the fluids did not improve simulations. Two
-models of transferring non-mean properties between fluids were tested
-but neither was plausible. There are clearly discrepancies between
-the single fluid resolved rising bubble and the two fluid single column
-rising bubble but we do not want to over fit the multi-fluid model
-to one, dry, two dimensional test case.
-
-\subsection{Radiative-Convective Equilibrium (RCE)}
-
-A two-dimensional, dry radiative convective equilibrium test case
-is devised to mimic some properties of atmospheric convection, in
-particular the difficulty resolving the flow at coarse resolution.
-The domain is 160km wide, 10km tall and is resolved by 640 cells in
-the horizontal and 40 in the vertical ($\Delta x=\Delta z=250$m).
-The top and bottom boundaries are zero velocity and the lateral boundaries
-are periodic. A heat flux of $h=10^{-3}\text{m}^{2}\text{s}^{-3}$
-is imposed at the bottom boundary leading to a boundary condition
-of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
-is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
-Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
-so as to give a Plank constant of $0.707$. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$
-is applied to the domain to maintain equilibrium.
-
-The fluid is initially stationary with $b=0$. In order to quickly
-and reproducibly initialise instability, $b=10^{-4}\text{m}^{2}\text{s}^{-1}$
-is imposed in a square of side length 2000m at the centre in the $x$
-direction and at the ground. The simulation is run using a time step
-of $5\ \text{s}$. A quasi-steady, choatic state is reached after
-about $3\times10^{4}\text{s}$ and the simulation is run for $2\times10^{5}\text{s}$
-and conditional averages are calculated over the final $10^{5}$s.
-
-\subsubsection{Single Fluid Solutions}
-
-This test case is designed to have strong updraughts in narrow plumes
-and weak descent elsewhere to mimic atmospheric convection but without
-the complication of moisture, phase changes and three spatial dimensions.
-A snapshot of the buoyancy, vertical velocity and pressure of the
-radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
-are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
-updraughts. The buoyant air at the ground rises in narrow plumes,
-accelerating due to buoyancy and pressure gradients then decelerating
-due to pressure gradients before reaching the top. The plumes spread
-out and the sinking air is a mixture of warm and cold with similar
-pressure gradients in the rising and falling air, accelerating then
-decelerating the flow so as to maintain continuity.
-
-\noindent 
-\begin{figure}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/bw}
-
-Buoyancy ($\text{m}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/bw_b}
-
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/Pw}
-
-Pressure ($\text{m}^{2}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/Pw_P}
-
-\caption{Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
-of the resolved radiative-convective equilibrium test case. Vertical
-velocity contours are black every 0.5m/s with negative contours dashed
-and the zero contour dotted. The domain is 10km high and 160km wide
-and the z-direction is stretched a factor of 2 in the plots. \label{fig:RCE_resolved}}
-\end{figure}
-
-Horizontal averages conditioned on $w$ and time averaged every 1000s
-between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
-in the top row of figure \ref{fig:RCE_singleColumn}. The rising and
-falling volume fractions, $\sigma_{1}$ and $\sigma_{0}$, remain
-close to $\frac{1}{2}$ throughout the depth. The rising plumes look
-narrow in figure \ref{fig:RCE_resolved} but there are wide regions
-of slowly rising air around the plume cores. The entrained rising
-cool air and warm air sinking that has hit the model top mean that
-the rising and falling air have similar average buoyancy away from
-the ground. The ascending air gradually accelerates towards the middle
-of the domain then decelerates towards the model top. At the ground
-the acceleration is forced by buoyancy and away from the ground the
-acceleration is controlled by pressure gradients. The descending air
-mean velocity is close to equal and opposite to the ascending air,
-as expected since $\sigma_{1}=0.5$.
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-The two fluid model is used to simulate the RCE test case in a single
-column of 40 cells with zero buoyancy gradient at the top and a buoyancy
-gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
-and uniform radiative cooling. The two fluids are initialised using
-the time mean conditional horizontal averages from the single fluid
-resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-is used for all simulations to account for transfers throughout the
-domain to represent cloud base mass flux (at the bottom boundary),
-cloud top detrainment and lateral entrainment. $\gamma$ is set from
-equation (\ref{eq:gammaDimAnal}) using the depth of the super adiabatic
-layer as the length scale ($L=800\text{m}$) and the buoyancy scale
-$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
-giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. A simulation using
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
-is shown in the second row of figure \ref{fig:RCE_singleColumn}.
-The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
-at about 0.5 throughout the depth, as in the resolved simulation,
-with entrainment in the lower half of the domain ($S_{01}>0$) and
-detrainment in the upper half ($S_{10}>0$), where the air decelerates
-towards the top. The single column model reproduces the super-adiabatic
-layer near the ground and the near uniform buoyancy away from the
-ground but the buoyancy difference between the fluids is too large.
-The updraught and downdraught velocities are captured well. The pressure
-differences between fluids are too large which is consistent with
-the over estimated buoyancy difference between fluids.
-
-Results of a simulations using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
-is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
-This model of the buoyancy of the transferred fluid is bad; it leads
-to strong cooling in fluid zero near the ground due to the large transfers.
-It is more accurate to assume that fluids take their mean properties
-when transferred, $b_{ij}^{T}=b_{i}$.
-
-\noindent 
-\begin{figure}
 \setlength\tabcolsep{0.5pt}%
@@
 versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/P_1}\tabularnewline
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P_1}\tabularnewline
 \multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
@@
 versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/P_1}\tabularnewline
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P_1}\tabularnewline
 \end{tabular}
-
-\caption{Results of the RCE simulations. The top row shows horizontal averages
-of the resolved case between $t=10^{5}$s and $2\times10^{5}$s. The
-bottom two rows show results of the single column multi-fluid model
-after $10^{4}\ \text{s}$. \label{fig:RCE_singleColumn}}
-\end{figure}
-
-\section{Summary, Conclusions and Further Work}
-
-This paper presents solutions of the multi-fluid Boussinesq equations
-for convection, reproducing aspects of highly resolved dry convection
-at coarse horizontal resolution. Two test cases are used to validate
-the multi-fluid model. The first is a Boussinesq version of the well
-known two dimensional dry rising bubble of \citet{BF02} and the second
-is a dry two dimensional version of radiative-convective equilibrium
-with heating at the ground and uniform radiative cooling. High resolution
-single fluid simulations are conditionally averaged based on the sign
-of vertical velocity ($w$) in order to create rising and falling
-fluids which each have their own mean buoyancy, velocity and pressure.
-The two-fluid, single column Boussinesq model reproduces mean vertical
-heat and mass transport of these test cases.
-
-The multi-fluid Boussinesq equations can have divergence in each fluid
-while the divergence averaged over all fluids is zero. A model is
-proposed and validated for the pressure difference between the rising
-and falling fluids based on the divergence of each fluid. The use
-of a different pressure for each fluid is not only realistic but also
-leads to stable solutions of the multi-fluid equations.
-
-Conditionally averaging the high resolution solutions based on $w$
-leads to convecting and non-convecting regions with area fractions,
-$\sigma_{i}$, which are approximately uniform with height. Models
-for entrainment and detrainment into and out of convecting regions
-must clearly be consistent with the definition of the convecting region.
-We propose a model for entrainment and detrainment based on divergence
-that leads to excellent agreement with $\sigma$ from the high resolution
-solutions. We also test a more conventional fractional entrainment
-rate based on the reciprocal of the plume width which leads to unrealistic
-convecting area fractions.
-
-A set of unknowns in the multi-fluid equations are the properties
-of the fluid that are transferred from one fluid to another. An obvious
-first guess would be that fluid takes its mean buoyancy and velocity
-with it when it is transferred. However sub-grid-scale variability
-of each fluid means that we expect that the most buoyant fluid will
-be transferred to the rising fluid or the fluid with the largest vertical
-velocity will be transferred to the rising fluid and vice versa. An
-accurate estimate of these would depend on knowledge of the sub-grid-scale
-variability of each fluid which we do not have. Instead we assume
-that the fluid transferred in each direction has zero vertical velocity
-which is consistent with our conditional averaging. We have tested
-three models for the buoyancy of the fluid transferred. The most successful
-is to assume that the fluid takes its mean buoyancy with it. Assuming
-that the buoyancy of the transferred fluid is an average of the buoyancy
-of both fluids can lead to unrealistically large or small, unbounded
-buoyancies. Similarly, if we assume that one fluid has negative buoyancy
-and the other positive buoyancy and we transfer fluid of zero buoyancy,
-then unbounded buoyancy can occur. A better model of the buoyancy
-of the fluid transferred would rely on more information the sub-grid-scale
-variability.
-
-Single column multi-fluid modelling with moisture has already been
-demonstrated by \citet{TEB19}. Two important next steps are to simulate
-convection in the grey zone (where it is partially resolved) and to
-represent sub-grid-scale variability within each fluid by solving
-multi-fluid prognostic equations for turbulent kinetic energy and
-other moments of the sub-grid variability. These can be used to inform
-cloud base mass flux (since only the most buoyant fluid will transfer
-from the stable environment to the buoyant plume) and inform models
-of the properties of the fluid that is transferred. This will lead
-to a unified parameterisation of turbulence and convection and will
-take multi-fluid modelling of convection beyond existing paradigms.
-
-\section*{Acknowledgements}
-
-Many thanks to John Thuburn and Chris Holloway for valuable discussions.
-Thanks to the NERC/Met Office Paracon project. We acknowledge funding
-from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1.
-
-\bibliographystyle{abbrvnat}
-\bibliography{numerics}
-
 \end{document}

### 2020-04-11 submit2/manuscript.tex
First complete draft with Hilary's revisions and responses to reviewers.

@@
 
-This paper presents \change[HW]{multi}{two}-fluid Boussinesq equations for representing
-under-resolved dry convection \add[HW]{with sinking and $w=0$ air in fluid 0 and rising air in fluid 1}. We present a \remove[HW]{new} model for entrainment
-and detrainment based on divergence which leads to excellent representation
-of the convective area fraction. Previous multi-fluid modelling of
-convection has assumed that \change[HW]{all}{both} fluids share the same pressure.
-\change[HW]{We show that this is}{This is shown to be} a bad assumption and \remove[HW]{we propose and validate} a model
+This paper presents \change[HW]{multi}{two}-fluid Boussinesq equations for representing under-resolved dry convection
+\add[HW]{with sinking and $w=0$ air in fluid 0 and rising air in fluid 1}. \change[HW]{We present a new}{A} model for entrainment
+and detrainment based on divergence \remove[HW]{which} leads to excellent representation of the convective area fraction.
+Previous multi-fluid modelling of convection has
+\change[HW]{assumed that all fluids share the same pressure.}
+{used the same pressure for both fluids.}
+\change[HW]{We show that this is}{This is shown to be} a bad \change[HW]{assumption}{approximation} and \remove[HW]{we propose and validate} a model
 for the pressure difference between the fluids based on divergence \add[HW]{is presented}.
 
-Two vertical slice test cases are \change[HW]{used}{developed} to \add[HW]{tune parameters and to} \change[HW]{validate}{evaluate} the \change[HW]{multi}{use of two}-fluid
-\change[HW]{model}{equations to represent dry, two-dimensional, sub-grid-scale convection}; a buoyant rising bubble and radiative convective equilibrium. \add[HW]{These}
+Two vertical slice test cases are \change[HW]{used}{developed} to \add[HW]{tune parameters and to} \change[HW]{validate}{evaluate} the \change[HW]{multi}{two}-fluid \change[HW]{model}{equations for representing dry, two-dimensional, sub-grid-scale convection}; a buoyant rising bubble and radiative convective equilibrium.
+\add[HW]{These}
 are \add[HW]{first} simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity \add[HW]{and next simulated with the two-fluid model in one vertical column}. The \change[HW]{multi}{two}-fluid model reproduces
+on the sign of the vertical velocity. \add[HW]{The test cases are next simulated with the two-fluid model which} \remove[HW]{The multi-fluid model} reproduces
 the mean properties of the rising and falling fluids in \change[HW]{a single}{one} column. 
@@
 
-\add[HW]{
-\protect\citeA{LR01} introduced the ``assumed-distribution higher-order closure'' (ADHOC) parameterisation of the boundary layer and convection which solves prognostic equations for higher-order moments of the sub-grid-scale flow, such as the triple correlation of the vertical velocity anomalies, and diagnoses updraft and downdraft means from the higher-order moments.
+\add[HW]{\protect\citeA{LR01} introduced the ``assumed-distribution higher-order closure'' (ADHOC) parameterisation of the boundary layer and convection which solves prognostic equations for higher-order moments of the sub-grid-scale flow, such as the triple correlation of the vertical velocity anomalies, and diagnoses updraft and downdraft means from the higher-order moments.
 Thus all necessary statistics can be calculated from the grid-box-mean values that are predicted by the dynamical core.
 Net mass transport by convection is included because it is part of the grid-box-mean.
-ADHOC was extended by \protect\citeA{GLC02} to use bi-Gaussian probability distribution functions (PDFs) rather than top-hat distributions to represent sub-grid-scale variability.
-This formed the basis of the ``Cloud Layers Unified By Binormals'' (CLUBB) parameterization \protect\cite<>{LSW+12} which was first used at grey zone resolutions.}
+ADHOC was extended by \protect\citeA{GLC02}
+to use bi-Gaussian probability distribution functions rather than top-hat distributions to represent sub-grid-scale variability.
+This formed the basis of the ``Cloud Layers Unified By Binormals'' (CLUBB) parameterization
+\protect\cite<>{LSW+12}
+ which was first used at grey zone resolutions.}
 
@@
 to treat non-equilibrium and net mass transport \remove[HW]{correctly and} consistently.
-\change{with}{This involves using} the same numerics and physics to \change[HW]{control thermals}{prognose properties of separate parts of the fluid, for example updrafts}, the stable environment and downdrafts \remove[HW]{dynamics}.
-\citeA{Yano14} derived similar
+\add[HW]{The multi-fluids approach has an advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments directly (means of eg.
+updraft and environment) rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment.
+Solving directly for sub-fluid means should be less sensitive to closure assumptions.}
+\remove{with the same numerics and physics to prognose properties of separate parts of the fluid, for example updrafts, the stable environment and downdrafts dynamics}. \citeA{Yano14} derived similar
 equations \remove[HW]{for multiple segments} and showed how this is a generalisation
 of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
-diffusivity mass flux'' or extended EDMF scheme also uses similar
+diffusivity mass flux'' or extended EDMF scheme \remove[HW]{also} uses similar
 equations but \citeA{TKP+18}
@@
 with the representation of turbulence, particularly at the grey zone.
-However, there is a long way to go, particularly as}
-{The multi-fluids approach has an advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments (means of eg.
-updraft and environment) directly rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment.
-Solving directly for sub-fluid means should be less sensitive to closure assumptions.
-However} multi-fluids require
+However, there is a long way to go, particularly as multi-fluids}
+{The disadvantage of the multi-fluids approach is that it} requires
 a dedicated model rather than being a stand alone parameterisation
 for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
-of the multi-fluid equations assuming two fluids that share the same
-pressure. \remove[HW]{(or that pressure differences are predominantly due to drag
+of \change[HW]{the multi}{two}-fluid equations
+\change[HW]{assuming two fluids that share}{using} the same pressure
+\add[HW]{for both fluids}.
+\remove[HW]{(or that pressure differences are predominantly due to drag
 between the fluids)}. \citeA{TEB19} showed that these equations \remove[HW]{(without
@@
 The numerical method for solving the equations is described in section
-\ref{sec:numerics}. We compare results of resolved dry convection
+\ref{sec:numerics}. \change[HW]{We compare results of resolved dry convection
 in a single-fluid two dimensional Boussinesq model with a two-fluid,
-\change[HW]{single}{one} column model in section \ref{sec:results} using two vertical slice test cases.
+single column model in section {\protect\ref{sec:results}} using two vertical slice test cases.
+}{Results of two vertical slice test cases are presented in section {\protect\ref{sec:results}}.
+These are first simulated at high resolution in a single fluid model and then statistics of the flow are reproduced solving the two-fluid equations in one column.}
 
 \section{The Multi-fluid Boussinesq Equations \label{sec:multiBouEqns}}
+
+\subsection{\add[HW]{Derivation}}
 
@@
 \begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
-$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
-$\mathbf{u}$ & 
-Velocity of the single-fluid equations  ($\text{m}\text{s}^{-1}$) and velocity averaged over all fluids of the multi-fluid equations
-\tabularnewline
-$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
+$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$
+\tabularnewline
+\add[HW]{$\mathbf{u}$} & 
+\add[HW]{Velocity of the single-fluid equations  ($\text{m}\text{s}^{-1}$) and velocity averaged over all fluids of the multi-fluid equations}
+\tabularnewline
+$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)
+\tabularnewline
 $w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
@@
 \tabularnewline
-$P$ & Non-hydrostatic pressure of the single-fluid equations $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$) and pressure averaged over all fluids of the multi-fluid equations
-\tabularnewline
-$P_{i}$ & Non-hydrostatic pressure of fluid $i$ 
-\tabularnewline
-$p_{i}$ & $P_i - P$
-\tabularnewline
-$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
+\add[HW]{$P$} & \add[HW]{Non-hydrostatic pressure of the single-fluid equations $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$) and pressure averaged over all fluids of the multi-fluid equations}
+\tabularnewline
+$P_i$ & Non-hydrostatic pressure of fluid $i$
+\tabularnewline
+\add[HW]{$p_i$} & \add[HW]{$P_i - P$}
+\tabularnewline
+$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$
+\tabularnewline
 $b$ & Buoyancy of single-fluid equations defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
 where $\rho^{\prime}$ are departures in density from a horizontally
-uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$) and buoyancy averaged over all fluids of the multi-fluid equations
-\tabularnewline
-$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
-$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
+uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$) \add[HW]{and buoyancy averaged over all fluids of the multi-fluid equations}
+\tabularnewline
+$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)
+\tabularnewline
+$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$
+\tabularnewline
+$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)
+\tabularnewline
+$\gamma$ & \change[HW]{Coefficient for setting the pressure local for each fluid}{Compressibility for calculating $p_i$} ($\text{m}^{2}\text{s}^{-1}$)
+\tabularnewline
+$C_{D}$ & Drag coefficient $=0$ or 1
+\tabularnewline
 $r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
 $\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
+$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)
+\tabularnewline
 \end{tabular}
@@
 Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere.
-In this paper, $I_0$ labels sinking and $w=0$ fluid and $I_1$ labels rising fluid.
-$I_i$ satisfies:
+For the derivation of the conditionally averaged equations we will not consider relabelling of fluid \add[HW]{and so} $I_i$ satisfies:
 \begin{equation}
@@
 The sub-filter-scale fluxes will be absorbed into the diffusion terms for momentum and buoyancy.
-
+%
 \note[HW]{Dan, can we do better than this?}
@@
 \end{eqnarray} 
-
+%
 Unlike \citeA{TWV+18} we define separate pressures for each fluid, $P_i$. The pressures are defined to satisfy:
@@
 \end{equation}
-
+%
 Combining these gives the conditionally averaged momentum and buoyancy equations:
@@
 
-\citeA{TEB19} and \citeA{WM19} assumed that each \remove[HW]{co-located} fluid
-shared the same pressure \change[HW]{leading}{field. This lead} to unstable equations that \citeA{TEB19}
+\citeA{TEB19} and \citeA{WM19}
+\change[HW]{assumed that each co-located fluid shared the same pressure leading.}
+{used the same pressure for both fluids.}
+\add[HW]{This led} to unstable equations that \citeA{TEB19}
 stabilised using diffusion of vertical velocity and \citeA{WM19}
@@
 \end{equation}
-\add[HW]{In order to derive a suitable form of parameterisation for $p_i$ we will first consider the} \citeA{BN86} \add{model.}
+\add[HW]{In order to derive a suitable form of parameterisation for $p_i$ we will first consider the} \citeA{BN86} \add{model of multi-phase flow.}
 
@@
 and engineering for simulating, \add[HW]{for example}, fluidised beds of granular material \cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}.
-\add[HW]{This model is not used here but is examined in order to derive a method suitable for atmospheric convection.}
+\add[HW]{This model is not used here but is examined in order to derive a parameterisation of pressure differences between fluids suitable for atmospheric convection.}
 \citeA{SA99} wrote transport equations for both the volume fraction,
@@
 refers to the other fluid in a two fluid system. In our Boussinesq
-system $\rho_{i}$ does not appear in the continuity equation. Different
+system, $\rho_{i}$ does not appear in the continuity equation. Different
 authors make different assumptions about the interface velocity but
@@
 where $\gamma$ is a \change[HW]{free coefficient}{compressibility with units $\text{m}^s \text{s}^{-1}$. 
-This parameterisation of $p_i$ has $\sigma_i$ inside the divergence in order to ensure that $\sum_i p_i =0$ and $\therefore$ that $\sum_i P_i = P$.}
+This parameterisation of $p_i$ has $\sigma_i$ inside the divergence in order to ensure that $\sum_i p_i =0$ and therefore that $\sum_i P_i = P$ which makes the equations more striaghtforward to solve.}
+\add[HW]{However it should be noted that this parameterisation destroys energy conservation.}
 
@@
 \end{equation}
-\add[HW]{Results using two formulations of entrainment are presented in section \protect\ref{sec:results}. The first is}
+\add[HW]{Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}. The first is}
 \remove[HW]{We consider dry air without turbulence so use}
@@
 \end{cases}
+\label{eq:Sdiv}
 \end{equation}
 \change[HW]{which is necessary to stop air in}{This formulation prevents} one fluid from accumulating when vertical motion ceases (at the top of a rising plume or at the bottom of descending air).
-\remove[HW]{We will also test a}{A} common form of lateral entrainment \cite<eg.>{DBF+13} \add[HW]{is also tested in section \protect\ref{sec:results}}:
+\remove[HW]{We will also test a}{A} common form of lateral entrainment \cite<eg.>{DBF+13} \add[HW]{is also tested in section {\protect\ref{sec:results}}}:
 \begin{equation}
 \varepsilon=\frac{0.2}{r_{c}}
+\label{eq:fracEnt}
 \end{equation}
@@
 \change[HW]{The different}{Each} fluid may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. In fact, 
-\change[HW]
-{the most buoyant air should be transferred from fluid 0 to
+may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. \change[HW]
+{In fact, the most buoyant air should be transferred from fluid 0 to
 fluid 1 and vice versa, and the air with least downward momentum}
-{since we are conditionally averaging based on the vertical velocity, $w$, the sub-set of fluid 0 that is accelerating and about to be rising}
+{Since conditional averaging is based on the vertical velocity, $w$, the sub-set of fluid 0 that is about to be rising}
 should be transferred from 0 to 1 and vice versa.
@@
 we conditionally average high resolution solutions based on the sign
-of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
+of $w$ so that $w\le 0$ air is in fluid 0 and $w>0$ air in fluid 1.
 Therefore the air that is transferred at the interface will have $w=0$.
-For two dimensional multi-fluid simulations we assume that the horizontal
+For two dimensional multi-fluid simulations we \add[HW]{could} assume that the horizontal
 velocity transferred is equal to the mean horizontal velocity of the
@@
 \end{equation}
-For buoyancy, following \citeA{TEB19}, we use:
-\begin{equation}
-b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
-\end{equation}
-and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
+\add[HW]{However two dimensional multi-fluid simulations are not presented in this paper.}
+
+\change[HW]{For}{The} buoyancy \add[HW]{transferred} follows \citeA{TEB19}: \remove[HW]{we use}
+\begin{equation}
+b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}.
+\label{eq:bijT_thetab}
+\end{equation}
+\change[HW]{and present results}{Results are presented} using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
 \add[HW]{
@@
 
+\add[HW]{The model $b_{ij}^T=0$ is also tested.
+The rationale is that if fluid zero contains negatively buoyant air and fluid one contains positively buoyant air then the air that is transferred has zero buoyancy.}
+
 \subsection{\label{subsec:dimAnal}\change[HW]{Dimensional}{Scale}
@@
 
-Dimensional analysis can guide our choice of $\gamma$ for the parameterisation of the pressure difference between fluids. We make the following assumptions
-\add[HW]{in this analysis}:
+\change[HW]{Dimensional}{Scale} analysis can guide our choice of $\gamma$ for the parameterisation of the pressure difference between fluids \change{We make}{using} the following assumptions:
 \begin{enumerate}
@@
 \item We consider only the vertical direction where $w_{ij}^{T}=0$.
-\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
+\item $P_{i}=P-\gamma\nabla\cdot\sigma_i \mathbf{u}_{i}\approx-\gamma\nabla\cdot\sigma_i\mathbf{u}_{i}=-\gamma\frac{\partial \sigma_i w_{i}}{\partial z}$
+\item \add[HW]{$\frac{\partial \sigma_i}{\partial z} \approx 0$}
 \item There are two fluids, \change[HW]{$i$ and $j$}{0 and 1.}
@@
 \end{enumerate}
-\change[HW]{This leads to the following balance in the momentum equation}{These assumptions can be used to simplify the multi-fluid $w$ equation, (\protect\ref{eq:mom})}:
-\begin{equation}
-\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
-\end{equation}
-We non-dimensionalise using a length scale $L$, a buoyancy scale
+\change[HW]{This leads to the following balance in the momentum equation}{These assumptions can be used to simplify the multi-fluid $w$ equation, ({\protect\ref{eq:mom})}}:
+\begin{equation}
+\frac{\partial w_{i}^{2}}{\partial z}-\gamma\sigma_i\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
+\end{equation}
+\change[HW]{We}{This is} non-dimensionalised using a length scale $L$, a buoyancy scale
 $B$ and a time scale $T$ to get the non-dimensional variables:
@@
 \tilde{b} & = & b_{i}/B\\
-\tilde{z} & = & z/L.
+\tilde{z} & = & z/L
 \end{eqnarray*}
-Then the non-dimensional version of (\ref{eq:wi_balances}) is:
-\begin{equation}
-\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
+\add[HW]{where $\sigma$ is a typical value of $\sigma_i$ which must be $O(1)$ for one of the fluids.}
+Then the non-dimensional version of (\ref{eq:wi_balances}) is \add[HW]{then}:
+\begin{equation}
+\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma\sigma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
 \end{equation}
 The flow is buoyancy dominated so the buoyancy term should be $O(1)$
-so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
-so the non-dimensional momentum equation becomes:
-\begin{equation}
-\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
+\change[HW]{so we choose}{which implies} the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$. \change[HW]{so}{Therefore} the non-dimensional momentum equation becomes:
+\begin{equation}
+\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma\sigma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
 \end{equation}
@@
 \begin{equation}
-\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
-\end{equation}
-\add[HW]{This will be used to guide the choice of $\gamma$ in section \protect\ref{sec:results}.}
+\sigma\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
+\end{equation}
+\add[HW]{This will be used to guide the choice of $\gamma$ in section {\protect\ref{sec:results}}.}
 \section{\label{sec:numerics}Numerical \change[HW]{Solution}{Method}}
@@
 with no off-centering and with deferred correction of explicitly solved
-variables. It differs from \citeA{WM19} because here we solve the
-Boussinesq equations and we need stable solutions for equations with
-a separate pressure in each fluid. We use two outer iterations per
+variables. \remove[HW]{It differs from} \citeA{WM19}
+\change[HW]{because here we solve the Boussinesq equations and we need stable solutions for equations with a separate pressure in each fluid.}
+{solved the Euler equations with a single pressure. The method of finding separate pressure for each fluid is new.}
+We use two outer iterations per
 time step to update explicitly solved variables. For the first outer
@@
 
-The prognostic variables are the $b_{i}$ in cell centres, the $\sigma_{i}$
+The prognostic variables are \remove[HW]{the} $b_{i}$ in cell centres, \remove[HW]{the} $\sigma_{i}$
 in cell centres and the velocity flux at cell faces, $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$,
@@
 
-The first equation to be solved each outer iteration is eqn (\ref{eq:sigma})
+\change[HW]{The first equation to be solved each outer iteration is eqn}
+{The first calculation each outer iteration is for the transfer terms, $S_{ij}$ using ({\protect\ref{eq:Sdiv}}) or ({\protect\ref{eq:fracEnt}}). Next}
+(\ref{eq:sigma}) \add[HW]{is solved}
 for each $\sigma_{i}$, operator split; first applying advection,
-then correcting $\sum_{i}\sigma_{i}=1$ and then applying mass transfers:
+then correcting $\sum_{i}\sigma_{i}=1$ and \change[HW]{then}{finally} applying mass transfers:
 \begin{eqnarray}
-\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\} \\
-\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}\\
-S_{ij} & = & \begin{cases}
--\nabla\cdot\mathbf{u}_{i}^{\ell} & \text{if }\nabla\cdot\mathbf{u}_{i}^{\ell}<0\\
-0 & \text{otherwise}
-\end{cases}\\
+\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\}
+\\
+\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}
+\\
 \sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
@@
 Next eqn (\ref{eq:b}) is solved for the buoyancy in each fluid, first
-transporting buoyancy and then applying the transfer terms. The transfer
+transporting buoyancy and then applying the transfer terms.
+\add[HW]{The advection term, $\mathbf{u}_i\nabla b_i$ is split into $\nabla\cdot(\mathbf{u}_i b_i) - b_i \nabla\cdot\mathbf{u}_i$ for better conservation as calculated by the finite volume method.}
+The transfer
 terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
@@
 an intermediate velocity flux is calculated with partial updates and
-updates from a previous value of $p_{i}$:
+updates from a previous value of $p_{i}$ \add[HW]{but without updates from $\nabla P^{n+1}$}:
 \begin{eqnarray}
@@
 only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
-converge and $p_{i}^{\ell}=p_{i}^{n+1}$.
+converge \change[HW]{and}{implying} $p_{i}^{\ell}=p_{i}^{n+1}$.
 
@@
 $p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
-The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$.
+The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$
+\add[HW]{using the OpenFOAM conjugate gradient solver with incomplete Cholesky preconditioning}.
 
@@
 This is based on the intersection between a grid box and the surface of $w=0$.
-Given a grid box with centre $\mathbf{x}_c$, the surface of points, $\mathbf{x}_w$ of $w=0$ satisfies:
+Given a grid box with centre $\mathbf{x}_c$, the surface of points, $\mathbf{x}_w$ of $w=0$ satisfy:
 \begin{equation}
@@
 Two test cases are developed to tune parameters and to \change[HW]{validate}{evaluate} the
-use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
+use of \change[HW]{multi}{two}-fluid equations to represent dry, two-dimensional, sub-grid-scale
 convection. The first is transient; the standard rising bubble of
@@
 Boussinesq equations at high horizontal and vertical resolution.
-\add[HW]{This will be compared with the two-fluid model run using one column.
-We aim to reproduce the vertical heat transport, the mean velocity of the rising air, the bouyancy of the rising air and the pressure differences between fluids in one column two-fluid model.}
+\add[HW]{These will be compared with the two-fluid model run using one column.
+We aim to reproduce the vertical heat transport, the mean velocity of the rising air, the bouyancy of the rising air and the pressure differences between fluids in one column of the two-fluid model.}
 
@@
 The \add[HW]{two dimensional} test case of \citeA{BF02} was designed for fully compressible
-models but similar solutions are obtained solving Boussinesq equations.
+\add[HW]{inviscid models ($\nu=0$, $\alpha=0$)} but similar solutions are obtained solving Boussinesq equations.
 The Boussinesq version has no background stratification in a domain
@@
 
-The solution of the \add[HW]{resolved 2D} rising buoyant bubble solving the Boussinesq equations
-for 1000s is shown in figure \ref{fig:bubble} with buoyancy coloured,
+\change[HW]{The solution of the  rising buoyant bubble solving the Boussinesq equations for 1000s}
+{The solution of the Boussinesq equations in two dimensions for the rising bubble at high resolution at the initial time, 500 seconds and 1000 seconds}
+is shown in figure \ref{fig:bubble} with buoyancy coloured,
 pressure contoured and the $w=0$ contour dotted. The solution is
-very similar to the fully compressible solution \cite{BF02}. The
-pressure gradients accelerate the flow beneath the bubble, decelerate
-the flow above the bubble and pull in air horizontally. Horizontally
-and conditionally averaged fields, conditioned on $w$, are shown
-in the top row of figure \ref{fig:bubble_singleUnderRes}. $\sigma_{1}$
-is the volume fraction of rising fluid at every height, $b_{0}$ and
-$b_{1}$ are the buoyancy conditioned on $w\le0$ and $w>0$, $w_{0}$
-and $w_{1}$ are the horizontal averaging rising and falling vertical
-velocity and $P_{0}$ and $P_{1}$ are the pressure of the rising
-and falling fluid. An accurate multi-fluid model of convection should
-reproduce these fields approximately at coarser horizontal resolution
-or in a \change[HW]{single}{one} column model.
+very similar to the fully compressible solution \cite{BF02}.
+The pressure gradients accelerate the flow beneath the bubble, decelerate
+the flow above the bubble and pull in air horizontally. 
+\add[HW]{The $w=0$ contour at the initial time shows the initial tendency of $w$ which demonstrates that there is no straightforward relationship between buoyancy and $w$; $w$ is the solution of an eliptic problem involving the momentum equation and the divergence free constraint.
+After 500 seconds the centre of the bubble has risen further than the edges and after 1000 seconds there is a complex region of entrainment inside the bubble consisting of both buoyant and neutral rising air and buoyant and neutral sinking air.
+It is unlikely that the simple parameterisations proposed here will be able to reproduce statistics of this complex behaviour.}
 
@@
 \noindent \begin{centering}
-\includegraphics[width=\textwidth]{figures/bubble.pdf}
+\includegraphics[width=0.9\textwidth]{figures/bubble.pdf}
 \par\end{centering}
-\caption{The single-fluid, resolved \add[HW]{2D} rising bubble after \add[HW]{0s, 500s and }1000s. Buoyancy is coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
-negative contours dashed. The $w=0$ contour is dotted.
-\label{fig:bubble}}
+\caption{\label{fig:bubble}The single-fluid, resolved \add[HW]{2D} rising bubble after \add[HW]{0s, 500s and }1000s. Buoyancy is coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
+negative contours dashed. The $w=0$ contour is dotted.}
 \end{figure}
 
-\citeA{TEB19} and \citeA{WM19} assumed that both fluids would share
-the same pressure with differences parameterised as drag. The pressure
-in figure \ref{fig:bubble} shows that this is a bad assumption since
-the large pressure anomalies are in the rising fluid. Drag would always
-act to slow down the fluids whereas the negative pressure gradients
-in the rising fluid just below the bubble are acting to accelerate
-the rising motion.
-
-The horizontal averages are shown in figure \ref{fig:bubble_singleUnderRes}
-for horizontal resolutions of nine columns, five columns, three columns
-and \change[HW]{a single}{one} column \change{HW}{all for}{covering} the 20km wide domain and all \remove[HW]{still} using
-$\Delta z=100\ \text{m}$. These simulations are initialised by conservative
-horizontal averaging from the full resolution solution. As the horizontal
-resolution is reduced, the vertical transport reduces until there
-is no movement at all for \change[HW]{a single column}{the one column simulation}: there is no possibility
-of fluid rising because in \change[HW]{a single}{one} column with a single-fluid there
-can be no compensating subsidence. The lack of vertical transport
-at coarse resolution motivates convection parameterisation.
+\citeA{TEB19} and \citeA{WM19}
+\change[HW]{assumed that both fluids would share}{used} the same pressure
+\add[HW]{for both fluids} with differences parameterised as drag. 
+\add[HW]{The high pressure above and low pressure below the bubble in figure {\protect\ref{fig:bubble}} are a manifestation of form drag and will act to slow the ascent.
+However the pressure patterns in figure {\protect\ref{fig:bubble}} also show the limitations of this approach; the low pressure region at the bottom of the bubble will also act to accelerate the rising flow into the bubble which is not accounted for by drag and there are also widespread pressure anomalies in the sinking fluid which will accelerate the descent whereas drag will always act to slow the fluid.}
+\remove[HW]{The pressure in figure {\protect\ref{fig:bubble}} shows that this is a bad assumption since the large pressure anomalies are in the rising fluid.
+Drag would always act to slow down the fluids whereas the negative pressure gradients in the rising fluid just below the bubble are acting to accelerate the rising motion.}
+
+\change[HW]{Horizontally and conditionally averaged fields, conditioned on $w$, are}
+{Large scale models of the atmosphere often have coarse horizontal resolution and relatively fine vertical resolution.
+The high resolution solution is horizontally averaged, conditioned based on the sign of $w$, to give the vertical profiles that we would like coarse resolution models or parameterisations to reproduce.
+Sinking air and air with $w=0$ is assigned to fluid zero and rising air to fluid one and an average is taken over the $x$ direction at time $t=1000\ \text{s}$ to give the profiles}
+shown in the top row of figure \ref{fig:bubble_singleUnderRes}.
+$\sigma_{1}$ is the volume fraction of rising fluid at every height and $b_{0}$ and $b_{1}$, $w_{0}$ and $w_{1}$ and $P_{0}$ and $P_{1}$
+are the average buoyancy vertical velocity and pressure of the rising and falling fluids. 
+\add[HW]{$\sigma_1$ varies little with height.
+The complex shape of the bubble is evident in $b_0$ which has two peaks; the lower peak associated with re-entrained air.
+The fastest ascent is at the bottom of the bubble, co-located with a large drop in pressure.
+}
+\remove[HW]{An accurate multi-fluid model of convection should
+reproduce these fields approximately at coarser horizontal resolution
+or in a single column model.}
 
@@
 
+\add[HW]{In order to see what happens in a single fluid atmospheric model at modest horizontal resolution without a parameterisation of convection, the bubble is simulated at coarser horizontal resolutions, using nine, five, three and one columns instead of the 200 columns of the fine resolution to cover the 20km wide domain and a vertical space of $\Delta z=100\ \text{m}$.}
+The \add[HW]{conditional and} horizontal averages \add[HW]{of these simulations} are shown in figure \ref{fig:bubble_singleUnderRes}
+\remove[HW]{for horizontal resolutions of nine columns, five columns, three columns and a single column all for the 20km wide domain and all still using
+$\Delta z=100\ \text{m}$.}
+These simulations are initialised by conservative
+horizontal averaging from the full resolution solution. As the horizontal
+resolution is reduced, the vertical transport reduces until there
+is no movement at all for \change[HW]{a single column}{the one column simulation}: there is no possibility
+of fluid rising because in \change[HW]{a single}{one} column with a single-fluid there can be no compensating subsidence. The lack of vertical transport
+at coarse resolution motivates convection parameterisation.
+
 \subsubsection{Results of the Two-fluid, \change[HW]{Single}{One} Column Simulations}
@@
 fluid one. The velocity field after one time step is used for initialisation
-as the air is stationary at $t=0$. Results are shown in figures \ref{fig:multiFluidSingleColumn-bad}
-and \ref{fig:multiFluidSingleColumn} for various assumptions about
+as the air is stationary at $t=0$. Results after 500 seconds are shown in figures \ref{fig:multiFluidBubble_500_1}
+and \ref{fig:multiFluidBubble_500_2} for various assumptions about
 transfers between fluids and various parameter values.
@@
 \includegraphics[width=\linewidth]{figures/multiFluidBubble_500_1.pdf}
-\caption{Results of the rising bubble at $t=500\ \text{s}$. Solid lines are
-the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
-lines are the single-fluid, resolved solutions.
-\label{fig:multiFluidBubble_500_1}}
+\caption{\label{fig:multiFluidBubble_500_1} Results of the rising bubble at $t=500\ \text{s}$.
+Solid lines are the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble.
+Dashed lines are the single-fluid, resolved solutions.}
 \end{figure}
+
+\change[HW]{If there is}
+{The solutions in the top row of figure {\protect\ref{fig:multiFluidBubble_500_1}} have}
+no drag between fluids, no transfers, no diffusion and
+the pressures of both fluids are assumed equal \add[HW]{meaning that} the multi-fluid
+equations \change[HW]{are}{should be} unstable \cite{TEB19}. The simulation with ($S_{ij}=0$)
+in the top row of figure \ref{fig:multiFluidBubble_500_1} actually
+has small transfers to prevent either $\sigma_{i}$ from becoming
+negative. This is sufficient to stabilise the solution but does not
+prevent oscillations from developing in all fields. The buoyant fluid
+has risen little from the initial conditions. $\sigma_1$ oscillates
+between zero and one meaning that only one fluid is present at some
+locations so there is no possibility for the fluids to move past each
+other.
+\add[HW]{The two fluids have mixed due to the two way stabilising transfers which has reduced the buoyancy in the rising fluid and increased the buoyancy in the sinking fluid.}
+
+Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ stabilises the solution and
+\add[HW]{leads to a realistic rising volume fraction} (second row of
+figure \ref{fig:multiFluidBubble_500_1}).
+The fluids move \add[HW]{a little further} past each other
+even without pressure differences between the fluids. However \change[HW]{too much is detrained from fluid 1, fluid 1 loses too much buoyancy}{there is too much mixing between the fluids}
+and a discontinuity arises at the bubble leading edge; the buoyancy force is producing vertical motion but there is no pressure to make it smooth.
+
+Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
+and pressure difference between the fluids controlled by divergence
+($P_{i}=P-\gamma\nabla\cdot\sigma_i\mathbf{u}_{i}$), \add[HW]{the} simulations are more realistic (bottom three rows of figure \ref{fig:multiFluidBubble_500_1}),
+\add[HW]{all with a realistic $\sigma_1$ profile}.
+Three values of $\gamma$ are tested, the first being set from equation
+(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
+radius, a buoyancy scale equal to the initial maximum \add[HW]{initial} buoyancy 
+\add[HW]{and $\sigma=1$}
+to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
+(third row of figure \ref{fig:multiFluidBubble_500_1}) makes
+the velocity profile
+\change[HW]{too smooth and the updraft too weak so the
+bubble does not rise enough.}
+{smoother and leads to pressure differences between the fluids with some similarity to the resolved simulation although the large drop in pressure at the trailing edge of the bubble is missed.
+There is still too much mixing between the fluids and the $w_1$ profile is too sharp at the leading edge of the bubble.}
+\change[HW]{It is reasonable to consider smaller
+values of $\gamma$ because the buoyancy does not retain its initial
+maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
+leads to the leading edge of the bubble rising too quickly.}
+{Larger values of $\gamma$ are used in order to increase the pressure difference between fluids and smooth out the discontinuity in the velocity.
+$\gamma=4\times 10^4\text{m}^{2}\text{s}^{-1}$ gives a bubble rise and buoyancy similar to the resolved simulation and a smooth velocity profile whereas $\gamma=6\times 10^4\text{m}^{2}\text{s}^{-1}$ smooths out the velocity too much and the bubble rises too slowly.}
+Smaller values of $\gamma$ leave a discontinuity in the updraft velocity at the leading edge of the bubble and larger values of $\gamma$ reduce the velocity further \remove[HW]{meaning that the bubble does not rise enough} (not shown).
+None of the values of $\gamma$ reproduce the \change[HW]{peak updraft velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest, meaning that the bubble rise and $\sigma_{1}$ are approximately correct and}{pressure dip at the trailing edge of the bubble but the }
+pressure increases above the centre of the bubble are realisitic.
+\remove[HW]{The large low pressure at the bottom of the bubble is not reproduced.
+This is located at the lobes of the highest buoyancy in the resolved simulation (figure {\protect\ref{fig:bubble}}).
+It would be tempting to model this by assuming hydrostatic pressure or the Bernouilli equation, but these are both forms of the momentum equation which is used to calculate the velocity and so cannot also be used to model the pressure.}
+
+The results in the top row of figure \ref{fig:multiFluidBubble_500_2}
+use
+\change[HW]{$\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ }
+{divergence transfer and pressure differences between fluids but, different from previous simulations, also use}
+\remove[HW]{but this time with}
+drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
+drag slows the updrafts without increasing the mixing between the
+fluids which makes the solutions less like the resolved simulations.
+Although drag is known to be an important term in the momentum equations for buoyant thermals and plumes \cite<e.g.,>{RC15}, the drag is related to
+\add[HW]{pressure differences caused by the relative motion and to}
+mixing with downdraft air.
+\change[HW]{which is accounted for in the entrainment
+term of the momentum equation.}
+{These are already accounted for in the pressure difference and entrainment parameterisations}
+so adding a separate term for drag risks double counting and slows the plume too much.
 
@@
 
-\begin{figure}
-\noindent
-\includegraphics[width=\linewidth]{figures/multiFluidBubble_1000.pdf}
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
-lines are the single-fluid, resolved solutions.
-\label{fig:multiFluidBubble_1000}}
-\end{figure}
-
-If there is no drag between fluids, no transfers, no diffusion and
-the pressures of both fluids are assumed equal then the multi-fluid
-equations are unstable \cite{TEB19}. The simulation with ($S_{ij}=0$)
-in the top row of figure \ref{fig:multiFluidSingleColumn-bad} actually
-has small transfers to prevent either $\sigma_{i}$ from becoming
-negative. This is sufficient to stabilise the solution but does not
-prevent oscillations from developing in all fields. The buoyant fluid
-has risen very little from the initial conditions. $\sigma$ oscillates
-between zero and one meaning that only one fluid is present at some
-locations so there is no possibility for the fluids to move past each
-other.
-
-Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-stabilises the solution and enable the fluids to move past each other
-even without pressure differences between the fluids (second row of
-figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
-detrained from fluid 1, fluid 1 loses too much buoyancy and a discontinuity
-arises at the bubble leading edge; the buoyancy force is producing
-vertical motion but there is no pressure to make it smooth.
-
-Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
-and pressure difference between the fluids controlled by divergence
-($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$), \add[HW]{the} simulations are more
-realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
-Three values of $\gamma$ are tested. $\gamma$ is set from equation
-(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
-radius and a buoyancy scale equal to the initial maximum buoyancy
-to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
-(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
-the velocity profile too smooth and the updraft too weak so the
-bubble does not rise enough. It is reasonable to consider smaller
-values of $\gamma$ because the buoyancy does not retain its initial
-maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
-gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
-leads to the leading edge of the bubble rising too quickly. Smaller
-values of $\gamma$ leave a discontinuity in the updraft velocity
-at the leading edge of the bubble and larger values of $\gamma$ reduce
-the velocity further, meaning that the bubble does not rise enough
-(not shown). None of the values of $\gamma$ reproduce the peak updraft
-velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
-meaning that the bubble rise and $\sigma_{1}$ are approximately correct
-and pressure increases above the centre of the bubble are realisitic.
-The large low pressure at the bottom of the bubble is not reproduced.
-This is located at the lobes of the highest buoyancy in the resolved
-simulation (figure \ref{fig:bubble}). It would be tempting to model
-this by assuming hydrostatic pressure or the Bernouilli equation,
-but these are both forms of the momentum equation which is used to
-calculate the velocity and so cannot also be used to model the pressure.
-
-The results in the top row of figure \ref{fig:multiFluidSingleColumn}
-use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
-this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
-drag slows the updrafts without increasing the mixing between the
-fluids which makes the solutions less like the resolved simulations.
-Although drag is known to be an important term in the momentum equations
-for buoyant thermals and plumes \cite<e.g.,>{RC15}, the drag is related
-to mixing with downdraft air which is accounted for in the entrainment
-term of the momentum equation. So adding a separate term from drag
-risks double counting and slows the plume too much.
-
-If we include pressure difference between fluids with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$but
-omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidSingleColumn})
-the fluids move past each other but there is an unrealistic discontinuity
-with no fluid 1 below the buoyant fluid and very little falling air
-at the lowest height of the rising fluid. With \change[HW]{single}{one} column and
+If we include pressure difference between fluids with $\gamma=4\times 10^{4}\text{m}^{2}\text{s}^{-1}$ but
+omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
+the fluids move past each other but there is an unrealistic discontinuity with \change[HW]{no}{very little} fluid 1 below the \change[HW]{buoyant fluid}{bubble.}
+\remove[HW]{and very little falling air at the lowest height of the rising fluid.}
+With \change[HW]{single}{one} column and
 two fluids, all air must rise in one fluid and sink in the other.
@@
 rate, $\varepsilon=0.2/r_{c}$. This is used \change[HW]{combined}{in combination with} with pressure
-differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
-This combination produces smooth solutions but the updraft is too
+differences between fluids in the third row of figure \ref{fig:multiFluidBubble_500_2}.
+This combination produces smooth solutions but the \add[HW]{rising volume fraction is not right, the} updraft is too
 weak and too much is entrained into fluid 1. Using this entrainment,
@@
 between updraft and downdraft have been tested. The results in
-the fourth row \change[HW]{if}{of} figure \ref{fig:multiFluidSingleColumn} assume
-that the fluid transferred has zero buoyancy in order to keep the
+the fourth row \change[HW]{if}{of} figure \ref{fig:multiFluidBubble_500_2} assume that the fluid transferred has zero buoyancy in order to keep the
 positively buoyant air in fluid one and the negatively buoyant air
@@
 buoyancy in fluid one which is not present in the resolved simulation.
-The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
+The results in the bottom row of figure \ref{fig:multiFluidBubble_500_2}
 use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citeA{TEB19}
 so that the fluid transferred is influenced by the fluid it is moving
-towards as well as where it has come from. This again leads to very
-large buoyancy in fluid one and also negative buoyancy in fluid zero
-which \change[HW]{should not occurfor this test case.}{does not occur in the conditionally averaged reference solution.} These simple models reinforce
+towards as well as where it has come from. 
+\change[HW]{These solutions are similar to the resolved solutions but the bubble has moved a little too fast.}
+{This again leads to very large buoyancy in fluid one.}
+\remove[HW]{These simple models reinforce
 the idea that the buoyancy of the fluid transferred should depend
-on knowledge of \change[HW]{sub-grid-scale}{sub-filter-scale} variability of $b$ within each fluid
-\textendash{} these simple assumptions can lead to unrealistic behaviour.
-The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
-fluid transferred takes the mean properties with it. \add[HW]{Modelling of higher-order moments of variability within each fluid is an area of active research.}
-
-This section has demonstrated the \change[HW]{value of using}{plausible utility of} \change[HW]{single column, multi-}{a two-}fluid model to simulate a \add[HW]{sub-grid-scale} buoyant rising bubble with a single
+on knowledge of sub-grid-scale variability of $b$ within each fluid.
+These simple assumptions can lead to unrealistic behaviour. The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the fluid transferred takes the mean properties with it.}
+
+\remove[HW]
+{This section has demonstrated the value of using single column, multi-fluid model to simulate a buoyant rising bubble with a single
 updraft fluid and a single downdraft fluid. Transfers between
-the fluids have been \remove[HW]{successfully} modelled using entrainment set by divergence giving \remove[HW]{realistic} updraft fractions \add[HW]{close to the conditionally averaged reference solution}.
-Entrainment calculated
+the fluids have been successfully modelled using entrainment set by divergence giving realistic updraft fractions. Entrainment calculated
 as the reciprocal of plume width was not successful. The pressure
 difference between the fluids has also been represented by divergence
-with a coefficient close to that expected from dimensional analysis.
-Including drag between the fluids did not improve simulations. Two
-models of transferring non-mean properties between fluids were tested
-but neither was plausible. There are clearly discrepancies between
-the single-fluid resolved rising bubble and the two fluid \change[HW]{single}{one} column
-rising bubble but we do not want to over fit the multi-fluid model
-to one, dry, two dimensional test case.
-
-\add[HW]{Using the lessons learned from modelling the rising bubble, a statistically stationary case with many plumes is simulated next.}
+with a coefficient close to that expected from dimensional analysis. Including drag between the fluids did not improve simulations.
+Two models of transferring non-mean properties between fluids were tested
+but neither was plausible}.
+
+\begin{figure}
+\noindent
+\includegraphics[width=\linewidth]{figures/multiFluidBubble_1000.pdf}
+\caption{\label{fig:multiFluidBubble_1000} Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
+the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
+lines are the single-fluid, resolved solutions.
+}
+\end{figure}
+
+\add[HW]{
+From the results at 500 seconds, we can conclude that:
+\protect\begin{itemize}
+\item divergence transfer (entrainment and detrainment) leads to realistic updraft area fractions,
+\item the pressure difference between fluids is usefully modelled by divergence with a coefficient close to theat expected from scale analysis,
+\item a drag term is not useful and
+\item entrainment calculated as the reciprocal of plume width is not useful.
+\protect\end{itemize}
+In order to examine further the effects of different assumptions about the buoyancy of the fluid transferred, a selection of results at 1000 seconds are presented in figure {\protect\ref{fig:multiFluidBubble_1000}}.
+None of the simulations reproduce the complex buoyancy pattern at the trailing edge of the bubble associated with a deep low pressure.
+The rising air fraction ($\sigma_1$) at and below the bubble is too low in all simulations.
+The top row which uses $b_{ij}^T=b_i$ (transferring the mean buoyancy) shows too much mixing between the fluids -- too much of the most buoyant air has been transferred out of fluid 1 but the leading edge of the bubble has risen about the right amount.
+In the other two simulations, the air that is transferred out of fluid 1 has lower buoyancy than the mean in fluid 1 ($b_{10}^T<b_1$) so the remaining rising fluid stays very buoyant and rises too far.
+The assumption that the buoyancy transferred is zero (middle row of figure {\protect\ref{fig:multiFluidBubble_1000}} means that the buoyant fluid increases its buoyancy above the initial conditions which would not be possible in the resolved single-fluid solution.}
+
+\add[HW]{It might be possible to improve aspects of this simulation by optimising $\gamma$ and $\theta_b$ (the coefficient from eqn ({\protect\ref{eq:bijT_thetab}}) for calculating $b_{ij}^T$) but it is probably not helpful to over fit the two-fluid model to this dry, two dimensional test case.
+There are clearly discrepancies between
+the single-fluid resolved rising bubble and the two fluid one column rising bubble but rather than trying to fit this test case closely, cases with multiple plumes in each column should be considered.
+Using the lessons learned from modelling the rising bubble, a statistically stationary case with many plumes is simulated next.}
 
@@
 
-\subsubsection{Single-Fluid Solutions}
-
 This test case is designed to have strong updrafts in narrow plumes
@@
 the complication of moisture, phase changes and three spatial dimensions.
+
+\subsubsection{Single-Fluid Solutions}
+
 A snapshot of the buoyancy, vertical velocity and pressure of the
@@
 
+\begin{figure}
 \noindent 
-\begin{figure}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/bw}
-
-Buoyancy ($\text{m}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/bw_b}
-
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/Pw}
-
-Pressure ($\text{m}^{2}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/Pw_P}
-
-\caption{Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
+\includegraphics[width=1\textwidth]{figures/RCE_resolved.pdf}
+\caption{\label{fig:RCE_resolved}
+Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
 of the resolved radiative-convective equilibrium test case. Vertical
@@
 and the zero contour dotted. The domain is 10km high and 160km wide
-and the z-direction is stretched a factor of 2 in the plots. \label{fig:RCE_resolved}}
+and the z-direction is stretched a factor of 2 in the plots.}
 \end{figure}
@@
 
+\begin{figure}
+\noindent
+\includegraphics[width=\linewidth]{figures/RCE_singleColumn.pdf}
+\caption{\label{fig:RCE_singleColumn}
+Results of the RCE simulations. The top row shows horizontal averages
+of the resolved case between $t=10^{5}\text{s}$ and $2\times10^{5}\text{s}$. The bottom two rows show results of the \change[HW]{single}{one} column multi-fluid model after $10^{4}\ \text{s}$. }
+\end{figure}
+
 Results of a simulations using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
 is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
-This model of the buoyancy of the transferred fluid is bad; it leads
+This model of the buoyancy of the transferred fluid is \change[HW]{bad}{not helpful}; it leads
 to strong cooling in fluid zero near the ground due to the large transfers.
@@
 
-\begin{figure}
-\setlength\tabcolsep{0.5pt}%
-\begin{tabular}{ccccc}
-$\sigma$
-&
-$\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
-\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case}\tabularnewline
-\includegraphics[scale=0.7]
-{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean}
-&
-\includegraphics[scale=0.7]
-{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer}
-&
-\includegraphics[scale=0.7]
-{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}
-\tabularnewline
-\multicolumn{5}{c}{\change[HW]{Single}{One} column with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=b_{i}$, $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
-}\tabularnewline
-\includegraphics[scale=0.7]
-{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma_1}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b_1}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u_1}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P_1}
-\tabularnewline
-\multicolumn{5}{c}{\change[HW]{Single}{One} column  with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma_1}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b_1}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u_1}
-&
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P_1}\tabularnewline
-\end{tabular}
-
-\caption{Results of the RCE simulations. The top row shows horizontal averages
-of the resolved case between $t=10^{5}\text{s}$ and $2\times10^{5}\text{s}$. The
-bottom two rows show results of the \change[HW]{single}{one} column multi-fluid model
-after $10^{4}\ \text{s}$. \label{fig:RCE_singleColumn}}
-\end{figure}
+\add[HW]{The two-fluid, one column model of RCE gave results closer to the reference solution than for the rising bubble.
+This is likely to be because for RCE the rising and falling fluids are averaged over a large area with plumes at different stages of development rather than trying to simulate the complex entrainment pattern behind a single bubble.}
 
@@
 
+\add[HW]{This paper demonstrate the plausible utility of using multi-fluid equations to represent sub-grid-scale convection.}
 \change[HW]{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
 at coarse horizontal resolution.}
-{This paper presents solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) which reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
+{Solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
 Two test cases are used to \change[HW]{validate}{evaluate}
@@
 with heating at the ground and uniform radiative cooling. High resolution
-single-fluid simulations are coditionally averaged based on the sign
-of vertical velocity ($w$) in order to \change[HW]{create}{define} rising and falling
-fluids which each have their own mean buoyancy, velocity and pressure.
-The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
-heat and mass transport of these test cases.
+single-fluid simulations are conditionally averaged based on the sign
+of vertical velocity ($w$) in order to \change[HW]{create}{define} rising and falling fluids which each have their own \remove[HW]{mean} buoyancy, velocity and pressure.
+The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical heat and mass transport of these test cases.
 
@@
 \change[HW]{zero}
-{constrained to be zero following the single-fluid Boussinesq equations.}
+{constrained to be zero by the single-fluid Boussinesq equations.}
 A model is proposed and \change[HW]{validated}{evaluated} for the pressure difference between the rising
@@
 Conditionally averaging the high resolution solutions based on $w$
-leads to convecting and non-convecting regions with area fractions,
+leads to
+\change[HW]{convecting and non-convecting regions}
+{rising and falling fluids} with area fractions,
 $\sigma_{i}$, which are approximately uniform with height. Models
-for entrainment and detrainment into and out of convecting regions
+for entrainment and detrainment into and out of \change[HW]{convecting}{these} regions
 \change[HW]{must clearly}{need to} be consistent with the definition of the convecting region.
@@
 solutions.
-\change[HW]{We also test a}{A} more conventional fractional entrainment rate based on the reciprocal of the plume width \add[HW]{is also tested} which leads to unrealistic convecting area fractions.
-
-\change{A set of unknowns in the multi-fluid equations are the}{The} properties of the fluid that are transferred from one fluid to another \add[HW]{are unknowns in the multi-fluid equations that require closure}.
+\change[HW]{We also test a}{A} more conventional fractional entrainment rate based on the reciprocal of the plume width \add[HW]{is also tested} which leads to unrealistic \change[HW]{convecting}{rising} area fractions.
+
+\change{A set of unknowns in the multi-fluid equations are the}{The} properties of the fluid that are transferred from one fluid to another \add[HW]{are unknowns in the multi-fluid equations and these require closure}.
 An obvious
-first guess would be that fluid takes its mean buoyancy and velocity
+first guess is that fluid takes its mean buoyancy and velocity
 with it when it is transferred.
@@
 {Improvements on this assumption will depend on knowledge of sub-filter-scale variablity.
-However since conditional averaging is on $w$, it is consistent to assume that the fluid transferred has $w=0$.}
+However since conditional averaging is on $w$, it is consistent to assume that the fluid transferred has $w=0$ ($w_{ij}^T=0$).}
 \remove[HW]{We have tested}
 Three models for the buoyancy of the fluid transferred 
-\add[HW]{are proposed}. The most successful
-is to assume that the fluid takes its mean buoyancy with it. Assuming
-that the buoyancy of the transferred fluid is an average of the buoyancy
-of both fluids can lead to unrealistically large or small, unbounded
-buoyancies. 
+\add[HW]{are tested}. The most successful
+is to assume that the fluid takes its mean buoyancy with it
+\add[HW]{($b_{ij}^T=b_i$)}.
+Assuming that the buoyancy of the transferred fluid is an average of the buoyancy of both fluids \add[HW]{($b_{ij}^T=\frac{1}{2}(b_i+b_j)$)} can lead to unrealistically large or small, unbounded buoyancies.
 \change[HW]{Similarly, if we assume}{Assuming}
@@
 \remove[HW]{we transfer}
-fluid of zero buoyancy \add[HW]{is transferred},
-then unbounded buoyancy can occur. A better model of the buoyancy
+fluid of zero buoyancy \add[HW]{is transferred ($b_{ij}^T=0$) also leads to}, unbounded buoyancy. A better model of the buoyancy
 of the fluid transferred would rely on more information \add[HW]{of} the
@@
 \change[HW]{Single}{One} column multi-fluid modelling with moisture has already been demonstrated by \citeA{TEB19} 
-\add[HW]{and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19} }.
+\add[HW]{and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19}}.
 Two important next steps are to simulate convection in the grey zone (where it is partially resolved) and to represent sub-\change[HW]{grid}{filter}-scale variability within each fluid by solving multi-fluid prognostic equations for turbulent kinetic energy and other moments of the sub-\change[HW]{grid}{filter} variability.

### 2020-04-11 submit2/makeFigs.sh

@@ -1,7 +1,7 @@
 #!/bin/bash -e
 cd makeFigs
 
-for file in bubble bubble_singleUnderRes multiFluidBubble_500_1 multiFluidBubble_500_2 multiFluidBubble_1000; do
+for file in bubble bubble_singleUnderRes multiFluidBubble_500_1 multiFluidBubble_500_2 multiFluidBubble_1000 RCE_resolved RCE_singleColumn; do
     echo $file
     lyx --export pdflatex -f $file
     pdflatex $file

### 2020-04-21 submit2/makeFigs/RCE_singleColumn.tex
Will's changes and Hilary's changes to figures

@@
 \setlength{\parindent}{0pt}
+\usepackage{calc}
 \usepackage{amstext}
@@
 \begin{tabular}{ccccc}
-$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
-\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case between $t=10^{5}\text{s}$
-and $2\times10^{5}\text{s}$}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=b_{i}$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P_1}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P_1}\tabularnewline
+$\sigma_{1}$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
+\multicolumn{5}{c}{%
+\fbox{\begin{minipage}[t]{0.7\columnwidth}%
+\begin{center}
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$,
+\hspace{6pt}  $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
+\par\end{center}%
+\end{minipage}}}\tabularnewline
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P}\tabularnewline
+\multicolumn{5}{c}{%
+\fbox{\begin{minipage}[t]{0.7\columnwidth}%
+\begin{center}
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$,
+\hspace{6pt} $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
+\par\end{center}%
+\end{minipage}}}\tabularnewline
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P}\tabularnewline
 \end{tabular}

### 2020-04-21 submit2/manuscript.tex
Will's changes and Hilary's changes to figures

@@
 \addeditor{HW}
+\addeditor{WM}
 
@@
 to treat non-equilibrium and net mass transport \remove[HW]{correctly and} consistently.
-\add[HW]{The multi-fluids approach has an advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments directly (means of eg.
+\add[HW]{The multi-fluids approach has an advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments directly (mean properties of eg.
 updraft and environment) rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment.
@@
 section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore for simplicity we focus on the
-\remove[HW]{multi-fluid} Boussinesq equations without background stratification:
+and Buossinesq equations. Therefore\change[WM]{ for simplicity we focus on the}{, the}
+\remove[HW]{multi-fluid} Boussinesq equations without background stratification \add[WM]{are chosen for simplicity}:
 \note[HW]{This is additional material until the start of 2.1}
@@
 \tabularnewline
+\add[WM]{$\mathbf{k}$} & \add[WM]{Unit vector in the $z$-direction.}
+\tabularnewline
 \end{tabular}
@@
 Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere.
-For the derivation of the conditionally averaged equations we will not consider relabelling of fluid \add[HW]{and so} $I_i$ satisfies:
+For the derivation of the conditionally averaged equations \change[WM]{we will not consider relabelling of fluid}{the relabelling of fluids will not be considered,} \add[HW]{and so} $I_i$ satisfies:
 \begin{equation}
@@
 \end{equation}
-Applying conditional volume average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$:
+\change[WM]{Applying conditional volume average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$}{By applying a conditional volume average (denoted by the overbar), the fluid $i$ volume fractions, velocities and buoyancies are defined by}:
 \begin{eqnarray}
@@
 \end{equation}
-As we are considering the Boussinesq equations we assume that variations in density only affect the buoyancy terms so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.
-
-To derive a transport equation for $\sigma_i$ we combine (\ref{eq:LagrangianLabel}) with $I_i$ times (\ref{eq:singleDivFree}) and volume average.
-After permuting operators with the averaging \cite<as described by>{TWV+18} and using the definitions of $\sigma_i$ and $\mathbf{u}_i$ we get the evolution equation for $\sigma_i$:
+\change[WM]{As we are considering the Boussinesq equations we assume}{As the system is governed by the Boussinesq equations, it is assumed} that variations in density only affect the \change[WM]{buoyancy terms}{definition of the buoyancy terms (table \protect\ref{tab:defns})} so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.
+
+To derive a transport equation for $\sigma_i$\change[WM]{ we combine (\protect\ref{eq:LagrangianLabel})}{, (\protect\ref{eq:LagrangianLabel}) is combined} with $I_i$ times (\ref{eq:singleDivFree}) and volume average.
+After permuting operators with the averaging \cite<as described by>{TWV+18}\add[WM]{,} and using the definitions of $\sigma_i$ and $\mathbf{u}_i$\add[WM]{,} \remove[WM]{we get} the evolution equation for $\sigma_i$\add[WM]{ is obtained}:
 \begin{equation}
@@
 
-Next we will consider conditionally averaging the terms of the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations.
+Next \change[WM]{we will consider conditionally averaging the terms of }{the conditional averaging of terms in} the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations\add[WM]{ is considered}.
 Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
@@
 \note[HW]{Dan, can we do better than this?}
-Lots of terms appear when attempting to conditionally average the diffusion terms which we do not know how to parameterise. Therefore we will use simply:
+\change[WM]{Lots of}{Many} terms appear when attempting to conditionally average the diffusion terms which we do not know how to parameterise.
+\change[WM]{Therefore we will use simply}{The conditionally averaged diffusion terms are therefore assumed to behave like}:
 \begin{eqnarray}
@@
 %
-Unlike \citeA{TWV+18} we define separate pressures for each fluid, $P_i$. The pressures are defined to satisfy:
-\begin{equation}
-\overline{I_i \nabla P} = \sigma_i \nabla P_i.
-\end{equation}
+\remove[WM]{Unlike \protect\citeA{TWV+18}} \change[WM]{we define separate pressures for each fluid, $P_i$.
+The pressures are defined to satisfy:}{The pressures for each fluid, $P_i$, are defined to satisfy:}
+\begin{equation}
+\overline{I_i \nabla P} = \sigma_i \nabla P_i
+\end{equation}
+\add[WM]{which differs from \protect\citeA{TWV+18} who use a shared fluid pressure.}
 %
-Combining these gives the conditionally averaged momentum and buoyancy equations:
+Combining \change[WM]{these}{the above terms} gives the conditionally averaged momentum and buoyancy equations:
 \begin{eqnarray}
@@
 However for multi-fluids if one of the volume fractions is too small then it cannot force pressure anomalies big enough to stabilise the divergence.
-Use of separate pressure for each fluid is proposed to ensure stability.}
-
-We will assume that pressure in each fluid is given by a \remove[HW]{parameterised}
+Use of a separate pressure for each fluid is therefore proposed to ensure stability.}
+
+\change[WM]{We will assume that}{It is assumed that the} pressure in each fluid is given by a \remove[HW]{parameterised}
 perturbation, $p_{i}$, from the total pressure, $P$:
@@
 authors make different assumptions about the interface velocity but
-if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
+if \change[WM]{we assume}{one assumes} that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
 $\rho_{i}$ is constant then eqns (\ref{eq:divFree}), (\ref{eq:sumOne}), (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport})
 imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
-If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
-we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.
+\change[WM]{If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
+we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.}{Instead assuming $\mathbf{V}=\mathbf{u}_{i}$ for each fluid results in $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.}
 
@@
 term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
-If a fluid perturbation pressure is set to $-\nu\partial w/\partial z$
-this is equivalent to the diffusion term in one dimension. However
+If a fluid perturbation pressure is set to \change[WM]{$-\nu\partial w/\partial z$}{$p_i=-\nu\partial w/\partial z$}
+\add[WM]{then} this is equivalent to the diffusion term in one dimension. However
 adding a diffusion term will harm three dimensional simulations of
@@
 perturbation pressure will not. Inspired by both \citeA{BN86} and
-\citeA{TEB19} we assume that the pressure in each fluid is given
-by:
+\citeA{TEB19}\change[WM]{ we assume that the pressure in each fluid is given
+by}{, the pessure in each fluid is chosen to be}:
 \begin{equation}
@@
 \end{equation}
-\change[HW]{which is necessary to stop air in}{This formulation prevents} one fluid from accumulating when vertical motion ceases (at the top of a rising plume or at the bottom of descending air).
+\change[HW]{which is necessary to stop air in}{This formulation prevents} one fluid from accumulating when \change[WM]{vertical motion ceases}{a fluid decelerates} (at the top of a rising plume or at the bottom of descending air).
 \remove[HW]{We will also test a}{A} common form of lateral entrainment \cite<eg.>{DBF+13} \add[HW]{is also tested in section {\protect\ref{sec:results}}}:
@@
 \change[HW]{The different}{Each} fluid may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. \change[HW]
-{In fact, the most buoyant air should be transferred from fluid 0 to
-fluid 1 and vice versa, and the air with least downward momentum}
-{Since conditional averaging is based on the vertical velocity, $w$, the sub-set of fluid 0 that is about to be rising}
+may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. \change[WM]{In fact, the most buoyant air should be transferred from fluid 0 to
+fluid 1 and vice versa, and the air with least downward momentum
 should be transferred from 0 to 1 and vice versa.
-\change[HW]{The properties of the fluids transferred should depend on the modelling of sub-grid-scale variability which}
-{A realistic estimate of the properties of the fluid transferred can only be made based on knowledge of sub-filter-scale variability (i.e.
+The properties of the fluids transferred should depend on the modelling of sub-grid-scale variability which
+is beyond the scope of this paper.}{A realistic estimate of the properties of the fluid transferred can only be based on knowledge of the sub-filter-scale variability (i.e.
 the variability within each fluid).
-Modelling of sub-filter-scale variability}
-is beyond the scope of this paper.
-%
-In section \ref{sec:results}
+However, modelling of sub-filter-scale variability is beyond the scope of this paper.}
+
+\change[WM]{In section 4
 we conditionally average high resolution solutions based on the sign
 of $w$ so that $w\le 0$ air is in fluid 0 and $w>0$ air in fluid 1.
-Therefore the air that is transferred at the interface will have $w=0$.
-For two dimensional multi-fluid simulations we \add[HW]{could} assume that the horizontal
+Therefore the air that is transferred at the interface will have $w=0$.}{Since conditional averaging is based on the vertical velocity in this study, the sub-set of fluid 0 that is about to rise (i.e.
+within the next timestep) should be transferred from fluid 0 to fluid 1, and vice versa for the fluid about to fall in fluid 1.
+The fluid transferred will pass through the fluid interface and will therefore have a vertical velocity of $w=0$.}
+For \change[WM]{two}{three} dimensional multi-fluid simulations \change[WM]{we}{one} \add[HW]{could} assume that the horizontal
 velocity transferred is equal to the mean horizontal velocity of the
-fluid transferred from. Therefore
+fluid transferred from\change[WM]{. Therefore}{:}
 \begin{equation}
@@
 \end{equation}
-\add[HW]{However two dimensional multi-fluid simulations are not presented in this paper.}
+\add[WM]{However, only one dimensional multi-fluid simulations are presented in this paper.}
 
@@
 \add[HW]{implying that the average over all fluids of $b_i$, $\mathbf{u}_i$ and $P_i$ are zero}.
-\item We consider only the vertical direction where $w_{ij}^{T}=0$.
+\item \change[WM]{We consider only the vertical direction}{Only the vertical direction is considered} where $w_{ij}^{T}=0$.
 \item $P_{i}=P-\gamma\nabla\cdot\sigma_i \mathbf{u}_{i}\approx-\gamma\nabla\cdot\sigma_i\mathbf{u}_{i}=-\gamma\frac{\partial \sigma_i w_{i}}{\partial z}$
@@
 \item There are two fluids, \change[HW]{$i$ and $j$}{0 and 1.}
-\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
-and $S_{ji}=0$.
+\item Without loss of generality\add[WM]{,} \change[WM]{we assume that}{the transfers} $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
+and $S_{ji}=0$ \add[WM]{are used}.
 \end{enumerate}
@@
 \add[HW]{where $\sigma$ is a typical value of $\sigma_i$ which must be $O(1)$ for one of the fluids.}
-Then the non-dimensional version of (\ref{eq:wi_balances}) is \add[HW]{then}:
+\change[WM]{Then the}{The} non-dimensional version of (\ref{eq:wi_balances}) is \add[HW]{then}:
 \begin{equation}
@@
 The flow is buoyancy dominated so the buoyancy term should be $O(1)$
-\change[HW]{so we choose}{which implies} the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$. \change[HW]{so}{Therefore} the non-dimensional momentum equation becomes:
+\change[HW]{so we choose}{which implies} the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$. \change[HW]{so}{Therefore,} the non-dimensional momentum equation becomes:
 \begin{equation}
@@
 with no off-centering and with deferred correction of explicitly solved
-variables. \remove[HW]{It differs from} \citeA{WM19}
-\change[HW]{because here we solve the Boussinesq equations and we need stable solutions for equations with a separate pressure in each fluid.}
-{solved the Euler equations with a single pressure. The method of finding separate pressure for each fluid is new.}
-We use two outer iterations per
-time step to update explicitly solved variables. For the first outer
+variables. \change[WM]{It differs from}{The method for calculating a separate pressure for each fluid is new because} \citeA{WM19}
+\change[WM]{because here we solve the Boussinesq equations and we need stable solutions for equations with a separate pressure in each fluid.}
+{solved the Euler equations with a single pressure.}
+\change[WM]{We use two outer iterations per
+time step}{Two outer iterations per timestep are used} to update explicitly solved variables. For the first outer
 iteration, predicted values for time $n+1$ are set to those from
@@
 \change[HW]{The first equation to be solved each outer iteration is eqn}
-{The first calculation each outer iteration is for the transfer terms, $S_{ij}$ using ({\protect\ref{eq:Sdiv}}) or ({\protect\ref{eq:fracEnt}}). Next}
+{The first calculation of each outer iteration is for the transfer terms, $S_{ij}$ using ({\protect\ref{eq:Sdiv}}) or ({\protect\ref{eq:fracEnt}}). Next}
 (\ref{eq:sigma}) \add[HW]{is solved}
@@
 gradient calculated from just the values of pressure either side of
-the face. Once we have calculated $P^{n+1}$, the velocity flux (without
+the face. Once \change[WM]{we have calculated $P^{n+1}$}{$P^{n+1}$ is calculated}, the velocity flux (without
 momentum transfers) is updated from the back-substitution:
@@
 Boussinesq equations at high horizontal and vertical resolution.
-\add[HW]{These will be compared with the two-fluid model run using one column.
-We aim to reproduce the vertical heat transport, the mean velocity of the rising air, the bouyancy of the rising air and the pressure differences between fluids in one column of the two-fluid model.}
+\add[HW]{These will be compared with the two-fluid model run using one column.} \add[WM]{The aim is to reproduce} \add[HW]{the vertical heat transport, the mean velocity of the rising air, the bouyancy of the rising air and the pressure differences between fluids in one column of the two-fluid model.}
 
@@
 \begin{equation}
-b=\frac{1}{15}\cos^{2}\frac{\pi L}{2}\label{eq:thetaPerturb}
+b=\frac{1}{15}\cos^{2}\left(\frac{\pi L}{2}\right)\label{eq:thetaPerturb}
 \end{equation}
@@
 {Large scale models of the atmosphere often have coarse horizontal resolution and relatively fine vertical resolution.
-The high resolution solution is horizontally averaged, conditioned based on the sign of $w$, to give the vertical profiles that we would like coarse resolution models or parameterisations to reproduce.
-Sinking air and air with $w=0$ is assigned to fluid zero and rising air to fluid one and an average is taken over the $x$ direction at time $t=1000\ \text{s}$ to give the profiles}
+The high resolution solution is horizontally averaged, conditioned based on the sign of $w$, to give the vertical profiles that coarse resolution models or parameterisations should reproduce.
+Sinking air and air with $w=0$ is assigned to fluid 0 and rising air to fluid 1 and an average is taken over the $x$ direction at time $t=1000\ \text{s}$ to give the profiles}
 shown in the top row of figure \ref{fig:bubble_singleUnderRes}.
@@
 
-If we include pressure difference between fluids with $\gamma=4\times 10^{4}\text{m}^{2}\text{s}^{-1}$ but
-omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
+If \change[WM]{we include pressure difference between fluids}{pressure differences between fluids are included} with $\gamma=4\times 10^{4}\text{m}^{2}\text{s}^{-1}$ \change[WM]{but
+omit}{without} entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
 the fluids move past each other but there is an unrealistic discontinuity with \change[HW]{no}{very little} fluid 1 below the \change[HW]{buoyant fluid}{bubble.}
@@
 \protect\begin{itemize}
-\item divergence transfer (entrainment and detrainment) leads to realistic updraft area fractions,
-\item the pressure difference between fluids is usefully modelled by divergence with a coefficient close to theat expected from scale analysis,
-\item a drag term is not useful and
-\item entrainment calculated as the reciprocal of plume width is not useful.
+\item Divergence transfer (entrainment and detrainment) leads to realistic updraft area fractions.
+\item Pressure differences between fluids are usefully modelled by divergence, with a coefficient close to the derived value from scale analysis.
+\item Drag terms are not useful.
+\item Entrainment calculated as the reciprocal of plume width is not useful.
 \protect\end{itemize}
@@
 In the other two simulations, the air that is transferred out of fluid 1 has lower buoyancy than the mean in fluid 1 ($b_{10}^T<b_1$) so the remaining rising fluid stays very buoyant and rises too far.
-The assumption that the buoyancy transferred is zero (middle row of figure {\protect\ref{fig:multiFluidBubble_1000}} means that the buoyant fluid increases its buoyancy above the initial conditions which would not be possible in the resolved single-fluid solution.}
+The assumption that the buoyancy transferred is zero (middle row of figure {\protect\ref{fig:multiFluidBubble_1000}}) means that the buoyant fluid increases its buoyancy above the initial conditions which would not be possible in the resolved single-fluid solution.}
 
@@
 between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
-in the top row of figure \ref{fig:RCE_singleColumn}. The rising and
+\change[HW]{in the top row of}{as dashed lines in} figure \ref{fig:RCE_singleColumn}. The rising and
 falling volume fractions, $\sigma_{1}$ and $\sigma_{0}$, remain
@@
 $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
-is shown in the second row of figure \ref{fig:RCE_singleColumn}.
+is shown in the top row of figure \ref{fig:RCE_singleColumn}.
 The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
@@
 \caption{\label{fig:RCE_singleColumn}
-Results of the RCE simulations. The top row shows horizontal averages
-of the resolved case between $t=10^{5}\text{s}$ and $2\times10^{5}\text{s}$. The bottom two rows show results of the \change[HW]{single}{one} column multi-fluid model after $10^{4}\ \text{s}$. }
+Results of the RCE simulations. \protect\change[HW]{The top line shows}{Dashed lines show} horizontal averages
+of the resolved case between $t=10^{5}\text{s}$ and $2\times10^{5}\text{s}$.
+\protect\change[HW]{The bottom two rows show}{Solid lines show} results of the \change[HW]{single}{one} column multi-fluid model after $10^{4}\ \text{s}$.
+}
 \end{figure}
 
-Results of a simulations using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
+Results of a simulation\remove[WM]{s} using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
 is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
@@
 \add[HW]{The two-fluid, one column model of RCE gave results closer to the reference solution than for the rising bubble.
-This is likely to be because for RCE the rising and falling fluids are averaged over a large area with plumes at different stages of development rather than trying to simulate the complex entrainment pattern behind a single bubble.}
+This is likely to be because} \add[WM]{the rising and falling fluids in the RCE test case} \add[HW]{are averaged over a large area with plumes at different stages of development rather than trying to simulate the complex entrainment pattern behind a single bubble.}
 
@@
 
-\add[HW]{This paper demonstrate the plausible utility of using multi-fluid equations to represent sub-grid-scale convection.}
+\add[HW]{This paper demonstrates the plausible utility of using multi-fluid equations to represent sub-grid-scale convection.}
 \change[HW]{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
@@
 {Improvements on this assumption will depend on knowledge of sub-filter-scale variablity.
-However since conditional averaging is on $w$, it is consistent to assume that the fluid transferred has $w=0$ ($w_{ij}^T=0$).}
+However since conditional averaging is based on the sign of $w$, it is consistent to assume that the fluid transferred has $w=0$ ($w_{ij}^T=0$).}
 \remove[HW]{We have tested}
@@
 \remove[HW]{we transfer}
-fluid of zero buoyancy \add[HW]{is transferred ($b_{ij}^T=0$) also leads to}, unbounded buoyancy. A better model of the buoyancy
-of the fluid transferred would rely on more information \add[HW]{of} the
-sub-\change[HW]{grid}{filter}-scale variability.
+fluid of zero buoyancy \add[HW]{is transferred ($b_{ij}^T=0$) also leads to}, unbounded buoyancy. \remove[WM]{A better model of the buoyancy
+of the fluid transferred would rely on more information of the
+sub-grid-scale variability.}
 

### 2020-05-04 submit2/makeFigs/multiFluidBubble_500_1.tex
Nearly ready to resubmit. A better pressure perturbation model is used.

@@
 \begin{center}
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
 \hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/Pcompare}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/Pcompare}\tabularnewline
 \multicolumn{4}{c}{%
@@
 \begin{center}
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=6\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{3}\text{m}^{2}\text{s}^{-1}$,
 \hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/Pcompare}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/Pcompare}\tabularnewline
 $\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline

### 2020-05-04 submit2/makeFigs/multiFluidBubble_500_2.tex
Nearly ready to resubmit. A better pressure perturbation model is used.

@@
 \begin{center}
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\times10^{4}\text{m}^{2}\text{s}^{-1}$,
 \hspace{6pt} $C_{D}/r_{c}=1/2000\text{m}^{-1}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/Pcompare}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/Pcompare}\tabularnewline
 \multicolumn{4}{c}{%
@@
 \begin{center}
-$S_{ij}=0$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,
+$S_{ij}=0$, \hspace{6pt} $\gamma=1\times10^{4}\text{m}^{2}\text{s}^{-1}$,
 \hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/Pcompare}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/Pcompare}\tabularnewline
 \multicolumn{4}{c}{%
@@
 \begin{center}
-$S_{ij}=w_{1}0.2/r_{c}$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,
+$S_{ij}=w_{1}0.2/r_{c}$, \hspace{6pt} $\gamma=1\times10^{4}\text{m}^{2}\text{s}^{-1}$,
 \hspace{6pt} $C_{D}/r_{c}=0/2000\text{m}^{-1}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/Pcompare}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/Pcompare}\tabularnewline
 \multicolumn{4}{c}{%
@@
 \begin{center}
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
 \hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=0$
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/Pcompare}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/Pcompare}\tabularnewline
 \multicolumn{4}{c}{%
@@
 \begin{center}
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
 \hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/Pcompare}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/Pcompare}\tabularnewline
 $\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline

### 2020-05-04 submit2/manuscript.tex
Nearly ready to resubmit. A better pressure perturbation model is used.

@@
 \usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
-\usepackage{soul}
+%\usepackage{soul}
+\soulregister\ref7
+\soulregister\cite7
 \linenumbers
@@
 updraft and environment) rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment.
-Solving directly for sub-fluid means should be less sensitive to closure assumptions.}
+Solving directly for sub-fluid means could be less sensitive to closure assumptions.}
 \remove{with the same numerics and physics to prognose properties of separate parts of the fluid, for example updrafts, the stable environment and downdrafts dynamics}. \citeA{Yano14} derived similar
@@
 \remove[HW]{multi-fluid} Boussinesq equations without background stratification \add[WM]{are chosen for simplicity}:
-\note[HW]{This is additional material until the start of 2.1}
+
+\note[HW]{Additional material until the start of 2.1}
 \begin{eqnarray}
@@
 The single-fluid Boussinesq equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations.
-Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere.
+Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and 0 elsewhere.
 For the derivation of the conditionally averaged equations \change[WM]{we will not consider relabelling of fluid}{the relabelling of fluids will not be considered,} \add[HW]{and so} $I_i$ satisfies:
@@
 %
-\remove[WM]{Unlike \protect\citeA{TWV+18}} \change[WM]{we define separate pressures for each fluid, $P_i$.
-The pressures are defined to satisfy:}{The pressures for each fluid, $P_i$, are defined to satisfy:}
+\change[WM]{Unlike Thuburn et al. (2018) we define separate pressures for each fluid, $P_i$. The pressures are defined to satisfy:}{The pressures for each fluid, $P_i$, are defined to satisfy:}
 \begin{equation}
@@
 \end{equation}
+\add[HW]{
+For stability and respect $\sum_i \nabla\cdot\sigma_i\mathbf{u}_i=0$, we propose four constraints on the pressure perturbations, $p_i$:}
+\begin{enumerate}
+\item $\sum_{i}\sigma_{i}p_{i}=0$.
+\item $\mathbf{u}_{i}=\mathbf{u} \implies p_i=0$ so that pressure perturbations do not force individual fluid anomalies away from the mean.
+\item $p_i \not\to 0$ when $\sigma_i\to 0$ so that pressure perturbations control divergence in vanishing fluids.
+\item $p_i\not\to\infty$ as $\sigma_j\to 0$ for any combination of $i,j$.
+\end{enumerate}
+
 \add[HW]{In order to derive a suitable form of parameterisation for $p_i$ we will first consider the} \citeA{BN86} \add{model of multi-phase flow.}
@@
 pressure of each fluid relaxes to the mean pressure and index $j$
-refers to the other fluid in a two fluid system. In our Boussinesq
-system, $\rho_{i}$ does not appear in the continuity equation. Different
-authors make different assumptions about the interface velocity but
-if \change[WM]{we assume}{one assumes} that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
-$\rho_{i}$ is constant then eqns (\ref{eq:divFree}), (\ref{eq:sumOne}), (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport})
-imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
-\change[WM]{If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
-we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.}{Instead assuming $\mathbf{V}=\mathbf{u}_{i}$ for each fluid results in $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.}
+refers to the other fluid in a two fluid system.
+\remove[HW]{In our Boussinesq system, $\rho_{i}$ does not appear in the continuity equation.}
+Different authors make different assumptions about the interface velocity.
+\change[HW]{but if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and $\rho_{i}$ is constant then eqns (\ref{eq:divFree}), (\ref{eq:sumOne}), (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport}) imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
+If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.}
+{The combination of equations (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport}) shows that the pressure difference between fluids is related to divergence.}
 
@@
 perturbation pressure will not. Inspired by both \citeA{BN86} and
-\citeA{TEB19}\change[WM]{ we assume that the pressure in each fluid is given
-by}{, the pessure in each fluid is chosen to be}:
-\begin{equation}
-p_{i}=-\gamma\nabla\cdot(\sigma_i \mathbf{u}_{i})
+\citeA{TEB19}
+\change[WM]{we assume that the pressure perturbation in each fluid is given
+by}{and obeying the constraints given above, the pressure in each fluid is chosen to be}:
+\begin{equation}
+p_{i}=\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j -\gamma\nabla\cdot\mathbf{u}_{i}
 \label{eq:Pi_div}
 \end{equation}
-where $\gamma$ is a \change[HW]{free coefficient}{compressibility with units $\text{m}^s \text{s}^{-1}$. 
-This parameterisation of $p_i$ has $\sigma_i$ inside the divergence in order to ensure that $\sum_i p_i =0$ and therefore that $\sum_i P_i = P$ which makes the equations more striaghtforward to solve.}
-\add[HW]{However it should be noted that this parameterisation destroys energy conservation.}
+where $\gamma$ is a \change[HW]{free coefficient}{compressibility with units $\text{m}^s \text{s}^{-1}$. It should be noted that this parameterisation destroys energy conservation.}
 
@@
 \end{equation}
-\add[HW]{Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}. The first is}
+\add[HW]{Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}. The first is similar to}
 \remove[HW]{We consider dry air without turbulence so use}
@@
 \item \change[WM]{We consider only the vertical direction}{Only the vertical direction is considered} where $w_{ij}^{T}=0$.
-\item $P_{i}=P-\gamma\nabla\cdot\sigma_i \mathbf{u}_{i}\approx-\gamma\nabla\cdot\sigma_i\mathbf{u}_{i}=-\gamma\frac{\partial \sigma_i w_{i}}{\partial z}$
+\item $P_{i} = P + \gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j 
+                              - \gamma\nabla\cdot\mathbf{u}_{i}
+             \approx-\gamma\nabla\cdot\mathbf{u}_{i}
+            =-\gamma\frac{\partial w_{i}}{\partial z}$
 \item \add[HW]{$\frac{\partial \sigma_i}{\partial z} \approx 0$}
@@
 \begin{equation}
-\frac{\partial w_{i}^{2}}{\partial z}-\gamma\sigma_i\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
+\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
 \end{equation}
@@
 \end{eqnarray*}
-\add[HW]{where $\sigma$ is a typical value of $\sigma_i$ which must be $O(1)$ for one of the fluids.}
 \change[WM]{Then the}{The} non-dimensional version of (\ref{eq:wi_balances}) is \add[HW]{then}:
 \begin{equation}
-\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma\sigma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
+\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
 \end{equation}
@@
 \begin{equation}
-\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma\sigma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
+\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
 \end{equation}
@@
 \begin{equation}
-\sigma\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
+\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
 \end{equation}
@@
 which is why they are calculated before $p_{i}$. The final stage
-of the time step iteration is to solve Helmholtz equations for each
-$p_{i}$:
-\begin{equation}
-\sigma_{i}^{n+1}p_{i}^{n+1}=-\gamma\nabla\cdot\left(\sigma_{if}^{n+1}u_{i}^{n+1}-\frac{\Delta t}{2}\sigma_{if}^{n+1}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right).\label{eq:pi_Helm}
+of the time step iteration is to solve Helmholtz equations implicitly for each
+$p_{i}^{n+1}$:
+\begin{equation}
+p_{i}^{n+1} = \gamma \sum_j \left(\sigma^{n+1}_j \nabla\cdot u_j^{n+1} \right)
+-\gamma\nabla\cdot
+\left(u_{i}^{n+1}-\frac{\Delta t}{2}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right)
+\label{eq:pi_Helm}
 \end{equation}
@@
 other.
-\add[HW]{The two fluids have mixed due to the two way stabilising transfers which has reduced the buoyancy in the rising fluid and increased the buoyancy in the sinking fluid.}
+\add[HW]{The two fluids have mixed due to the two way stabilising transfers which have reduced the buoyancy in the rising fluid and increased the buoyancy in the sinking fluid.}
 
@@
 and pressure difference between the fluids controlled by divergence
-($P_{i}=P-\gamma\nabla\cdot\sigma_i\mathbf{u}_{i}$), \add[HW]{the} simulations are more realistic (bottom three rows of figure \ref{fig:multiFluidBubble_500_1}),
-\add[HW]{all with a realistic $\sigma_1$ profile}.
-Three values of $\gamma$ are tested, the first being set from equation
-(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
-radius, a buoyancy scale equal to the initial maximum \add[HW]{initial} buoyancy 
-\add[HW]{and $\sigma=1$}
-to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
-(third row of figure \ref{fig:multiFluidBubble_500_1}) makes
-the velocity profile
-\change[HW]{too smooth and the updraft too weak so the
-bubble does not rise enough.}
-{smoother and leads to pressure differences between the fluids with some similarity to the resolved simulation although the large drop in pressure at the trailing edge of the bubble is missed.
-There is still too much mixing between the fluids and the $w_1$ profile is too sharp at the leading edge of the bubble.}
-\change[HW]{It is reasonable to consider smaller
-values of $\gamma$ because the buoyancy does not retain its initial
-maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
-leads to the leading edge of the bubble rising too quickly.}
-{Larger values of $\gamma$ are used in order to increase the pressure difference between fluids and smooth out the discontinuity in the velocity.
-$\gamma=4\times 10^4\text{m}^{2}\text{s}^{-1}$ gives a bubble rise and buoyancy similar to the resolved simulation and a smooth velocity profile whereas $\gamma=6\times 10^4\text{m}^{2}\text{s}^{-1}$ smooths out the velocity too much and the bubble rises too slowly.}
-Smaller values of $\gamma$ leave a discontinuity in the updraft velocity at the leading edge of the bubble and larger values of $\gamma$ reduce the velocity further \remove[HW]{meaning that the bubble does not rise enough} (not shown).
-None of the values of $\gamma$ reproduce the \change[HW]{peak updraft velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest, meaning that the bubble rise and $\sigma_{1}$ are approximately correct and}{pressure dip at the trailing edge of the bubble but the }
-pressure increases above the centre of the bubble are realisitic.
-\remove[HW]{The large low pressure at the bottom of the bubble is not reproduced.
+($P_{i}=P+\gamma\sum_j \sigma_j \nabla\cdot\mathbf{u}_j-\gamma\nabla\cdot\mathbf{u}_{i}$), \add[HW]{the} simulations are more realistic (bottom three rows of figure \ref{fig:multiFluidBubble_500_1}).
+The first value, $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$, is set from equation
+(\ref{eq:gammaDimAnal}) using length scale equal to the initial bubble
+radius and a buoyancy scale equal to the initial maximum buoyancy. This makes
+the velocity profile too smooth and the updraft too weak so the
+bubble does not rise enough.
+It is reasonable to consider smaller values of $\gamma$ because the buoyancy does not retain its initial maximum for very long.
+Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$ leads to the leading edge of the bubble rising too quickly \add[HW]{and does not fully remove the discontinuity in the updraft velocity at the leading edge of the bubble}.
+\add[HW]{Pressure differences between the fluids have some similarity with the resolved simulation but none of the values of $\gamma$ reproduce the pressure dip at the trailing edge of the bubble.
+$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives the closest approximation to the resolved simulation.}
+\remove[HW]{peak updraft velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest, meaning that the bubble rise and $\sigma_{1}$ are approximately correct.
+The large low pressure at the bottom of the bubble is not reproduced.
 This is located at the lobes of the highest buoyancy in the resolved simulation (figure {\protect\ref{fig:bubble}}).
@@
 
-If \change[WM]{we include pressure difference between fluids}{pressure differences between fluids are included} with $\gamma=4\times 10^{4}\text{m}^{2}\text{s}^{-1}$ \change[WM]{but
-omit}{without} entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
-the fluids move past each other but there is an unrealistic discontinuity with \change[HW]{no}{very little} fluid 1 below the \change[HW]{buoyant fluid}{bubble.}
+If
+\change[WM]{we include pressure difference between fluids}
+{pressure differences between fluids are included}
+with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
+\change[WM]{but omit}{without}
+entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
+the fluids move past each other but there is 
+\change[HW]{an unrealistic discontinuity with no}
+{a build up of fluid 1 at the leading edge of the bubble and very little}
+fluid 1 below the \change[HW]{buoyant fluid}{bubble.}
 \remove[HW]{and very little falling air at the lowest height of the rising fluid.}
@@
 The other entrainment option is the commonly used fractional entrainment
-rate, $\varepsilon=0.2/r_{c}$. This is used \change[HW]{combined}{in combination with} with pressure
-differences between fluids in the third row of figure \ref{fig:multiFluidBubble_500_2}.
-This combination produces smooth solutions but the \add[HW]{rising volume fraction is not right, the} updraft is too
-weak and too much is entrained into fluid 1. Using this entrainment,
-the updraft will entrain more and more air until $\sigma_{1}=1$.
-The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives
+rate, $\varepsilon=0.2/r_{c}$. This is used \change[HW]{combined}{in combination with} with pressure differences between fluids in the third row of figure \ref{fig:multiFluidBubble_500_2}.
+\change[HW]{This combination produces smooth solutions}
+{The solutions are smooth}
+but the \add[HW]{rising volume fraction is not right with a build up of fluid 1 at the bubble leading edge, the} updraft is too
+weak and too much is entrained into fluid 1 \add[HW]{above the bubble}.
+Using this entrainment, the updraft will entrain more and more air until $\sigma_{1}=1$. The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives
 \change[HW]{much more accurate entrainment and detrainment for this test case using conditional averaging based on $w$.}
-{results closer to the reference solution conditionally averaged based on $w$.}
+{results closer to the reference solution.}
 
@@
 in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraft),
-the mean buoyancy of fluid one increases. This leads to very high
-buoyancy in fluid one which is not present in the resolved simulation.
+the mean buoyancy of fluid one increases. This leads to
+\change[HW]{very high buoyancy in fluid one which is not present in the resolved simulation.}
+{higher buoyancy in fluid one than when using $b_{ij}^T=b_i$ and gives results close to the reference solution.}
 The results in the bottom row of figure \ref{fig:multiFluidBubble_500_2}
@@
 towards as well as where it has come from. 
-\change[HW]{These solutions are similar to the resolved solutions but the bubble has moved a little too fast.}
-{This again leads to very large buoyancy in fluid one.}
+These solutions are \add[HW]{also} similar to the resolved solutions.
+\remove[HW]{but the bubble has moved a little too fast.}
 \remove[HW]{These simple models reinforce

### 2020-05-04 submit2/makeAllFigs.sh

@@ -1,0 +1,8 @@
+#!/bin/bash -e
+
+for file in bubble bubble_singleUnderRes multiFluidBubble_500_1 multiFluidBubble_500_2 multiFluidBubble_1000 RCE_resolved RCE_singleColumn; do
+    echo $file
+
+    (cd makeFigs; ./makeFig.sh $file)
+done
+

### 2020-05-04 submit2/makeFigs.sh

@@ -1,18 +1,0 @@
-#!/bin/bash -e
-cd makeFigs
-
-for file in bubble bubble_singleUnderRes multiFluidBubble_500_1 multiFluidBubble_500_2 multiFluidBubble_1000 RCE_resolved RCE_singleColumn; do
-    echo $file
-    lyx --export pdflatex -f $file
-    pdflatex $file
-    pdf2ps $file.pdf
-    makebb $file.ps
-    mv $file.ps $file.eps
-    pdfcrop $file.pdf $file.cropped.pdf
-    mv $file.cropped.pdf $file.pdf
-    mv $file.eps $file.pdf ../figures
-    gv ../figures/$file.eps &
-done
-
-cd ..
-

### 2020-05-04 submit2/makeFigs/makeFig.sh

@@ -1,0 +1,19 @@
+#!/bin/bash -e
+
+if [ "$#" -ne 1 ]
+then
+   echo usage: makeFig.sh $file
+   exit
+fi
+file=$1
+
+lyx --export pdflatex -f $file
+pdflatex $file
+pdf2ps $file.pdf
+makebb $file.ps
+mv $file.ps $file.eps
+pdfcrop $file.pdf $file.cropped.pdf
+mv $file.cropped.pdf $file.pdf
+mv $file.eps $file.pdf ../figures
+gv ../figures/$file.eps &
+

### 2020-07-03 submit2/PeterComments/Boussinesque_scaling.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

\documentclass[a4paper,10pt]{article}
\usepackage{a4wide,graphicx,fancyhdr,texdraw}
\usepackage{parskip}
\usepackage{natbib}

\usepackage{amssymb,amsmath,amsfonts,titlesec,graphicx,placeins}
\usepackage[export]{adjustbox}
\usepackage[margin=1.2in]{geometry}
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}
\begin{document}

\section{Boussinesq equations}

\subsection{Scaling}
Returning to the single fluid equations, we introduce external length scale $L$ and buoyancy scale $B$ determined by the initial or boundary conditions. 
We also introduce internal scales for time ($T$) and pressure ($P$) to be determined. 
Velocities thus scale by $L/T$. 
Note, we could equally have chose a velocity scale $U$, and the time scales by $L/U$.
Denoting scaled variables by hats, we can write the scaled equations as: 
\begin{equation}
\frac{L}{T^2}\left[\frac{\partial {\hat{\mathbf{u}}} }{\partial \hat{t}} +\hat{\nabla} \cdot \left(\hat{\mathbf{u}}\hat{\mathbf{u}}\right)\right]+\frac{P}{L}\hat{\nabla}\hat{P} = B\hat{b} {\mathbf{k}} + \frac{\nu}{L T}\hat{\nabla}^2 {\hat{\mathbf{u}}}
\end{equation}
\begin{equation}
\frac{B}{T}\left[\frac{\partial \hat{b} }{\partial \hat{t}} +\hat{\nabla} \cdot \left(\hat{\mathbf{u}}\hat{b}\right)\right] =\frac{\alpha B}{L^2} \hat{\nabla}^2 \hat{b}
\end{equation}
\begin{equation}
\frac{1}{T}\hat{\nabla} \cdot  \hat{\mathbf{u}} =0
\end{equation}
Rearranging and simplifying leads to:
\begin{equation}
\frac{\partial {\hat{\mathbf{u}}} }{\partial \hat{t}} +\hat{\nabla} \cdot \left(\hat{\mathbf{u}}\hat{\mathbf{u}}\right)
+\frac{PT^2}{L^2}\hat{\nabla}\hat{P} = \frac{BT^2}{L}\hat{b} {\mathbf{k}} + \frac{\nu T}{L^2}\hat{\nabla}^2 {\hat{\mathbf{u}}}
\label{eq:scaled_momentum}
\end{equation}
\begin{equation}
\frac{\partial \hat{b} }{\partial \hat{t}} +\hat{\nabla} \cdot \left(\hat{\mathbf{u}}\hat{b}\right) = \frac{\alpha T}{L^2} \hat{\nabla}^2 \hat{b}
\label{eq:scaled_buoyancy}
\end{equation}
\begin{equation}
\hat{\nabla} \cdot  \hat{\mathbf{u}} =0
\label{eq:scaled_continuity}
\end{equation}

The Boussinesq continuity equation, eq. \eqref{eq:scaled_continuity} says nothing about the choice of scales.
The parameter in front of the viscous term in eq. \eqref{eq:scaled_momentum} can be identified as the inverse Reynolds number, $Re^{-1}=\nu T / L^2 = \nu /(U L)$.
Problems with very high Reynolds number are of primary interest, so $Re^{-1}\rightarrow 0$. 
Likewise, the thermal diffusion term on the right of eq. \eqref{eq:scaled_buoyancy} can be identified as $(\sigma Re)^{-1}$, where $\sigma = \nu/\alpha$ is the Prandtl number, generally $O(1)$. 
Thus, eq. \eqref{eq:scaled_buoyancy} also says nothing about choice of scales when $Re^{-1} \rightarrow 0$.    
It does, however, imply that in these circumstances, buoyancy is conserved on fluid parcels.

To identify the appropriate choice of scales, eq. \eqref{eq:scaled_momentum} must be examined.
The last term is small in high $Re$ flow. 
The choice of timescale should be such that, together, the first two terms are $O(1)$; this must be balanced by either the pressure gradient term, the buoyancy term, or a combination of the two. 
If the last, we can factor out a stationary solution (which would be in hydrostatic balance).
Assuming this has been done so, it is further assumed that the flow is dominated by buoyancy (i.e. convection), which implies the first term on the right to be $O(1)$. 
Thus:
\begin{equation}
\frac{BT^2}{L}=1 \Rightarrow T = \left(\frac{L}{B}\right)^{\frac{1}{2}}.
\label{eq:T_scale}
\end{equation} 
The velocity scale is thus
\begin{equation}
U = \frac{L}{T} = \left(BL\right)^{\frac{1}{2}}.
\end{equation}
It makes sense to choose a pressure scale, $P$ such that the parameter in front of the pressure gradient term is also 1, i.e.
\begin{equation}
\frac{PT^2}{L^2}=1 \Rightarrow P = B L = U^2
\end{equation}
The final equality identifies this as Bernoulli scaling.
Note, however, that $\hat{\nabla}\hat{P}$ is only expected to be $O(1)$ in regions where buoyancy is not the main driver.

The Reynolds number can also be predicted from the external parameters:
\begin{equation}
Re=\frac{B^{\frac{1}{2}}L^{\frac{3}{2}}}{\nu}
\end{equation}

A central feature of the two-fluid model is the intermingling of fluids. 
A well-developed turbulent flow, tends to be filamentary, with the width of filaments limited by the flow viscosity and thermal diffusivity.
Assume such a filament has lateral scale $\delta$, and orient a local coordinate system with $x$ along the filament and $z$ across it. 
Scale $x$ by $L$, as above, but $z$ by $\delta$.
The continuity equation then implies that if the along-filament flow, $u$, is scaled by $U=L/T$, the across-filament flow should be scaled by $W=\delta U / L = \delta / T$.
For clarity, introduce a different time scale $T_d$.
Consider the buoyancy equation scaled in this way and re-arranged as above:
\begin{equation}
\left[\frac{\partial \hat{b} }{\partial \hat{t}} +
\frac{\partial ~}{\partial \hat{x}}\left(\hat{u} \hat{b}\right) 
+ \frac{\partial ~}{\partial\hat{z}}\left(\hat{w} \hat{b}\right)
\right] =
\frac{\alpha T_d}{\delta^2}
\left(\frac{\delta^2}{\L^2} \frac{\partial^2 \hat{b}}{\partial \hat{x}^2} + \frac{\partial^2 \hat{b}}{\partial \hat{z}^2} \right)
\end{equation}
The natural choice of time scale is the thermal diffusion time scale such that the coefficient of the right hand side is 1, so:
\begin{equation}
\frac{\alpha T_d}{\delta^2} \Rightarrow T_d = \frac{\delta^2}{\alpha}=\frac{\delta^2\sigma}{\nu}
\end{equation}

The momentum equation, oriented similarly, can also be scaled with this time scale but the along-filament velocity will be scaled by U above. 
Thus, along the filament:
\begin{equation}
\frac{U}{T_d}\left[\frac{\partial {\hat{u}} }{\partial \hat{t}} +
\frac{\partial ~}{\partial \hat{x}}\left(\hat{u} \hat{u}\right) 
+ \frac{\partial ~}{\partial\hat{z}}\left(\hat{w} \hat{u}\right)
\right]+\frac{P}{L}\frac{\partial \hat{P}}{\partial \hat{x}} = B\hat{b} k_\parallel + 
\frac{\nu U}{\delta^2}
\left(\frac{\delta^2}{\L^2} \frac{\partial^2 \hat{u}}{\partial \hat{x}^2} + \frac{\partial^2 \hat{u}}{\partial \hat{z}^2} \right)
\end{equation}
where $k_\parallel$ is the component of $\mathbf{k}$ along the filament.
Thus:
\begin{equation}
\left[\frac{\partial {\hat{u}} }{\partial \hat{t}} +
\frac{\partial ~}{\partial \hat{x}}\left(\hat{u} \hat{u}\right) 
+ \frac{\partial ~}{\partial\hat{z}}\left(\hat{w} \hat{u}\right)
\right]
+\frac{\delta^2\sigma}{\nu U}\frac{P}{L}\frac{\partial \hat{P}}{\partial \hat{x}} = \frac{\delta^2\sigma B}{\nu U}\hat{b} k_\parallel + 
\sigma
\left(\frac{\delta^2}{\L^2} \frac{\partial^2 \hat{u}}{\partial \hat{x}^2} + \frac{\partial^2 \hat{u}}{\partial \hat{z}^2} \right)
\end{equation}
If we use $P=U^2$ and $U^2=BL$, as above, the coefficient of the non-dimensional pressure gradient and the buoyancy both become $\sigma \frac{\delta^2}{L^2} Re$.
Since the combination of these terms drives the flow, and it is reasonable to suppose that the momentum time scale is $ T_m=T_d/\sigma$, we must have:
\begin{equation}
\frac{\delta^2}{L^2} Re = 1 \Rightarrow \frac{\delta}{L} =  Re^{-\frac{1}{2}}
\end{equation}

This is a classical Prandtl-Blasius scaling argument in the boundary layer that justifies ignoring the along-flow diffusion, but it applies equally well here (and, indeed, is consistent with the idea that the filaments start of as segments of boundary layer peeling away from the surface in surface-driven flows). Note that it is straightforward to show that this choice of $\delta$ leads to $T_m=T$, i.e. diffusion across filaments occurs in the same time scale as acceleration along, i.e. acceleration along collapses the filament at the same rate that diffusion broadens it.

It makes sense to conclude that the pressure difference across the filament scales as $\frac{\delta}{L}P = B \delta$ and hence that velocity perturbations across the filament scale as $(B\delta)^{1/2}$. 
If we call this $u_p$, and we parametrise these pressure perturbations as $p_i=-\gamma \nabla \cdot u_i$ then, nondimensionalising:
\begin{equation}
u_p^2 \hat{p}_i = -\gamma \frac{u_p}{\delta} \hat{\nabla} \hat{\mathbf{u}}_i\Rightarrow \gamma \propto u_p \delta = B^{1/2}\delta^{3/2}=B^\frac{1}{8} L^\frac{3}{8} \nu^\frac{3}{4} 
\end{equation}

\subsection{Choice of viscosity and thermal diffusivity in the RCE case.}
The chose values of $\alpha$ and $\nu$ are, of course, huge compared with the values for air.
We are assuming that our reference simulation is essentially a form of 'large eddy simulation' (LES), and the constant values chosen are eddy diffusivity and viscosity.
If we were to use a Smagorinsky (1963) formulation, $\nu = \lambda^2 \left|S\right|$; the maximum shear will be $\left|S\right|\sim U/\delta$, leading to $\lambda \sim 137$ m. 
This is somewhat large given the usual LES formulation $\lambda \approx 0.2 \delta x$, since $\delta x=250$ m, but it is the appropriate order of magnitude, bearing in mind that we have used an estimate of shear and could easily adjust this by a factro of two either way. 
A somewhat larger value has been chosen to attempt to encompass the idea that $\nu$ and $\alpha$ parametrize the majority of the incoherent turbulence that mixes the two fluids.

\subsection{Scales in the RCE problem}
If we take the standard buoyancy scaling above, then $U=(BL)^{1/2}$. 
In steady state, the surface buoyancy flux $h$ is carried through the fluid with a flux:
\begin{equation}
UB = h
\end{equation}
Thus 
\begin{equation}
\left(BL\right)^\frac{1}{2} B = h \Rightarrow B = h^\frac{2}{3} L^{-\frac{1}{3}}
\end{equation}
and hence
\begin{equation}
U=\left(hL \right)^\frac{1}{3}
\end{equation}
Taking the numerical values $L=10000$ m, $\nu = 70.7$~m$^2$~s$^{-1}$ and $h=10^{-3}$~m$^2$~s$^{-3}$ leads to $B=4.64\times 10^{-4}$ m~s$^{-2}$, $U = 2.154$~m~s$^{-1}$, $Re=304.7$, $\delta=572.8$ m and $\gamma=295.4$~m$^2$~s$^{-1}$.

\subsection{Scales in the rising bubble problem}
We assume $B=1/30$ m~s$^{-2}$, the mean initial perturbation, $L=2000$ m, the initial perturbation size, then with the standard buoyancy scaling above $U = 8.16$~m~s$^{-1}$. To estimate other scales we need to know the viscosity. Taking the same value as the RCE problem, $\nu = 70.7$~m$^2$~s$^{-1}$, leads to  $Re=231$, $\delta=131.6$ m and $\gamma=275.6$~m$^2$~s$^{-1}$.

Note to Hilary: I guess you're going to say the bubble is inviscid - in which case the effective viscosity comes from numerical diffusion and hence the resolution. 
The $\delta$ scale above is certainly not larger than the actual filament width in the reference solution, so I'd suggest that the actual effective viscosity is larger. 
Quadrupling $\nu$ gives $\delta = 263$ m and $\gamma = 779.6$ ~m$^2$~s$^{-1}$ which tallies quite well with your results (and also $\lambda=95$ m).

\end{document}

### 2020-07-03 submit3/makeFigs/RCE_singleColumn.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

--- 2020-04-21 submit2/makeFigs/RCE_singleColumn.tex
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P}\tabularnewline
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/P}\tabularnewline
 \multicolumn{5}{c}{%
@@
 \end{minipage}}}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P}\tabularnewline
+\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/P}\tabularnewline
 \end{tabular}

### 2020-07-03 submit3/makeFigs/bubble.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

--- 2020-07-03 submit3/makeFigs/RCE_singleColumn.tex
@@
 \setlength{\parindent}{0pt}
-\usepackage{calc}
-\usepackage{amstext}
 \usepackage{amssymb}
@@
 \makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
@@
 \begin{document}
-\setlength\tabcolsep{0.5pt}%
-\begin{tabular}{ccccc}
-$\sigma_{1}$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
-\multicolumn{5}{c}{%
-\fbox{\begin{minipage}[t]{0.7\columnwidth}%
-\begin{center}
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$,
-\hspace{6pt}  $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
-\par\end{center}%
-\end{minipage}}}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3/100000/P}\tabularnewline
-\multicolumn{5}{c}{%
-\fbox{\begin{minipage}[t]{0.7\columnwidth}%
-\begin{center}
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$,
-\hspace{6pt} $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
-\par\end{center}%
-\end{minipage}}}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi_2e3_bT05/100000/P}\tabularnewline
-\end{tabular}
+\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/0/bP}
+
+\hspace{2cm}\raisebox{3cm}[0cm][0cm]{$t=0$ s}
+
+\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/500/bP}
+
+\hspace{2cm}\raisebox{4cm}[0cm][0cm]{$t=500$ s}
+
+\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
+
+\hspace{2cm}\raisebox{5cm}[0cm][0cm]{$t=1000$ s}
+
+\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
 \end{document}

### 2020-07-03 submit3/makeFigs/bubble_singleUnderRes.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

--- 2020-03-23 preSubmission/manuscript.tex
@@
 \usepackage[latin9]{inputenc}
-\usepackage{geometry}
-\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
-\usepackage{array}
+\usepackage[a4paper]{geometry}
+\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
+\pagestyle{empty}
+\setcounter{secnumdepth}{5}
+\setcounter{tocdepth}{5}
+\setlength{\parskip}{\smallskipamount}
+\setlength{\parindent}{0pt}
 \usepackage{rotating}
-\usepackage{amsmath}
+\usepackage{amstext}
 \usepackage{amssymb}
 \usepackage{graphicx}
-\usepackage[authoryear]{natbib}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
-\usepackage { fancybox}
-\usepackage[export]{adjustbox}
-
-\usepackage{todonotes}
-%\usepackage{afterpage}
-
-%\usepackage[switch]{lineno}
-
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
-
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-%\usepackage{moreverb}
-
-\usepackage{flushend}
-
 \makeatother
 
+\usepackage{babel}
 \begin{document}
-
-\title{Multi-fluids for Representing Sub-filter-scale Buoyant Convection}
-
-\author{Hilary Weller, William McIntyre, Daniel Shipley and Peter Clark}
-\maketitle
-\begin{abstract}
-Multi-fluid modelling is a promising new method of representing sub
-and near grid-scale convection allowing for consistent and accurate
-treatment of net mass transport by convection, non-equilibrium and
-turbulence. The air is partitioned into convecting and non-convecting
-fluids each with their own velocity, temperature and constituents
-so that separate equations of motion can be solved for each fluid,
-thus representing features that cannot be resolved in a single fluid
-at coarse resolution.
-
-This paper presents multi-fluid Boussinesq equations for representing
-under resolved dry convection. We present a new model for entrainment
-and detrainment based on divergence which leads to excellent representation
-of the convective area fraction. Previous multi-fluid modelling of
-convection has assumed that all fluids share the same pressure. We
-show that this is a bad assumption and we propose and validate a model
-for the pressure difference between the fluids based on divergence.
-
-Two vertical slice test cases are used to validate the multi-fluid
-model; a buoyant rising bubble and radiative convective equilibrium
-are simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity. The multi-fluid model reproduces
-the mean properties of the rising and falling fluids in a single column. 
-\end{abstract}
-
-\section{Introduction}
-
-Slow progress has been made improving the parameterisation of sub-grid-scale
-convection since \citet{AS74,Tied89,GR90,KF90}. Convection is still
-one of the weakest aspects of large scale models of the atmosphere
-\citep{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
-the quasi-equilibrium assumption \citep{PR98,GG05,Par14}, including
-stochasticity \citep{PC08} and allowing net mass transport by convection
-\citep{KB08,MB19}. These developments have enabled limited simulation
-in the grey zone, where convection is partially resolved. However
-there are still systematic biases implying that improvements should
-still be possible.
-
-\citet{TWV+18} proposed multi-fluid modelling of convection in order
-to treat non-equilibrium and net mass transport correctly and consistently
-with the same numerics and physics controlling thermals, the stable
-environment and downdraught dynamics. \citet{Yano14} derived similar
-equations for multiple segments and showed how this is a generalisation
-of the mass-flux formulation. The \citet{TKP+18} ``extended eddy
-diffusivity mass flux'' or extended EDMF scheme also uses similar
-equations but \citet{TKP+18} didn't propose a suitable numerical
-method for solving the equations. Multi-fluids promises big improvements
-in the representation of sub-grid-scale convection and unification
-with the representation of turbulence, particularly at the grey zone.
-However, there is a long way to go, particularly as multi-fluids requires
-a dedicated model rather than being a stand alone parameterisation
-for a dynamical core. \citet{TEB19} and \citet{WM19} presented solutions
-of the multi-fluid equations assuming two fluids that share the same
-pressure (or that pressure differences are predominantly due to drag
-between the fluids). \citet{TEB19} showed that these equations (without
-drag) are in fact unstable and can be stabilised by diffusion of vertical
-velocity whereas \citet{WM19} stabilised the equations with diffusion
-and drag between fluids. Neither of these stabilisation techniques
-are acceptable and in this paper we show that there are significant
-and sustained pressure differences between the fluids (section \ref{sec:results}).
-
-This paper presents the multi-fluid Boussinesq equations for representing
-sub-grid-scale convection including a parameterisation of the pressure
-difference between fluids (section \ref{subsec:fluidPressure}) and
-a new model of entrainment and detrainment (section \ref{subsec:Sij}).
-The numerical method for solving the equations is described in section
-\ref{sec:numerics}. We compare results of resolved dry convection
-in a single-fluid two dimensional Boussinesq model with a two-fluid,
-single column model in section \ref{sec:results} using two vertical
-slice test cases.
-
-\section{The Multi-fluid Boussinesq Equations}
-
-Many of the challenges of representing convection with the multi-fluid
-Navier-Stokes equations \citep[eg those described in][]{WM19} carry
-over to the Boussinesq equations; convection is buoyancy dominated
-and close to incompressible. The resolved test cases presented in
-section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore for simplicity we focus on the
-multi-fluid Boussinesq equations without background stratification:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\} \label{eq:sigma}\\
-\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\} \label{eq:mom}\\
-\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}\\
-\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
-\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
-\end{eqnarray}
-with variables defined in table \ref{tab:defns}.
-
-\begin{table}[h]
-\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
-$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
-$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
-$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
-$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
-$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
-where $\rho^{\prime}$ are departures in density from a horizontally
-uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
-$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
-$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
-$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-\end{tabular}
-
-\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
-\end{table}
-
-\subsection{Pressure of each fluid \label{subsec:fluidPressure}}
-
-\citet{TEB19} and \citet{WM19} assumed that each co-located fluid
-shared the same pressure, leading to unstable equations that \citet{TEB19}
-stabilised using diffusion of vertical velocity and \citet{WM19}
-stabilised using mass exchanges or drag between the fluids. \citet{TEB19}
-achieved realistic results in single column experiments of convective
-boundary layer but the amount of diffusion needed would spoil simulations
-in the free troposphere. The stabilisation used by \citet{WM19} meant
-that the two fluids tended to move as one which defeats the purpose
-of using multi-fluid modelling.
-
-The instabilities reported by \citet{WM19} showed growing divergence
-in a fluid with vanishing volume fraction. It is mass convergence
-rather than velocity convergence that leads to pressure anomalies
-that remove the convergence. Therefore if the volume (or mass) fraction
-of fluid is vanishingly low then convergence cannot lead to an anomaly
-in the total pressure.
-
-We will assume that pressure in each fluid is given by a parameterised
-perturbation, $p_{i}$, from the total pressure, $P$:
-\begin{equation}
-P_{i}=P+p_{i}.
-\end{equation}
-
-\citet{BN86} proposed a parameterisation for pressure differences
-in a multi-phase explosion model that has been widely used in mathematics
-and engineering for simulating fluidised beds of granular material
-\citep[eg.][]{EHM92} and two compressible fluids \citep[eg.][]{SA99}.
-In these methods, advection equations are written for the volume fraction,
-$\sigma_{i}$, and conservation equations are written for mass fraction,
-$\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
-fluids, the \citet{BN86} equations would be:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)\label{eq:BNcompaction}\\
-\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0\label{eq:rhoTransport}
-\end{eqnarray}
-where $\mathbf{V}$ is the velocity of the interface between fluids,
-$\mu$ is the compaction viscosity which controls how quickly the
-pressure of each fluid relaxes to the mean pressure and index $j$
-refers to the other fluid in a two fluid system. In our Boussinesq
-system $\rho_{i}$ does not appear in the continuity equation. Different
-authors make different assumptions about the interface velocity but
-if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
-$\rho_{i}$ is constant then eqns (\ref{eq:divFree}-\ref{eq:rhoTransport})
-imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
-If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
-we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.
-
-\citet{TEB19} stabilised the multi-fluid equations by adding a diffusion
-term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
-If a fluid perturbation pressure is set to $-\nu\partial w/\partial z$
-this is equivalent to the diffusion term in one dimension. However
-adding a diffusion term will harm three dimensional simulations of
-resolved convection in the free troposphere whereas adding a fluid
-perturbation pressure will not. Inspired by both \citet{BN86} and
-\citet{TEB19} we assume that the pressure in each fluid is given
-by:
-\begin{equation}
-p_{i}=-\gamma\nabla\cdot\mathbf{u}_{i}\label{eq:Pi_div}
-\end{equation}
-where $\gamma$ is a free coefficient. Dimensional analysis in section
-\ref{subsec:dimAnal} will inform the choice of $\gamma$ and sensitivity
-to $\gamma$ will be evaluated in section \ref{sec:results}.
-
-\subsection{Entrainment and Detrainment \label{subsec:Sij}}
-
-We consider dry air without turbulence so use the dynamic entrainment
-described by \citet{HC51,AK67,DBF+13}:
-\begin{equation}
-S_{ij}=\begin{cases}
--\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
-0 & \text{otherwise}
-\end{cases}
-\end{equation}
-which is necessary to stop air in one fluid from accumulating when
-vertical motion ceases (at the top of a rising plume or at the bottom
-of descending air). We will also test a common form of lateral entrainment
-\citep{DBF+13}:
-\begin{equation}
-\varepsilon=\frac{0.2}{r_{c}}\implies S_{01}=w_{1}\frac{0.2}{r_{c}}
-\end{equation}
-where $\varepsilon$ is the well know fractional entrainment rate
-and $r_{c}$ is the cloud or plume radius.
-
-\subsection{Drag in the Momentum Equation\label{subsec:drag}}
-
-Pressure differences between the fluids can lead to form drag which
-is parameterised following \citet{SW69,RC15,WM19} as: 
-\begin{equation}
-\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
-\end{equation}
-where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
-Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.
-
-\subsection{The Buoyancy and the Momentum of the Mass that is Transferred \label{subsec:transferProperties}}
-
-The different fluids may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \citep[as was assumed by][]{WM19}.
-In fact, the most buoyant air should be transferred from fluid 0 to
-fluid 1 and vice versa, and the air with least downward momentum should
-be transferred from 0 to 1 and vice versa. The properties of the fluids
-transferred should depend on the modelling of sub-grid-scale variability
-which is beyond the scope of this paper. In section \ref{sec:results}
-we conditionally average high resolution solutions based on the sign
-of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
-Therefore the air that is transferred at the interface will have $w=0$.
-For two dimensional multi-fluid simulations we assume that the horizontal
-velocity transferred is equal to the mean horizontal velocity of the
-fluid transferred from. Therefore
-\begin{equation}
-\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
-v_{i}\\
-0
-\end{pmatrix}.
-\end{equation}
-For buoyancy, following \citet{TEB19}, we use:
-\begin{equation}
-b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
-\end{equation}
-and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
-Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
-transferred depends on the properties of the receiving fluid which
-is not logical and can lead to unbounded values of $b_{i}$ in the
-fluid that is loosing mass (as demonstrated in section \ref{sec:results}).
-
-\subsection{Dimensional Analysis\label{subsec:dimAnal}}
-
-Dimensional analysis can guide our choice of $\gamma$ for the parameterisation
-of the pressure difference between fluids. We make the following assumptions:
-\begin{enumerate}
-\item The flow is buoyancy dominated.
-\item The flow is close to inviscid.
-\item The flow is slowly varying.
-\item Fluid $i$ properties are anomalies from a neutrally stable resting
-mean state.
-\item We consider only the vertical direction where $w_{ij}^{T}=0$.
-\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
-\item There are two fluids, $i$ and $j$
-\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
-and $S_{ji}=0$.
-\end{enumerate}
-This leads to the following balance in the momentum equation:
-\begin{equation}
-\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
-\end{equation}
-We non-dimensionalise using a length scale $L$, a buoyancy scale
-$B$ and a time scale $T$ to get the non-dimensional variables:
-\begin{eqnarray*}
-\tilde{w} & = & w_{i}T/L\\
-\tilde{b} & = & b_{i}/B\\
-\tilde{z} & = & z/L.
-\end{eqnarray*}
-Then the non-dimensional version of (\ref{eq:wi_balances}) is:
-\begin{equation}
-\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
-\end{equation}
-The flow is buoyancy dominated so the buoyancy term should be $O(1)$
-so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
-so the non-dimensional momentum equation becomes:
-\begin{equation}
-\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
-\end{equation}
-The stabilisation term must be large enough to smooth out oscillations
-in $\tilde{w}$ due to advection and buoyancy but not too large to
-remove all variability in $\tilde{w}$ so we need:
-\begin{equation}
-\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
-\end{equation}
-
-\section{Numerical Solution \label{sec:numerics}}
-
-The spatial discretisation follows exactly \citet{WM19}, solving
-advective form equations using monotonic, finite volume advection
-and C-grid, Lorenz staggering. The time-stepping is Crank-Nicolson
-with no off-centering and with deferred correction of explicitly solved
-variables. It differs from \citet{WM19} because here we solve the
-Boussinesq equations and we need stable solutions for equations with
-a separate pressure in each fluid. We use two outer iterations per
-time step to update explicitly solved variables. For the first outer
-iteration, predicted values for time $n+1$ are set to those from
-time level $n$ and are given the superscript $\ell$. For the second
-iteration, values at $\ell$ are set to those from the end of the
-first iteration. The implicit numerical method for applying the transfers
-between fluids is specific for two fluids because it involves the
-inversion of $2\times2$ matrices.
-
-The prognostic variables are the $b_{i}$ in cell centres, the $\sigma_{i}$
-in cell centres and the velocity flux at cell faces, $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$,
-which is the velocity at cell faces dotted with the area vector for
-each face (normal to the face). The pressures, $P$ and $p_{i}$ are
-diagnostic.
-
-The first equation to be solved each outer iteration is eqn (\ref{eq:sigma})
-for each $\sigma_{i}$, operator split; first applying advection,
-then correcting $\sum_{i}\sigma_{i}=1$ and then applying mass transfers:
-\begin{eqnarray}
-\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\} \\
-\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}\\
-S_{ij} & = & \begin{cases}
--\nabla\cdot\mathbf{u}_{i}^{\ell} & \text{if }\nabla\cdot\mathbf{u}_{i}^{\ell}<0\\
-0 & \text{otherwise}
-\end{cases}\\
-\sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
-\end{eqnarray}
-where $\Delta t$ is the time step and the superscripts $\prime$
-and $\prime\prime$ denote intermediate values. $\sigma_{i}^{n}$
-is interpolated from cell centres onto cell faces using monotonic
-van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citet{WM19}
-and values exclusively at time level $n$ for best accuracy and guaranteed
-monotonicity. For calculating the divergence, the normal component
-of $\mathbf{u}_{i}$ is needed at cell faces which are prognostic
-variables of the C-grid. The $S_{ij}$ are limited to ensure $0<\sigma_{i}<1\ \forall i$.
-
-Next eqn (\ref{eq:b}) is solved for the buoyancy in each fluid, first
-transporting buoyancy and then applying the transfer terms. The transfer
-terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
-in the transfer term for $b_{i}$ so they are treated operator split
-and implicitly:
-\begin{eqnarray}
-b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
- &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
-b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
-b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
-\end{eqnarray}
-where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
-from before the mass transfers is necessary to ensure bounded and
-conservative transfers, as described by \cite{MWH1x}. Simultaneous
-solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
-\begin{eqnarray}
-b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
-b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
-\end{eqnarray}
-where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$
-
-Next a Poisson equation is solved to calculate the total pressure,
-$P$ to ensure that the total velocity is divergence free. The pressure
-equation also provides updates for the velocity flux, $u_{i}$. First
-an intermediate velocity flux is calculated with partial updates and
-updates from a previous value of $p_{i}$:
-\begin{eqnarray}
-u_{i}^{\prime}= & u_{i}^{n}+\frac{\Delta t}{2} & \biggl(\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{\ell}\cdot\mathbf{S}-\nabla_{f}p_{i}^{\ell}\\
- &  & +\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{n}\cdot\mathbf{S}-\nabla_{f}(P+p_{i})^{n}\biggr)
-\end{eqnarray}
-where operator $()_{f}$ means linear interpolation from cell centres
-onto cell faces and $\nabla_{f}P$ is a compact discretisation of
-$(\nabla P)_{f}\cdot\mathbf{S}$: ie the normal component of the pressure
-gradient calculated from just the values of pressure either side of
-the face. Once we have calculated $P^{n+1}$, the velocity flux (without
-momentum transfers) is updated from the back-substitution:
-\begin{equation}
-u_{i}^{\prime\prime}=u_{i}^{\prime}-\frac{\Delta t}{2}\nabla_{f}P^{n+1}.\label{eq:backSub}
-\end{equation}
-The Poisson equation for $P^{n+1}$ is found by multiplying each eqn
-(\ref{eq:backSub}) by $\sigma_{i}$, summing over all fluids and
-taking the divergence. Knowing that $\nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0$,
-$\sum_{i}\sigma_{i}=1$ and $\sum_{i}\sigma_{i}p_{i}=0$ gives:
-\begin{equation}
-\nabla\cdot\sum_{i}\sigma_{i}u_{i}^{\prime}-\frac{\Delta t}{2}\nabla^{2}P^{n+1}=0
-\end{equation}
-which is solved to find $P^{n+1}$.
-
-Next, the momentum transfers due to mass transfer and due to drag
-are calculated implicitly, similar to the implicit transfers of buoyancy,
-calculating $u_{i}^{n+1}$ from $u_{i}^{\prime\prime}$. These do
-not influence the total $P$ or total divergence because momentum
-is transferred conservatively. However they do influence $p_{i}$
-which is why they are calculated before $p_{i}$. The final stage
-of the time step iteration is to solve Helmholtz equations for each
-$p_{i}$:
-\begin{equation}
-\sigma_{i}^{n+1}p_{i}^{n+1}=-\gamma\nabla\cdot\left(\sigma_{if}^{n+1}u_{i}^{n+1}-\frac{\Delta t}{2}\sigma_{if}^{n+1}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right).\label{eq:pi_Helm}
-\end{equation}
-Both $p_{i}^{n+1}$ and $p_{i}^{\ell}$ appear in eqn (\ref{eq:pi_Helm})
-because $u_{i}^{n+1}$ already contains contributions from $p_{i}^{\ell}$
-so these are removed before updating $p_{i}^{n+1}$. No back substitution
-for $u_{i}$ is done after calculating $p_{i}^{n+1}$ because this
-would destroy the divergence free constraint. Therefore $p_{i}^{n+1}$
-only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
-converge and $p_{i}^{\ell}=p_{i}^{n+1}$.
-
-The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
-from $u_{i}$ following \citet{WM19}. The stages calculating $P$,
-$p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
-The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$.
-
-\section{Validation Test Cases\label{sec:results}}
-
-Two test cases are developed to tune parameters and to validate the
-use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
-convection. The first is transient; the standard rising bubble of
-\citet{BF02}. We aim to reproduce the vertical heat transport, the
-mean velocity of the rising air, the bouyancy of the rising air and
-pressure differences between two fluids in a single column two fluid
-model. The second test case is steady state with heat transfer at
-the ground and uniform radiative cooling. For both test cases the
-reference solution is a single fluid solution of the two-dimensional
-Boussinesq equations at high horizontal and vertical resolution.
-
-\subsection{Rising Bubble}
-
-The test case of \citet{BF02} was designed for fully compressible
-models but similar solutions are obtained solving Boussinesq equations.
-The Boussinesq version has no background stratification in a domain
-of height 10\,km and width 20\,km initially at rest. The buoyant
-perturbation is given by:
-\begin{equation}
-b=\frac{1}{15}\cos^{2}\frac{\pi L}{2}\label{eq:thetaPerturb}
-\end{equation}
-for $L<1$ where $L=\sqrt{\left(\frac{x-x_{c}}{x_{r}}\right)^{2}+\left(\frac{z-z_{c}}{z_{r}}\right)^{2}}$,
-$x_{c}=10\ \text{km}$, $z_{c}=2\ \text{km}$ and $x_{r}=z_{r}=2\ \text{km}$.
-100\,m grid spacing is used in the $x$ and $z$ directions for the
-two dimensional reference simulation and $\Delta z=100\ \text{m}$
-is used in the vertical for the single column simulations. All simulations
-use a time-step of 2\,s.
-
-\subsubsection{Single Fluid Solutions}
-
-The solution of the rising buoyant bubble solving the Boussinesq equations
-for 1000s is shown in figure \ref{fig:bubble} with buoyancy coloured,
-pressure contoured and the $w=0$ contour dotted. The solution is
-very similar to the fully compressible solution \citep{BF02}. The
-pressure gradients accelerate the flow beneath the bubble, decelerate
-the flow above the bubble and pull in air horizontally. Horizontally
-and conditionally averaged fields, conditioned on $w$, are shown
-in the top row of figure \ref{fig:bubble_singleUnderRes}. $\sigma_{1}$
-is the volume fraction of rising fluid at every height, $b_{0}$ and
-$b_{1}$ are the buoyancy conditioned on $w\le0$ and $w>0$, $w_{0}$
-and $w_{1}$ are the horizontal averaging rising and falling vertical
-velocity and $P_{0}$ and $P_{1}$ are the pressure of the rising
-and falling fluid. An accurate multi-fluid model of convection should
-reproduce these fields approximately at coarser horizontal resolution
-or in a single column model.
-
-\begin{figure}
-\noindent \begin{centering}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
-\par\end{centering}
-\noindent \begin{centering}
-\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
-\par\end{centering}
-\caption{The single fluid, resolved rising bubble after 1000s. Buoyancy is
-coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
-negative contours dashed. The $w=0$ contour is dotted. \label{fig:bubble}}
-\end{figure}
-
-\citet{TEB19} and \citet{WM19} assumed that both fluids would share
-the same pressure with differences parameterised as drag. The pressure
-in figure \ref{fig:bubble} shows that this is a bad assumption since
-the large pressure anomalies are in the rising fluid. Drag would always
-act to slow down the fluids whereas the negative pressure gradients
-in the rising fluid just below the bubble are acting to accelerate
-the rising motion.
-
-The horizontal averages are shown in figure \ref{fig:bubble_singleUnderRes}
-for horizontal resolutions of nine columns, five columns, three columns
-and a single column all for the 20km wide domain and all still using
-$\Delta z=100\ \text{m}$. These simulations are initialised by conservative
-horizontal averaging from the full resolution solution. As the horizontal
-resolution is reduced, the vertical transport reduces until there
-is no movement at all for a single column: there is no possibility
-of fluid rising because in a single column with a single fluid there
-can be no compensating subsidence. The lack of vertical transport
-at coarse resolution motivates convection parameterisation.
-
-\begin{figure}
-\noindent %
+\setlength{\tabcolsep}{2pt}%
 \begin{tabular}{ccccc}
 \begin{turn}{90}
-200 Columns
+\end{turn} & $\sigma$ & $b\ (\text{m}\text{s}^{-2})$ & $w\ (\text{m}\text{s}^{-1})$ & $P_{i}\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
+\begin{turn}{90}
+\hspace{1cm}200 Columns
 \end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
 \begin{turn}{90}
-9 Columns
+\hspace{1cm}9 Columns
 \end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
 \begin{turn}{90}
-5 Columns
+\hspace{1cm}5 Columns
 \end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
 \begin{turn}{90}
-3 Columns
+\hspace{1cm}3 Columns
 \end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
 \begin{turn}{90}
-1 Column
+\hspace{1cm}1 Column
 \end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
 \end{tabular}
-
-\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
-and a single fluid. Horizontal averages are conditioned based on $w$.
-\label{fig:bubble_singleUnderRes}}
-\end{figure}
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-Multi-fluid, single column simulations are initialised by horizontally
-and conditionally averaging the high resolution single fluid initial
-conditions. Sinking air is put into fluid zero and rising air into
-fluid one. The velocity field after one time step is used for initialisation
-as the air is stationary at $t=0$. Results are shown in figures \ref{fig:multiFluidSingleColumn-bad}
-and \ref{fig:multiFluidSingleColumn} for various assumptions about
-transfers between fluids and various parameter values.
-
-\begin{figure}
-\begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
-\end{figure}
-
-\begin{figure}
-\begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=1/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{01}=w_{1}0.2/r_{c}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=0$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.25\columnwidth}%
-$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions.\label{fig:multiFluidSingleColumn}}
-\end{figure}
-
-If there is no drag between fluids, no transfers, no diffusion and
-the pressures of both fluids are assumed equal then the multi-fluid
-equations are unstable \citep{TEB19}. The simulation with ($S_{ij}=0$)
-in the top row of figure \ref{fig:multiFluidSingleColumn-bad} actually
-has small transfers to prevent either $\sigma_{i}$ from becoming
-negative. This is sufficient to stabilise the solution but does not
-prevent oscillations from developing in all fields. The buoyant fluid
-has risen very little from the initial conditions. $\sigma$ oscillates
-between zero and one meaning that only one fluid is present at some
-locations so there is no possibility for the fluids to move past each
-other.
-
-Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-stabilises the solution and enable the fluids to move past each other
-even without pressure differences between the fluids (second row of
-figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
-detrained from fluid 1, fluid 1 looses too much buoyancy and a discontinuity
-arises at the bubble leading edge; the buoyancy force is producing
-vertical motion but there is no pressure to make it smooth.
-
-Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
-and pressure difference between the fluids controlled by divergence
-($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
-realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
-Three values of $\gamma$ are tested. $\gamma$ is set from equation
-(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
-radius and a buoyancy scale equal to the initial maximum buoyancy
-to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
-(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
-the velocity profile too smooth and the updraught too weak so the
-bubble does not rise enough. It is reasonable to consider smaller
-values of $\gamma$ because the buoyancy does not retain its initial
-maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
-gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
-leads to the leading edge of the bubble rising too quickly. Smaller
-values of $\gamma$ leave a discontinuity in the updraught velocity
-at the leading edge of the bubble and larger values of $\gamma$ reduce
-the velocity further, meaning that the bubble does not rise enough
-(not shown). None of the values of $\gamma$ reproduce the peak updraught
-velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
-meaning that the bubble rise and $\sigma_{1}$ are approximately correct
-and pressure increases above the centre of the bubble are realisitic.
-The large low pressure at the bottom of the bubble is not reproduced.
-This is located at the lobes of the highest buoyancy in the resolved
-simulation (figure \ref{fig:bubble}). It would be tempting to model
-this by assuming hydrostatic pressure or the Bernouilli equation,
-but these are both forms of the momentum equation which is used to
-calculate the velocity and so cannot also be used to model the pressure.
-
-The results in the top row of figure \ref{fig:multiFluidSingleColumn}
-use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
-this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
-drag slows the updraughts without increasing the mixing between the
-fluids which makes the solutions less like the resolved simulations.
-Although drag is known to be an important term in the momentum equations
-for buoyant thermals and plumes \citep[eg][]{RC15}, the drag is related
-to mixing with downdraught air which is accounted for in the entrainment
-term of the momentum equation. So adding a separate term from drag
-risks double counting and slows the plume too much.
-
-If we include pressure difference between fluids with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$but
-omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidSingleColumn})
-the fluids move past each other but there is an unrealistic discontinuity
-with no fluid 1 below the buoyant fluid and very little falling air
-at the lowest height of the rising fluid. With a single column and
-two fluids, all air must rise in one fluid and sink in the other.
-Continuity does not allow for any other solution. Pressure gradients
-can accelerate or decelerate this flow but as the model is set up,
-with no transfers between fluids, no fluid can change direction. It
-is therefore essential to have transfers between fluids.
-
-The other entrainment option is the commonly used fractional entrainment
-rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
-differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
-This combination produces smooth solutions but the updraught is too
-weak and too much is entrained into fluid 1. Using this entrainment,
-the updraught will entrain more and more air until $\sigma_{1}=1$.
-The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
-entrainment and detrainment for this test case using conditional averaging
-based on $w$.
-
-Two alternative models for estimating the buoyancy of the fluid transferred
-between updraught and downdraught have been tested. The results in
-the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
-that the fluid transferred has zero buoyancy in order to keep the
-positively buoyant air in fluid one and the negatively buoyant air
-in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
-the mean buoyancy of fluid one increases. This leads to very high
-buoyancy in fluid one which is not present in the resolved simulation.
-The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
-use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citet{TEB19}
-so that the fluid transferred is influenced by the fluid it is moving
-towards as well as where it has come from. This again leads to very
-large buoyancy in fluid one and also negative buoyancy in fluid zero
-which should not occur for this test case. These simple models reinforce
-the idea that the buoyancy of the fluid transferred should depend
-on knowledge of sub-grid-scale variability of $b$ within each fluid
-\textendash{} these simple assumptions can lead to unrealistic behaviour.
-The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
-fluid transferred takes the mean properties with it.
-
-This section has demonstrated the value of using a single column,
-multi-fluid model to simulate a buoyant rising bubble with a single
-updraught fluid and a single downdraught fluid. Transfers between
-the fluids have been successfully modelled using entrainment set by
-divergence giving realistic updraught fractions. Entrainment calculated
-as the reciprocal of plume width was not successful. The pressure
-difference between the fluids has also been represented by divergence
-with a coefficient close to that expected from dimensional analysis.
-Including drag between the fluids did not improve simulations. Two
-models of transferring non-mean properties between fluids were tested
-but neither was plausible. There are clearly discrepancies between
-the single fluid resolved rising bubble and the two fluid single column
-rising bubble but we do not want to over fit the multi-fluid model
-to one, dry, two dimensional test case.
-
-\subsection{Radiative-Convective Equilibrium (RCE)}
-
-A two-dimensional, dry radiative convective equilibrium test case
-is devised to mimic some properties of atmospheric convection, in
-particular the difficulty resolving the flow at coarse resolution.
-The domain is 160km wide, 10km tall and is resolved by 640 cells in
-the horizontal and 40 in the vertical ($\Delta x=\Delta z=250$m).
-The top and bottom boundaries are zero velocity and the lateral boundaries
-are periodic. A heat flux of $h=10^{-3}\text{m}^{2}\text{s}^{-3}$
-is imposed at the bottom boundary leading to a boundary condition
-of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
-is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
-Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
-so as to give a Plank constant of $0.707$. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$
-is applied to the domain to maintain equilibrium.
-
-The fluid is initially stationary with $b=0$. In order to quickly
-and reproducibly initialise instability, $b=10^{-4}\text{m}^{2}\text{s}^{-1}$
-is imposed in a square of side length 2000m at the centre in the $x$
-direction and at the ground. The simulation is run using a time step
-of $5\ \text{s}$. A quasi-steady, choatic state is reached after
-about $3\times10^{4}\text{s}$ and the simulation is run for $2\times10^{5}\text{s}$
-and conditional averages are calculated over the final $10^{5}$s.
-
-\subsubsection{Single Fluid Solutions}
-
-This test case is designed to have strong updraughts in narrow plumes
-and weak descent elsewhere to mimic atmospheric convection but without
-the complication of moisture, phase changes and three spatial dimensions.
-A snapshot of the buoyancy, vertical velocity and pressure of the
-radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
-are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
-updraughts. The buoyant air at the ground rises in narrow plumes,
-accelerating due to buoyancy and pressure gradients then decelerating
-due to pressure gradients before reaching the top. The plumes spread
-out and the sinking air is a mixture of warm and cold with similar
-pressure gradients in the rising and falling air, accelerating then
-decelerating the flow so as to maintain continuity.
-
-\noindent 
-\begin{figure}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/bw}
-
-Buoyancy ($\text{m}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/bw_b}
-
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/Pw}
-
-Pressure ($\text{m}^{2}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/Pw_P}
-
-\caption{Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
-of the resolved radiative-convective equilibrium test case. Vertical
-velocity contours are black every 0.5m/s with negative contours dashed
-and the zero contour dotted. The domain is 10km high and 160km wide
-and the z-direction is stretched a factor of 2 in the plots. \label{fig:RCE_resolved}}
-\end{figure}
-
-Horizontal averages conditioned on $w$ and time averaged every 1000s
-between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
-in the top row of figure \ref{fig:RCE_singleColumn}. The rising and
-falling volume fractions, $\sigma_{1}$ and $\sigma_{0}$, remain
-close to $\frac{1}{2}$ throughout the depth. The rising plumes look
-narrow in figure \ref{fig:RCE_resolved} but there are wide regions
-of slowly rising air around the plume cores. The entrained rising
-cool air and warm air sinking that has hit the model top mean that
-the rising and falling air have similar average buoyancy away from
-the ground. The ascending air gradually accelerates towards the middle
-of the domain then decelerates towards the model top. At the ground
-the acceleration is forced by buoyancy and away from the ground the
-acceleration is controlled by pressure gradients. The descending air
-mean velocity is close to equal and opposite to the ascending air,
-as expected since $\sigma_{1}=0.5$.
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-The two fluid model is used to simulate the RCE test case in a single
-column of 40 cells with zero buoyancy gradient at the top and a buoyancy
-gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
-and uniform radiative cooling. The two fluids are initialised using
-the time mean conditional horizontal averages from the single fluid
-resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-is used for all simulations to account for transfers throughout the
-domain to represent cloud base mass flux (at the bottom boundary),
-cloud top detrainment and lateral entrainment. $\gamma$ is set from
-equation (\ref{eq:gammaDimAnal}) using the depth of the super adiabatic
-layer as the length scale ($L=800\text{m}$) and the buoyancy scale
-$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
-giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. A simulation using
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
-is shown in the second row of figure \ref{fig:RCE_singleColumn}.
-The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
-at about 0.5 throughout the depth, as in the resolved simulation,
-with entrainment in the lower half of the domain ($S_{01}>0$) and
-detrainment in the upper half ($S_{10}>0$), where the air decelerates
-towards the top. The single column model reproduces the super-adiabatic
-layer near the ground and the near uniform buoyancy away from the
-ground but the buoyancy difference between the fluids is too large.
-The updraught and downdraught velocities are captured well. The pressure
-differences between fluids are too large which is consistent with
-the over estimated buoyancy difference between fluids.
-
-Results of a simulations using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
-is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
-This model of the buoyancy of the transferred fluid is bad; it leads
-to strong cooling in fluid zero near the ground due to the large transfers.
-It is more accurate to assume that fluids take their mean properties
-when transferred, $b_{ij}^{T}=b_{i}$.
-
-\noindent 
-\begin{figure}
-\setlength\tabcolsep{0.5pt}%
-\begin{tabular}{ccccc}
-$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
-\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case between $t=10^{5}\text{s}$
-and $2\times10^{5}\text{s}$}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=b_{i}$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/P_1}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/P_1}\tabularnewline
-\end{tabular}
-
-\caption{Results of the RCE simulations. The top row shows horizontal averages
-of the resolved case between $t=10^{5}$s and $2\times10^{5}$s. The
-bottom two rows show results of the single column multi-fluid model
-after $10^{4}\ \text{s}$. \label{fig:RCE_singleColumn}}
-\end{figure}
-
-\section{Summary, Conclusions and Further Work}
-
-This paper presents solutions of the multi-fluid Boussinesq equations
-for convection, reproducing aspects of highly resolved dry convection
-at coarse horizontal resolution. Two test cases are used to validate
-the multi-fluid model. The first is a Boussinesq version of the well
-known two dimensional dry rising bubble of \citet{BF02} and the second
-is a dry two dimensional version of radiative-convective equilibrium
-with heating at the ground and uniform radiative cooling. High resolution
-single fluid simulations are conditionally averaged based on the sign
-of vertical velocity ($w$) in order to create rising and falling
-fluids which each have their own mean buoyancy, velocity and pressure.
-The two-fluid, single column Boussinesq model reproduces mean vertical
-heat and mass transport of these test cases.
-
-The multi-fluid Boussinesq equations can have divergence in each fluid
-while the divergence averaged over all fluids is zero. A model is
-proposed and validated for the pressure difference between the rising
-and falling fluids based on the divergence of each fluid. The use
-of a different pressure for each fluid is not only realistic but also
-leads to stable solutions of the multi-fluid equations.
-
-Conditionally averaging the high resolution solutions based on $w$
-leads to convecting and non-convecting regions with area fractions,
-$\sigma_{i}$, which are approximately uniform with height. Models
-for entrainment and detrainment into and out of convecting regions
-must clearly be consistent with the definition of the convecting region.
-We propose a model for entrainment and detrainment based on divergence
-that leads to excellent agreement with $\sigma$ from the high resolution
-solutions. We also test a more conventional fractional entrainment
-rate based on the reciprocal of the plume width which leads to unrealistic
-convecting area fractions.
-
-A set of unknowns in the multi-fluid equations are the properties
-of the fluid that are transferred from one fluid to another. An obvious
-first guess would be that fluid takes its mean buoyancy and velocity
-with it when it is transferred. However sub-grid-scale variability
-of each fluid means that we expect that the most buoyant fluid will
-be transferred to the rising fluid or the fluid with the largest vertical
-velocity will be transferred to the rising fluid and vice versa. An
-accurate estimate of these would depend on knowledge of the sub-grid-scale
-variability of each fluid which we do not have. Instead we assume
-that the fluid transferred in each direction has zero vertical velocity
-which is consistent with our conditional averaging. We have tested
-three models for the buoyancy of the fluid transferred. The most successful
-is to assume that the fluid takes its mean buoyancy with it. Assuming
-that the buoyancy of the transferred fluid is an average of the buoyancy
-of both fluids can lead to unrealistically large or small, unbounded
-buoyancies. Similarly, if we assume that one fluid has negative buoyancy
-and the other positive buoyancy and we transfer fluid of zero buoyancy,
-then unbounded buoyancy can occur. A better model of the buoyancy
-of the fluid transferred would rely on more information the sub-grid-scale
-variability.
-
-Single column multi-fluid modelling with moisture has already been
-demonstrated by \citet{TEB19}. Two important next steps are to simulate
-convection in the grey zone (where it is partially resolved) and to
-represent sub-grid-scale variability within each fluid by solving
-multi-fluid prognostic equations for turbulent kinetic energy and
-other moments of the sub-grid variability. These can be used to inform
-cloud base mass flux (since only the most buoyant fluid will transfer
-from the stable environment to the buoyant plume) and inform models
-of the properties of the fluid that is transferred. This will lead
-to a unified parameterisation of turbulence and convection and will
-take multi-fluid modelling of convection beyond existing paradigms.
-
-\section*{Acknowledgements}
-
-Many thanks to John Thuburn and Chris Holloway for valuable discussions.
-Thanks to the NERC/Met Office Paracon project. We acknowledge funding
-from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1.
-
-\bibliographystyle{abbrvnat}
-\bibliography{numerics}
-
 \end{document}

### 2020-07-03 submit3/makeFigs/bubble_singleUnderResTmp.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{amssymb}
\usepackage[authoryear]{natbib}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage { fancybox}
\usepackage[pdftex]{graphicx,color}
\usepackage{rotating}
\newcommand{\nicefrac}[2]{\ensuremath ^{#1}\!\!/\!_{#2}}
\usepackage { fancybox}
\usepackage[export]{adjustbox}
\usepackage{amsmath}

\makeatother

\usepackage{babel}
\begin{document}
\setlength{\tabcolsep}{2pt}
\noindent%
\begin{tabular}{ccccc}
& $\sigma$ & Buoyancy ($\text{m} \text{s}^{-2}$) &
$w$ ($\text{m} \text{s}^{-1}$) &
$P_i \; (\text{m}^2 \text{s}^{-2}$) 
\\
\begin{turn}{90} \hspace{1cm}
200 Columns
\end{turn}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}
\\
\begin{turn}{90} \hspace{1cm}
9 Columns
\end{turn}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}
\\
\begin{turn}{90} \hspace{1cm}
5 Columns
\end{turn}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}
\\
\begin{turn}{90} \hspace{1cm}
3 Columns
\end{turn}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}
\\
\begin{turn}{90} \hspace{1cm}
1 Column
\end{turn}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w}
&
\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\\
\end{tabular}
\end{document}

### 2020-07-03 submit3/makeFigs/multiFluidBubble_1000.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

--- 2020-03-23 preSubmission/manuscript.tex
@@
 \usepackage[latin9]{inputenc}
-\usepackage{geometry}
-\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
-\usepackage{array}
-\usepackage{rotating}
-\usepackage{amsmath}
+\usepackage[pdftex,a4paper]{geometry}
+\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
+\pagestyle{empty}
+\setcounter{secnumdepth}{5}
+\setcounter{tocdepth}{5}
+\setlength{\parskip}{\smallskipamount}
+\setlength{\parindent}{0pt}
+\usepackage{calc}
+\usepackage{amstext}
 \usepackage{amssymb}
-\usepackage{graphicx}
+\usepackage[pdftex]{graphicx}
 \usepackage[authoryear]{natbib}
@@
 
+\usepackage{babel}
 \begin{document}
-
-\title{Multi-fluids for Representing Sub-filter-scale Buoyant Convection}
-
-\author{Hilary Weller, William McIntyre, Daniel Shipley and Peter Clark}
-\maketitle
-\begin{abstract}
-Multi-fluid modelling is a promising new method of representing sub
-and near grid-scale convection allowing for consistent and accurate
-treatment of net mass transport by convection, non-equilibrium and
-turbulence. The air is partitioned into convecting and non-convecting
-fluids each with their own velocity, temperature and constituents
-so that separate equations of motion can be solved for each fluid,
-thus representing features that cannot be resolved in a single fluid
-at coarse resolution.
-
-This paper presents multi-fluid Boussinesq equations for representing
-under resolved dry convection. We present a new model for entrainment
-and detrainment based on divergence which leads to excellent representation
-of the convective area fraction. Previous multi-fluid modelling of
-convection has assumed that all fluids share the same pressure. We
-show that this is a bad assumption and we propose and validate a model
-for the pressure difference between the fluids based on divergence.
-
-Two vertical slice test cases are used to validate the multi-fluid
-model; a buoyant rising bubble and radiative convective equilibrium
-are simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity. The multi-fluid model reproduces
-the mean properties of the rising and falling fluids in a single column. 
-\end{abstract}
-
-\section{Introduction}
-
-Slow progress has been made improving the parameterisation of sub-grid-scale
-convection since \citet{AS74,Tied89,GR90,KF90}. Convection is still
-one of the weakest aspects of large scale models of the atmosphere
-\citep{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
-the quasi-equilibrium assumption \citep{PR98,GG05,Par14}, including
-stochasticity \citep{PC08} and allowing net mass transport by convection
-\citep{KB08,MB19}. These developments have enabled limited simulation
-in the grey zone, where convection is partially resolved. However
-there are still systematic biases implying that improvements should
-still be possible.
-
-\citet{TWV+18} proposed multi-fluid modelling of convection in order
-to treat non-equilibrium and net mass transport correctly and consistently
-with the same numerics and physics controlling thermals, the stable
-environment and downdraught dynamics. \citet{Yano14} derived similar
-equations for multiple segments and showed how this is a generalisation
-of the mass-flux formulation. The \citet{TKP+18} ``extended eddy
-diffusivity mass flux'' or extended EDMF scheme also uses similar
-equations but \citet{TKP+18} didn't propose a suitable numerical
-method for solving the equations. Multi-fluids promises big improvements
-in the representation of sub-grid-scale convection and unification
-with the representation of turbulence, particularly at the grey zone.
-However, there is a long way to go, particularly as multi-fluids requires
-a dedicated model rather than being a stand alone parameterisation
-for a dynamical core. \citet{TEB19} and \citet{WM19} presented solutions
-of the multi-fluid equations assuming two fluids that share the same
-pressure (or that pressure differences are predominantly due to drag
-between the fluids). \citet{TEB19} showed that these equations (without
-drag) are in fact unstable and can be stabilised by diffusion of vertical
-velocity whereas \citet{WM19} stabilised the equations with diffusion
-and drag between fluids. Neither of these stabilisation techniques
-are acceptable and in this paper we show that there are significant
-and sustained pressure differences between the fluids (section \ref{sec:results}).
-
-This paper presents the multi-fluid Boussinesq equations for representing
-sub-grid-scale convection including a parameterisation of the pressure
-difference between fluids (section \ref{subsec:fluidPressure}) and
-a new model of entrainment and detrainment (section \ref{subsec:Sij}).
-The numerical method for solving the equations is described in section
-\ref{sec:numerics}. We compare results of resolved dry convection
-in a single-fluid two dimensional Boussinesq model with a two-fluid,
-single column model in section \ref{sec:results} using two vertical
-slice test cases.
-
-\section{The Multi-fluid Boussinesq Equations}
-
-Many of the challenges of representing convection with the multi-fluid
-Navier-Stokes equations \citep[eg those described in][]{WM19} carry
-over to the Boussinesq equations; convection is buoyancy dominated
-and close to incompressible. The resolved test cases presented in
-section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore for simplicity we focus on the
-multi-fluid Boussinesq equations without background stratification:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\} \label{eq:sigma}\\
-\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\} \label{eq:mom}\\
-\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}\\
-\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
-\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
-\end{eqnarray}
-with variables defined in table \ref{tab:defns}.
-
-\begin{table}[h]
-\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
-$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
-$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
-$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
-$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
-$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
-where $\rho^{\prime}$ are departures in density from a horizontally
-uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
-$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
-$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
-$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
-$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
-\end{tabular}
-
-\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
-\end{table}
-
-\subsection{Pressure of each fluid \label{subsec:fluidPressure}}
-
-\citet{TEB19} and \citet{WM19} assumed that each co-located fluid
-shared the same pressure, leading to unstable equations that \citet{TEB19}
-stabilised using diffusion of vertical velocity and \citet{WM19}
-stabilised using mass exchanges or drag between the fluids. \citet{TEB19}
-achieved realistic results in single column experiments of convective
-boundary layer but the amount of diffusion needed would spoil simulations
-in the free troposphere. The stabilisation used by \citet{WM19} meant
-that the two fluids tended to move as one which defeats the purpose
-of using multi-fluid modelling.
-
-The instabilities reported by \citet{WM19} showed growing divergence
-in a fluid with vanishing volume fraction. It is mass convergence
-rather than velocity convergence that leads to pressure anomalies
-that remove the convergence. Therefore if the volume (or mass) fraction
-of fluid is vanishingly low then convergence cannot lead to an anomaly
-in the total pressure.
-
-We will assume that pressure in each fluid is given by a parameterised
-perturbation, $p_{i}$, from the total pressure, $P$:
-\begin{equation}
-P_{i}=P+p_{i}.
-\end{equation}
-
-\citet{BN86} proposed a parameterisation for pressure differences
-in a multi-phase explosion model that has been widely used in mathematics
-and engineering for simulating fluidised beds of granular material
-\citep[eg.][]{EHM92} and two compressible fluids \citep[eg.][]{SA99}.
-In these methods, advection equations are written for the volume fraction,
-$\sigma_{i}$, and conservation equations are written for mass fraction,
-$\sigma_{i}\rho_{i}$. In our notation, ignoring transfers between
-fluids, the \citet{BN86} equations would be:
-\begin{eqnarray}
-\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)\label{eq:BNcompaction}\\
-\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0\label{eq:rhoTransport}
-\end{eqnarray}
-where $\mathbf{V}$ is the velocity of the interface between fluids,
-$\mu$ is the compaction viscosity which controls how quickly the
-pressure of each fluid relaxes to the mean pressure and index $j$
-refers to the other fluid in a two fluid system. In our Boussinesq
-system $\rho_{i}$ does not appear in the continuity equation. Different
-authors make different assumptions about the interface velocity but
-if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and
-$\rho_{i}$ is constant then eqns (\ref{eq:divFree}-\ref{eq:rhoTransport})
-imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
-If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then
-we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.
-
-\citet{TEB19} stabilised the multi-fluid equations by adding a diffusion
-term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
-If a fluid perturbation pressure is set to $-\nu\partial w/\partial z$
-this is equivalent to the diffusion term in one dimension. However
-adding a diffusion term will harm three dimensional simulations of
-resolved convection in the free troposphere whereas adding a fluid
-perturbation pressure will not. Inspired by both \citet{BN86} and
-\citet{TEB19} we assume that the pressure in each fluid is given
-by:
-\begin{equation}
-p_{i}=-\gamma\nabla\cdot\mathbf{u}_{i}\label{eq:Pi_div}
-\end{equation}
-where $\gamma$ is a free coefficient. Dimensional analysis in section
-\ref{subsec:dimAnal} will inform the choice of $\gamma$ and sensitivity
-to $\gamma$ will be evaluated in section \ref{sec:results}.
-
-\subsection{Entrainment and Detrainment \label{subsec:Sij}}
-
-We consider dry air without turbulence so use the dynamic entrainment
-described by \citet{HC51,AK67,DBF+13}:
-\begin{equation}
-S_{ij}=\begin{cases}
--\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
-0 & \text{otherwise}
-\end{cases}
-\end{equation}
-which is necessary to stop air in one fluid from accumulating when
-vertical motion ceases (at the top of a rising plume or at the bottom
-of descending air). We will also test a common form of lateral entrainment
-\citep{DBF+13}:
-\begin{equation}
-\varepsilon=\frac{0.2}{r_{c}}\implies S_{01}=w_{1}\frac{0.2}{r_{c}}
-\end{equation}
-where $\varepsilon$ is the well know fractional entrainment rate
-and $r_{c}$ is the cloud or plume radius.
-
-\subsection{Drag in the Momentum Equation\label{subsec:drag}}
-
-Pressure differences between the fluids can lead to form drag which
-is parameterised following \citet{SW69,RC15,WM19} as: 
-\begin{equation}
-\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
-\end{equation}
-where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
-Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.
-
-\subsection{The Buoyancy and the Momentum of the Mass that is Transferred \label{subsec:transferProperties}}
-
-The different fluids may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \citep[as was assumed by][]{WM19}.
-In fact, the most buoyant air should be transferred from fluid 0 to
-fluid 1 and vice versa, and the air with least downward momentum should
-be transferred from 0 to 1 and vice versa. The properties of the fluids
-transferred should depend on the modelling of sub-grid-scale variability
-which is beyond the scope of this paper. In section \ref{sec:results}
-we conditionally average high resolution solutions based on the sign
-of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
-Therefore the air that is transferred at the interface will have $w=0$.
-For two dimensional multi-fluid simulations we assume that the horizontal
-velocity transferred is equal to the mean horizontal velocity of the
-fluid transferred from. Therefore
-\begin{equation}
-\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
-v_{i}\\
-0
-\end{pmatrix}.
-\end{equation}
-For buoyancy, following \citet{TEB19}, we use:
-\begin{equation}
-b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
-\end{equation}
-and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
-Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
-transferred depends on the properties of the receiving fluid which
-is not logical and can lead to unbounded values of $b_{i}$ in the
-fluid that is loosing mass (as demonstrated in section \ref{sec:results}).
-
-\subsection{Dimensional Analysis\label{subsec:dimAnal}}
-
-Dimensional analysis can guide our choice of $\gamma$ for the parameterisation
-of the pressure difference between fluids. We make the following assumptions:
-\begin{enumerate}
-\item The flow is buoyancy dominated.
-\item The flow is close to inviscid.
-\item The flow is slowly varying.
-\item Fluid $i$ properties are anomalies from a neutrally stable resting
-mean state.
-\item We consider only the vertical direction where $w_{ij}^{T}=0$.
-\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
-\item There are two fluids, $i$ and $j$
-\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
-and $S_{ji}=0$.
-\end{enumerate}
-This leads to the following balance in the momentum equation:
-\begin{equation}
-\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
-\end{equation}
-We non-dimensionalise using a length scale $L$, a buoyancy scale
-$B$ and a time scale $T$ to get the non-dimensional variables:
-\begin{eqnarray*}
-\tilde{w} & = & w_{i}T/L\\
-\tilde{b} & = & b_{i}/B\\
-\tilde{z} & = & z/L.
-\end{eqnarray*}
-Then the non-dimensional version of (\ref{eq:wi_balances}) is:
-\begin{equation}
-\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
-\end{equation}
-The flow is buoyancy dominated so the buoyancy term should be $O(1)$
-so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
-so the non-dimensional momentum equation becomes:
-\begin{equation}
-\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
-\end{equation}
-The stabilisation term must be large enough to smooth out oscillations
-in $\tilde{w}$ due to advection and buoyancy but not too large to
-remove all variability in $\tilde{w}$ so we need:
-\begin{equation}
-\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
-\end{equation}
-
-\section{Numerical Solution \label{sec:numerics}}
-
-The spatial discretisation follows exactly \citet{WM19}, solving
-advective form equations using monotonic, finite volume advection
-and C-grid, Lorenz staggering. The time-stepping is Crank-Nicolson
-with no off-centering and with deferred correction of explicitly solved
-variables. It differs from \citet{WM19} because here we solve the
-Boussinesq equations and we need stable solutions for equations with
-a separate pressure in each fluid. We use two outer iterations per
-time step to update explicitly solved variables. For the first outer
-iteration, predicted values for time $n+1$ are set to those from
-time level $n$ and are given the superscript $\ell$. For the second
-iteration, values at $\ell$ are set to those from the end of the
-first iteration. The implicit numerical method for applying the transfers
-between fluids is specific for two fluids because it involves the
-inversion of $2\times2$ matrices.
-
-The prognostic variables are the $b_{i}$ in cell centres, the $\sigma_{i}$
-in cell centres and the velocity flux at cell faces, $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$,
-which is the velocity at cell faces dotted with the area vector for
-each face (normal to the face). The pressures, $P$ and $p_{i}$ are
-diagnostic.
-
-The first equation to be solved each outer iteration is eqn (\ref{eq:sigma})
-for each $\sigma_{i}$, operator split; first applying advection,
-then correcting $\sum_{i}\sigma_{i}=1$ and then applying mass transfers:
-\begin{eqnarray}
-\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\} \\
-\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}\\
-S_{ij} & = & \begin{cases}
--\nabla\cdot\mathbf{u}_{i}^{\ell} & \text{if }\nabla\cdot\mathbf{u}_{i}^{\ell}<0\\
-0 & \text{otherwise}
-\end{cases}\\
-\sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
-\end{eqnarray}
-where $\Delta t$ is the time step and the superscripts $\prime$
-and $\prime\prime$ denote intermediate values. $\sigma_{i}^{n}$
-is interpolated from cell centres onto cell faces using monotonic
-van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citet{WM19}
-and values exclusively at time level $n$ for best accuracy and guaranteed
-monotonicity. For calculating the divergence, the normal component
-of $\mathbf{u}_{i}$ is needed at cell faces which are prognostic
-variables of the C-grid. The $S_{ij}$ are limited to ensure $0<\sigma_{i}<1\ \forall i$.
-
-Next eqn (\ref{eq:b}) is solved for the buoyancy in each fluid, first
-transporting buoyancy and then applying the transfer terms. The transfer
-terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
-in the transfer term for $b_{i}$ so they are treated operator split
-and implicitly:
-\begin{eqnarray}
-b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
- &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
-b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
-b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
-\end{eqnarray}
-where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
-from before the mass transfers is necessary to ensure bounded and
-conservative transfers, as described by \cite{MWH1x}. Simultaneous
-solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
-\begin{eqnarray}
-b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
-b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
-\end{eqnarray}
-where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$
-
-Next a Poisson equation is solved to calculate the total pressure,
-$P$ to ensure that the total velocity is divergence free. The pressure
-equation also provides updates for the velocity flux, $u_{i}$. First
-an intermediate velocity flux is calculated with partial updates and
-updates from a previous value of $p_{i}$:
-\begin{eqnarray}
-u_{i}^{\prime}= & u_{i}^{n}+\frac{\Delta t}{2} & \biggl(\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{\ell}\cdot\mathbf{S}-\nabla_{f}p_{i}^{\ell}\\
- &  & +\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{n}\cdot\mathbf{S}-\nabla_{f}(P+p_{i})^{n}\biggr)
-\end{eqnarray}
-where operator $()_{f}$ means linear interpolation from cell centres
-onto cell faces and $\nabla_{f}P$ is a compact discretisation of
-$(\nabla P)_{f}\cdot\mathbf{S}$: ie the normal component of the pressure
-gradient calculated from just the values of pressure either side of
-the face. Once we have calculated $P^{n+1}$, the velocity flux (without
-momentum transfers) is updated from the back-substitution:
-\begin{equation}
-u_{i}^{\prime\prime}=u_{i}^{\prime}-\frac{\Delta t}{2}\nabla_{f}P^{n+1}.\label{eq:backSub}
-\end{equation}
-The Poisson equation for $P^{n+1}$ is found by multiplying each eqn
-(\ref{eq:backSub}) by $\sigma_{i}$, summing over all fluids and
-taking the divergence. Knowing that $\nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0$,
-$\sum_{i}\sigma_{i}=1$ and $\sum_{i}\sigma_{i}p_{i}=0$ gives:
-\begin{equation}
-\nabla\cdot\sum_{i}\sigma_{i}u_{i}^{\prime}-\frac{\Delta t}{2}\nabla^{2}P^{n+1}=0
-\end{equation}
-which is solved to find $P^{n+1}$.
-
-Next, the momentum transfers due to mass transfer and due to drag
-are calculated implicitly, similar to the implicit transfers of buoyancy,
-calculating $u_{i}^{n+1}$ from $u_{i}^{\prime\prime}$. These do
-not influence the total $P$ or total divergence because momentum
-is transferred conservatively. However they do influence $p_{i}$
-which is why they are calculated before $p_{i}$. The final stage
-of the time step iteration is to solve Helmholtz equations for each
-$p_{i}$:
-\begin{equation}
-\sigma_{i}^{n+1}p_{i}^{n+1}=-\gamma\nabla\cdot\left(\sigma_{if}^{n+1}u_{i}^{n+1}-\frac{\Delta t}{2}\sigma_{if}^{n+1}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right).\label{eq:pi_Helm}
-\end{equation}
-Both $p_{i}^{n+1}$ and $p_{i}^{\ell}$ appear in eqn (\ref{eq:pi_Helm})
-because $u_{i}^{n+1}$ already contains contributions from $p_{i}^{\ell}$
-so these are removed before updating $p_{i}^{n+1}$. No back substitution
-for $u_{i}$ is done after calculating $p_{i}^{n+1}$ because this
-would destroy the divergence free constraint. Therefore $p_{i}^{n+1}$
-only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
-converge and $p_{i}^{\ell}=p_{i}^{n+1}$.
-
-The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
-from $u_{i}$ following \citet{WM19}. The stages calculating $P$,
-$p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
-The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$.
-
-\section{Validation Test Cases\label{sec:results}}
-
-Two test cases are developed to tune parameters and to validate the
-use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
-convection. The first is transient; the standard rising bubble of
-\citet{BF02}. We aim to reproduce the vertical heat transport, the
-mean velocity of the rising air, the bouyancy of the rising air and
-pressure differences between two fluids in a single column two fluid
-model. The second test case is steady state with heat transfer at
-the ground and uniform radiative cooling. For both test cases the
-reference solution is a single fluid solution of the two-dimensional
-Boussinesq equations at high horizontal and vertical resolution.
-
-\subsection{Rising Bubble}
-
-The test case of \citet{BF02} was designed for fully compressible
-models but similar solutions are obtained solving Boussinesq equations.
-The Boussinesq version has no background stratification in a domain
-of height 10\,km and width 20\,km initially at rest. The buoyant
-perturbation is given by:
-\begin{equation}
-b=\frac{1}{15}\cos^{2}\frac{\pi L}{2}\label{eq:thetaPerturb}
-\end{equation}
-for $L<1$ where $L=\sqrt{\left(\frac{x-x_{c}}{x_{r}}\right)^{2}+\left(\frac{z-z_{c}}{z_{r}}\right)^{2}}$,
-$x_{c}=10\ \text{km}$, $z_{c}=2\ \text{km}$ and $x_{r}=z_{r}=2\ \text{km}$.
-100\,m grid spacing is used in the $x$ and $z$ directions for the
-two dimensional reference simulation and $\Delta z=100\ \text{m}$
-is used in the vertical for the single column simulations. All simulations
-use a time-step of 2\,s.
-
-\subsubsection{Single Fluid Solutions}
-
-The solution of the rising buoyant bubble solving the Boussinesq equations
-for 1000s is shown in figure \ref{fig:bubble} with buoyancy coloured,
-pressure contoured and the $w=0$ contour dotted. The solution is
-very similar to the fully compressible solution \citep{BF02}. The
-pressure gradients accelerate the flow beneath the bubble, decelerate
-the flow above the bubble and pull in air horizontally. Horizontally
-and conditionally averaged fields, conditioned on $w$, are shown
-in the top row of figure \ref{fig:bubble_singleUnderRes}. $\sigma_{1}$
-is the volume fraction of rising fluid at every height, $b_{0}$ and
-$b_{1}$ are the buoyancy conditioned on $w\le0$ and $w>0$, $w_{0}$
-and $w_{1}$ are the horizontal averaging rising and falling vertical
-velocity and $P_{0}$ and $P_{1}$ are the pressure of the rising
-and falling fluid. An accurate multi-fluid model of convection should
-reproduce these fields approximately at coarser horizontal resolution
-or in a single column model.
-
-\begin{figure}
-\noindent \begin{centering}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/1000/bP}
-\par\end{centering}
-\noindent \begin{centering}
-\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
-\par\end{centering}
-\caption{The single fluid, resolved rising bubble after 1000s. Buoyancy is
-coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
-negative contours dashed. The $w=0$ contour is dotted. \label{fig:bubble}}
-\end{figure}
-
-\citet{TEB19} and \citet{WM19} assumed that both fluids would share
-the same pressure with differences parameterised as drag. The pressure
-in figure \ref{fig:bubble} shows that this is a bad assumption since
-the large pressure anomalies are in the rising fluid. Drag would always
-act to slow down the fluids whereas the negative pressure gradients
-in the rising fluid just below the bubble are acting to accelerate
-the rising motion.
-
-The horizontal averages are shown in figure \ref{fig:bubble_singleUnderRes}
-for horizontal resolutions of nine columns, five columns, three columns
-and a single column all for the 20km wide domain and all still using
-$\Delta z=100\ \text{m}$. These simulations are initialised by conservative
-horizontal averaging from the full resolution solution. As the horizontal
-resolution is reduced, the vertical transport reduces until there
-is no movement at all for a single column: there is no possibility
-of fluid rising because in a single column with a single fluid there
-can be no compensating subsidence. The lack of vertical transport
-at coarse resolution motivates convection parameterisation.
-
-\begin{figure}
-\noindent %
-\begin{tabular}{ccccc}
-\begin{turn}{90}
-200 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-9 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/nineColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-5 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/fiveColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-3 Columns
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/threeColumn/hMean/1000/P}\tabularnewline
-\begin{turn}{90}
-1 Column
-\end{turn} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/sigma} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/b} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/w} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/singleColumn/hMean/1000/P}\tabularnewline
-\end{tabular}
-
-\caption{The rising bubble after 1000s simulated with coarse horizontal resolution
-and a single fluid. Horizontal averages are conditioned based on $w$.
-\label{fig:bubble_singleUnderRes}}
-\end{figure}
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-Multi-fluid, single column simulations are initialised by horizontally
-and conditionally averaging the high resolution single fluid initial
-conditions. Sinking air is put into fluid zero and rising air into
-fluid one. The velocity field after one time step is used for initialisation
-as the air is stationary at $t=0$. Results are shown in figures \ref{fig:multiFluidSingleColumn-bad}
-and \ref{fig:multiFluidSingleColumn} for various assumptions about
-transfers between fluids and various parameter values.
-
-\begin{figure}
 \begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_noTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=0$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_2p3e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
+\multicolumn{4}{c}{%
+\fbox{\begin{minipage}[t]{0.7\columnwidth}%
+\begin{center}
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
+\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=b_{i}$
+\par\end{center}%
+\end{minipage}}}\tabularnewline
 \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.2\columnwidth}%
-$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage} %
-\begin{minipage}[t]{0.15\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/1000/Pcompare}\tabularnewline
+\multicolumn{4}{c}{%
+\fbox{\begin{minipage}[t]{0.7\columnwidth}%
+\begin{center}
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
+\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=0$
+\par\end{center}%
+\end{minipage}}}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
+\multicolumn{4}{c}{%
+\fbox{\begin{minipage}[t]{0.7\columnwidth}%
+\begin{center}
+$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,
+\hspace{6pt} $C_{D}/r_{c}=0$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$
+\par\end{center}%
+\end{minipage}}}\tabularnewline
+\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
 $\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
 \end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions. \label{fig:multiFluidSingleColumn-bad}}
-\end{figure}
-
-\begin{figure}
-\begin{tabular}{cccc}
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=1/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{01}=w_{1}0.2/r_{c}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0/2000\text{m}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=b_{i}$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.15\columnwidth}%
-$b_{ij}^{T}=0$%
-\end{minipage} }\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/1000/Pcompare}\tabularnewline
-\multicolumn{4}{l}{%
-\begin{minipage}[t]{0.17\columnwidth}%
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
-\end{minipage}%
-\begin{minipage}[t]{0.18\columnwidth}%
-$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
-\end{minipage}%
-\begin{minipage}[t]{0.24\columnwidth}%
-$C_{D}/r_{c}=0$%
-\end{minipage}%
-\begin{minipage}[t]{0.25\columnwidth}%
-$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$%
-\end{minipage}}\tabularnewline
-\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/1000/Pcompare}\tabularnewline
-$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline
-\end{tabular}
-
-\caption{Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, single column solutions of the rising bubble. Dashed
-lines are the single fluid, resolved solutions.\label{fig:multiFluidSingleColumn}}
-\end{figure}
-
-If there is no drag between fluids, no transfers, no diffusion and
-the pressures of both fluids are assumed equal then the multi-fluid
-equations are unstable \citep{TEB19}. The simulation with ($S_{ij}=0$)
-in the top row of figure \ref{fig:multiFluidSingleColumn-bad} actually
-has small transfers to prevent either $\sigma_{i}$ from becoming
-negative. This is sufficient to stabilise the solution but does not
-prevent oscillations from developing in all fields. The buoyant fluid
-has risen very little from the initial conditions. $\sigma$ oscillates
-between zero and one meaning that only one fluid is present at some
-locations so there is no possibility for the fluids to move past each
-other.
-
-Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-stabilises the solution and enable the fluids to move past each other
-even without pressure differences between the fluids (second row of
-figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
-detrained from fluid 1, fluid 1 looses too much buoyancy and a discontinuity
-arises at the bubble leading edge; the buoyancy force is producing
-vertical motion but there is no pressure to make it smooth.
-
-Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
-and pressure difference between the fluids controlled by divergence
-($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
-realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
-Three values of $\gamma$ are tested. $\gamma$ is set from equation
-(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
-radius and a buoyancy scale equal to the initial maximum buoyancy
-to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
-(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
-the velocity profile too smooth and the updraught too weak so the
-bubble does not rise enough. It is reasonable to consider smaller
-values of $\gamma$ because the buoyancy does not retain its initial
-maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
-gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
-leads to the leading edge of the bubble rising too quickly. Smaller
-values of $\gamma$ leave a discontinuity in the updraught velocity
-at the leading edge of the bubble and larger values of $\gamma$ reduce
-the velocity further, meaning that the bubble does not rise enough
-(not shown). None of the values of $\gamma$ reproduce the peak updraught
-velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
-meaning that the bubble rise and $\sigma_{1}$ are approximately correct
-and pressure increases above the centre of the bubble are realisitic.
-The large low pressure at the bottom of the bubble is not reproduced.
-This is located at the lobes of the highest buoyancy in the resolved
-simulation (figure \ref{fig:bubble}). It would be tempting to model
-this by assuming hydrostatic pressure or the Bernouilli equation,
-but these are both forms of the momentum equation which is used to
-calculate the velocity and so cannot also be used to model the pressure.
-
-The results in the top row of figure \ref{fig:multiFluidSingleColumn}
-use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
-this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
-drag slows the updraughts without increasing the mixing between the
-fluids which makes the solutions less like the resolved simulations.
-Although drag is known to be an important term in the momentum equations
-for buoyant thermals and plumes \citep[eg][]{RC15}, the drag is related
-to mixing with downdraught air which is accounted for in the entrainment
-term of the momentum equation. So adding a separate term from drag
-risks double counting and slows the plume too much.
-
-If we include pressure difference between fluids with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$but
-omit entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidSingleColumn})
-the fluids move past each other but there is an unrealistic discontinuity
-with no fluid 1 below the buoyant fluid and very little falling air
-at the lowest height of the rising fluid. With a single column and
-two fluids, all air must rise in one fluid and sink in the other.
-Continuity does not allow for any other solution. Pressure gradients
-can accelerate or decelerate this flow but as the model is set up,
-with no transfers between fluids, no fluid can change direction. It
-is therefore essential to have transfers between fluids.
-
-The other entrainment option is the commonly used fractional entrainment
-rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
-differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
-This combination produces smooth solutions but the updraught is too
-weak and too much is entrained into fluid 1. Using this entrainment,
-the updraught will entrain more and more air until $\sigma_{1}=1$.
-The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
-entrainment and detrainment for this test case using conditional averaging
-based on $w$.
-
-Two alternative models for estimating the buoyancy of the fluid transferred
-between updraught and downdraught have been tested. The results in
-the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
-that the fluid transferred has zero buoyancy in order to keep the
-positively buoyant air in fluid one and the negatively buoyant air
-in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
-the mean buoyancy of fluid one increases. This leads to very high
-buoyancy in fluid one which is not present in the resolved simulation.
-The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
-use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citet{TEB19}
-so that the fluid transferred is influenced by the fluid it is moving
-towards as well as where it has come from. This again leads to very
-large buoyancy in fluid one and also negative buoyancy in fluid zero
-which should not occur for this test case. These simple models reinforce
-the idea that the buoyancy of the fluid transferred should depend
-on knowledge of sub-grid-scale variability of $b$ within each fluid
-\textendash{} these simple assumptions can lead to unrealistic behaviour.
-The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
-fluid transferred takes the mean properties with it.
-
-This section has demonstrated the value of using a single column,
-multi-fluid model to simulate a buoyant rising bubble with a single
-updraught fluid and a single downdraught fluid. Transfers between
-the fluids have been successfully modelled using entrainment set by
-divergence giving realistic updraught fractions. Entrainment calculated
-as the reciprocal of plume width was not successful. The pressure
-difference between the fluids has also been represented by divergence
-with a coefficient close to that expected from dimensional analysis.
-Including drag between the fluids did not improve simulations. Two
-models of transferring non-mean properties between fluids were tested
-but neither was plausible. There are clearly discrepancies between
-the single fluid resolved rising bubble and the two fluid single column
-rising bubble but we do not want to over fit the multi-fluid model
-to one, dry, two dimensional test case.
-
-\subsection{Radiative-Convective Equilibrium (RCE)}
-
-A two-dimensional, dry radiative convective equilibrium test case
-is devised to mimic some properties of atmospheric convection, in
-particular the difficulty resolving the flow at coarse resolution.
-The domain is 160km wide, 10km tall and is resolved by 640 cells in
-the horizontal and 40 in the vertical ($\Delta x=\Delta z=250$m).
-The top and bottom boundaries are zero velocity and the lateral boundaries
-are periodic. A heat flux of $h=10^{-3}\text{m}^{2}\text{s}^{-3}$
-is imposed at the bottom boundary leading to a boundary condition
-of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
-is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
-Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
-so as to give a Plank constant of $0.707$. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$
-is applied to the domain to maintain equilibrium.
-
-The fluid is initially stationary with $b=0$. In order to quickly
-and reproducibly initialise instability, $b=10^{-4}\text{m}^{2}\text{s}^{-1}$
-is imposed in a square of side length 2000m at the centre in the $x$
-direction and at the ground. The simulation is run using a time step
-of $5\ \text{s}$. A quasi-steady, choatic state is reached after
-about $3\times10^{4}\text{s}$ and the simulation is run for $2\times10^{5}\text{s}$
-and conditional averages are calculated over the final $10^{5}$s.
-
-\subsubsection{Single Fluid Solutions}
-
-This test case is designed to have strong updraughts in narrow plumes
-and weak descent elsewhere to mimic atmospheric convection but without
-the complication of moisture, phase changes and three spatial dimensions.
-A snapshot of the buoyancy, vertical velocity and pressure of the
-radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
-are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
-updraughts. The buoyant air at the ground rises in narrow plumes,
-accelerating due to buoyancy and pressure gradients then decelerating
-due to pressure gradients before reaching the top. The plumes spread
-out and the sinking air is a mixture of warm and cold with similar
-pressure gradients in the rising and falling air, accelerating then
-decelerating the flow so as to maintain continuity.
-
-\noindent 
-\begin{figure}
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/bw}
-
-Buoyancy ($\text{m}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/bw_b}
-
-\includegraphics[width=1\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/200000/Pw}
-
-Pressure ($\text{m}^{2}\text{s}^{-2}$) \includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/legends/Pw_P}
-
-\caption{Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
-of the resolved radiative-convective equilibrium test case. Vertical
-velocity contours are black every 0.5m/s with negative contours dashed
-and the zero contour dotted. The domain is 10km high and 160km wide
-and the z-direction is stretched a factor of 2 in the plots. \label{fig:RCE_resolved}}
-\end{figure}
-
-Horizontal averages conditioned on $w$ and time averaged every 1000s
-between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
-in the top row of figure \ref{fig:RCE_singleColumn}. The rising and
-falling volume fractions, $\sigma_{1}$ and $\sigma_{0}$, remain
-close to $\frac{1}{2}$ throughout the depth. The rising plumes look
-narrow in figure \ref{fig:RCE_resolved} but there are wide regions
-of slowly rising air around the plume cores. The entrained rising
-cool air and warm air sinking that has hit the model top mean that
-the rising and falling air have similar average buoyancy away from
-the ground. The ascending air gradually accelerates towards the middle
-of the domain then decelerates towards the model top. At the ground
-the acceleration is forced by buoyancy and away from the ground the
-acceleration is controlled by pressure gradients. The descending air
-mean velocity is close to equal and opposite to the ascending air,
-as expected since $\sigma_{1}=0.5$.
-
-\subsubsection{Results of the Two-fluid, Single Column Simulations}
-
-The two fluid model is used to simulate the RCE test case in a single
-column of 40 cells with zero buoyancy gradient at the top and a buoyancy
-gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
-and uniform radiative cooling. The two fluids are initialised using
-the time mean conditional horizontal averages from the single fluid
-resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
-is used for all simulations to account for transfers throughout the
-domain to represent cloud base mass flux (at the bottom boundary),
-cloud top detrainment and lateral entrainment. $\gamma$ is set from
-equation (\ref{eq:gammaDimAnal}) using the depth of the super adiabatic
-layer as the length scale ($L=800\text{m}$) and the buoyancy scale
-$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
-giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. A simulation using
-$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
-is shown in the second row of figure \ref{fig:RCE_singleColumn}.
-The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
-at about 0.5 throughout the depth, as in the resolved simulation,
-with entrainment in the lower half of the domain ($S_{01}>0$) and
-detrainment in the upper half ($S_{10}>0$), where the air decelerates
-towards the top. The single column model reproduces the super-adiabatic
-layer near the ground and the near uniform buoyancy away from the
-ground but the buoyancy difference between the fluids is too large.
-The updraught and downdraught velocities are captured well. The pressure
-differences between fluids are too large which is consistent with
-the over estimated buoyancy difference between fluids.
-
-Results of a simulations using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
-is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
-This model of the buoyancy of the transferred fluid is bad; it leads
-to strong cooling in fluid zero near the ground due to the large transfers.
-It is more accurate to assume that fluids take their mean properties
-when transferred, $b_{ij}^{T}=b_{i}$.
-
-\noindent 
-\begin{figure}
-\setlength\tabcolsep{0.5pt}%
-\begin{tabular}{ccccc}
-$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
-\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case between $t=10^{5}\text{s}$
-and $2\times10^{5}\text{s}$}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=b_{i}$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_w/100000/P_1}\tabularnewline
-\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
-$b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
-versus resolved (dashed)}\tabularnewline
-\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi2e3_bT05_w/100000/P_1}\tabularnewline
-\end{tabular}
-
-\caption{Results of the RCE simulations. The top row shows horizontal averages
-of the resolved case between $t=10^{5}$s and $2\times10^{5}$s. The
-bottom two rows show results of the single column multi-fluid model
-after $10^{4}\ \text{s}$. \label{fig:RCE_singleColumn}}
-\end{figure}
-
-\section{Summary, Conclusions and Further Work}
-
-This paper presents solutions of the multi-fluid Boussinesq equations
-for convection, reproducing aspects of highly resolved dry convection
-at coarse horizontal resolution. Two test cases are used to validate
-the multi-fluid model. The first is a Boussinesq version of the well
-known two dimensional dry rising bubble of \citet{BF02} and the second
-is a dry two dimensional version of radiative-convective equilibrium
-with heating at the ground and uniform radiative cooling. High resolution
-single fluid simulations are conditionally averaged based on the sign
-of vertical velocity ($w$) in order to create rising and falling
-fluids which each have their own mean buoyancy, velocity and pressure.
-The two-fluid, single column Boussinesq model reproduces mean vertical
-heat and mass transport of these test cases.
-
-The multi-fluid Boussinesq equations can have divergence in each fluid
-while the divergence averaged over all fluids is zero. A model is
-proposed and validated for the pressure difference between the rising
-and falling fluids based on the divergence of each fluid. The use
-of a different pressure for each fluid is not only realistic but also
-leads to stable solutions of the multi-fluid equations.
-
-Conditionally averaging the high resolution solutions based on $w$
-leads to convecting and non-convecting regions with area fractions,
-$\sigma_{i}$, which are approximately uniform with height. Models
-for entrainment and detrainment into and out of convecting regions
-must clearly be consistent with the definition of the convecting region.
-We propose a model for entrainment and detrainment based on divergence
-that leads to excellent agreement with $\sigma$ from the high resolution
-solutions. We also test a more conventional fractional entrainment
-rate based on the reciprocal of the plume width which leads to unrealistic
-convecting area fractions.
-
-A set of unknowns in the multi-fluid equations are the properties
-of the fluid that are transferred from one fluid to another. An obvious
-first guess would be that fluid takes its mean buoyancy and velocity
-with it when it is transferred. However sub-grid-scale variability
-of each fluid means that we expect that the most buoyant fluid will
-be transferred to the rising fluid or the fluid with the largest vertical
-velocity will be transferred to the rising fluid and vice versa. An
-accurate estimate of these would depend on knowledge of the sub-grid-scale
-variability of each fluid which we do not have. Instead we assume
-that the fluid transferred in each direction has zero vertical velocity
-which is consistent with our conditional averaging. We have tested
-three models for the buoyancy of the fluid transferred. The most successful
-is to assume that the fluid takes its mean buoyancy with it. Assuming
-that the buoyancy of the transferred fluid is an average of the buoyancy
-of both fluids can lead to unrealistically large or small, unbounded
-buoyancies. Similarly, if we assume that one fluid has negative buoyancy
-and the other positive buoyancy and we transfer fluid of zero buoyancy,
-then unbounded buoyancy can occur. A better model of the buoyancy
-of the fluid transferred would rely on more information the sub-grid-scale
-variability.
-
-Single column multi-fluid modelling with moisture has already been
-demonstrated by \citet{TEB19}. Two important next steps are to simulate
-convection in the grey zone (where it is partially resolved) and to
-represent sub-grid-scale variability within each fluid by solving
-multi-fluid prognostic equations for turbulent kinetic energy and
-other moments of the sub-grid variability. These can be used to inform
-cloud base mass flux (since only the most buoyant fluid will transfer
-from the stable environment to the buoyant plume) and inform models
-of the properties of the fluid that is transferred. This will lead
-to a unified parameterisation of turbulence and convection and will
-take multi-fluid modelling of convection beyond existing paradigms.
-
-\section*{Acknowledgements}
-
-Many thanks to John Thuburn and Chris Holloway for valuable discussions.
-Thanks to the NERC/Met Office Paracon project. We acknowledge funding
-from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1.
-
-\bibliographystyle{abbrvnat}
-\bibliography{numerics}
-
 \end{document}

### 2020-07-03 submit3/manuscript.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
%
% This file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements, including customized APA reference formatting.
%
% You may copy this file and give it your
% article name, and enter your text.
%
%
% Step 1: Set the \documentclass
%
%

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option
%\usepackage[finalnew]{trackchanges}
\soulregister\ref7
\soulregister\cite7
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  Text to add
%  
%  Text to add
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

\draftfalse

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}

\usepackage{mathptmx}
\usepackage{array}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\begin{document}

\title{Multi-fluids for Representing Sub-filter-scale Convection}

\authors
{
    Hilary Weller\affil{1}\thanks{Meteorology, University of Reading, UK}
    ,
    William McIntyre\affil{1}
    ,
    Daniel Shipley\affil{1}
}

\affiliation{1}{Meteorology, University of Reading, UK}

\correspondingauthor{Hilary Weller}{h.weller@reading.ac.uk}

\begin{keypoints}
\item Multi-fluid modeling enables net mass transport by sub-grid-scale convection and non-equlibrium.
\item Multi-fluid modeling means a new dynamical core rather than a parameterization for an existing core
\item Closures for the pressure difference between fluids and entrainment and detrainment are provided
\end{keypoints}

\begin{abstract}
Multi-fluid modeling is a promising new method of representing sub- and near-grid-scale convection allowing for consistent and accurate
treatment of net mass transport by convection and of non-equilibrium dynamics . The air is partitioned into two or more
fluids which may represent, for example, updrafts and the stable environment. Each fluid has its own velocity, temperature and constituents
with separate equations of motion.

This paper presents two-fluid Boussinesq equations for representing under-resolved dry convection
with sinking and $w=0$ air in fluid 0 and rising air in fluid 1. A model for entrainment
and detrainment based on divergence  leads to excellent representation of the convective area fraction.
Previous multi-fluid modeling of convection has
used the same pressure for both fluids.
This is shown to be a bad approximation and  a model
for the pressure difference between the fluids based on divergence is presented.

Two vertical slice test cases are developed to tune parameters and to evaluate the two-fluid equations for representing dry, sub-grid-scale convection: a buoyant rising bubble and radiative convective equilibrium. These
are first simulated at high resolution and conditionally averaged based
on the sign of the vertical velocity. The test cases are next simulated with the two-fluid model which  reproduces
the mean properties of the rising and falling fluids in one column. 
\end{abstract}

\section*{Plain Language Summary}
Clouds and buoyant convection are often smaller than the grid size in weather and climate prediction models but they are of central importance. Therefore their effects are parameterized -- their interactions with the larger scales are estimated based on properties of the larger scales. Convection parameterizations are a large source of error in models of the atmosphere despite decades of effort to improve them. 
Some unrealistic assumptions remain such as that convection does not transport mass upwards, convection is in equilibrium with the surroundings and that the variations in the horizontal direction are not relevant. These make
it much simpler to incorporate convection parameterizations into existing models. 
Multi-fluid modeling
does not rely on these assumptions
but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model. This paper provides some closures necessary for multi-fluid modeling and evaluation of the technique for two dimensional dry convection.

\section{Introduction \label{sec:intro}}

Slow progress has been made improving the parameterization of sub-grid-scale
convection since \citeA{AS74}, \citeA{Tied89}, \citeA{GR90} and \citeA{KF90}. Convection is still
one of the weakest aspects of large scale models of the atmosphere
\cite{HPB+14,SAB+13,ipcc41}. Improvements have been made by relaxing
the quasi-equilibrium assumption \cite{PR98,GG05,Par14}, including
stochasticity \cite{PC08} and allowing net mass transport by convection
\cite{KB08,MB19}. These developments have enabled limited simulation
in the gray zone, where convection is partially resolved. However
there are still systematic biases implying that improvements should
still be possible.

\protect\citeA{LR01} introduced the ``assumed-distribution higher-order closure'' (ADHOC) parameterization of the boundary layer and convection which solves prognostic equations for higher-order moments of the sub-grid-scale flow, such as the triple correlation of the vertical velocity anomalies, and diagnoses updraft and downdraft means from the higher-order moments. Thus all necessary statistics can be calculated from the grid-box-mean values that are predicted by the dynamical core. Net mass transport by convection is included because it is part of the grid-box-mean. ADHOC was extended by \protect\citeA{GLC02}
to use bi-Gaussian probability distribution functions rather than top-hat distributions to represent sub-grid-scale variability. This formed the basis of the ``Cloud Layers Unified By Binormals'' (CLUBB) parameterization 
\protect\cite<>{LSW+12}
 which was first used at gray zone resolutions.

\citeA{TWV+18} proposed multi-fluid modeling of convection in order
to treat non-equilibrium and net mass transport  consistently.
The multi-fluids approach has a potential advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments directly (mean properties of e.g. updraft and environment) rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment. Solving directly for first-order moments in each fluid could be less sensitive to closure assumptions.
The multi-fluids approach has an advantage over prognostic plume models such as \protect\citeA{GG05} as multi-fluids enables the mass transported by convection to feed back onto the continuity equation. \citeA{Yano14} derived similar
equations to \citeA{TWV+18}  and showed how this is a generalization
of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
diffusivity mass flux'' or extended EDMF scheme  uses similar
equations but \citeA{TKP+18}
only solve the equations in a single column without
\change[HW]{coupling to the continuity equation of a dynamical core.}
{mass transported by convection feeding back onto the continuity equation.}

The disadvantage of the multi-fluids approach is that it requires
a dedicated model rather than being a stand alone parameterization
for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
of two-fluid equations
using the same pressure
for both fluids.
. \citeA{TEB19} showed that these equations  are in fact unstable and can be stabilized by diffusion of vertical
velocity whereas \citeA{WM19} stabilized the equations with diffusion
and drag between fluids. Neither of these stabilization techniques
are acceptable;
sufficient diffusion to stabilize the multi-fluid equations may smooth out real features of the flow and the diffusion between fluids and drag used by \protect\citeA{WM19} meant that both fluids tended to move together rather than through each other.
In this paper,  significant
and sustained pressure differences between the fluids are shown to exist (section \ref{sec:results}) and that the use of separate pressures stabilizes the equations.

This paper presents the multi-fluid Boussinesq equations for representing
sub-grid-scale convection including a parameterization of the pressure
difference between fluids (section \ref{subsec:fluidPressure}) and
a new model of entrainment and detrainment (section \ref{subsec:Sij}).
The numerical method for solving the equations is described in section
\ref{sec:numerics}. Results of two vertical slice test cases are presented in section {\protect\ref{sec:results}}. These are first simulated at high resolution in a single fluid model and then statistics of the flow are reproduced solving the two-fluid equations in one column.

\section{The Multi-fluid Boussinesq Equations \label{sec:multiBouEqns}}

\subsection{Derivation}

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
over to the Boussinesq equations because convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Boussinesq equations. Therefore, the Boussinesq equations without background stratification are chosen for simplicity:
\begin{eqnarray}
\frac{\partial \mathbf{u}}{\partial t} + \nabla\cdot(\mathbf{u}\mathbf{u})
+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
\label{eq:singleMom}
\\
\frac{\partial b}{\partial t} + \nabla\cdot(\mathbf{u}b)
 & = & \alpha\nabla^{2}b
\label{eq:singleb}
\\
\nabla\cdot\mathbf{u} & = & 0
\label{eq:singleDivFree}
\end{eqnarray}
where variables are defined in table \ref{tab:defns}. Note that the \add[HW]{Boussinesq} pressure \add[HW]{potential}, $P$, is actually pressure divided by a constant reference density\add[HW]{ and is referred to as just the pressure when considering the Boussinesq equations}.
\add[HW]{The pressure variations are determined up to a constant in order to ensure the divergence free constraint.}

\begin{table}
\begin{tabular}{l>{\raggedright}p{0.8\textwidth}}
$\sigma_{i}$ (-) & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$
\tabularnewline\hline
$\mathbf{u}$ ($\text{m}\text{s}^{-1}$)& 
Velocity of the single-fluid equations and velocity averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$) & Velocity of fluid $i$ 
\tabularnewline\hline
$w_{i}$ ($\text{m}\text{s}^{-1})$& Vertical component of $\mathbf{u}_{i}$\tabularnewline\hline
$S_{ij}$ ($\text{s}^{-1}$)& Rate of volume fraction transfer from fluid $i$ to $j$ 
\tabularnewline\hline
$P$ ($\text{m}^{2}\text{s}^{-2}$)& \add[HW]{Boussinesq} pressure \add[HW]{potential} of the single-fluid equations $=p^{\prime}/\rho_{r}$  and pressure \add[HW]{potential} averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$P_i$ ($\text{m}^{2}\text{s}^{-2}$)& Pressure \add[HW]{potential} of fluid $i$
\tabularnewline\hline
$p_i$ ($\text{m}^{2}\text{s}^{-2}$)& $P_i - P$
\tabularnewline\hline
$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$
\tabularnewline\hline
$b$ ($\text{m}\text{s}^{-2}$)& Buoyancy of single-fluid equations defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
where $\rho^{\prime}$ are departures in density from a horizontally
uniform reference, $\rho_{r}$  and buoyancy averaged over all fluids of the multi-fluid equations
\tabularnewline\hline
$b_{i}$ ($\text{m}\text{s}^{-2}$)& Buoyancy of fluid $i$ 
\tabularnewline\hline
$D_{i}\big/Dt$ ($\text{s}^{-1}$)& Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$
\tabularnewline\hline
$\mathbf{D}_{ij}$ ($\text{m}\text{s}^{-2}$)& Drag on fluid $i$ from fluid $j$ 
\tabularnewline\hline
$\gamma$ ($\text{m}^{2}\text{s}^{-1}$)& Compressibility for calculating $p_i$ 
\tabularnewline\hline
$C_{D}$ (-)& Drag coefficient $=0$ or 1
\tabularnewline\hline
$r_{c}$ (m) & Plume radius used for defining the drag between fluids (m)\tabularnewline\hline
$\alpha$ ($\text{m}^{2}\text{s}^{-1}$)& Diffusivity of buoyancy 
\tabularnewline\hline
$\nu$ ($\text{m}^{2}\text{s}^{-1}$)& Viscosity 
\tabularnewline\hline
$\mathbf{k}$ (-)& Unit vector in the $z$-direction.
\tabularnewline
\end{tabular}
\caption{Definitions of variables (and units) for the single- and multi-fluid Boussinesq equations.\label{tab:defns}}
\end{table}

The single-fluid Boussinesq equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations. Lagrangian labels, $I_i$, pick out different fluid types or regions. $I_i=1$ in fluid $i$ and 0 elsewhere. $I_i$ satisfies Lagrangian conservation without transfers:
\begin{equation}
\frac{\partial I_i}{\partial t} + \mathbf{u}\cdot\nabla I_i = 0.
\label{eq:LagrangianLabel}
\end{equation}
It is more straightforward to introduce transfers after volume averaging because the transfer terms for (\ref{eq:LagrangianLabel}) involve delta functions (this will be addressed in future publications). 
By applying a volume average (denoted by the overbar), the fluid $i$ volume fractions, velocities and buoyancies are defined by:
\begin{eqnarray}
\sigma_i &=& \overline{I_i} \\
\sigma_i \mathbf{u}_i &=& \overline{I_i \mathbf{u}} \\
\sigma_i b_i &=& \overline{I_i b}
\label{eq:defineFluidFields}
\end{eqnarray}
which implies
\begin{equation}
\sum_{i}\sigma_{i}  =  1.
\label{eq:sumOne}
\end{equation}
As the system is governed by the Boussinesq equations, it is assumed that variations in density only affect the definition of the buoyancy terms (table \protect\ref{tab:defns}) so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.

To derive a transport equation for $\sigma_i$, (\ref{eq:LagrangianLabel}) is combined with $I_i$ times (\ref{eq:singleDivFree}) and volume averaged. 
It is necessary to assume that operators permute with the averaging \cite<as described by>{TWV+18}. \add[HW]{Terms that appear because the averaging does not commute with the operators can be included in the transfers between fluids} \remove[HW]{Transfers between fluids are included at this stage} \add[HW]{which take the form}:
\begin{equation}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i}  =  \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\}
\label{eq:sigma}
\end{equation}
where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$.

Next the conditional averaging of terms in the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations is considered. Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
\begin{eqnarray}
\overline{I_i \nabla \cdot (\mathbf{u} \mathbf{u})} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
\overline{I_i \nabla (\mathbf{u} b)} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
\label{eq:filterAdvection}
\end{eqnarray}
The sub-filter-scale fluxes are represented by constant viscosity diffusion terms for each fluid. The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialized to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
\begin{eqnarray}
\overline{I_i \nu \nabla^2 \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
\overline{I_i \alpha \nabla^2 b} &\approx& \sigma_i \alpha \nabla^2b_i .
\end{eqnarray} 
%
The \add[HW]{Boussinesq} pressure \add[HW]{potetials} within each fluid are defined as:
\begin{equation}
\sigma_i P_i = \overline{I_i P}.
\end{equation}
The pressure gradient can then be decomposed as:
\begin{equation}
\overline{I_i \nabla P} = \sigma_i \nabla P_i + 
    \left[ P_i\nabla\sigma_i - \overline{P\nabla I_i} \right]
\end{equation}
The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using resolved variables and the full resolved version of the same force, both of which are related to drag. They will be represented by a drag, $\mathbf{D}_{ij}$. However this drag is likely to be smaller than the drag that is used, for example, in multi-phase modeling \cite<e.g.>{GBB+07} as it is representing the difference between two representations of drag, rather than the whole drag. Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.

Combining all terms gives the conditionally averaged momentum and buoyancy equations:
\begin{eqnarray}
\frac{\partial\sigma_i\mathbf{u}_{i}}{\partial t} + 
\nabla\cdot(\sigma_i \mathbf{u}_{i} \mathbf{u}_{i})
+ \sigma_i \nabla P_{i}
& = &
\sigma_i b_{i}\mathbf{k}
+
\nu\sigma_i\nabla^{2}\mathbf{u}_{i}
+
\sum_{j\ne i}\left\{
     \sigma_{j} S_{ji}\mathbf{u}_{ji}^{T}
   - \sigma_{i} S_{ij}\mathbf{u}_{ij}^{T}
   - \sigma_{i}\mathbf{D}_{ij}\right\}
\label{eq:momFlux}\\
\frac{\partial\sigma_i b_{i}}{\partial t} + 
\nabla\cdot(\sigma_i \mathbf{u}_{i} b_{i})
& = &
\alpha\sigma_i\nabla^{2}b_{i}
+
\sum_{j\ne i}\left\{
    \sigma_{j} S_{ji} b_{ji}^{T}
  - \sigma_{i} S_{ij} b_{ij}^{T}
\right\}.
\label{eq:bFlux}
\end{eqnarray}
These equations include mass transfers between fluids with $\mathbf{u}_{ij}^T$ being the velocity of the fluid transferred from $i$ to $j$ and $b_{ij}^T$ being the buoyancy of the fluid transferred from $i$ to $j$.

Equations (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated: 
\begin{eqnarray}
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i}
& = &
b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\}
\label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt}
& = &
\alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}
\end{eqnarray}
where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$,

Finally the multi-fluid version of incompressibility is
\begin{equation}
\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i}  = \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0.
\label{eq:divFree}
\end{equation}

\subsection{Pressure of each fluid \label{subsec:fluidPressure}}

\citeA{TEB19} and \citeA{WM19}
used the same pressure for both fluids.
This led to unstable equations that \citeA{TEB19}
stabilized using diffusion of vertical velocity and \citeA{WM19}
stabilized using mass exchanges or drag between the fluids. \citeA{TEB19}
achieved realistic results in one column experiments of the convective
boundary layer but the amount of diffusion needed would spoil simulations
in the free troposphere by diffusing real features as well as spurious artifacts. The stabilization used by \citeA{WM19} meant
that the two fluids tended to move as one which defeats the purpose
of using multi-fluid modeling.

The instabilities reported by \citeA{WM19} showed growing divergence
in a fluid with vanishing volume fraction. For single-fluid equations, divergence would lead to pressure anomalies which would act as a negative feedback on the divergence. However for multi-fluids with just one pressure, if one of the volume fractions is too small then it cannot force pressure anomalies big enough to stabilize the divergence. Use of a separate pressure for each fluid is therefore proposed to ensure stability.

It is assumed that the \add[HW]{Boussinesq} pressure \add[HW]{potential} in each fluid is given by a perturbation, $p_{i}$, from the total, $P$:
\begin{equation}
P_{i}=P+p_{i}.
\end{equation}
For stability and to respect $\sum_i \nabla\cdot\sigma_i\mathbf{u}_i=0$, we propose four constraints on the pressure perturbations, $p_i$:
\begin{enumerate}
\item $\sum_{i}\sigma_{i}p_{i}=0$.
\item $p_i=0$ when $\mathbf{u}_{i}=\mathbf{u}$ so that pressure perturbations do not force individual fluid anomalies away from the mean.
\item $p_i \not\to 0$ when $\sigma_i\to 0$ so that pressure perturbations control divergence in vanishing fluids.
\item $p_i\not\to\infty$ as $\sigma_j\to 0$ for any combination of $i,j$.
\end{enumerate}

In order to derive a suitable form of parameterization for $p_i$ we will first consider the \citeA{BN86} model of multi-phase flow.

\subsubsection{The \protect\citeA{BN86} model}

\citeA{BN86} proposed a parameterization for pressure differences
in a multi-phase explosion model that has been widely used in mathematics
and engineering for simulating, for example, fluidized beds of granular material \cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}. This model is not used here but is examined in order to derive a parameterization of pressure differences between fluids suitable for atmospheric convection.
\citeA{SA99} wrote transport equations for both the volume fraction,
$\sigma_{i}$, and for the mass fraction,
$\sigma_{i}\rho_{i}$, without transfers between fluids which in our notation are:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\mathbf{V}\cdot\nabla\sigma_{i} & = & \mu\left(P_{i}-P_{j}\right)
\label{eq:BNcompaction}
\\
\frac{\partial\sigma_{i}\rho_{i}}{\partial t}+\nabla\cdot\left(\sigma_{i}\rho_{i}\mathbf{u}_{i}\right) & = & 0
\label{eq:rhoTransport}
\end{eqnarray}
where $\mathbf{V}$ is the velocity of the interface between fluids,
$\mu$ is the compaction viscosity which controls how quickly the
pressure of each fluid relaxes to the mean pressure and index $j$
refers to the other fluid in a two fluid system.

Different authors make different assumptions about the interface velocity.
Assuming uniform density, the combination of equations (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport}) (to eliminate $\partial\sigma_i/\partial t$) shows that the pressure difference between fluids is related to divergence.

\subsubsection{Proposed Model for Pressure Differences between Fluids}

\citeA{TEB19} stabilized the multi-fluid equations by adding a diffusion
term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
If a fluid perturbation pressure is set to $p_i=-\nu\partial w/\partial z$
then this is equivalent to the diffusion term in one dimension. However adding an artificial diffusion term will harm three dimensional simulations of
resolved convection in the free troposphere whereas adding a fluid
perturbation pressure will not. Inspired by both \citeA{BN86} and
\citeA{TEB19}
and obeying the constraints given above, the pressure in each fluid is chosen to be:
\begin{equation}
p_{i}=
-\underbrace{\gamma\nabla\cdot\mathbf{u}_{i}}_{\text{stabilization}}
+
\underbrace{\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j}_{\text{correction}}
\label{eq:Pi_div}
\end{equation}
where $\gamma$ is a compressibility with units $\text{m}^2 \text{s}^{-1}$. The ``stabilization'' term reduces to that of \protect{\citeA{TEB19}} in one dimension and the ``correction'' term ensures that $\sum_i \sigma_i p_i =0$. It should be noted that this parameterization destroys \add[HW]{exact} energy conservation. \add[HW]{In future work solving the compressible equations we plan to re-insert the energy lost due to this stabilization as heat.}

Scale analysis in section
\ref{subsec:dimAnal} will inform the choice of $\gamma$ and sensitivity
to $\gamma$ will be evaluated in section \ref{sec:results}.

\subsection{Entrainment and Detrainment \label{subsec:Sij}}

It is useful to compare the transfer terms, $S_{ij}$, with models of entrainment, $\varepsilon$, and detrainment, $\delta$ used in convection parameterizations. If fluid 0 is the environment and fluid 1 is updrafts then the relationship is:
\begin{equation}
S_{01} = w_1\varepsilon, \;\;\;\;\;\;\;
S_{10} = w_0\delta.
\end{equation}
Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}. The first is similar to

the dynamic entrainment described by
\citeA{HC51}, \citeA{AK67} and \citeA{DBF+13}:
\begin{equation}
S_{ij}=\begin{cases}
-\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
0 & \text{otherwise.}
\end{cases}
\label{eq:Sdiv}
\end{equation}
This formulation prevents one fluid from accumulating when a fluid decelerates (at the top of a rising plume or at the bottom of descending air). {A} common form of lateral entrainment \cite<e.g.>{DBF+13} is also tested in section {\protect\ref{sec:results}}:
\begin{equation}
\varepsilon=\frac{0.2}{r_{c}}
\label{eq:fracEnt}
\end{equation}
where $r_{c}$ is the cloud or plume radius.

\subsection{Drag in the Momentum Equation\label{subsec:drag}}

Pressure differences between the fluids can lead to form drag which
is parameterized following \citeA{SW69}, \citeA{RC15} and \citeA{WM19} as: 
\begin{equation}
\mathbf{D}_{ij}=\frac{\sigma_{j}C_{D}}{r_{c}}|\mathbf{u}_{i}-\mathbf{u}_{j}|\left(\mathbf{u}_{i}-\mathbf{u}_{j}\right)\label{eq:dragBubble}
\end{equation}
where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.

\subsection{The Buoyancy and the Momentum of the Mass that is Transferred \label{subsec:transferProperties}}

Each fluid may not be well mixed so the fluid transferred
may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. A realistic estimate of the properties of the fluid transferred can only be based on knowledge of the sub-filter-scale variability (i.e. the variability within each fluid). Modeling of sub-filter-scale variability is beyond the scope of this paper.
%
However, since conditional averaging in this study is based on the vertical velocity, it is possible to say something about the vertical velocity transfer. The subset of fluid 0 that is about to rise (i.e. within the next time step) should be transferred from fluid 0 to fluid 1, and vice versa for the fluid about to fall in fluid 1. The fluid transferred will therefore have a vertical velocity of $w=0$.
For three dimensional multi-fluid simulations one could assume that the horizontal
velocity transferred is equal to the mean horizontal velocity of the
fluid transferred from:
\begin{equation}
\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
v_{i}\\
0
\end{pmatrix}.
\end{equation}
However, only one dimensional multi-fluid simulations are presented in this paper.

\add[HW]{The assumption that $w_{ij}^T=0$ does not imply anything about $b_{ij}^T$. In the absence of knowledge of the sub-filter-scale variability,} the buoyancy transferred follows \citeA{TEB19}: 
\begin{equation}
b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}.
\label{eq:bijT_thetab}
\end{equation}
Results are presented using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.

$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<e.g.>{AK67,AS74}.

Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
transferred depends on the properties of the receiving fluid which
is not logical and can lead to unbounded values of $b_{i}$ in the
fluid that is losing mass (as demonstrated in section \ref{sec:results}).

The model $b_{ij}^T=0$ is also tested. The rationale is that if fluid zero contains negatively buoyant air and fluid one contains positively buoyant air then the air that is transferred has zero buoyancy.

\subsection{\label{subsec:dimAnal}Scale
 Analysis}

Scale analysis can guide our choice of $\gamma$ for the parameterization of the pressure difference between fluids using the following assumptions:
\begin{enumerate}
\item The flow is buoyancy dominated.
\item The flow is close to inviscid.
\item The flow is slowly varying.
\item Fluid $i$ properties are anomalies from a neutrally stable resting
mean state 
implying that the average over all fluids of $b_i$, $\mathbf{u}_i$ and $P_i$ are zero.
\item Only the vertical direction is considered where $w_{ij}^{T}=0$.
\item $P_{i} = P + \gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j 
                              - \gamma\nabla\cdot\mathbf{u}_{i}
             \approx-\gamma\nabla\cdot\mathbf{u}_{i}
            =-\gamma\frac{\partial w_{i}}{\partial z}$
\item $\frac{\partial \sigma_i}{\partial z} \approx 0$
\item There are two fluids 
\item Without loss of generality, the transfers $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
and $S_{ji}=0$ are used.
\item The drag term, $\mathbf{D}_{ij}$, is zero.
\end{enumerate}
These assumptions can be used to simplify the multi-fluid $w$ equation, ({\protect\ref{eq:mom})}:
\begin{equation}
\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
\end{equation}
This is non-dimensionalized using a length scale $L$, a buoyancy scale
$B$ and a time scale $T$ to get the non-dimensional variables:
\begin{eqnarray*}
\tilde{w} & = & w_{i}T/L\\
\tilde{b} & = & b_{i}/B\\
\tilde{z} & = & z/L
\end{eqnarray*}
The non-dimensional version of (\ref{eq:wi_balances}) is then:
\begin{equation}
\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilization}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
\end{equation}
The flow is buoyancy dominated so the buoyancy term should be $O(1)$
which implies the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$. Therefore, the non-dimensional momentum equation becomes:
\begin{equation}
\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilization}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
\end{equation}
The stabilization term must be large enough to smooth out oscillations
in $\tilde{w}$ due to advection and buoyancy but not too large to
remove all variability in $\tilde{w}$. Therefore the stabilization term should be $O(1)$ which implies that:
\begin{equation}
\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
\end{equation}
This will be used to guide the choice of $\gamma$ in section {\protect\ref{sec:results}}.

\section{\label{sec:numerics}Numerical Method}

The spatial discretization follows exactly \citeA{WM19}, solving
advective form equations using monotonic, finite volume advection
and C-grid, Lorenz staggering. The time-stepping is Crank-Nicolson
with no off-centering and with deferred correction of explicitly solved
variables. The method for calculating a separate pressure for each fluid is new because \citeA{WM19}
solved the Euler equations with a single pressure.
Two outer iterations per time step are used to update explicitly solved variables. For the first outer
iteration, predicted values for time $n+1$ are set to those from
time level $n$ and are given the superscript $\ell$. For the second
iteration, values at $\ell$ are set to those from the end of the
first iteration. The implicit numerical method for applying the transfers
between fluids is specific for two fluids because it involves the
inversion of $2\times2$ matrices.

The prognostic variables are  $b_{i}$ in cell centers,  $\sigma_{i}$
in cell centers and the velocity flux at cell faces, $u_{i}=\mathbf{u}_{i}\cdot\mathbf{S}$,
which is the velocity at cell faces dotted with the area vector for
each face (normal to the face). The pressures, $P$ and $p_{i}$ are
diagnostic and are located at cell centers.

The first calculation of each outer iteration is for the transfer terms, $S_{ij}$ using ({\protect\ref{eq:Sdiv}}) or ({\protect\ref{eq:fracEnt}}). Next
(\ref{eq:sigma}) is solved
for each $\sigma_{i}$, operator split; first applying advection,
then correcting $\sum_{i}\sigma_{i}=1$ and finally applying mass transfers:
\begin{eqnarray}
\sigma_{i}^{\prime} & = & \sigma_{i}^{n}-\frac{\Delta t}{2}\nabla\cdot\left\{ \left(\mathbf{u}_{i}^{n}+\mathbf{u}_{i}^{\ell}\right)\left(\sigma_{i}^{n}\right)_{vL}\right\}
\\
\sigma_{i}^{\prime\prime} & = & \sigma_{i}^{\prime}\bigg/\sum_{i}\sigma_{i}^{\prime}
\\
\sigma_{i}^{n+1} & = & \sigma_{i}^{\prime\prime}+\Delta t\sum_{j\ne i}\sigma_{j}^{\prime\prime}S_{ji}-\sigma_{i}^{\prime\prime}S_{ij}
\end{eqnarray}
where $\Delta t$ is the time step and the superscripts $\prime$
and $\prime\prime$ denote intermediate values. $\sigma_{i}^{n}$
is interpolated from cell centers onto cell faces using monotonic
van Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citeA{WM19}
and values exclusively at time level $n$ for best accuracy and guaranteed
monotonicity. For calculating the divergence, the normal component
of $\mathbf{u}_{i}$ is needed at cell faces which are prognostic
variables of the C-grid. The $S_{ij}$ are limited to ensure $0<\sigma_{i}<1\ \forall i$.

Next \remove[HW]{eqn} (\ref{eq:b}) is solved for the buoyancy in each fluid, first
transporting buoyancy and then applying the transfer terms.
The advection term, $\mathbf{u}_i\nabla b_i$ is split into $\nabla\cdot(\mathbf{u}_i b_i) - b_i \nabla\cdot\mathbf{u}_i$ for better conservation as calculated by the finite volume method.
The transfer
terms can be very large due to the presence of $\frac{\sigma_{j}}{\sigma_{i}}S_{ij}$
in the transfer term for $b_{i}$ so they are treated operator split
and implicitly:
\begin{eqnarray}
b_{i}^{\prime} & = & b_{i}^{n}-\frac{\Delta t}{2}\Biggl(\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{n}\label{eq:transportb}\\
 &  & \hfill+\left(\nabla\cdot\left(\mathbf{u}_{i}(b_{i})_{vL}\right)+b_{i}\nabla\cdot\mathbf{u}_{i}+\alpha\nabla^{2}b_{i}\right)^{\ell}\Biggr)\\
b_{0}^{n+1} & = & b_{0}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{1}}{\sigma_{0}}\right)^{\prime\prime}S_{10}\left(b_{1}^{n+1}+b_{10}^{t}-b_{0}^{n+1}\right)-S_{01}b_{01}^{t}\right\} \label{eq:b0np1}\\
b_{1}^{n+1} & = & b_{1}^{\prime}+\Delta t\left\{ \left(\frac{\sigma_{0}}{\sigma_{1}}\right)^{\prime\prime}S_{01}\left(b_{0}^{n+1}+b_{01}^{t}-b_{1}^{n+1}\right)-S_{10}b_{10}^{t}\right\} \label{eq:b1np1}
\end{eqnarray}
where $b_{ij}^{t}=b_{ij}^{T}-b_{i}$. The use of $(\sigma_{0}/\sigma_{1})^{\prime\prime}$
from before the mass transfers is necessary to ensure bounded and
conservative transfers, as described by \cite{MWH20}. Simultaneous
solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
\begin{eqnarray}
b_{0}^{n+1} & = & \frac{\left(1+T_{01}\right)\left(b_{0}^{\prime}-\Delta tS_{01}b_{01}^{t}+T_{10}b_{10}^{t}\right)+T_{10}\left(b_{1}^{\prime}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}\right)}{1+T_{01}+T_{10}}\\
b_{1}^{n+1} & = & \frac{b_{1}^{\prime}+T_{01}b_{0}^{n+1}+T_{01}b_{01}^{t}-\Delta tS_{10}b_{10}^{t}}{1+T_{01}}
\end{eqnarray}
where $T_{ij}=\Delta t\left(\frac{\sigma_{i}}{\sigma_{j}}\right)^{\prime\prime}S_{ij}$

Next a Poisson equation is solved to calculate the total pressure,
$P$ to ensure that the total velocity is divergence free. This is the standard approach for ensuring divergence constraints \protect\cite<e.g.>{SKW14}. The pressure
equation also provides updates for the velocity flux, $u_{i}$. First
an intermediate velocity flux is calculated with partial updates and
updates from a previous value of $p_{i}$ but without updates from $\nabla P^{n+1}$:
\begin{eqnarray}
u_{i}^{\prime}= & u_{i}^{n}+\frac{\Delta t}{2} & \biggl(\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{\ell}\cdot\mathbf{S}-\nabla_{f}p_{i}^{\ell}\\
 &  & +\left(-\nabla\cdot(\mathbf{u}_{i}\mathbf{u}_{i})+\mathbf{u}_{i}\nabla\cdot\mathbf{u}_{i}+b_{i}\mathbf{k}\right)_{f}^{n}\cdot\mathbf{S}-\nabla_{f}(P+p_{i})^{n}\biggr)
\end{eqnarray}
where operator $()_{f}$ means linear interpolation from cell centers
onto cell faces and $\nabla_{f}P$ is a compact discretization of
$(\nabla P)_{f}\cdot\mathbf{S}$: i.e. the normal component of the pressure
gradient calculated from just the values of pressure either side of
the face. Once $P^{n+1}$ is calculated, the velocity flux (without
momentum transfers) is updated from the back-substitution:
\begin{equation}
u_{i}^{\prime\prime}=u_{i}^{\prime}-\frac{\Delta t}{2}\nabla_{f}P^{n+1}.\label{eq:backSub}
\end{equation}
The Poisson equation for $P^{n+1}$ is found by multiplying each \remove[HW]{eqn}
(\ref{eq:backSub}) by $\sigma_{i}$, summing over all fluids and
taking the divergence. Knowing that $\nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0$,
$\sum_{i}\sigma_{i}=1$ and $\sum_{i}\sigma_{i}p_{i}=0$ gives:
\begin{equation}
\nabla\cdot\sum_{i}\sigma_{i}u_{i}^{\prime}-\frac{\Delta t}{2}\nabla^{2}P^{n+1}=0
\end{equation}
which is solved to find $P^{n+1}$.

Next, the momentum transfers due to mass transfer and due to drag
are calculated implicitly, similar to the implicit transfers of buoyancy,
calculating $u_{i}^{n+1}$ from $u_{i}^{\prime\prime}$. These do
not influence the total $P$ or total divergence because momentum
is transferred conservatively. However they do influence $p_{i}$
which is why they are calculated before $p_{i}$. 
The next step
is to solve Helmholtz equations implicitly for each $p_{i}^{n+1}$:
\begin{equation}
p_{i}^{n+1} = \gamma \sum_j \left(\sigma^{n+1}_j \nabla\cdot u_j^{n+1} \right)
-\gamma\nabla\cdot
\left(u_{i}^{n+1}-\frac{\Delta t}{2}\nabla_{f}\left(p_{i}^{n+1}-p_{i}^{\ell}\right)\right)
\label{eq:pi_Helm}
\end{equation}
Both $p_{i}^{n+1}$ and $p_{i}^{\ell}$ appear in \remove[HW]{eqn} (\ref{eq:pi_Helm})
because $u_{i}^{n+1}$ already contains contributions from $p_{i}^{\ell}$
so these are removed before updating $p_{i}^{n+1}$. No back substitution
for $u_{i}$ is done after calculating $p_{i}^{n+1}$ because this
would destroy the divergence free constraint. Therefore $p_{i}^{n+1}$
only satisfies \remove[HW]{eqn} (\ref{eq:Pi_div}) exactly if the outer iterations
converge, when $p_{i}^{\ell}=p_{i}^{n+1}$.

The final stage of the time step iteration is to reconstruct $\mathbf{u}_{i}$
from $u_{i}$ following \citeA{WM19}. The stages calculating $P$,
$p_{i}$ and $\mathbf{u}_{i}$ are repeated twice per time step iteration.
The Poisson and Helmholtz equations are solved to a tolerance of $10^{-6}$
using the OpenFOAM conjugate gradient solver with incomplete Cholesky preconditioning.

\subsection{\label{sec:cAveraging}Discrete Conditional Averaging }

The multi-fluid equations will be evaluated in section \ref{sec:results} by comparison with high resolution single fluid solutions. This has to be done carefully as even these reference solutions exist on a discrete grid. A single-fluid solution is conditionally averaged by:
\begin{equation}
i =
\begin{cases}
    0 & \text{ if }w\le 0 \\
    1 & \text{ otherwise.}
\end{cases}
\end{equation}
If an entire grid box is assigned to be either in fluid 0 or fluid 1 based on $w$ at the cell center then $\sigma$ can only take a small number of discrete values depending on the resolution of the conditional averaging. For example, if conditional averaging goes from $n$ columns to 1 column with vertical resolution staying the same, then $\sigma$ can only take values $\frac{k}{n}$ where $k$ is an integer between zero and $n$. This means that $\sigma$ is either uniform (for small $n$) or has jumps in the vertical (for larger $n$). An alternative is therefore proposed in order to approximate $\sigma$ based on $w$ and $\nabla w$ at cell centers. This is based on the intersection between a grid box and the surface of $w=0$. Given a grid box with center $\mathbf{x}_c$, the surface of points, $\mathbf{x}_w$ of $w=0$ satisfy:
\begin{equation}
\nabla w \cdot \left(\mathbf{x}_c - \mathbf{x}_w\right) = 0
\end{equation}
Rather than the expense of calculating exact grid box volume fractions either side of this surface, the signed distance of each grid box vertex, $\mathbf{x}_v$, to the surface is calculated:
\begin{equation}
d_v = \left(
     \mathbf{x}_v - \mathbf{x}_c + \frac{w \nabla w}{|\nabla w|^2} 
\right) \cdot \frac{\nabla w}{|\nabla w|}.
\end{equation}
The volume fraction either side of the $w=0$ surface is approximated by the average distance to vertices in one side of the surface divided by the average distance to vertices on both side:
\begin{equation}
\sigma_0 = 
\frac{-\text{mean}\bigl(\text{all } d_v \text{ with } d_v \le 0\bigr)}
{\text{mean}\bigl(\text{all } |d_v| \bigl)}
\;\;\;\;\;\;
\sigma_1 = 
\frac{\text{mean}\bigl(\text{all } d_v \text{ with } d_v > 0\bigr)}
{\text{mean}\bigl(\text{all } |d_v| \bigl)}.
\end{equation}
This gives smooth $\sigma$ fields that will be shown in section \ref{sec:results}.

\section{\label{sec:results}Evaluation Test Cases}

Two test cases are developed to tune parameters and to evaluate the
use of two-fluid equations to represent dry, two-dimensional, sub-grid-scale
convection. The first is transient; the standard rising bubble of
\citeA{BF02}.  The second  is steady state with heat transfer at
the ground and uniform radiative cooling (radiative convective equilibrium). For both test cases, the
reference solution is a single-fluid solution of the two-dimensional
Boussinesq equations at high horizontal and vertical resolution. These will be compared with the two-fluid model run using one column. The aim is to reproduce the vertical heat transport, the mean velocity of the rising air, the buoyancy of the rising air and the pressure differences between fluids in one column of the two-fluid model.

\subsection{Rising Bubble}

The two dimensional test case of \citeA{BF02} was designed for fully compressible
inviscid models but similar solutions are obtained solving inviscid Boussinesq equations ($\nu=0$, $\alpha=0$).
The Boussinesq version has no background stratification in a domain
of height 10\,km and width 20\,km initially at rest. The buoyant
perturbation is given by:
\begin{equation}
b=\frac{1}{15}\cos^{2}\left(\frac{\pi L}{2}\right)\label{eq:thetaPerturb}
\end{equation}
for $L<1$ where $L=\sqrt{\left(\frac{x-x_{c}}{x_{r}}\right)^{2}+\left(\frac{z-z_{c}}{z_{r}}\right)^{2}}$,
$x_{c}=10\ \text{km}$, $z_{c}=2\ \text{km}$ and $x_{r}=z_{r}=2\ \text{km}$.
100\,m grid spacing is used in the $x$ and $z$ directions for the
two dimensional reference simulation and $\Delta z=100\ \text{m}$
is used in the vertical for the one column simulations. All simulations
use a time-step of 2\,s.

\subsubsection{Single-Fluid Solutions}

The solution of the Boussinesq equations in two dimensions for the rising bubble at high resolution is shown in figure \ref{fig:bubble}, at the initial time, 500 seconds and 1000 seconds,
with buoyancy colored, pressure contoured and the $w=0$ contour dotted.
The solution is very similar to the fully compressible solution \cite{BF02}.
The pressure gradients accelerate the flow beneath the bubble, decelerate
the flow above the bubble and pull in air horizontally. 
The $w=0$ contour at the initial time shows the initial tendency of $w$ which demonstrates that there is no straightforward relationship between buoyancy and $w$; $w$ is the solution of an elliptic problem involving the momentum equation and the divergence-free constraint. After 500 seconds the center of the bubble has risen further than the edges and after 1000 seconds there is a complex region of entrainment inside the bubble consisting of both buoyant and neutral rising air and buoyant and neutral sinking air. It is unlikely that the simple parameterizations proposed here will be able to reproduce statistics of this complex behavior.

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=0.9\textwidth]{figures/bubble.pdf}
\par\end{centering}
\caption{\label{fig:bubble}The single-fluid, resolved 2D rising bubble after 0s, 500s and 1000s. Buoyancy is coloured and pressure is contoured every $10\text{m}^{2}\text{s}^{-2}$,
negative contours dashed. The $w=0$ contour is dotted.
\add[HW]{At $t=0$, $w=0$ everywhere so the dotted contour shows $\partial w/\partial t=0$ for the top panel.}
}
\end{figure}

\citeA{TEB19} and \citeA{WM19}
used the same pressure
for both fluids with differences parameterized as drag. 
The high pressure above and low pressure below the bubble in figure {\protect\ref{fig:bubble}} are a manifestation of form drag and will act to slow the ascent. However the pressure patterns in figure {\protect\ref{fig:bubble}} also show the limitations of this approach; the low pressure region at the bottom of the bubble will also act to accelerate the rising flow into the bubble which is not accounted for by drag and there are also widespread pressure anomalies in the sinking fluid which will accelerate the descent whereas drag will always act to slow the fluid.

Large scale models of the atmosphere often have coarse horizontal resolution and relatively fine vertical resolution. The high resolution solution is horizontally averaged, conditioned based on the sign of $w$, to give the vertical profiles that coarse resolution models or parameterizations should reproduce. Sinking air and air with $w=0$ is assigned to fluid 0 and rising air to fluid 1 and an average is taken over the $x$ direction at time $t=1000\ \text{s}$ to give the profiles
shown in the top row of figure \ref{fig:bubble_singleUnderRes}.
$\sigma_{1}$ is the volume fraction of rising fluid at every height and $b_{0}$ and $b_{1}$, $w_{0}$ and $w_{1}$ and $P_{0}$ and $P_{1}$
are the average buoyancy, vertical velocity and pressure of the rising and falling fluids. 
$\sigma_1$ varies little with height. The complex shape of the bubble is evident in $b_0$ which has two peaks; the lower peak associated with re-entrained air. The fastest ascent is at the bottom of the bubble, co-located with a large drop in pressure.

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=\textwidth]{figures/bubble_singleUnderRes.pdf}
\par\end{centering}
\caption{The rising bubble after 1000s simulated with varying horizontal resolution
and a single-fluid. Horizontal averages are conditioned based on $w$.
\label{fig:bubble_singleUnderRes}}
\end{figure}

In order to see what happens in a single fluid atmospheric model at modest horizontal resolution without a parameterization of convection, the bubble is simulated at coarser horizontal resolutions, using nine, five, three and one columns instead of the 200 columns of the fine resolution to cover the 20km wide domain and a vertical space of $\Delta z=100\ \text{m}$.
The conditional and horizontal averages of these simulations are shown in figure \ref{fig:bubble_singleUnderRes}

These simulations are initialized by conservative
horizontal averaging from the full resolution solution. As the horizontal
resolution is reduced, the vertical transport reduces until there
is no movement at all for the one column simulation: there is no possibility
of fluid rising because in one column with a single-fluid there can be no compensating subsidence. The lack of vertical transport
at coarse resolution motivates convection parameterization.

\subsubsection{Results of the Two-fluid, One Column Simulations}

Two-fluid, one column simulations are initialized by horizontally
and conditionally averaging the high resolution single-fluid initial
conditions. Sinking air is put into fluid zero and rising air into
fluid one. The velocity field after one time step is used for initialization
as the air is stationary at $t=0$. Results after 500 seconds are shown in figures \ref{fig:multiFluidBubble_500_1}
and \ref{fig:multiFluidBubble_500_2} for various assumptions about
transfers between fluids and various parameter values.

\begin{figure}
\noindent
\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_1.pdf}
\caption{\label{fig:multiFluidBubble_500_1} Results of the rising bubble at $t=500\ \text{s}$. Solid lines are the multi-fluid, one column solutions of the rising bubble. Dashed lines are the single-fluid, resolved solutions.}
\end{figure}

The solutions in the top row of figure {\protect\ref{fig:multiFluidBubble_500_1}} have
no drag between fluids, almost no transfers, no diffusion and
the pressures of both fluids are assumed equal meaning that the multi-fluid equations should be unstable \cite{TEB19}. 
Small transfers are applied
to prevent either $\sigma_{i}$ from becoming negative. This is sufficient to stabilize the solution but does not prevent oscillations from developing in all fields. The buoyant fluid has risen little from the initial conditions. $\sigma_1$ oscillates between zero and one meaning that only one fluid is present at some locations so there is no possibility for the fluids to move past each other.
The two fluids have mixed due to the two-way stabilizing transfers which have reduced the buoyancy in the rising fluid and increased the buoyancy in the sinking fluid.

Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ stabilizes the solution and
leads to a realistic rising volume fraction (second row of
figure \ref{fig:multiFluidBubble_500_1}).
The fluids move a little further past each other
even without pressure differences between the fluids. However there is too much mixing between the fluids
and a discontinuity arises at the bubble leading edge; the buoyancy force is producing vertical motion but there is no pressure to make it smooth.

Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
and pressure difference between the fluids controlled by divergence
($P_{i}=P+\gamma\sum_j \sigma_j \nabla\cdot\mathbf{u}_j-\gamma\nabla\cdot\mathbf{u}_{i}$), the simulations are more realistic (bottom three rows of figure \ref{fig:multiFluidBubble_500_1}).
The first value, $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$, is set from equation
(\ref{eq:gammaDimAnal}) using length scale equal to the initial bubble
radius and a buoyancy scale equal to the initial maximum buoyancy. This makes
the velocity profile too smooth and the updraft too weak so the
bubble does not rise enough. It is reasonable to consider smaller values of $\gamma$ because the buoyancy does not retain its initial maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$ leads to the leading edge of the bubble rising too quickly and does not fully remove the discontinuity in the updraft velocity at the leading edge of the bubble. The pressure differences between the fluids have some similarity with the resolved simulation but none of the values of $\gamma$ reproduce the pressure dip at the trailing edge of the bubble. $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives the closest approximation to the resolved simulation.

The results in the top row of figure \ref{fig:multiFluidBubble_500_2}
use
divergence transfer and pressure differences between fluids but, different from previous simulations, also use drag \change[HW]{set by}{with a coefficient satisfying} $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The drag slows the updrafts without increasing the mixing between the fluids which makes the solutions less like the resolved simulations.
Although drag is known to be an important term in the momentum equations for buoyant thermals and plumes \cite<e.g.,>{RC15}, the drag is related to
pressure differences caused by the relative motion and to
mixing with downdraft air.
The mixing with downdraft air is already accounted for in the entrainment and the pressure differences are already accounted for in the pressure parameterization. Therefore the drag parameterization is not a useful contribution to the multi-fluid Boussinesq equations.

\begin{figure}
\noindent
\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_2.pdf}
\caption{As figure \ref{fig:multiFluidBubble_500_1} but different parameterization options.
\label{fig:multiFluidBubble_500_2}}
\end{figure}

If
pressure differences between fluids are included
with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
without
entrainment ($S_{ij}\approx 0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
the fluids move past each other but there is 
a build up of fluid 1 at the leading edge of the bubble and very little
fluid 1 below the bubble.

With one column and
two fluids, all air must rise in one fluid and sink in the other.
Continuity does not allow for any other solution. Pressure gradients
can accelerate or decelerate this flow but as the model is set up,
with no transfers between fluids, no fluid can change direction. It
is therefore essential to have transfers between fluids.

The other entrainment option is the commonly used fractional entrainment
rate, $\varepsilon=0.2/r_{c}$. This is used in combination with with pressure differences between fluids in the third row of figure \ref{fig:multiFluidBubble_500_2}.
The solutions are smooth
but the rising volume fraction is not right with a build up of fluid 1 at the bubble leading edge, the updraft is too
weak and too much is entrained into fluid 1 above the bubble.
Using this entrainment, the updraft will entrain more and more air until $\sigma_{1}=1$. The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives
results closer to the reference solution.

Two alternative models for estimating the buoyancy of the fluid transferred
between updraft and downdraft have been tested. The results in
the fourth row of figure \ref{fig:multiFluidBubble_500_2} assume that the fluid transferred has zero buoyancy in order to keep the
positively buoyant air in fluid one and the negatively buoyant air
in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraft),
the mean buoyancy of fluid one increases. This leads to
higher buoyancy in fluid one than when using $b_{ij}^T=b_i$ and gives results close to the reference solution.
The results in the bottom row of figure \ref{fig:multiFluidBubble_500_2}
use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citeA{TEB19}
so that the fluid transferred is influenced by the fluid it is moving
towards as well as where it has come from. 
These solutions are also similar to the resolved solutions.

\begin{figure}
\noindent
\includegraphics[width=\linewidth]{figures/multiFluidBubble_1000.pdf}
\caption{\label{fig:multiFluidBubble_1000} Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are the multi-fluid, one column solutions of the rising bubble. Dashed lines are the single-fluid, resolved solutions.
}
\end{figure}

From the results at 500 seconds, we can conclude that:
\protect\begin{itemize}
\item Divergence transfer (entrainment and detrainment) leads to realistic updraft area fractions.
\item Pressure differences between fluids are usefully modelled by divergence, with a coefficient close to the derived value from scale analysis.
\item Drag terms are not useful.
\item Entrainment calculated as the reciprocal of plume width is not useful.
\protect\end{itemize}
In order to examine further the effects of different assumptions about the buoyancy of the fluid transferred, a selection of results at 1000 seconds are presented in figure {\protect\ref{fig:multiFluidBubble_1000}}. 
None of the simulations reproduce the complex buoyancy pattern at the trailing edge of the bubble associated with a deep low pressure. The rising air fraction ($\sigma_1$) at and below the bubble is too low in all simulations. The top row which uses $b_{ij}^T=b_i$ (transferring the mean buoyancy) shows too much mixing between the fluids -- too much of the most buoyant air has been transferred out of fluid 1 but the leading edge of the bubble has risen about the right amount. In the other two simulations, the air that is transferred out of fluid 1 has lower buoyancy than the mean in fluid 1 ($b_{10}^T<b_1$) so the remaining rising fluid stays very buoyant and rises too far. The assumption that the buoyancy transferred is zero (middle row of figure {\protect\ref{fig:multiFluidBubble_1000}}) means that the buoyant fluid increases its buoyancy above the initial conditions which would not be possible in the resolved single-fluid solution.

It might be possible to improve aspects of this simulation by optimising $\gamma$ and $\theta_b$ (the coefficient from \remove[HW]{eqn} ({\protect\ref{eq:bijT_thetab}}) for calculating $b_{ij}^T$) but it is probably not helpful to over fit the two-fluid model to this dry, two dimensional test case.
There are clearly discrepancies between
the single-fluid resolved rising bubble and the two fluid one column rising bubble but rather than trying to fit this test case closely, cases with multiple plumes in each column should be considered. Using the lessons learned from modeling the rising bubble, a statistically stationary case with many plumes is simulated next.

\subsection{Radiative-Convective Equilibrium (RCE)}

A two-dimensional, dry radiative convective equilibrium test case
is devised to mimic some properties of atmospheric convection, in
particular the difficulty resolving the flow at coarse resolution.
The domain is 160km wide, 10km tall and is resolved by 640 cells in
the horizontal and 40 in the vertical ($\Delta x=\Delta z=250$m).
The top and bottom boundaries are zero velocity and the lateral boundaries
are periodic. A heat flux of $h=10^{-3}\text{m}^{2}\text{s}^{-3}$
is imposed at the bottom boundary leading to a boundary condition
of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
so as to give a Prandtl number of $0.707$, the value for dry air. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$ is applied to the domain to maintain equilibrium.

The fluid is initially stationary with $b=0$. In order to quickly
and reproducibly initialize instability, $b=10^{-4}\text{m}^{2}\text{s}^{-1}$
is imposed in a square of side length 2000m at the center in the $x$
direction and at the ground. The simulation is run using a time step
of $5\ \text{s}$. A quasi-steady, chaotic state is reached after
about $3\times10^{4}\text{s}$ and the simulation is run for $2\times10^{5}\text{s}$
and conditional averages are calculated over the final $10^{5}$s.

This test case is designed to have strong updrafts in narrow plumes
and weak descent elsewhere to mimic atmospheric convection but without
the complication of moisture, phase changes and three spatial dimensions.

\subsubsection{Single-Fluid Solutions}

A snapshot of the buoyancy, vertical velocity and pressure of the
radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
updrafts. The buoyant air at the ground rises in narrow plumes,
accelerating due to buoyancy and pressure gradients then decelerating
due to pressure gradients before reaching the top. The plumes spread
out and the sinking air is a mixture of warm and cold with similar
pressure gradients in the rising and falling air, accelerating then
decelerating the flow so as to maintain continuity.

\begin{figure}
\noindent 
\includegraphics[width=1\textwidth]{figures/RCE_resolved.pdf}
\caption{\label{fig:RCE_resolved}
Buoyancy, vertical velocity and pressure at $t=2\times10^{5}\ \text{s}$
of the resolved radiative-convective equilibrium test case. Vertical
velocity contours are black every 0.5m/s with negative contours dashed
and the zero contour dotted. The domain is 10km high and 160km wide
and the z-direction is stretched a factor of 2 in the plots.}
\end{figure}

Horizontal averages conditioned on $w$ and time averaged every 1000s
between $10^{5}\ \text{s}$ and $2\times10^{5}\ \text{s}$ are shown
as dashed lines in figure \ref{fig:RCE_singleColumn}. The rising and
falling volume fractions, $\sigma_{1}$ and $\sigma_{0}$, remain
close to $\frac{1}{2}$ throughout the depth. The rising plumes look
narrow in figure \ref{fig:RCE_resolved} but there are wide regions
of slowly rising air around the plume cores. The entrained rising
cool air and warm air sinking that has hit the model top mean that
the rising and falling air have similar average buoyancy away from
the ground. The ascending air gradually accelerates towards the middle
of the domain then decelerates towards the model top. At the ground
the acceleration is forced by buoyancy and away from the ground the
acceleration is controlled by pressure gradients. The descending air
mean velocity is close to equal and opposite to the ascending air,
as expected since $\sigma_{1}=0.5$.

\subsubsection{Results of the Two-fluid, One Column Simulations}

The two fluid model is used to simulate the RCE test case in one
column of 40 cells with zero buoyancy gradient at the top and a buoyancy
gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
and uniform radiative cooling. The two fluids are initialized using
the time mean conditional horizontal averages from the single-fluid
resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
is used for all simulations to account for transfers throughout the
domain to represent cloud base mass flux (at the bottom boundary),
cloud top detrainment and lateral entrainment. $\gamma$ is set from
equation (\ref{eq:gammaDimAnal}) using the depth of the high resolution solution super adiabatic
layer as the length scale ($L=800\text{m}$) and the buoyancy scale
$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. (Scale analysis or boundary layer parameterization could instead be used to estimate $L$ independently.)
A simulation using
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
is shown in the top row of figure \ref{fig:RCE_singleColumn}.
The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
at about 0.5 throughout the depth, as in the resolved simulation,
with entrainment in the lower half of the domain ($S_{01}>0$) and
detrainment in the upper half ($S_{10}>0$), where the air decelerates
towards the top. The one column model reproduces the super-adiabatic
layer near the ground and the near uniform buoyancy away from the
ground but the buoyancy difference between the fluids is too large.
The updraft and downdraft velocities are captured well. The pressure
differences between fluids are too large which is consistent with
the over estimated buoyancy difference between fluids.

\begin{figure}
\noindent
\includegraphics[width=\linewidth]{figures/RCE_singleColumn.pdf}
\caption{\label{fig:RCE_singleColumn}
Results of the RCE simulations. Dashed lines show horizontal averages
of the resolved case between $t=10^{5}\text{s}$ and $2\times10^{5}\text{s}$. Solid lines show results of the one column multi-fluid model after $10^{4}\ \text{s}$. }
\end{figure}

Results of a simulation using $b_{ij}^{T}=\frac{1}{2}(b_{0}+b_{1})$
is shown in the bottom row of figure \ref{fig:RCE_singleColumn}.
This model of the buoyancy of the transferred fluid is not helpful; it leads
to strong cooling in fluid zero near the ground due to the large transfers.
It is more accurate to assume that fluids take their mean properties
when transferred, $b_{ij}^{T}=b_{i}$.

The two-fluid, one column model of RCE gave results closer to the reference solution than for the rising bubble. This is likely to be because the rising and falling fluids in the RCE test case are averaged over a large area with plumes at different stages of development rather than trying to simulate the complex entrainment pattern behind a single bubble. The RCE test case is horizontally homogeneous and in equilibrium making it more straightforward.

\section{Summary, Conclusions and Further Work \label{sec:concs}}

This paper demonstrates the plausible utility of using multi-fluid equations to represent sub-grid-scale convection.
Solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.
Two test cases are used to evaluate
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citeA{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single-fluid simulations are conditionally averaged based on the sign
of vertical velocity ($w$) in order to define rising and falling fluids which each have their own  buoyancy, velocity and pressure. The two-fluid, one column Boussinesq model reproduces mean vertical heat and mass transport of these test cases.

The radiative-convective equilibrium (RCE) test case complies with the assumptions of a traditional mass-flux convection scheme --  an ensemble of plumes per column, horizontal homogeneity and equilibrium. The rising bubble test does not satisfy these constraints. The multi-fluid model gives good solutions for the RCE test case and good solutions for the bubble for the first part of the simulation but does not represent the complex re-entrainment as the bubble continues to rise.

The multi-fluid Boussinesq equations can have divergence in each fluid
while the divergence averaged over all fluids is 
constrained to be zero by the single-fluid Boussinesq equations.
A model is proposed and evaluated for the pressure difference between the rising
and falling fluids based on the divergence of each fluid. The use
of a different pressure for each fluid is not only realistic but also
leads to stable solutions of the multi-fluid equations.

Conditionally averaging the high resolution solutions based on $w$
leads to
rising and falling fluids with area fractions, $\sigma_{i}$, which are approximately uniform with height. Models for entrainment and detrainment into and out of these regions
need to be consistent with the definition of the convecting region.
A model for entrainment and detrainment based on divergence is proposed
that leads to excellent agreement with $\sigma$ from the high resolution
solutions. A more conventional fractional entrainment rate based on the reciprocal of the plume width is also tested which leads to unrealistic rising area fractions.

The properties of the fluid that are transferred from one fluid to another are unknowns in the multi-fluid equations and these require closure. An obvious
first guess is that fluid takes its mean buoyancy and velocity
with it when it is transferred.
Improvements on this assumption will depend on knowledge of sub-filter-scale variability. However since conditional averaging is based on the sign of $w$, it is consistent to assume that the fluid transferred has $w=0$ ($w_{ij}^T=0$).
Three models for the buoyancy of the fluid transferred 
are tested. The most successful
is to assume that the fluid takes its mean buoyancy with it
($b_{ij}^T=b_i$).
Assuming that the buoyancy of the transferred fluid is an average of the buoyancy of both fluids ($b_{ij}^T=\frac{1}{2}(b_i+b_j)$) can lead to unrealistically large or small, unbounded buoyancies. 
Assuming that one fluid has negative buoyancy and the other positive buoyancy and fluid of zero buoyancy is transferred ($b_{ij}^T=0$) also leads to unbounded buoyancy.

One column multi-fluid modeling with moisture has already been demonstrated by \citeA{TEB19} and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19}.
Next steps are to simulate convection in the gray zone (where it is partially resolved) and to represent sub-filter-scale variability within each fluid, \add[HW]{further extending the EDMF scheme \protect\cite{TKP+18}}.
Cloud base mass flux could then be estimated based on higher-order moments of the vertical velocity and buoyancy within the environment fluid \add[HW]{and vertical transport of turbulence by plumes can inform estimates of entrainment}.
This will lead to a unified parameterization of turbulence and convection and will take multi-fluid modeling of convection beyond existing paradigms.

\acknowledgments

Many thanks to Peter Clark, John Thuburn and Chris Holloway for valuable discussions and comments on the manuscript.
Thanks to the NERC/Met Office Paracon project. We acknowledge funding
from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1. The code is built using \url{https://openfoam.org/version/7/} and is part of \url{https://github.com/AtmosFOAM/}. The code releases are \url{https://doi.org/10.5281/zenodo.3828474} and \url{https://doi.org/10.5281/zenodo.3832130}.

\bibliography{numerics}

\end{document}

### 2020-07-03 submit3/manuscript2.tex
First draft of revisions and responses to second set of reviews from reviewer 1. Still to respond to reviewer 2. I have currently not followed all of Dan's suggestions because Dan's work should go into Dan's first author papers. I still need to reponsd to and revise based on reviewer 2. I also need to add a couple of lines about the boundary layer depth for the RCE test case.

--- 2020-05-04 submit2/manuscript.tex
@@
 \usepackage{lineno}
-\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
-%\usepackage{soul}
+%\usepackage[inline]{trackchanges} %for better track changes. finalnew option
+\usepackage[finalnew]{trackchanges}
 \soulregister\ref7
@@
     Daniel Shipley\affil{1}
-    , and 
-    Peter Clark\affil{1}
 }
@@
 \begin{keypoints}
-\item Multi-fluid modelling enables net mass transport by parameterised convection and non-equlibrium.
+\item Multi-fluid modelling enables net mass transport by \change[HW]{parameterised}{sub-grid-scale} convection and non-equlibrium.
 \item Multi-fluid modelling means a new dynamical core rather than a parameterisation for an existing core
-\item Closure for the pressure difference between fluids and entrainment and detrainment are provided
+\item Closures for the pressure difference between fluids and entrainment and detrainment are provided
 \end{keypoints}
@@
 \begin{abstract}
-Multi-fluid modelling is a promising new method of representing sub
-and near grid-scale convection allowing for consistent and accurate
+Multi-fluid modelling is a promising new method of representing sub- and near-grid-scale convection allowing for consistent and accurate
 treatment of net mass transport by convection \add[HW]{and of} non-equilibrium \add[HW]{dynamics} \remove[HW]{and turbulence}.
@@
 Previous multi-fluid modelling of convection has
-\change[HW]{assumed that all fluids share the same pressure.}
-{used the same pressure for both fluids.}
+\change[HW]{assumed that all fluids share the same pressure.}{used the same pressure for both fluids.}
 \change[HW]{We show that this is}{This is shown to be} a bad \change[HW]{assumption}{approximation} and \remove[HW]{we propose and validate} a model
@@
 
-Two vertical slice test cases are \change[HW]{used}{developed} to \add[HW]{tune parameters and to} \change[HW]{validate}{evaluate} the \change[HW]{multi}{two}-fluid \change[HW]{model}{equations for representing dry, two-dimensional, sub-grid-scale convection}; a buoyant rising bubble and radiative convective equilibrium.
+Two vertical slice test cases are \change[HW]{used}{developed} to \add[HW]{tune parameters and to} \change[HW]{validate}{evaluate} the \change[HW]{multi}{two}-fluid \change[HW]{model}{equations for representing dry, sub-grid-scale convection}: a buoyant rising bubble and radiative convective equilibrium.
 \add[HW]{These}
@@
 Convection parameterisations are a large source of error in models of the atmosphere despite decades of effort to improve them.
-An important assumption in most convection parameterisations is that convection moves heat and moisture upwards but not mass.
-This makes it much simpler to incorporate convection parameterisations into existing models.
-Multi-fluid modelling will enable mass transport by convection but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model.
+\change[HW]{An important assumption in most convection parameterisations is that convection moves heat and moisture upwards but not mass.
+This makes }{Some unrealistic assumptions remain such as that convection does not transport mass upwards, convection is in equilibrium with the surroundings and that the variations in the horizontal direction are not relevant.
+These make}
+it much simpler to incorporate convection parameterisations into existing models. 
+Multi-fluid modelling
+\change[HW]{will enable mass transport by convection}{does not rely on these assumptions}
+but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model.
 This paper provides some closures necessary for multi-fluid modelling and \change[HW]{validation}{evaluation} of the technique for two dimensional dry convection.
@@
 to treat non-equilibrium and net mass transport \remove[HW]{correctly and} consistently.
-\add[HW]{The multi-fluids approach has an advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments directly (mean properties of eg.
+\add[HW]{The multi-fluids approach has a potential advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments directly (mean properties of e.g.
 updraft and environment) rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment.
-Solving directly for sub-fluid means could be less sensitive to closure assumptions.}
+Solving directly for first-order moments in each fluid could be less sensitive to closure assumptions.}
+\add[HW]{The multi-fluids approach has an advantage over prognostic plume models such as \protect\citeA{GG05} as multi-fluids enables the mass transported by convection to feed back onto the continuity equation.}
 \remove{with the same numerics and physics to prognose properties of separate parts of the fluid, for example updrafts, the stable environment and downdrafts dynamics}. \citeA{Yano14} derived similar
-equations \remove[HW]{for multiple segments} and showed how this is a generalisation
+equations to \citeA{TWV+18} \remove[HW]{for multiple segments} and showed how this is a generalisation
 of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
@@
 equations but \citeA{TKP+18}
-\change[HW]{didn't propose a suitable numerical method for solving the equations.}
-{only solve the equations in a single column without coupling to the continuity equation of a dynamical core.}
-\change[HW]{Multi-fluids promises big improvements
-in the representation of sub-grid-scale convection and unification
-with the representation of turbulence, particularly at the grey zone.
-However, there is a long way to go, particularly as multi-fluids}
-{The disadvantage of the multi-fluids approach is that it} requires
+\change[HW]{didn't propose a suitable numerical method for solving the equations.}{only solve the equations in a single column without coupling to the continuity equation of a dynamical core.}
+
+\change[HW]{Multi-fluids promises big improvements in the representation of sub-grid-scale convection and unification with the representation of turbulence, particularly at the grey zone.
+However, there is a long way to go, particularly as multi-fluids}{The disadvantage of the multi-fluids approach is that it} requires
 a dedicated model rather than being a stand alone parameterisation
@@
 \add[HW]{sufficient diffusion to stabilise the multi-fluid equations may smooth out real features of the flow and the diffusion between fluids and drag used by \protect\citeA{WM19} meant that both fluids tended to move together rather than through each other.}
-In this paper we show that there are significant
-and sustained pressure differences between the fluids (section \ref{sec:results}) \add[HW]{and that the use of separate pressures stabilises the equations}.
+In this paper, \remove[HW]{we show that there are} significant
+and sustained pressure differences between the fluids \add[HW]{are shown to exist} (section \ref{sec:results}) \add[HW]{and that the use of separate pressures stabilises the equations}.
 
@@
 section \ref{sec:results} give very similar results for Navier-Stokes
-and Buossinesq equations. Therefore\change[WM]{ for simplicity we focus on the}{, the}
+and Boussinesq equations. Therefore\change[WM]{ for simplicity we focus on the}{, the}
 \remove[HW]{multi-fluid} Boussinesq equations without background stratification \add[WM]{are chosen for simplicity}:
-
-\note[HW]{Additional material until the start of 2.1}
 \begin{eqnarray}
@@
 \end{eqnarray}
-where variables are defined in table \ref{tab:defns}.
+where variables are defined in table \ref{tab:defns}. \add[HW]{Note that the ``pressure'' variable, $P$, is actually pressure divided by a constant reference density.}
 
@@
 $w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
-$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)
-\tabularnewline
-\add[HW]{$P$} & \add[HW]{Non-hydrostatic pressure of the single-fluid equations $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$) and pressure averaged over all fluids of the multi-fluid equations}
-\tabularnewline
-$P_i$ & Non-hydrostatic pressure of fluid $i$
+$S_{ij}$ & Rate of volume fraction transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)
+\tabularnewline
+\add[HW]{$P$} & \add[HW]{Perturbation pressure of the single-fluid equations $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$) and pressure averaged over all fluids of the multi-fluid equations}
+\tabularnewline
+$P_i$ & Perturbation pressure of fluid $i$
 \tabularnewline
@@
 
+\note[HW]{Additional material until the start of 2.2}
+
 The single-fluid Boussinesq equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations.
-Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and 0 elsewhere.
-For the derivation of the conditionally averaged equations \change[WM]{we will not consider relabelling of fluid}{the relabelling of fluids will not be considered,} \add[HW]{and so} $I_i$ satisfies:
-\begin{equation}
-\frac{DI_i}{Dt}=0.
+Lagrangian labels, $I_i$, pick out different fluid types or regions.
+$I_i=1$ in fluid $i$ and 0 elsewhere.
+$I_i$ satisfies Lagrangian conservation without transfers:
+\begin{equation}
+\frac{\partial I_i}{\partial t} + \mathbf{u}\cdot\nabla I_i = 0.
 \label{eq:LagrangianLabel}
 \end{equation}
-\change[WM]{Applying conditional volume average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$}{By applying a conditional volume average (denoted by the overbar), the fluid $i$ volume fractions, velocities and buoyancies are defined by}:
+It is more straightforward to introduce transfers after volume averaging because the transfer terms for (\ref{eq:LagrangianLabel}) involve delta functions (this will be addressed in future publications).
+By applying a volume average (denoted by the overbar), the fluid $i$ volume fractions, velocities and buoyancies are defined by:
 \begin{eqnarray}
@@
 \end{equation}
-\change[WM]{As we are considering the Boussinesq equations we assume}{As the system is governed by the Boussinesq equations, it is assumed} that variations in density only affect the \change[WM]{buoyancy terms}{definition of the buoyancy terms (table \protect\ref{tab:defns})} so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.
-
-To derive a transport equation for $\sigma_i$\change[WM]{ we combine (\protect\ref{eq:LagrangianLabel})}{, (\protect\ref{eq:LagrangianLabel}) is combined} with $I_i$ times (\ref{eq:singleDivFree}) and volume average.
-After permuting operators with the averaging \cite<as described by>{TWV+18}\add[WM]{,} and using the definitions of $\sigma_i$ and $\mathbf{u}_i$\add[WM]{,} \remove[WM]{we get} the evolution equation for $\sigma_i$\add[WM]{ is obtained}:
+As the system is governed by the Boussinesq equations, it is assumed that variations in density only affect the definition of the buoyancy terms (table \protect\ref{tab:defns}) so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.
+
+To derive a transport equation for $\sigma_i$, (\ref{eq:LagrangianLabel}) is combined with $I_i$ times (\ref{eq:singleDivFree}) and volume averaged. 
+It is necessary to assume that
+operators permute with the averaging \cite<as described by>{TWV+18}. Transfers between fluids are included at this stage:
 \begin{equation}
@@
 \end{equation}
-which also includes transfers between fluids with $\sigma_{i}S_{ij}$ being the transfer from fluid $i$ to $j$.
-
-Next \change[WM]{we will consider conditionally averaging the terms of }{the conditional averaging of terms in} the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations\add[WM]{ is considered}.
+where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$.
+
+Next the conditional averaging of terms in the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations is considered.
 Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
@@
 \end{eqnarray}
-The sub-filter-scale fluxes will be absorbed into the diffusion terms for momentum and buoyancy.
-%
-\note[HW]{Dan, can we do better than this?}
-\change[WM]{Lots of}{Many} terms appear when attempting to conditionally average the diffusion terms which we do not know how to parameterise.
-\change[WM]{Therefore we will use simply}{The conditionally averaged diffusion terms are therefore assumed to behave like}:
+The sub-filter-scale fluxes are represented by constant viscosity diffusion terms for each fluid.
+The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialised to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
 \begin{eqnarray}
-\overline{I_i \nu \nabla^2 \mathbf{u}} &=& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
-\overline{I_i \alpha \nabla^2 b} &=& \sigma_i \alpha \nabla^2b_i .
+\overline{I_i \nu \nabla^2 \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
+\overline{I_i \alpha \nabla^2 b} &\approx& \sigma_i \alpha \nabla^2b_i .
 \end{eqnarray} 
 %
-\change[WM]{Unlike Thuburn et al. (2018) we define separate pressures for each fluid, $P_i$. The pressures are defined to satisfy:}{The pressures for each fluid, $P_i$, are defined to satisfy:}
-\begin{equation}
-\overline{I_i \nabla P} = \sigma_i \nabla P_i
-\end{equation}
-\add[WM]{which differs from \protect\citeA{TWV+18} who use a shared fluid pressure.}
-%
-Combining \change[WM]{these}{the above terms} gives the conditionally averaged momentum and buoyancy equations:
+The pressures within each fluid are defined as:
+\begin{equation}
+\sigma_i P_i = \overline{I_i P}.
+\end{equation}
+The pressure gradient can then be decomposed as:
+\begin{equation}
+\overline{I_i \nabla P} = \sigma_i \nabla P_i + 
+    \left[ P_i\nabla\sigma_i - \overline{P\nabla I_i} \right]
+\end{equation}
+The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using resolved variables and the full resolved version of the same force, both of which are related to drag.
+They will be represented by a drag, $\mathbf{D}_{ij}$.
+However this drag is likely to be smaller than the drag that is used, for example, in multi-phase modelling \cite<e.g.>{GBB+07} as it is representing the difference between two representations of drag, rather than the whole drag.
+Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.
+
+Combining all terms gives the conditionally averaged momentum and buoyancy equations:
 \begin{eqnarray}
@@
 +
-\sum_{j\ne i}\left\{ \sigma_{j}S_{ji}\mathbf{u}_{ji}^{T}
+\sum_{j\ne i}\left\{
+     \sigma_{j} S_{ji}\mathbf{u}_{ji}^{T}
+   - \sigma_{i} S_{ij}\mathbf{u}_{ij}^{T}
    - \sigma_{i}\mathbf{D}_{ij}\right\}
@@
 +
-\sum_{j\ne i} \sigma_{j}S_{ji} b_{ji}^{T}.
+\sum_{j\ne i}\left\{
+    \sigma_{j} S_{ji} b_{ji}^{T}
+  - \sigma_{i} S_{ij} b_{ij}^{T}
+\right\}.
 \label{eq:bFlux}
@@
 These equations include mass transfers between fluids with $\mathbf{u}_{ij}^T$ being the velocity of the fluid transferred from $i$ to $j$ and $b_{ij}^T$ being the buoyancy of the fluid transferred from $i$ to $j$.
-A drag term, $\mathbf{D}_{ij}$ is also included to parameterise some of the missing terms because it is commonly used when conditional averaging is applied in fields such as multi-phase modelling \cite<eg>{GBB+07}.
-Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.
-
-Eqns (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated due to the mass transfer terms in \ref{eq:sigma}:
+
+Eqns (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated: \remove[HW]{due to the mass transfer terms in \protect\ref{eq:sigma}}
 \begin{eqnarray}
@@
 
-Finally the multi-fluid version incompressibility is
+Finally the multi-fluid version of incompressibility is
 \begin{equation}
@@
 \citeA{TEB19} and \citeA{WM19}
-\change[HW]{assumed that each co-located fluid shared the same pressure leading.}
-{used the same pressure for both fluids.}
+\change[HW]{assumed that each co-located fluid shared the same pressure leading.}{used the same pressure for both fluids.}
 \add[HW]{This led} to unstable equations that \citeA{TEB19}
@@
 in the total pressure.}{For single-fluid equations, divergence would lead to pressure anomalies which would act as a negative feedback on the divergence.
-However for multi-fluids if one of the volume fractions is too small then it cannot force pressure anomalies big enough to stabilise the divergence.
+However for multi-fluids with just one pressure, if one of the volume fractions is too small then it cannot force pressure anomalies big enough to stabilise the divergence.
 Use of a separate pressure for each fluid is therefore proposed to ensure stability.}
@@
 \end{equation}
-\add[HW]{
-For stability and respect $\sum_i \nabla\cdot\sigma_i\mathbf{u}_i=0$, we propose four constraints on the pressure perturbations, $p_i$:}
+\add[HW]{For stability and to respect $\sum_i \nabla\cdot\sigma_i\mathbf{u}_i=0$, we propose four constraints on the pressure perturbations, $p_i$:}
 \begin{enumerate}
 \item $\sum_{i}\sigma_{i}p_{i}=0$.
-\item $\mathbf{u}_{i}=\mathbf{u} \implies p_i=0$ so that pressure perturbations do not force individual fluid anomalies away from the mean.
+\item $p_i=0$ when $\mathbf{u}_{i}=\mathbf{u}$ so that pressure perturbations do not force individual fluid anomalies away from the mean.
 \item $p_i \not\to 0$ when $\sigma_i\to 0$ so that pressure perturbations control divergence in vanishing fluids.
@@
 $\sigma_{i}$, and for the mass fraction,
-$\sigma_{i}\rho_{i}$  without transfers between fluids which in our notation are:
+$\sigma_{i}\rho_{i}$, without transfers between fluids which in our notation are:
 \begin{eqnarray}
@@
 \change[HW]{but if we assume that $\mathbf{V}=\sum_{i}\sigma_{i}\mathbf{u}_{i}$ and $\rho_{i}$ is constant then eqns (\ref{eq:divFree}), (\ref{eq:sumOne}), (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport}) imply that $\mu p_{i}=-\sigma_{i}^{2}\nabla\cdot\mathbf{u}_{i}$.
-If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.}
-{The combination of equations (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport}) shows that the pressure difference between fluids is related to divergence.}
+If we assume that $\mathbf{V}=\mathbf{u}_{i}$ for each fluid then we get $\mu p_{i}=-\sigma_{i}\nabla\cdot\mathbf{u}_{i}$.}{Assuming uniform density, the combination of equations (\ref{eq:BNcompaction}) and (\ref{eq:rhoTransport}) (to eliminate $\partial\sigma_i/\partial t$) shows that the pressure difference between fluids is related to divergence.}
 
@@
 If a fluid perturbation pressure is set to \change[WM]{$-\nu\partial w/\partial z$}{$p_i=-\nu\partial w/\partial z$}
-\add[WM]{then} this is equivalent to the diffusion term in one dimension. However
-adding a diffusion term will harm three dimensional simulations of
+\add[WM]{then} this is equivalent to the diffusion term in one dimension. However adding an \add[HW]{artificial} diffusion term will harm three dimensional simulations of
 resolved convection in the free troposphere whereas adding a fluid
@@
 \citeA{TEB19}
-\change[WM]{we assume that the pressure perturbation in each fluid is given
-by}{and obeying the constraints given above, the pressure in each fluid is chosen to be}:
-\begin{equation}
-p_{i}=\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j -\gamma\nabla\cdot\mathbf{u}_{i}
+\change[WM]{we assume that the pressure perturbation in each fluid is given by}{and obeying the constraints given above, the pressure in each fluid is chosen to be}:
+\begin{equation}
+p_{i}=
+-\underbrace{\gamma\nabla\cdot\mathbf{u}_{i}}_{\text{stabilisation}}
++
+\underbrace{\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j}_{\text{correction}}
 \label{eq:Pi_div}
 \end{equation}
-where $\gamma$ is a \change[HW]{free coefficient}{compressibility with units $\text{m}^s \text{s}^{-1}$. It should be noted that this parameterisation destroys energy conservation.}
+where $\gamma$ is a \change[HW]{free coefficient}{compressibility with units $\text{m}^2 \text{s}^{-1}$.
+The ``stabilistation'' term reduces to that of \protect{\citeA{TEB19}} in one dimension and the ``correction'' term ensures that $\sum_i \sigma_i p_i =0$.
+It should be noted that this parameterisation destroys energy conservation.}
 
@@
 
-\add[HW]{The transfers between fluids are related to entrainment, $\varepsilon$, and detrainment, $\delta$. Fluid 0 is the environment and fluid 1 is updrafts implying:}
+\add[HW]{It is useful to compare the transfer terms, $S_{ij}$, with models of entrainment, $\varepsilon$, and detrainment, $\delta$ used in convection parameterisations.
+If fluid 0 is the environment and fluid 1 is updrafts then the relationship is:}
 \begin{equation}
@@
 \change[HW]{which is necessary to stop air in}{This formulation prevents} one fluid from accumulating when \change[WM]{vertical motion ceases}{a fluid decelerates} (at the top of a rising plume or at the bottom of descending air).
-\remove[HW]{We will also test a}{A} common form of lateral entrainment \cite<eg.>{DBF+13} \add[HW]{is also tested in section {\protect\ref{sec:results}}}:
+\remove[HW]{We will also test a}{A} common form of lateral entrainment \cite<e.g.>{DBF+13} \add[HW]{is also tested in section {\protect\ref{sec:results}}}:
 \begin{equation}
@@
 \change[HW]{The different}{Each} fluid may not be well mixed so the fluid transferred
-may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. \change[WM]{In fact, the most buoyant air should be transferred from fluid 0 to
-fluid 1 and vice versa, and the air with least downward momentum
-should be transferred from 0 to 1 and vice versa.
-The properties of the fluids transferred should depend on the modelling of sub-grid-scale variability which
-is beyond the scope of this paper.}{A realistic estimate of the properties of the fluid transferred can only be based on knowledge of the sub-filter-scale variability (i.e.
+may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}.
+\change[WM]{In fact, the most buoyant air should be transferred from fluid 0 to fluid 1 and vice versa, and the air with least downward momentum should be transferred from 0 to 1 and vice versa.
+The properties of the fluids transferred should depend on the modelling of sub-grid-scale variability which is beyond the scope of this paper.}{A realistic estimate of the properties of the fluid transferred can only be based on knowledge of the sub-filter-scale variability (i.e.
 the variability within each fluid).
-However, modelling of sub-filter-scale variability is beyond the scope of this paper.}
-
-\change[WM]{In section 4
-we conditionally average high resolution solutions based on the sign
-of $w$ so that $w\le 0$ air is in fluid 0 and $w>0$ air in fluid 1.
-Therefore the air that is transferred at the interface will have $w=0$.}{Since conditional averaging is based on the vertical velocity in this study, the sub-set of fluid 0 that is about to rise (i.e.
+Modelling of sub-filter-scale variability is beyond the scope of this paper.}
+%
+\change[WM]{In section 4 we conditionally average high resolution solutions based on the sign of $w$ so that $w\le 0$ air is in fluid 0 and $w>0$ air in fluid 1.
+Therefore the air that is transferred at the interface will have $w=0$.}{However, since conditional averaging in this study is based on the vertical velocity, it is possible to say something about the vertical velocity transfer.
+The subset of fluid 0 that is about to rise (i.e.
 within the next timestep) should be transferred from fluid 0 to fluid 1, and vice versa for the fluid about to fall in fluid 1.
-The fluid transferred will pass through the fluid interface and will therefore have a vertical velocity of $w=0$.}
+The fluid transferred will therefore have a vertical velocity of $w=0$.}
 For \change[WM]{two}{three} dimensional multi-fluid simulations \change[WM]{we}{one} \add[HW]{could} assume that the horizontal
@@
 \add[HW]{
-$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<eg.>{AK67,AS74}.
+$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<e.g.>{AK67,AS74}.
 }
@@
 is not logical and can lead to unbounded values of $b_{i}$ in the
-fluid that is loosing mass (as demonstrated in section \ref{sec:results}).
+fluid that is losing mass (as demonstrated in section \ref{sec:results}).
 
@@
 \item \add[HW]{$\frac{\partial \sigma_i}{\partial z} \approx 0$}
-\item There are two fluids, \change[HW]{$i$ and $j$}{0 and 1.}
+\item There are two fluids \remove[HW]{$i$ and $j$}
 \item Without loss of generality\add[WM]{,} \change[WM]{we assume that}{the transfers} $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
 and $S_{ji}=0$ \add[WM]{are used}.
+\item \add[Dan]{The drag term, $\mathbf{D}_{ij}$, is zero.}
 \end{enumerate}
@@
 \add[HW]{This will be used to guide the choice of $\gamma$ in section {\protect\ref{sec:results}}.}
+
 \section{\label{sec:numerics}Numerical \change[HW]{Solution}{Method}}
@@
 variables. \change[WM]{It differs from}{The method for calculating a separate pressure for each fluid is new because} \citeA{WM19}
-\change[WM]{because here we solve the Boussinesq equations and we need stable solutions for equations with a separate pressure in each fluid.}
-{solved the Euler equations with a single pressure.}
+\change[WM]{because here we solve the Boussinesq equations and we need stable solutions for equations with a separate pressure in each fluid.}{solved the Euler equations with a single pressure.}
 \change[WM]{We use two outer iterations per
@@
 each face (normal to the face). The pressures, $P$ and $p_{i}$ are
-diagnostic.
-
-\change[HW]{The first equation to be solved each outer iteration is eqn}
-{The first calculation of each outer iteration is for the transfer terms, $S_{ij}$ using ({\protect\ref{eq:Sdiv}}) or ({\protect\ref{eq:fracEnt}}). Next}
+diagnostic \add[Dan]{and are located at cell centres}.
+
+\change[HW]{The first equation to be solved each outer iteration is eqn}{The first calculation of each outer iteration is for the transfer terms, $S_{ij}$ using ({\protect\ref{eq:Sdiv}}) or ({\protect\ref{eq:fracEnt}}).
+Next}
 (\ref{eq:sigma}) \add[HW]{is solved}
@@
 is interpolated from cell centres onto cell faces using monotonic
-van-Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citeA{WM19}
+van Leer advection (operator $(\sigma_{i}^{n})_{vL}$) as in \citeA{WM19}
 and values exclusively at time level $n$ for best accuracy and guaranteed
@@
 from before the mass transfers is necessary to ensure bounded and
-conservative transfers, as described by \cite{MWH1x}. Simultaneous
+conservative transfers, as described by \cite{MWH20}. Simultaneous
 solutions of (\ref{eq:b0np1}) and (\ref{eq:b1np1}) give:
@@
 Next a Poisson equation is solved to calculate the total pressure,
-$P$ to ensure that the total velocity is divergence free. \add[HW]{This is the standard approach for ensuring divergence constraints \protect\cite<eg>{SKW14}.} The pressure
+$P$ to ensure that the total velocity is divergence free. \add[HW]{This is the standard approach for ensuring divergence constraints \protect\cite<e.g.>{SKW14}.} The pressure
 equation also provides updates for the velocity flux, $u_{i}$. First
@@
 onto cell faces and $\nabla_{f}P$ is a compact discretisation of
-$(\nabla P)_{f}\cdot\mathbf{S}$: ie the normal component of the pressure
+$(\nabla P)_{f}\cdot\mathbf{S}$: i.e. the normal component of the pressure
 gradient calculated from just the values of pressure either side of
@@
 is transferred conservatively. However they do influence $p_{i}$
-which is why they are calculated before $p_{i}$. The final stage
-of the time step iteration is to solve Helmholtz equations implicitly for each
-$p_{i}^{n+1}$:
+which is why they are calculated before $p_{i}$. 
+\change[Dan]{The final stage of the time step iteration}{The next step}
+is to solve Helmholtz equations implicitly for each $p_{i}^{n+1}$:
 \begin{equation}
@@
 only satisfies eqn (\ref{eq:Pi_div}) exactly if the outer iterations
-converge \change[HW]{and}{implying} $p_{i}^{\ell}=p_{i}^{n+1}$.
+converge, \change[HW]{and}{when} $p_{i}^{\ell}=p_{i}^{n+1}$.
 
@@
 
+The multi-fluid equations will be evaluated in section \ref{sec:results} by comparison with high resolution single fluid solutions.
+This has to be done carefully as even these reference solutions exist on a discrete grid.
 A single-fluid solution is conditionally averaged by:
@@
 The \add[HW]{two dimensional} test case of \citeA{BF02} was designed for fully compressible
-\add[HW]{inviscid models ($\nu=0$, $\alpha=0$)} but similar solutions are obtained solving Boussinesq equations.
+\add[HW]{inviscid models} but similar solutions are obtained solving \add[Dan]{inviscid} Boussinesq equations \add[HW]{($\nu=0$, $\alpha=0$)}.
 The Boussinesq version has no background stratification in a domain
@@
 
-\change[HW]{The solution of the  rising buoyant bubble solving the Boussinesq equations for 1000s}
-{The solution of the Boussinesq equations in two dimensions for the rising bubble at high resolution at the initial time, 500 seconds and 1000 seconds}
-is shown in figure \ref{fig:bubble} with buoyancy coloured,
-pressure contoured and the $w=0$ contour dotted. The solution is
-very similar to the fully compressible solution \cite{BF02}.
+\change[HW]{The solution of the rising buoyant bubble solving the Boussinesq equations for 1000s is shown in figure \ref{fig:bubble}}{The solution of the Boussinesq equations in two dimensions for the rising bubble at high resolution is shown in figure \ref{fig:bubble}, at the initial time, 500 seconds and 1000 seconds,}
+with buoyancy coloured, pressure contoured and the $w=0$ contour dotted.
+The solution is very similar to the fully compressible solution \cite{BF02}.
 The pressure gradients accelerate the flow beneath the bubble, decelerate
 the flow above the bubble and pull in air horizontally. 
-\add[HW]{The $w=0$ contour at the initial time shows the initial tendency of $w$ which demonstrates that there is no straightforward relationship between buoyancy and $w$; $w$ is the solution of an eliptic problem involving the momentum equation and the divergence free constraint.
+\add[HW]{The $w=0$ contour at the initial time shows the initial tendency of $w$ which demonstrates that there is no straightforward relationship between buoyancy and $w$; $w$ is the solution of an elliptic problem involving the momentum equation and the divergence-free constraint.
 After 500 seconds the centre of the bubble has risen further than the edges and after 1000 seconds there is a complex region of entrainment inside the bubble consisting of both buoyant and neutral rising air and buoyant and neutral sinking air.
@@
 \noindent \begin{centering}
-\includegraphics[width=0.9\textwidth]{figures/bubble.pdf}
+\includegraphics[width=0.9\textwidth]{bubble.pdf}
 \par\end{centering}
@@
 
-\change[HW]{Horizontally and conditionally averaged fields, conditioned on $w$, are}
-{Large scale models of the atmosphere often have coarse horizontal resolution and relatively fine vertical resolution.
+\change[HW]{Horizontally and conditionally averaged fields, conditioned on $w$, are}{Large scale models of the atmosphere often have coarse horizontal resolution and relatively fine vertical resolution.
 The high resolution solution is horizontally averaged, conditioned based on the sign of $w$, to give the vertical profiles that coarse resolution models or parameterisations should reproduce.
@@
 $\sigma_{1}$ is the volume fraction of rising fluid at every height and $b_{0}$ and $b_{1}$, $w_{0}$ and $w_{1}$ and $P_{0}$ and $P_{1}$
-are the average buoyancy vertical velocity and pressure of the rising and falling fluids. 
+are the average buoyancy, vertical velocity and pressure of the rising and falling fluids. 
 \add[HW]{$\sigma_1$ varies little with height.
@@
 \noindent \begin{centering}
-\includegraphics[width=\textwidth]{figures/bubble_singleUnderRes.pdf}
+\includegraphics[width=\textwidth]{bubble_singleUnderRes.pdf}
 \par\end{centering}
@@
 \noindent
-\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_1.pdf}
+\includegraphics[width=\linewidth]{multiFluidBubble_500_1.pdf}
 \caption{\label{fig:multiFluidBubble_500_1} Results of the rising bubble at $t=500\ \text{s}$.
@@
 
-\change[HW]{If there is}
-{The solutions in the top row of figure {\protect\ref{fig:multiFluidBubble_500_1}} have}
-no drag between fluids, no transfers, no diffusion and
-the pressures of both fluids are assumed equal \add[HW]{meaning that} the multi-fluid
-equations \change[HW]{are}{should be} unstable \cite{TEB19}. The simulation with ($S_{ij}=0$)
-in the top row of figure \ref{fig:multiFluidBubble_500_1} actually
-has small transfers to prevent either $\sigma_{i}$ from becoming
-negative. This is sufficient to stabilise the solution but does not
-prevent oscillations from developing in all fields. The buoyant fluid
-has risen little from the initial conditions. $\sigma_1$ oscillates
-between zero and one meaning that only one fluid is present at some
-locations so there is no possibility for the fluids to move past each
-other.
-\add[HW]{The two fluids have mixed due to the two way stabilising transfers which have reduced the buoyancy in the rising fluid and increased the buoyancy in the sinking fluid.}
+\change[HW]{If there is}{The solutions in the top row of figure {\protect\ref{fig:multiFluidBubble_500_1}} have}
+no drag between fluids, almost no transfers, no diffusion and
+the pressures of both fluids are assumed equal \add[HW]{meaning that} the multi-fluid equations \change[HW]{are}{should be} unstable \cite{TEB19}. 
+\change[HW]{The simulation with $S_{ij}=0$ in the top row of figure \ref{fig:multiFluidBubble_500_1} actually has small transfers }{Small transfers are applied}
+to prevent either $\sigma_{i}$ from becoming negative.
+This is sufficient to stabilise the solution but does not prevent oscillations from developing in all fields.
+The buoyant fluid has risen little from the initial conditions.
+$\sigma_1$ oscillates between zero and one meaning that only one fluid is present at some locations so there is no possibility for the fluids to move past each other.
+\add[HW]{The two fluids have mixed due to the two-way stabilising transfers which have reduced the buoyancy in the rising fluid and increased the buoyancy in the sinking fluid.}
 
@@
 It is reasonable to consider smaller values of $\gamma$ because the buoyancy does not retain its initial maximum for very long.
-Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$ leads to the leading edge of the bubble rising too quickly \add[HW]{and does not fully remove the discontinuity in the updraft velocity at the leading edge of the bubble}.
-\add[HW]{Pressure differences between the fluids have some similarity with the resolved simulation but none of the values of $\gamma$ reproduce the pressure dip at the trailing edge of the bubble.
+Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$ leads to the leading edge of the bubble rising too quickly \add[HW]{and does not fully remove the discontinuity in the updraft velocity at the leading edge of the bubble.
+The pressure differences between the fluids have some similarity with the resolved simulation but none of the values of $\gamma$ reproduce the pressure dip at the trailing edge of the bubble.
 $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ gives the closest approximation to the resolved simulation.}
@@
 use
-\change[HW]{$\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ }
-{divergence transfer and pressure differences between fluids but, different from previous simulations, also use}
+\change[HW]{$\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ }{divergence transfer and pressure differences between fluids but, different from previous simulations, also use}
 \remove[HW]{but this time with}
@@
 mixing with downdraft air.
-\change[HW]{which is accounted for in the entrainment
-term of the momentum equation.}
-{These are already accounted for in the pressure difference and entrainment parameterisations}
-so adding a separate term for drag risks double counting and slows the plume too much.
+\change[HW]{which is accounted for in the entrainment term of the momentum equation.}{The mixing with downdraft air is already accounted for in the entrainment and the pressure differences are already accounted for in the pressure parameterisation.
+Therefore the drag parameterisation is not a useful contribution to the multi-fluid Boussinesq equations.}
 
@@
 \noindent
-\includegraphics[width=\linewidth]{figures/multiFluidBubble_500_2.pdf}
+\includegraphics[width=\linewidth]{multiFluidBubble_500_2.pdf}
 \caption{As figure \ref{fig:multiFluidBubble_500_1} but different parameterisation options.
@@
 If
-\change[WM]{we include pressure difference between fluids}
-{pressure differences between fluids are included}
+\change[WM]{we include pressure difference between fluids}{pressure differences between fluids are included}
 with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
 \change[WM]{but omit}{without}
-entrainment ($S_{ij}=0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
+entrainment ($S_{ij}\approx 0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
 the fluids move past each other but there is 
-\change[HW]{an unrealistic discontinuity with no}
-{a build up of fluid 1 at the leading edge of the bubble and very little}
+\change[HW]{an unrealistic discontinuity with no}{a build up of fluid 1 at the leading edge of the bubble and very little}
 fluid 1 below the \change[HW]{buoyant fluid}{bubble.}
@@
 rate, $\varepsilon=0.2/r_{c}$. This is used \change[HW]{combined}{in combination with} with pressure differences between fluids in the third row of figure \ref{fig:multiFluidBubble_500_2}.
-\change[HW]{This combination produces smooth solutions}
-{The solutions are smooth}
+\change[HW]{This combination produces smooth solutions}{The solutions are smooth}
 but the \add[HW]{rising volume fraction is not right with a build up of fluid 1 at the bubble leading edge, the} updraft is too
@@
 Using this entrainment, the updraft will entrain more and more air until $\sigma_{1}=1$. The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives
-\change[HW]{much more accurate entrainment and detrainment for this test case using conditional averaging based on $w$.}
-{results closer to the reference solution.}
+\change[HW]{much more accurate entrainment and detrainment for this test case using conditional averaging based on $w$.}{results closer to the reference solution.}
 
@@
 the mean buoyancy of fluid one increases. This leads to
-\change[HW]{very high buoyancy in fluid one which is not present in the resolved simulation.}
-{higher buoyancy in fluid one than when using $b_{ij}^T=b_i$ and gives results close to the reference solution.}
+\change[HW]{very high buoyancy in fluid one which is not present in the resolved simulation.}{higher buoyancy in fluid one than when using $b_{ij}^T=b_i$ and gives results close to the reference solution.}
 The results in the bottom row of figure \ref{fig:multiFluidBubble_500_2}
@@
 \remove[HW]{but the bubble has moved a little too fast.}
-\remove[HW]{These simple models reinforce
-the idea that the buoyancy of the fluid transferred should depend
-on knowledge of sub-grid-scale variability of $b$ within each fluid.
-These simple assumptions can lead to unrealistic behaviour. The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the fluid transferred takes the mean properties with it.}
-
-\remove[HW]
-{This section has demonstrated the value of using single column, multi-fluid model to simulate a buoyant rising bubble with a single
-updraft fluid and a single downdraft fluid. Transfers between
-the fluids have been successfully modelled using entrainment set by divergence giving realistic updraft fractions. Entrainment calculated
-as the reciprocal of plume width was not successful. The pressure
-difference between the fluids has also been represented by divergence
-with a coefficient close to that expected from dimensional analysis. Including drag between the fluids did not improve simulations.
-Two models of transferring non-mean properties between fluids were tested
-but neither was plausible}.
+\remove[HW]{These simple models reinforce the idea that the buoyancy of the fluid transferred should depend on knowledge of sub-grid-scale variability of $b$ within each fluid.
+These simple assumptions can lead to unrealistic behaviour.
+The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the fluid transferred takes the mean properties with it.}
+
+\remove[HW]{This section has demonstrated the value of using single column, multi-fluid model to simulate a buoyant rising bubble with a single updraft fluid and a single downdraft fluid.
+Transfers between the fluids have been successfully modelled using entrainment set by divergence giving realistic updraft fractions.
+Entrainment calculated as the reciprocal of plume width was not successful.
+The pressure difference between the fluids has also been represented by divergence with a coefficient close to that expected from dimensional analysis.
+Including drag between the fluids did not improve simulations.
+Two models of transferring non-mean properties between fluids were tested but neither was plausible.}
 
@@
 \noindent
-\includegraphics[width=\linewidth]{figures/multiFluidBubble_1000.pdf}
-\caption{\label{fig:multiFluidBubble_1000} Results of the rising bubble at $t=1000\ \text{s}$. Solid lines are
-the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble. Dashed
-lines are the single-fluid, resolved solutions.
+\includegraphics[width=\linewidth]{multiFluidBubble_1000.pdf}
+\caption{\label{fig:multiFluidBubble_1000} Results of the rising bubble at $t=1000\ \text{s}$.
+Solid lines are the multi-fluid, \change[HW]{single}{one} column solutions of the rising bubble.
+Dashed lines are the single-fluid, resolved solutions.
 }
@@
 Diffusion is applied to the momentum equation with a coefficient $\nu=70.7\ \text{m}^{2}\text{s}^{-1}$
-so as to give a Plank constant of $0.707$. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$
-is applied to the domain to maintain equilibrium.
+so as to give a Prandtl number of $0.707$, the value for dry air. Uniform cooling of $-1\times10^{-7}\text{m}\text{s}^{-3}$ is applied to the domain to maintain equilibrium.
 
@@
 \noindent 
-\includegraphics[width=1\textwidth]{figures/RCE_resolved.pdf}
+\includegraphics[width=1\textwidth]{RCE_resolved.pdf}
 \caption{\label{fig:RCE_resolved}
@@
 cloud top detrainment and lateral entrainment. $\gamma$ is set from
-equation (\ref{eq:gammaDimAnal}) using the depth of the super adiabatic
+equation (\ref{eq:gammaDimAnal}) using the depth of the \add[HW]{high resolution solution} super adiabatic
 layer as the length scale ($L=800\text{m}$) and the buoyancy scale
 $B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
-giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. A simulation using
+giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. \add[HW]{(Scale analysis or boundary layer parameterisation could instead be used to estimate $L$ independently.)}
+A simulation using
 $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
@@
 \noindent
-\includegraphics[width=\linewidth]{figures/RCE_singleColumn.pdf}
+\includegraphics[width=\linewidth]{RCE_singleColumn.pdf}
 \caption{\label{fig:RCE_singleColumn}
@@
 \add[HW]{The two-fluid, one column model of RCE gave results closer to the reference solution than for the rising bubble.
-This is likely to be because} \add[WM]{the rising and falling fluids in the RCE test case} \add[HW]{are averaged over a large area with plumes at different stages of development rather than trying to simulate the complex entrainment pattern behind a single bubble.}
+This is likely to be because} \add[WM]{the rising and falling fluids in the RCE test case} \add[HW]{are averaged over a large area with plumes at different stages of development rather than trying to simulate the complex entrainment pattern behind a single bubble.
+The RCE test case is horizontally homogeneous and in equilibrium making it more straightforward.}
 
@@
 \change[HW]{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
-at coarse horizontal resolution.}
-{Solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
+at coarse horizontal resolution.}{Solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
 Two test cases are used to \change[HW]{validate}{evaluate}
@@
 
+\add[HW]{The radiative-convective equilibrium (RCE) test case complies with the assumptions of a traditional mass-flux convection scheme --  an ensemble of plumes per column, horizontal homogeneity and equilibrium.
+The rising bubble test does not satisfy these constraints.
+The multi-fluid model gives good solutions for the RCE test case and good solutions for the bubble for the first part of the simulation but does not represent the complex re-entrainment as the bubble continues to rise.}
+
 The multi-fluid Boussinesq equations can have divergence in each fluid
 while the divergence averaged over all fluids is 
-\change[HW]{zero}
-{constrained to be zero by the single-fluid Boussinesq equations.}
+\change[HW]{zero}{constrained to be zero by the single-fluid Boussinesq equations.}
 A model is proposed and \change[HW]{validated}{evaluated} for the pressure difference between the rising
@@
 leads to
-\change[HW]{convecting and non-convecting regions}
-{rising and falling fluids} with area fractions,
-$\sigma_{i}$, which are approximately uniform with height. Models
-for entrainment and detrainment into and out of \change[HW]{convecting}{these} regions
+\change[HW]{convecting and non-convecting regions}{rising and falling fluids} with area fractions, $\sigma_{i}$, which are approximately uniform with height.
+Models for entrainment and detrainment into and out of \change[HW]{convecting}{these} regions
 \change[HW]{must clearly}{need to} be consistent with the definition of the convecting region.
@@
 with it when it is transferred.
-\change[HW]{However sub-grid-scale variability
-of each fluid means that we expect that the most buoyant fluid will
-be transferred to the rising fluid or the fluid with the largest vertical
-velocity will be transferred to the rising fluid and vice versa. An accurate estimate of these would depend on knowledge of the sub-grid-scale
-variability of each fluid which we do not have. Instead we assume
-that the fluid transferred in each direction has zero vertical velocity
-which is consistent with our conditional averaging.}
-{Improvements on this assumption will depend on knowledge of sub-filter-scale variablity.
+\change[HW]{However sub-grid-scale variability of each fluid means that we expect that the most buoyant fluid will be transferred to the rising fluid or the fluid with the largest vertical velocity will be transferred to the rising fluid and vice versa.
+An accurate estimate of these would depend on knowledge of the sub-grid-scale variability of each fluid which we do not have.
+Instead we assume that the fluid transferred in each direction has zero vertical velocity
+which is consistent with our conditional averaging.}{Improvements on this assumption will depend on knowledge of sub-filter-scale variablity.
 However since conditional averaging is based on the sign of $w$, it is consistent to assume that the fluid transferred has $w=0$ ($w_{ij}^T=0$).}
@@
 \remove[HW]{we transfer}
-fluid of zero buoyancy \add[HW]{is transferred ($b_{ij}^T=0$) also leads to}, unbounded buoyancy. \remove[WM]{A better model of the buoyancy
+fluid of zero buoyancy \add[HW]{is transferred ($b_{ij}^T=0$) also leads to} unbounded buoyancy. \remove[WM]{A better model of the buoyancy
 of the fluid transferred would rely on more information of the
@@
 
-Many thanks to John Thuburn and Chris Holloway for valuable discussions.
+Many thanks to Peter Clark, John Thuburn and Chris Holloway for valuable discussions and comments on the manuscript.
 Thanks to the NERC/Met Office Paracon project. We acknowledge funding
 from the Circle-A and RevCon Paracon projects NE/N013743/1 and NE/N013735/1.
-All the code can be downloaded from \url{https://github.com/AtmosFOAM/AtmosFOAM-multiFluid} and the test cases from \url{https://github.com/AtmosFOAM/hilaryRun}.
+The code is built using \url{https://openfoam.org/version/7/} and is part of \url{https://github.com/AtmosFOAM/}.
+The code releases are \url{https://doi.org/10.5281/zenodo.3828474} and \url{https://doi.org/10.5281/zenodo.3832130}.
 

### 2020-07-03 submit3/acceptChanges.sh

@@ -1,0 +1,1 @@
+python acceptchanges.py --infile=manuscript2.tex --outfile=manuscript.tex -c

### 2020-07-16 submit3/manuscript.tex
Hilary's first complete draft of responses to 2nd reviewer comments

@@
 
-\title{Multi-fluids for Representing Sub-filter-scale Convection}
+\title{Multi-fluids for Representing Sub-\change[HW]{filter}{grid}-scale Convection}
 
@@
 \begin{abstract}
-Multi-fluid modeling is a promising new method of representing sub- and near-grid-scale convection allowing for consistent and accurate
-treatment of net mass transport by convection and of non-equilibrium dynamics . The air is partitioned into two or more
-fluids which may represent, for example, updrafts and the stable environment. Each fluid has its own velocity, temperature and constituents
-with separate equations of motion.
-
-This paper presents two-fluid Boussinesq equations for representing under-resolved dry convection
-with sinking and $w=0$ air in fluid 0 and rising air in fluid 1. A model for entrainment
-and detrainment based on divergence  leads to excellent representation of the convective area fraction.
-Previous multi-fluid modeling of convection has
-used the same pressure for both fluids.
-This is shown to be a bad approximation and  a model
-for the pressure difference between the fluids based on divergence is presented.
-
-Two vertical slice test cases are developed to tune parameters and to evaluate the two-fluid equations for representing dry, sub-grid-scale convection: a buoyant rising bubble and radiative convective equilibrium.
+\add[HW]{Traditional parameterizations of convection are a large source of error in weather and climate prediction models and the assumptions behind them are worse as resolution increases.}
+Multi-fluid modeling is a promising new method of representing sub- and near-grid-scale convection allowing for \remove[HW]{consistent and accurate
+treatment of} net mass transport by convection and \remove[HW]{of} non-equilibrium dynamics. The air is partitioned into two or more
+fluids which may represent, for example, updrafts and the \change[HW]{stable}{non-updraft} environment. Each fluid has its own velocity, temperature and constituents with separate equations of motion.
+
+This paper presents two-fluid Boussinesq equations for representing \change[HW]{under-resolved}{sub-grid-scale} dry convection with sinking and $w=0$ air in fluid 0 and rising air in fluid 1.
+Two vertical slice test cases are developed to tune parameters and to evaluate the two-fluid equations: a buoyant rising bubble and radiative convective equilibrium.
 These
-are first simulated at high resolution and conditionally averaged based
-on the sign of the vertical velocity. The test cases are next simulated with the two-fluid model which  reproduces
-the mean properties of the rising and falling fluids in one column. 
+are first simulated at high resolution \add[HW]{with a single-fluid model} and conditionally averaged based
+on the sign of the vertical velocity. The test cases are next simulated with the two-fluid model \remove[HW]{which reproduces
+the mean properties of the rising and falling fluids} in one column. 
+A model for entrainment and detrainment based on divergence  leads to excellent representation of the convective area fraction.
+Previous multi-fluid modeling of convection has used the same pressure for both fluids.
+This is shown to be a bad approximation and  a model for the pressure difference between the fluids based on divergence is presented.
 \end{abstract}
@@
 These make
-it much simpler to incorporate convection parameterizations into existing models. 
-Multi-fluid modeling
-does not rely on these assumptions
+it much simpler to incorporate convection parameterizations into existing models.Multi-fluid modeling does not rely on these assumptions
 but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model.
@@
 Note that the \add[HW]{Boussinesq} pressure \add[HW]{potential}, $P$, is actually pressure divided by a constant reference density\add[HW]{ and is referred to as just the pressure when considering the Boussinesq equations}.
-\add[HW]{The pressure variations are determined up to a constant in order to ensure the divergence free constraint.}
+\add[HW]{The pressure variations are determined up to a constant in order to ensure that the velocity is divergence free.}
 
@@
 It is necessary to assume that operators permute with the averaging \cite<as described by>{TWV+18}.
-\add[HW]{Terms that appear because the averaging does not commute with the operators can be included in the transfers between fluids} \remove[HW]{Transfers between fluids are included at this stage} \add[HW]{which take the form}:
+\add[HW]{Terms that appear because the averaging does not commute with the operators can be included in the transfers between fluids.} \remove[HW]{Transfers between fluids are included at this stage} \add[HW]{The equation for $\sigma_i$ is then}:
 \begin{equation}
@@
 Next the conditional averaging of terms in the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations is considered.
-Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
+\add[HW]{The filter scale is assumed to be equal to the grid scale but the derivation does not rely on this.} Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
 \begin{eqnarray}
@@
 These equations include mass transfers between fluids with $\mathbf{u}_{ij}^T$ being the velocity of the fluid transferred from $i$ to $j$ and $b_{ij}^T$ being the buoyancy of the fluid transferred from $i$ to $j$.
-
 Equations (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated: 
@@
 \end{eqnarray}
-where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$,
+where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$.
 
@@
 
-In order to derive a suitable form of parameterization for $p_i$ we will first consider the \citeA{BN86} model of multi-phase flow.
+In order to derive a suitable form of \change[HW]{parameterization}{model} for $p_i$ we will first consider the \citeA{BN86} model of multi-phase flow.
 
@@
 It should be noted that this parameterization destroys \add[HW]{exact} energy conservation.
-\add[HW]{In future work solving the compressible equations we plan to re-insert the energy lost due to this stabilization as heat.}
+\add[HW]{In future work solving the compressible equations we plan to re-insert the energy lost due to this stabilization as turbulent kinetic energy and heat.}
 
@@
 \end{equation}
-Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}. The first is similar to
-
-the dynamic entrainment described by
-\citeA{HC51}, \citeA{AK67} and \citeA{DBF+13}:
+Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}.
+The first is similar to the dynamic entrainment described by \citeA{HC51}, \citeA{AK67} and \citeA{DBF+13}:
 \begin{equation}
@@
 $B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
-giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. (Scale analysis or boundary layer parameterization could instead be used to estimate $L$ independently.)
+giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. \add[HW]{(If scale analysis is used to estimate $L$ and $B$, values within a factor of 10 are calculated, depending on the assumptions.)}
 A simulation using

### 2020-07-17 submit3/manuscript.tex
Included Will's comments

@@
 \begin{abstract}
-\add[HW]{Traditional parameterizations of convection are a large source of error in weather and climate prediction models and the assumptions behind them are worse as resolution increases.}
+\add[HW]{Traditional parameterizations of convection are a large source of error in weather and climate prediction models and the assumptions behind them become worse as resolution increases.}
 Multi-fluid modeling is a promising new method of representing sub- and near-grid-scale convection allowing for \remove[HW]{consistent and accurate
@@
 \begin{eqnarray}
-\overline{I_i \nabla \cdot (\mathbf{u} \mathbf{u})} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
-\overline{I_i \nabla (\mathbf{u} b)} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
+\nabla \cdot \overline{I_i \mathbf{u} \mathbf{u}} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
+\nabla \cdot \overline{I_i \mathbf{u} b} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
 \label{eq:filterAdvection}
@@
 \begin{eqnarray}
-\overline{I_i \nu \nabla^2 \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
-\overline{I_i \alpha \nabla^2 b} &\approx& \sigma_i \alpha \nabla^2b_i .
+\nu \nabla^2 \overline{I_i \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
+\alpha \nabla^2 \overline{I_i b} &\approx& \sigma_i \alpha \nabla^2b_i .
 \end{eqnarray} 
 %
-The \add[HW]{Boussinesq} pressure \add[HW]{potetials} within each fluid are defined as:
+The \add[HW]{Boussinesq} pressure \add[HW]{potentials} within each fluid are defined as:
 \begin{equation}
@@
 \end{equation}
-The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using resolved variables and the full resolved version of the same force, both of which are related to drag.
+The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using \change[HW]{resolved variables and the full resolved version}{the filtered variables and the fully resolved version} of the same force, both of which are related to drag.
 They will be represented by a drag, $\mathbf{D}_{ij}$.
@@
 For single-fluid equations, divergence would lead to pressure anomalies which would act as a negative feedback on the divergence.
-However for multi-fluids with just one pressure, if one of the volume fractions is too small then it cannot force pressure anomalies big enough to stabilize the divergence.
+\change[HW]{However for multi-fluids with just one pressure, if one of the volume fractions is too small then it} {In the multi-fluid case with just one pressure, fluids with a sufficiently small volume fraction} cannot force pressure anomalies big enough to stabilize the divergence.
 Use of a separate pressure for each fluid is therefore proposed to ensure stability.
@@
 
-In order to derive a suitable form of \change[HW]{parameterization}{model} for $p_i$ we will first consider the \citeA{BN86} model of multi-phase flow.
+In order to derive a suitable \change[HW]{form of parameterization}{model} for $p_i$ we will first consider the \citeA{BN86} model of multi-phase flow.
 
@@
 It should be noted that this parameterization destroys \add[HW]{exact} energy conservation.
-\add[HW]{In future work solving the compressible equations we plan to re-insert the energy lost due to this stabilization as turbulent kinetic energy and heat.}
+\add[HW]{In future work solving the compressible equations, the energy lost due to this stabilization will be re-inserted as turbulent kinetic energy or heat.}
 
@@
 and pressure difference between the fluids controlled by divergence
-($P_{i}=P+\gamma\sum_j \sigma_j \nabla\cdot\mathbf{u}_j-\gamma\nabla\cdot\mathbf{u}_{i}$), the simulations are more realistic (bottom three rows of figure \ref{fig:multiFluidBubble_500_1}).
+($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}+\gamma\sum_j \sigma_j \nabla\cdot\mathbf{u}_j$), the simulations are more realistic (bottom three rows of figure \ref{fig:multiFluidBubble_500_1}).
 The first value, $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$, is set from equation
@@
 Improvements on this assumption will depend on knowledge of sub-filter-scale variability.
-However since conditional averaging is based on the sign of $w$, it is consistent to assume that the fluid transferred has $w=0$ ($w_{ij}^T=0$).
+However since conditional averaging is based on the sign of $w$, it is consistent to assume that the fluid transferred has zero vertical velocity ($w_{ij}^T=0$).
 Three models for the buoyancy of the fluid transferred 
@@
 ($b_{ij}^T=b_i$).
-Assuming that the buoyancy of the transferred fluid is an average of the buoyancy of both fluids ($b_{ij}^T=\frac{1}{2}(b_i+b_j)$) can lead to unrealistically large or small, unbounded buoyancies. 
+Assuming that the buoyancy of the transferred fluid is an average of the buoyancy of both fluids $\bigl(b_{ij}^T=\frac{1}{2}(b_i+b_j)\bigr)$ can lead to unrealistically large or small, unbounded buoyancies.
 Assuming that one fluid has negative buoyancy and the other positive buoyancy and fluid of zero buoyancy is transferred ($b_{ij}^T=0$) also leads to unbounded buoyancy.

### 2020-07-31 submit3/manuscript.tex
Started to incorporate Dan's suggested changes

@@
 \begin{keypoints}
-\item Multi-fluid modeling enables net mass transport by sub-grid-scale convection and non-equlibrium.
+\item Multi-fluid modeling enables net mass transport by sub-grid-scale convection and non-equlibrium\add[DS]{ dynamics}.
 \item Multi-fluid modeling means a new dynamical core rather than a parameterization for an existing core
@@
 Convection parameterizations are a large source of error in models of the atmosphere despite decades of effort to improve them.
-Some unrealistic assumptions remain such as that convection does not transport mass upwards, convection is in equilibrium with the surroundings and that the variations in the horizontal direction are not relevant.
+Some unrealistic assumptions remain such as that convection does not \change[DS]{transport mass upwards}{provide a net upward transport of mass}, convection is in equilibrium with the surroundings and that the variations in the horizontal direction are not relevant.
 These make
-it much simpler to incorporate convection parameterizations into existing models.Multi-fluid modeling does not rely on these assumptions
+it much simpler to incorporate convection parameterizations into existing models. Multi-fluid modeling does not rely on these assumptions
 but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model.
@@
 for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
-of two-fluid equations
-using the same pressure
-for both fluids.
-. \citeA{TEB19} showed that these equations  are in fact unstable and can be stabilized by diffusion of vertical
+of two-fluid equations using the same pressure for both fluids.
+\citeA{TEB19} showed that these equations  are in fact unstable and can be stabilized by diffusion of vertical
 velocity whereas \citeA{WM19} stabilized the equations with diffusion
@@
 sufficient diffusion to stabilize the multi-fluid equations may smooth out real features of the flow and the diffusion between fluids and drag used by \protect\citeA{WM19} meant that both fluids tended to move together rather than through each other.
-In this paper,  significant
-and sustained pressure differences between the fluids are shown to exist (section \ref{sec:results}) and that the use of separate pressures stabilizes the equations.
+In this paper, \add[DS]{it is shown that} significant
+and sustained pressure differences between the fluids \add[DS]{exist} \remove[DS]{are shown to exist} (section \ref{sec:results}) and that the use of separate pressures stabilizes the equations.
 
@@
 To derive a transport equation for $\sigma_i$, (\ref{eq:LagrangianLabel}) is combined with $I_i$ times (\ref{eq:singleDivFree}) and volume averaged. 
-It is necessary to assume that operators permute with the averaging \cite<as described by>{TWV+18}.
-\add[HW]{Terms that appear because the averaging does not commute with the operators can be included in the transfers between fluids.} \remove[HW]{Transfers between fluids are included at this stage} \add[HW]{The equation for $\sigma_i$ is then}:
+It is necessary to assume that \change[DS]{operators permute}{partial derivatives commute} with the averaging \cite<as described by>{TWV+18}. \add[HW]{The equation for $\sigma_i$ is then}:
 \begin{equation}
@@
 \end{equation}
-where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$.
+where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$ which must satisfy:
+\begin{equation}
+\sum_i \sum_{j\ne i} \bigl( \sigma_j S_{ji} - \sigma_i S_{ij} \bigr) =0.
+\end{equation}
+\add[DS]{These transfer terms account for the fact that the labels $I_i$ are not truly Lagrangian conserved (\ie\ fluid can transform from fluid $i$ to fluid $j$).}
 

### 2020-08-03 submit3/makeFigs/bubble.tex
Finished responding to Dan's comments

@@
 \setlength{\parindent}{0pt}
+\usepackage{amstext}
 \usepackage{amssymb}
@@
 
-\includegraphics[width=0.8\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}
+\includegraphics[width=0.75\textwidth]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/singleFluid/resolved/legends/bP_b}\hspace{-0.2cm}\raisebox{0.5cm}{$\text{m}\text{s}^{-2}$}
 \end{document}

### 2020-08-03 submit3/manuscript.tex
Finished responding to Dan's comments

@@
 \tabularnewline\hline
-$\gamma$ ($\text{m}^{2}\text{s}^{-1}$)& Compressibility for calculating $p_i$ 
+$\gamma$ ($\text{m}^{2}\text{s}^{-1}$)& \change[DS]{Compressibility}{Volume viscosity} for calculating $p_i$ 
 \tabularnewline\hline
@@
 \end{equation}
-\add[DS]{These transfer terms account for the fact that the labels $I_i$ are not truly Lagrangian conserved (\ie\ fluid can transform from fluid $i$ to fluid $j$).}
+\add[DS]{These transfer terms account for the fact that the labels $I_i$ are not truly Lagrangian conserved (i.e. fluid can transform from fluid $i$ to fluid $j$).}
 
@@
 The sub-filter-scale fluxes are represented by constant viscosity diffusion terms for each fluid.
-The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialized to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
+\add[DS]{Molecular diffusion is assumed to be of much smaller magnitude than this constant-viscosity turbulent diffusive mixing, so molecular diffusion is neglected hereafter.} The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialized to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
 \begin{eqnarray}
-\nu \nabla^2 \overline{I_i \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
-\alpha \nabla^2 \overline{I_i b} &\approx& \sigma_i \alpha \nabla^2b_i .
+F_\text{SF}^{\mathbf{u}_i}
+%\nu \nabla^2 \overline{I_i \mathbf{u}}
+&\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
+F_\text{SF}^{b_i}
+%\alpha \nabla^2 \overline{I_i b}
+&\approx& \sigma_i \alpha \nabla^2b_i .
 \end{eqnarray} 
@@
 
-\citeA{BN86} proposed a parameterization for pressure differences
-in a multi-phase explosion model that has been widely used in mathematics
+\citeA{BN86} proposed a \remove[HW]{parameterization for pressure differences in a}
+multi-phase explosion model that has been widely used in mathematics
 and engineering for simulating, for example, fluidized beds of granular material \cite<e.g.>{EHM92} and two compressible fluids \cite<e.g.>{SA99}.
+\add[HW]{This model has a separate pressure for each phase, $P_i$, and provides a transport equation for the phase fraction (equivalent of $\sigma_i$) which closes the system enabling diagnosis of $P_i$.}
 This model is not used here but is examined in order to derive a parameterization of pressure differences between fluids suitable for atmospheric convection.
-\citeA{SA99} wrote transport equations for both the volume fraction,
-$\sigma_{i}$, and for the mass fraction,
+\citeA{SA99} wrote \add[HW]{the \protect\citeA{BN86} model using} transport equations for both the volume fraction, $\sigma_{i}$, and for the mass fraction,
 $\sigma_{i}\rho_{i}$, without transfers between fluids which in our notation are:
@@
 \end{equation}
-where $\gamma$ is a compressibility with units $\text{m}^2 \text{s}^{-1}$.
+where $\gamma$ is a \change[DS]{compressibility}{volume viscosity} with units $\text{m}^2 \text{s}^{-1}$.
 The ``stabilization'' term reduces to that of \protect{\citeA{TEB19}} in one dimension and the ``correction'' term ensures that $\sum_i \sigma_i p_i =0$.
@@
 \end{equation}
-where $C_{D}$ is a drag coefficient, $r_{c}$ is a cloud radius.
+where $C_{D}$ is a drag coefficient and $r_{c}$ is a cloud radius.
 Sensitivity to $C_{D}/r_{c}$is explored in section \ref{sec:results}.
@@
 
-Scale analysis can guide our choice of $\gamma$ for the parameterization of the pressure difference between fluids using the following assumptions:
+Scale analysis can guide our choice of $\gamma$ for the parameterization of the pressure difference between.
+\change[HW]{fluids using the following assumptions:}{The scaling presented can be derived using fewer assumptions than those below but these assumptions simplify the analysis:}
 \begin{enumerate}
@@
 transporting buoyancy and then applying the transfer terms.
-The advection term, $\mathbf{u}_i\nabla b_i$ is split into $\nabla\cdot(\mathbf{u}_i b_i) - b_i \nabla\cdot\mathbf{u}_i$ for better conservation as calculated by the finite volume method.
+The advection term, $\mathbf{u}_i\cdot\nabla b_i$ is split into $\nabla\cdot(\mathbf{u}_i b_i) - b_i \nabla\cdot\mathbf{u}_i$ for better conservation as calculated by the finite volume method.
 The transfer
@@
 \end{equation}
-The Poisson equation for $P^{n+1}$ is found by multiplying each \remove[HW]{eqn}
+The Poisson equation for $P^{n+1}$ is found by multiplying \remove[DS]{each} \remove[HW]{eqn}
 (\ref{eq:backSub}) by $\sigma_{i}$, summing over all fluids and
@@
 \end{equation}
-The volume fraction either side of the $w=0$ surface is approximated by the average distance to vertices in one side of the surface divided by the average distance to vertices on both side:
+The volume fraction either side of the $w=0$ surface is approximated by the average distance to vertices in one side of the surface divided by the average distance to vertices on both sides:
 \begin{equation}
@@
 In order to see what happens in a single fluid atmospheric model at modest horizontal resolution without a parameterization of convection, the bubble is simulated at coarser horizontal resolutions, using nine, five, three and one columns instead of the 200 columns of the fine resolution to cover the 20km wide domain and a vertical space of $\Delta z=100\ \text{m}$.
-The conditional and horizontal averages of these simulations are shown in figure \ref{fig:bubble_singleUnderRes}
+The conditional and horizontal averages of these simulations are shown in figure \ref{fig:bubble_singleUnderRes}.
 
@@
 
-If
-pressure differences between fluids are included
-with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
-without
-entrainment ($S_{ij}\approx 0$) (second row of figure \ref{fig:multiFluidBubble_500_2})
-the fluids move past each other but there is 
-a build up of fluid 1 at the leading edge of the bubble and very little
-fluid 1 below the bubble.
-
-With one column and
-two fluids, all air must rise in one fluid and sink in the other.
-Continuity does not allow for any other solution. Pressure gradients
-can accelerate or decelerate this flow but as the model is set up,
-with no transfers between fluids, no fluid can change direction. It
-is therefore essential to have transfers between fluids.
+If pressure differences between fluids are included with $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ without entrainment ($S_{ij}\approx 0$) (second row of figure \ref{fig:multiFluidBubble_500_2}) the fluids move past each other but there is
+a build up of fluid 1 at the leading edge of the bubble and very little fluid 1 below the bubble.
+With one column and two fluids, all air must rise in one fluid and sink in the other.
+Continuity does not allow for any other solution.
+Pressure gradients
+can accelerate or decelerate this flow but as the model is set up, with no transfers between fluids, no fluid can change direction. It is therefore essential to have transfers between fluids.
 
@@
 is imposed at the bottom boundary leading to a boundary condition
-of $\partial b/\partial z=-h/\alpha\text{s}^{-2}$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
+of $\partial b/\partial z=-h/\alpha$ where $\alpha=100\ \text{m}^{2}\text{s}^{-1}$
 is the buoyancy diffusivity. The top boundary has $\partial b/\partial z=0$.
@@
 of $5\ \text{s}$. A quasi-steady, chaotic state is reached after
-about $3\times10^{4}\text{s}$ and the simulation is run for $2\times10^{5}\text{s}$
+about $3\times10^{4}\text{s}$; the simulation is run for $2\times10^{5}\text{s}$
 and conditional averages are calculated over the final $10^{5}$s.
@@
 $B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
-giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. \add[HW]{(If scale analysis is used to estimate $L$ and $B$, values within a factor of 10 are calculated, depending on the assumptions.)}
-A simulation using
+giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. A simulation using
 $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
